### 2014-09-18 sideband/obe/obe.tex
[sideband/obe]

\documentclass[10pt,fleqn]{article}
%\usepackage[journal=rsc]{chemstyle}
%\usepackage{mhchem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{esint}
\usepackage{bbm}
\usepackage{amscd}
\usepackage{picinpar}
\usepackage[pdftex]{graphicx}
\usepackage{indentfirst}
\usepackage{wrapfig}
\usepackage{units}
\usepackage{textcomp}
\usepackage[utf8x]{inputenc}
\usepackage{feyn}
\usepackage{feynmp}
\DeclareGraphicsRule{*}{mps}{*}{}
\newcommand{\ud}{\mathrm{d}}
\newcommand{\ue}{\mathrm{e}}
\newcommand{\ui}{\mathrm{i}}
\newcommand{\res}{\mathrm{Res}}
\newcommand{\Tr}{\mathrm{Tr}}
\newcommand{\dsum}{\displaystyle\sum}
\newcommand{\dprod}{\displaystyle\prod}
\newcommand{\dlim}{\displaystyle\lim}
\newcommand{\dint}{\displaystyle\int}
\newcommand{\fsno}[1]{{\!\not\!{#1}}}
\newcommand{\eqar}[1]
{
  \begin{align*}
    #1
  \end{align*}
}
\newcommand{\texp}[2]{\ensuremath{{#1}\times10^{#2}}}
\newcommand{\dexp}[2]{\ensuremath{{#1}\cdot10^{#2}}}
\newcommand{\eval}[2]{{\left.{#1}\right|_{#2}}}
\newcommand{\paren}[1]{{\left({#1}\right)}}
\newcommand{\lparen}[1]{{\left({#1}\right.}}
\newcommand{\rparen}[1]{{\left.{#1}\right)}}
\newcommand{\abs}[1]{{\left|{#1}\right|}}
\newcommand{\sqr}[1]{{\left[{#1}\right]}}
\newcommand{\crly}[1]{{\left\{{#1}\right\}}}
\newcommand{\angl}[1]{{\left\langle{#1}\right\rangle}}
\newcommand{\tpdiff}[4][{}]{{\paren{\frac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}}_{#4}}}
\newcommand{\tpsdiff}[4][{}]{{\paren{\frac{\partial^{#1}}{\partial {#3}{}^{#1}}{#2}}_{#4}}}
\newcommand{\pdiff}[3][{}]{{\frac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}}}
\newcommand{\diff}[3][{}]{{\frac{\ud^{#1} {#2}}{\ud {#3}{}^{#1}}}}
\newcommand{\psdiff}[3][{}]{{\frac{\partial^{#1}}{\partial {#3}{}^{#1}} {#2}}}
\newcommand{\sdiff}[3][{}]{{\frac{\ud^{#1}}{\ud {#3}{}^{#1}} {#2}}}
\newcommand{\tpddiff}[4][{}]{{\left(\dfrac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}\right)_{#4}}}
\newcommand{\tpsddiff}[4][{}]{{\paren{\dfrac{\partial^{#1}}{\partial {#3}{}^{#1}}{#2}}_{#4}}}
\newcommand{\pddiff}[3][{}]{{\dfrac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}}}
\newcommand{\ddiff}[3][{}]{{\dfrac{\ud^{#1} {#2}}{\ud {#3}{}^{#1}}}}
\newcommand{\psddiff}[3][{}]{{\frac{\partial^{#1}}{\partial{}^{#1} {#3}} {#2}}}
\newcommand{\sddiff}[3][{}]{{\frac{\ud^{#1}}{\ud {#3}{}^{#1}} {#2}}}
\usepackage{fancyhdr}
\usepackage{multirow}
\usepackage{fontenc}
%\usepackage{tipa}
\usepackage{ulem}
\usepackage{color}
\usepackage{cancel}
\newcommand{\hcancel}[2][black]{\setbox0=\hbox{#2}%
\rlap{\raisebox{.45\ht0}{\textcolor{#1}{\rule{\wd0}{1pt}}}}#2}
\pagestyle{fancy}
\setlength{\headheight}{67pt}
\fancyhead{}
\fancyfoot{}
\fancyfoot[C]{\thepage}
\renewcommand{\footruleskip}{0pt}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\hoffset}{-1.3cm}
\addtolength{\voffset}{-2cm}
\addtolength{\textwidth}{3cm}
\addtolength{\textheight}{2.5cm}
\renewcommand{\footskip}{10pt}
\setlength{\headwidth}{\textwidth}
\setlength{\headsep}{20pt}
\setlength{\marginparwidth}{0pt}
\parindent=0pt
\begin{document}
\section{Simplifies Optical Bloch Equation for Sideband Cooling Simulation.}
Rabi frequency between state $m$ and $n$ (assume to be real since the phase is not important for sidband cooling.): $\Omega_{mn}$\\
Pumping rate from state $n$ to $m$: $\Gamma_{mn}$\\

Diagonal terms,
\eqar{
  \pdiff{\rho_{mm}}{t}=&-\rho_{mm}\sum_k\Gamma_{km}+\sum_k\rho_{kk}\Gamma_{mk}+\ui\sum_k\paren{\rho_{mk}\Omega_{km}-\Omega_{mk}\rho_{km}}
}
Off-diagnal terms,
\eqar{
  \pdiff{\rho_{mn}}{t}=&-\frac{\rho_{mn}}{2}\sum_k\paren{\Gamma_{km}+\Gamma_{kn}}+\ui\sum_k\paren{\rho_{mk}\Omega_{kn}-\Omega_{mk}\rho_{kn}}
}

\end{document}

### 2014-09-18 sideband/obe/obe.tex
[sideband/obe]

@@
 
+When only one sideband is driven,
+\eqar{
+  \Omega_{mn}=&\Omega_{m}\delta_{m,n-\Delta}+\Omega_{n}\delta_{n,m-\Delta}
+}
+where $Delta$ include both the change in vibrational level and internal level.\\
+With $p_n=\rho{nn}$, the equations becomes,
+\eqar{
+  \pdiff{p_{m}}{t}=&\sum_k\paren{p_{k}\Gamma_{mk}-p_{m}\Gamma_{km}}+\ui\paren{\rho_{m,m-\Delta}\Omega_{m-\Delta}-\Omega_{m}\rho_{m+\Delta, m}+\rho_{m,m+\Delta}\Omega_{m}-\Omega_{m-\Delta}\rho_{m-\Delta,m}}\\
+  \pdiff{\rho_{m,m+\Delta}}{t}=&-\frac{\rho_{m,m+\Delta}}{2}\sum_k\paren{\Gamma_{km}+\Gamma_{k,m+\Delta}}+\ui\Omega_{m}\paren{\rho_{mm}-\rho_{m+\Delta,m+\Delta}}
+}
+$\rho_{mn}$'s with $\abs{m-n}\neq0,\Delta$ are ignored since they are $0$. In particular, since $\Delta$ includes change of internal levels, elements with $\abs{m-n}\geqslant2\Delta$ does not exist.
+
 \end{document}

### 2014-09-18 sideband/obe/obe.tex
[sideband/obe] final equation for simulation

--- 2014-09-18 sideband/obe/obe.tex
@@
 \eqar{
-  \pdiff{\rho_{mm}}{t}=&-\rho_{mm}\sum_k\Gamma_{km}+\sum_k\rho_{kk}\Gamma_{mk}+\ui\sum_k\paren{\rho_{mk}\Omega_{km}-\Omega_{mk}\rho_{km}}
+  \diff{\rho_{mm}}{t}=&-\rho_{mm}\sum_k\Gamma_{km}+\sum_k\rho_{kk}\Gamma_{mk}+\ui\sum_k\paren{\rho_{mk}\Omega_{km}-\Omega_{mk}\rho_{km}}
 }
@@
 \eqar{
-  \pdiff{\rho_{mn}}{t}=&-\frac{\rho_{mn}}{2}\sum_k\paren{\Gamma_{km}+\Gamma_{kn}}+\ui\sum_k\paren{\rho_{mk}\Omega_{kn}-\Omega_{mk}\rho_{kn}}
+  \diff{\rho_{mn}}{t}=&-\frac{\rho_{mn}}{2}\sum_k\paren{\Gamma_{km}+\Gamma_{kn}}+\ui\sum_k\paren{\rho_{mk}\Omega_{kn}-\Omega_{mk}\rho_{kn}}
+}
+
+When only one sideband is driven,
+\eqar{
+  \Omega_{mn}=&\Omega_{m}\delta_{m,n-\Delta}+\Omega_{n}\delta_{n,m-\Delta}
+}
+where $Delta$ include both the change in vibrational level and internal level.\\
+Define $p_n=\rho_{nn}$, the equations becomes,
+\eqar{
+  \diff{p_{m}}{t}=&\sum_k\paren{p_{k}\Gamma_{mk}-p_{m}\Gamma_{km}}+\ui\paren{\rho_{m,m-\Delta}\Omega_{m-\Delta}-\Omega_{m}\rho_{m+\Delta, m}+\rho_{m,m+\Delta}\Omega_{m}-\Omega_{m-\Delta}\rho_{m-\Delta,m}}\\
+  \diff{\rho_{m,m+\Delta}}{t}=&-\frac{\rho_{m,m+\Delta}}{2}\sum_k\paren{\Gamma_{km}+\Gamma_{k,m+\Delta}}+\ui\Omega_{m}\paren{p_{m}-p_{m+\Delta}}
+}
+$\rho_{mn}$'s with $\abs{m-n}\neq0,\Delta$ are ignored since they are $0$. In particular, since $\Delta$ includes change of internal levels, elements with $\abs{m-n}\geqslant2\Delta$ does not exist.\\
+
+Define $q_n=\ui\rho_{n,n+\Delta}$,
+\eqar{
+  \rho_{n,n+\Delta}=&-\ui q_n\\
+  \rho_{n+\Delta,n}=&\ui q_n^*
+}
+\eqar{
+  \diff{p_{m}}{t}=&\sum_k\paren{p_{k}\Gamma_{mk}-p_{m}\Gamma_{km}}+\ui\paren{\ui q_{m-\Delta}^*\Omega_{m-\Delta}-\ui\Omega_{m}q_{m}^*-\ui q_m\Omega_{m}+\ui\Omega_{m-\Delta}q_{m-\Delta}}\\
+  -\ui\diff{q_m}{t}=&\ui\frac{q_{m}}{2}\sum_k\paren{\Gamma_{km}+\Gamma_{k,m+\Delta}}+\ui\Omega_{m}\paren{p_{m}-p_{m+\Delta}}\\
+  \diff{p_{m}}{t}=&\sum_k\paren{p_{k}\Gamma_{mk}-p_{m}\Gamma_{km}}+\Omega_{m}\paren{q_{m}^*+q_m}-\Omega_{m-\Delta}\paren{q_{m-\Delta}^*+q_{m-\Delta}}\\
+  \diff{q_m}{t}=&-\frac{q_{m}}{2}\sum_k\paren{\Gamma_{km}+\Gamma_{k,m+\Delta}}+\Omega_{m}\paren{p_{m+\Delta}-p_{m}}
+}
+For a process starting with $q_m=0$, $q_m$ will always remain real.
+\eqar{
+  \diff{p_{m}}{t}=&\sum_kp_{k}\Gamma_{mk}-p_{m}\Gamma_{m}+2\Omega_{m}q_m-2\Omega_{m-\Delta}q_{m-\Delta}\\
+  \diff{q_m}{t}=&-\frac{q_{m}}{2}\paren{\Gamma_{m}+\Gamma_{m+\Delta}}+\Omega_{m}\paren{p_{m+\Delta}-p_{m}}
+}
+where $\Gamma_m\equiv\displaystyle\sum_k\Gamma_{km}$ is the decay rate of state $m$.\\
+
+After writing the two internal states ($a$ and $b$) explicitly,
+\eqar{
+  \diff{p^a_{m}}{t}=&\sum_{\alpha=a,b;k}p^\alpha_{k}\Gamma^{a\alpha}_{mk}-p^a_{m}\Gamma^a_{m}+2\Omega_{m}q_m\\
+  \diff{p^b_{m}}{t}=&\sum_{\alpha=a,b;k}p^\alpha_{k}\Gamma^{b\alpha}_{mk}-p^b_{m}\Gamma^b_{m}-2\Omega_{m-\delta}q_{m-\delta}\\
+  \diff{q_m}{t}=&-\frac{q_{m}}{2}\paren{\Gamma^a_{m}+\Gamma^b_{m+\delta}}+\Omega_{m}\paren{p^b_{m+\delta}-p^a_{m}}
 }

### 2014-09-19 sideband/obe/obe.tex
[sideband/obe] more precise description of pumping

@@
 
-After writing the two internal states ($a$ and $b$) explicitly,
+After writing the two internal states ($a$ and $b$) explicitly and adding a third state ($c$) to take into account $m_F$ pumping,
 \eqar{
-  \diff{p^a_{m}}{t}=&\sum_{\alpha=a,b;k}p^\alpha_{k}\Gamma^{a\alpha}_{mk}-p^a_{m}\Gamma^a_{m}+2\Omega_{m}q_m\\
-  \diff{p^b_{m}}{t}=&\sum_{\alpha=a,b;k}p^\alpha_{k}\Gamma^{b\alpha}_{mk}-p^b_{m}\Gamma^b_{m}-2\Omega_{m-\delta}q_{m-\delta}\\
+  \diff{p^a_{m}}{t}=&\sum_{\alpha=a,b,c;k}p^\alpha_{k}\Gamma^{a\alpha}_{mk}-p^a_{m}\Gamma^a_{m}+2\Omega_{m}q_m\\
+  \diff{p^b_{m}}{t}=&\sum_{\alpha=a,b,c;k}p^\alpha_{k}\Gamma^{b\alpha}_{mk}-p^b_{m}\Gamma^b_{m}-2\Omega_{m-\delta}q_{m-\delta}\\
+  \diff{p^c_{m}}{t}=&\sum_{\alpha=a,b,c;k}p^\alpha_{k}\Gamma^{c\alpha}_{mk}-p^c_{m}\Gamma^c_{m}\\
   \diff{q_m}{t}=&-\frac{q_{m}}{2}\paren{\Gamma^a_{m}+\Gamma^b_{m+\delta}}+\Omega_{m}\paren{p^b_{m+\delta}-p^a_{m}}
 }
+For sodium, states $a$, $b$ and $c$ corresponds to $|F=1, m_F=1\rangle$, $|F=2, m_F=2\rangle$ and  $|F=2, m_F=1\rangle$.\\
+
+When the trapping frequency is much smaller than the line width, $\Gamma^\alpha_m$ is independent with $m$ and is proportional to the corresponding pumping power.
+$\Gamma^{\alpha\beta}_{mn}$ can be written as,
+\eqar{
+  \Gamma^{\alpha\beta}_{mn}=&\Gamma^{\alpha\beta}\gamma_{mn}\\
+  =&\begin{pmatrix}
+    \Gamma^{aa}&\Gamma^{ab}&\Gamma^{ac}\\
+    \Gamma^{ba}&\Gamma^{bb}&\Gamma^{bc}\\
+    \Gamma^{ca}&\Gamma^{cb}&\Gamma^{cc}
+  \end{pmatrix}\gamma_{mn}\\
+  =&\begin{pmatrix}
+    \Gamma^aB^{aa}&\Gamma^bB^{ab}&\Gamma^cB^{ac}\\
+    \Gamma^aB^{ba}&\Gamma^bB^{bb}&\Gamma^cB^{bc}\\
+    \Gamma^aB^{ca}&\Gamma^bB^{cb}&\Gamma^cB^{cc}
+  \end{pmatrix}\gamma_{mn}\\
+  =&\begin{pmatrix}
+    \Gamma_1B^{aa}&\varepsilon\Gamma_2B^{ab}&\Gamma_2B^{ac}\\
+    \Gamma_1B^{ba}&\varepsilon\Gamma_2B^{bb}&\Gamma_2B^{bc}\\
+    \Gamma_1B^{ca}&\varepsilon\Gamma_2B^{cb}&\Gamma_2B^{cc}
+  \end{pmatrix}\gamma_{mn}
+}
+where $B^{\alpha\beta}$ is the branching ratio, $\Gamma_1$ is the $F$ pumping power ($(1, 1) \rightarrow (2, 2)'$ light), $\Gamma_2$ is the $m_F$ pumping power ($(2, 1) \rightarrow (2, 2)'$ light) and $\varepsilon$ is the off-resonance coupling of the $m_F$ pumping light to the $(2, 2) \rightarrow (2, 3)'$ transition.
 

### 2014-10-19 sideband/sideband.py
[sideband] memory access alignment

@@ -13,8 +13,8 @@ from pyscical.atomic import sideband_strength, sideband_scatter_strength
 
 _ffi = FFI()
 _ffi.cdef('''
-void _fill_gidx_minmax(unsigned dim, float *gamma,
-                       float *min_out, float *max_out);''')
+void _fill_gidx_minmax(unsigned dim, float *gamma, float *min_out,
+                       float *max_out, unsigned idx_align);''')
 _lib = _ffi.verify('''
 #include <math.h>
 
@@ -22,7 +22,7 @@ static const float gamma_thresh = 1e-10;
 
 static void
 _fill_gidx_minmax(unsigned dim, float *gamma, unsigned *min_out,
-                  unsigned *max_out)
+                  unsigned *max_out, unsigned idx_align)
 {
 #pragma omp parallel for
     for (unsigned i = 0;i < dim;i++) {
@@ -33,7 +33,7 @@ _fill_gidx_minmax(unsigned dim, float *gamma, unsigned *min_out,
                 break;
             }
         }
-        min_out[i] = j;
+        min_out[i] = (j / idx_align) * idx_align;
 
         j = dim - 1;
         for (;j >= 0;j--) {
@@ -41,13 +41,15 @@ _fill_gidx_minmax(unsigned dim, float *gamma, unsigned *min_out,
                 break;
             }
         }
-        max_out[i] = j + 1;
+        j = (j / idx_align + 1) * idx_align;
+        max_out[i] = j > dim - 1 ? dim - 1 : j;
     }
 }
 ''', extra_compile_args=['-w', '-fopenmp', '-O2', '-std=gnu99'],
 extra_link_args=['-fopenmp'])
 
-def _get_gidx_minmax_xyz(dim_x, dim_y, dim_z, gamma_x, gamma_y, gamma_z):
+def _get_gidx_minmax_xyz(dim_x, dim_y, dim_z, gamma_x, gamma_y, gamma_z,
+                         align=True):
     # Probably faster if done on GPU
     gidx_minmax_xyz = np.empty((dim_x + dim_y + dim_z) * 2, np.uint32)
 
@@ -60,15 +62,21 @@ def _get_gidx_minmax_xyz(dim_x, dim_y, dim_z, gamma_x, gamma_y, gamma_z):
     gidxmax_y = gidx_minmax_xyz[dim_x * 2 + dim_y + dim_z:
[…]

### 2015-11-12 calculations/practical-lz/two-levels.jl
[calculations/practical-lz] new simulation for LZ sweep. Constant frequency drive first

@@ -1,0 +1,100 @@
+#!/usr/bin/julia -f
+
+# Abstract interface
+abstract AbstractDrive
+
+function update_dt end
+function get_detuning end
+function get_rabi end
+function get_phase end
+
+abstract AbstractMeasure
+
+function measure_snapshot end
+
+# Propagate function
+function propagate!(y0::Vector, drive::AbstractDrive, dt, nsteps,
+                    measure::AbstractMeasure)
+    # @assert size(y0) == (2,)
+    measure_snapshot(measure, y0, 1)
+    @inbounds for i in 1:nsteps
+        # Update drive state
+        update_dt(drive, dt)
+
+        # original parameters
+        δ = get_detuning(drive)::Real
+        Ω = get_rabi(drive)::Real
+        ϕ₀ = get_phase(drive)::Real
+
+        # derived values
+        δ′ = δ
+        Ω′ = √(Ω^2 + δ′^2 / 4)
+        δt_2 = δ′ * dt / 2
+        Ωt = Ω′ * dt
+
+        @fastmath cosΩ = cos(Ωt)
+        @fastmath sinΩ = sin(Ωt)
+        @fastmath expδ = Complex(cos(δt_2), sin(δt_2))
+        @fastmath expϕ = Complex(cos(ϕ₀), sin(ϕ₀))
+
+        y_1 = y0[1]
+        y_2 = y0[2]
+
+        T22 = expδ * Complex(cosΩ, -δ′ / (2Ω′) * sinΩ)
+        T11 = conj(T22)
+        T21′ = Ω / Ω′ * expϕ * expδ * sinΩ
+        T21 = Complex(imag(T21′), -real(T21′))
+        T12 = Complex(-imag(T21′), -real(T21′))
+
+        y0[1] = muladd(T12, y_2, T11 * y_1)
+        y0[2] = muladd(T21, y_1, T22 * y_2)
+        measure_snapshot(measure, y0, i + 1)
+    end
+    y0
+end
+
+# Constant drive
+immutable ConstDrive <: AbstractDrive
+    δ::Float32
+    Ω::Float32
+    ϕ::typeof(Ref(1f0))
+    ConstDrive(δ, Ω, ϕ₀=0f0) = new(δ, Ω, Ref(Float32(ϕ₀)))
+end
+
+@inline update_dt(drive::ConstDrive, dt) = drive.ϕ[] += dt * drive.δ
[…]

### 2015-11-12 calculations/practical-lz/two-levels.jl
[calculations/practical-lz] normalize state vector

@@ -46,8 +46,11 @@ function propagate!(y0::Vector, drive::AbstractDrive, dt, nsteps,
         T21 = Complex(imag(T21′), -real(T21′))
         T12 = Complex(-imag(T21′), -real(T21′))
 
-        y0[1] = muladd(T12, y_2, T11 * y_1)
-        y0[2] = muladd(T21, y_1, T22 * y_2)
+        y_1′ = muladd(T12, y_2, T11 * y_1)
+        y_2′ = muladd(T21, y_1, T22 * y_2)
+        y_scale = 1 / sqrt(abs2(y_1) + abs2(y_2))
+        y0[1] = y_1′ * y_scale
+        y0[2] = y_2′ * y_scale
         measure_snapshot(measure, y0, i + 1)
     end
     y0

### 2015-11-12 calculations/practical-lz/two-levels.jl
[calculations/practical-lz] LZ drive

@@ -69,6 +69,24 @@ end
 @inline get_rabi(drive::ConstDrive) = drive.Ω
 @inline get_phase(drive::ConstDrive) = drive.ϕ[]
 
+# LZ drive
+immutable LZDrive <: AbstractDrive
+    δ0::Float32
+    dδ::Float32
+    Ω::Float32
+    ϕ₀::Float32
+    t::typeof(Ref(1f0))
+    LZDrive(δ0, dδ, Ω, ϕ₀=0f0) = new(δ0, dδ, Ω, ϕ₀, Ref(0f0))
+end
+
+@inline update_dt(drive::LZDrive, dt) = drive.t[] += dt
+@inline get_detuning(drive::LZDrive) = muladd(drive.dδ, drive.t[], drive.δ0)
+@inline get_rabi(drive::LZDrive) = drive.Ω
+@inline function get_phase(drive::LZDrive)
+    t = drive.t[]
+    t * muladd(drive.dδ / 2, t, drive.δ0)
+end
+
 # Full measure
 
 immutable FullMeasure <: AbstractMeasure

### 2015-11-12 calculations/practical-lz/two-levels.jl
[calculations/practical-lz] Move handling of initial phase

@@ -14,7 +14,7 @@ function measure_snapshot end
 
 # Propagate function
 function propagate!(y0::Vector, drive::AbstractDrive, dt, nsteps,
-                    measure::AbstractMeasure)
+                    measure::AbstractMeasure, ϕ₀=0f0)
     # @assert size(y0) == (2,)
     measure_snapshot(measure, y0, 1)
     @inbounds for i in 1:nsteps
@@ -24,7 +24,7 @@ function propagate!(y0::Vector, drive::AbstractDrive, dt, nsteps,
         # original parameters
         δ = get_detuning(drive)::Real
         Ω = get_rabi(drive)::Real
-        ϕ₀ = get_phase(drive)::Real
+        ϕ = get_phase(drive)::Real + ϕ₀
 
         # derived values
         δ′ = δ
@@ -35,7 +35,7 @@ function propagate!(y0::Vector, drive::AbstractDrive, dt, nsteps,
         @fastmath cosΩ = cos(Ωt)
         @fastmath sinΩ = sin(Ωt)
         @fastmath expδ = Complex(cos(δt_2), sin(δt_2))
-        @fastmath expϕ = Complex(cos(ϕ₀), sin(ϕ₀))
+        @fastmath expϕ = Complex(cos(ϕ), sin(ϕ))
 
         y_1 = y0[1]
         y_2 = y0[2]
@@ -61,7 +61,7 @@ immutable ConstDrive <: AbstractDrive
     δ::Float32
     Ω::Float32
     ϕ::typeof(Ref(1f0))
-    ConstDrive(δ, Ω, ϕ₀=0f0) = new(δ, Ω, Ref(Float32(ϕ₀)))
+    ConstDrive(δ, Ω) = new(δ, Ω, Ref(0f0))
 end
 
 @inline update_dt(drive::ConstDrive, dt) = drive.ϕ[] += dt * drive.δ
@@ -74,9 +74,8 @@ immutable LZDrive <: AbstractDrive
     δ0::Float32
     dδ::Float32
     Ω::Float32
-    ϕ₀::Float32
     t::typeof(Ref(1f0))
-    LZDrive(δ0, dδ, Ω, ϕ₀=0f0) = new(δ0, dδ, Ω, ϕ₀, Ref(0f0))
+    LZDrive(δ0, dδ, Ω) = new(δ0, dδ, Ω, Ref(0f0))
 end
 
 @inline update_dt(drive::LZDrive, dt) = drive.t[] += dt

### 2016-01-29 presentations/damop-2016/abstract.tex
[presentations/damop-2016] latex version

\documentclass{article}
\begin{document}
In order to create a diatomic molecule with a large electric dipole moment,
it is generally necessary to use atoms with very different electronegativities.
In the context of bi-alkali molecules,
this means combining a light alkali atom with a heavy one.
This is the reason why we use NaCs in our molecule assembler experiment;
NaCs has the largest induced dipole moment in few kV/cm lab fields.
However, the use of sodium atoms also poses challenges.
\begin{itemize}
\item The higher Doppler temperature and lack of efficient D2 polarization
  gradient cooling increases the necessary depth of our optical dipole
  (tweezer) traps.
\item The lack of a convenient magic wavelength for the dipole trap
  creates a large AC stark shift on the optical transition as well as
  additional heating mechanisms.
\item The light mass of the sodium, and therefore larger Lamb-Dicke
  parameter and higher recoil temperature, makes it more difficult to
  perform efficient Raman sideband cooling on the atom in the trap.
\end{itemize}
I will discuss the techniques we use to overcome these challenges,
in particular a method to eliminate the light shifts and associated heating
mechanisms in tight optical traps.
\end{document}

### 2016-05-16 calculations/single-atom/test/heating-tests/param-plot.jl
[calculations/single-atom] larger beta

@@ -60,7 +60,7 @@
 
         grid_size = 512
         grid_space = 0.0025f0
-        tstep = 0.002f0
+        tstep = 0.001f0
         nstep = round(Int, totalt ÷ tstep)
         p_sys = SystemPropagator(h_system, tstep, grid_space,
                                  nstep, grid_size)
@@ -77,16 +77,17 @@ end
 println("start")
 
 # βs = [1.67, 1, 0.6, -0.6]
-βs = [1.67 ,1]
+βs = [2.5 ,1]
 det_list = [
-            [-20, -18.75, -17.5, -17.1875, -16.875, -16.5625, -16.25, -15],
+            [-55, -50, -45, -40, -35, -30, -25, -20],
+            # [-20, -18.75, -17.5, -17.1875, -16.875, -16.5625, -16.25, -15],
             [-5, -3.75, -2.5, -2.1875, -1.875, -1.5625, -1.25, 0],
             # [-20, -15, -10, -5, 0, 5, 10, 15],
             # [-35, -30, -25, -20, -15, -10, -5, 0,
             #  5, 10, 15, 20, 25, 30, 35, 40],
             ]
 # ts = [10000, 6000, 3000]
-ts = [10000, 3000]
+ts = [8000, 3000]
 
 # t = 10_000, β = 1
 # params = [-15, -10, -7.5, -6.25, -5, 0, 5, 10]

### 2016-05-17 calculations/single-atom/results/imaging_line/plot_combine.jl
[calculations/single-atom] combined plot

@@ -1,0 +1,69 @@
+#!/usr/bin/julia -f
+
+# β, δ, t, <final energy ± unc>, <escape time ± unc>, <photon count ± unc>
+# const global_t = 10000
+const global_t = 8000
+data = readcsv("gamma_5_$(global_t)_comb.csv")
+
+using PyPlot
+
+const cmap = PyPlot.ColorMap("brg_r")
+
+function plot_params(name, all_data, val_idx)
+    # {β: {δs: (vals, uncs)}}
+    data_dict = Dict{Float64,Dict{Float64,NTuple{2,Float64}}}()
+    for i in 1:size(all_data, 1)
+        β = all_data[i, 1]
+        δ = all_data[i, 2]
+        t = all_data[i, 3]
+
+        val = all_data[i, val_idx]
+        unc = all_data[i, val_idx + 1]
+        data = if !(β in keys(data_dict))
+            data_dict[β] = Dict{Float64,NTuple{2,Float64}}()
+        else
+            data_dict[β]
+        end
+        if !(δ in keys(data))
+            data[δ] = (val, unc)
+        else
+            oldval, oldunc = data[δ]
+            oldw = 1 / oldunc^2
+            w = 1 / unc^2
+            newval = (oldval * oldw + val * w) / (oldw + w)
+            newunc = 1 / sqrt(oldw + w)
+            data[δ] = (newval, newunc)
+        end
+    end
+    βs = collect(keys(data_dict))
+    sort!(βs)
+    βmin = βs[1]
+    βmax = βs[end]
+    for β in βs
+        color = cmap((β - βmin) / (βmax - βmin))
+        data = data_dict[β]
+        δs = collect(keys(data))
+        sort!(δs)
+        vals = similar(δs)
+        uncs = similar(δs)
+        for i in 1:length(δs)
+            vals[i], uncs[i] = data[δs[i]]
+        end
+        errorbar(δs, vals, uncs, color=color, label="\$\\beta=$β\$")
+    end
+    title("\$t=$(global_t)\$")
+    ylabel(name)
+    xlabel("Detuning (MHz)")
+    # legend()
+    legend(loc=2)
+    grid()
+end
+
+# figure()
+# plot_params("Final Energy", data, 4)
+# figure()
+# plot_params("Escape Time", data, 6)
+figure()
+plot_params("Photon Count", data, 8)
+# show()
+savefig("gamma_5_comb_$(global_t).png")

### 2016-05-19 presentations/damop-2016/plot.jl
[presentations/damop-2016] tweak problems

@@ -1,0 +1,18 @@
+#!/usr/bin/julia -f
+
+using PyPlot
+
+data = readdlm("CsPhotonsVsDetuning-4.txt")
+data2 = readdlm("CsPhotonsVsDetuning-7.txt")
+
+errorbar(data[:, 1], data[:, 2], data[:, 3],
+         label="\$\\lambda=970nm\$", linewidth=2)
+errorbar(data2[:, 1], data2[:, 2], data2[:, 3],
+         label="\$\\lambda=930nm\$", linewidth=2)
+ylim([0, 25000])
+legend()
+grid()
+xlabel("Detuning (MHz)", size=20)
+ylabel("Photon count", size=20)
+# show()
+savefig("det-vs-photon-dc.png", bbox_inches="tight")

### 2016-05-19 presentations/damop-2016/plot.jl
[presentations/damop-2016] fix plot

@@ -8,7 +8,7 @@ data2 = readdlm("CsPhotonsVsDetuning-7.txt")
 errorbar(data[:, 1], data[:, 2], data[:, 3],
          label="\$\\lambda=970nm\$", linewidth=2)
 errorbar(data2[:, 1], data2[:, 2], data2[:, 3],
-         label="\$\\lambda=930nm\$", linewidth=2)
+         label="\$\\lambda=935nm\$", linewidth=2)
 ylim([0, 25000])
 legend()
 grid()

### 2016-05-19 presentations/damop-2016/plot.jl
[presentations/damop-2016] solution plot 1

@@ -4,15 +4,42 @@ using PyPlot
 
 data = readdlm("CsPhotonsVsDetuning-4.txt")
 data2 = readdlm("CsPhotonsVsDetuning-7.txt")
+data3 = readdlm("CsPhotonsVsDetuning-3.txt")
+
+# errorbar(data[:, 1], data[:, 2], data[:, 3],
+#          label="\$\\lambda=970nm\$", linewidth=2)
+# errorbar(data2[:, 1], data2[:, 2], data2[:, 3],
+#          label="\$\\lambda=935nm\$", linewidth=2)
+# ylim([0, 25000])
+# legend()
+# grid()
+# xlabel("Detuning (MHz)", size=20)
+# ylabel("Photon count", size=20)
+# # show()
+# savefig("det-vs-photon-dc.png", bbox_inches="tight")
+
+# errorbar(data[:, 1], data[:, 2], data[:, 3],
+#          label="DC,\$\\lambda=970nm\$", linewidth=2)
+# errorbar(data2[:, 1], data2[:, 2], data2[:, 3],
+#          label="DC,\$\\lambda=935nm\$", linewidth=2)
+# ylim([0, 30000])
+# legend()
+# grid()
+# xlabel("Detuning (MHz)", size=20)
+# ylabel("Photon count", size=20)
+# # show()
+# savefig("det-vs-photon-dc2.png", bbox_inches="tight")
 
 errorbar(data[:, 1], data[:, 2], data[:, 3],
-         label="\$\\lambda=970nm\$", linewidth=2)
+         label="DC,\$\\lambda=970nm\$", linewidth=2)
 errorbar(data2[:, 1], data2[:, 2], data2[:, 3],
-         label="\$\\lambda=935nm\$", linewidth=2)
-ylim([0, 25000])
+         label="DC,\$\\lambda=935nm\$", linewidth=2)
+errorbar(data3[:, 1], data3[:, 2], data3[:, 3],
+         label="AC,\$\\lambda=970nm\$", linewidth=2)
+ylim([0, 30000])
 legend()
 grid()
 xlabel("Detuning (MHz)", size=20)
 ylabel("Photon count", size=20)
 # show()
-savefig("det-vs-photon-dc.png", bbox_inches="tight")
+savefig("det-vs-photon-ac.png", bbox_inches="tight")

### 2016-05-20 presentations/damop-2016/setup.tex
[presentations/damop-2016] separate setup image

\documentclass{beamer}
\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage{times}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{esint}
\usepackage{hyperref}
\usepackage{tikz}
\usepackage{xkeyval}
\usepackage{xargs}
\usepackage{verbatim}
\usepackage{listings}
\usepackage{multimedia}
\usepackage{pgfplots}
\usepgfplotslibrary{colormaps}
\usetikzlibrary{
  arrows,
  calc,
  decorations.pathmorphing,
  decorations.pathreplacing,
  decorations.markings,
  fadings,
  positioning,
  shapes
}

\pgfdeclareradialshading{glow}{\pgfpoint{0cm}{0cm}}{
  color(0mm)=(white);
  color(3mm)=(white);
  color(7mm)=(black);
  color(10mm)=(black)
}
\pgfdeclareverticalshading{beam}{2cm}{
  % manual 1082-1083; later - shading is assumed to be 100bp diameter ??
  color(0cm)=(black);
  color(0.3cm)=(black);
  color(1cm)=(white);
  color(1.7cm)=(black);
  color(2cm)=(black)
}

\begin{tikzfadingfrompicture}[name=glow fading]
  \shade [shading=glow] (0,0) circle (1);
\end{tikzfadingfrompicture}

\begin{tikzfadingfrompicture}[name=beam fading]
  \shade [shading=beam] (-1,-1) rectangle (1, 1);
\end{tikzfadingfrompicture}

\beamertemplatenavigationsymbolsempty

\begin{document}

\begin{frame}
  \begin{tikzpicture}
    \visible<2-3>{
      \shade[shading=radial,rotate=90,yscale=1,fill opacity=0.6,
      inner color=red]
      plot[draw,samples=200,domain=-3:3] function {sqrt(0.0025 + x**2 / 10)}
      -- plot[draw,samples=200,domain=3:-3] function {-sqrt(0.0025 + x**2 / 10)};
      \path (0, 3) node[below] {Tweezer};
    }
    \visible<1-2>{
      \fill[orange,opacity=0.8,path fading=glow fading] (0,0) circle (1.5);
    }
    \visible<3>{
      \path (2, 0) node[align=center] {Imaging\\beams};
      \fill[orange,opacity=0.7,path fading=beam fading,transform canvas={rotate=25}]
      (-2, -0.2) rectangle (2, 0.2);
      \fill[orange,opacity=0.7,path fading=beam fading,transform canvas={rotate=-25}]
      (-2, -0.2) rectangle (2, 0.2);
    }
    \visible<2-3>{
      \fill [blue,path fading=glow fading] (0,0) circle (0.08);
    }
  \end{tikzpicture}
\end{frame}

\end{document}

### 2016-05-20 presentations/damop-2016/plot.jl
[presentations/damop-2016] tweak photon count plot

@@ -6,36 +6,41 @@ data = readdlm("CsPhotonsVsDetuning-4.txt")
 data2 = readdlm("CsPhotonsVsDetuning-7.txt")
 data3 = readdlm("CsPhotonsVsDetuning-3.txt")
 
-# errorbar(data[:, 1], data[:, 2], data[:, 3],
-#          label="\$\\lambda=970nm\$", linewidth=2)
-# errorbar(data2[:, 1], data2[:, 2], data2[:, 3],
-#          label="\$\\lambda=935nm\$", linewidth=2)
-# ylim([0, 25000])
-# legend()
-# grid()
-# xlabel("Detuning (MHz)", size=20)
-# ylabel("Photon count", size=20)
-# # show()
-# savefig("det-vs-photon-dc.png", bbox_inches="tight")
-
-# errorbar(data[:, 1], data[:, 2], data[:, 3],
-#          label="DC,\$\\lambda=970nm\$", linewidth=2)
-# errorbar(data2[:, 1], data2[:, 2], data2[:, 3],
-#          label="DC,\$\\lambda=935nm\$", linewidth=2)
-# ylim([0, 30000])
-# legend()
-# grid()
-# xlabel("Detuning (MHz)", size=20)
-# ylabel("Photon count", size=20)
-# # show()
-# savefig("det-vs-photon-dc2.png", bbox_inches="tight")
-
+figure()
 errorbar(data[:, 1], data[:, 2], data[:, 3],
-         label="DC,\$\\lambda=970nm\$", linewidth=2)
+         label="\$\\lambda=970nm\$", fmt="o-", linewidth=3, markersize=8)
 errorbar(data2[:, 1], data2[:, 2], data2[:, 3],
-         label="DC,\$\\lambda=935nm\$", linewidth=2)
+         label="\$\\lambda=935nm\$", fmt="o-", linewidth=3, markersize=8)
+ylim([0, 25000])
+legend()
+grid()
+xlabel("Detuning (MHz)", size=20)
+ylabel("Photon count", size=20)
+# show()
+savefig("det-vs-photon-dc.png", bbox_inches="tight")
+close()
+
+figure()
+errorbar(data[:, 1], data[:, 2], data[:, 3],
+         label="DC,\$\\lambda=970nm\$", fmt="o-", linewidth=3, markersize=8)
+errorbar(data2[:, 1], data2[:, 2], data2[:, 3],
[…]

### 2016-05-20 presentations/damop-2016/plot_switching.jl
[presentations/damop-2016] tweak solution

@@ -1,0 +1,16 @@
+#!/usr/bin/julia -f
+
+using PyPlot
+
+ts = linspace(0, 4π, 10000)
+trap = atan(exp(15 * cos(ts) - 10)) * 2
+img = atan(exp(-20 * cos(ts))) * 2
+
+figure()
+plot(ts, trap, "b", label="Trap", linewidth=3)
+plot(ts, img, "r", label="Resonant", linewidth=3)
+ylim([0, 4])
+axis("off")
+legend()
+# show()
+savefig("switching.png", bbox_inches="tight")

### 2016-05-20 presentations/damop-2016/setup.tex
[presentations/damop-2016] rotate the plot

@@
 
+\begin{frame}
+  \begin{tikzpicture}
+    \visible<2-3>{
+      \shade[shading=radial,yscale=1,fill opacity=0.6,
+      inner color=red]
+      plot[draw,samples=200,domain=-3:3] function {sqrt(0.0025 + x**2 / 10)}
+      -- plot[draw,samples=200,domain=3:-3] function {-sqrt(0.0025 + x**2 / 10)};
+      \path (2.5, 0) node {Tweezer};
+    }
+    \visible<1-2>{
+      \fill[orange,opacity=0.8,path fading=glow fading] (0,0) circle (1.5);
+    }
+    \visible<3>{
+      \path (0, 1.5) node[left,align=center] {Imaging\\beams};
+      \fill[orange,opacity=0.7,path fading=beam fading,transform canvas={rotate=90}]
+      (-1.5, -0.2) rectangle (1.5, 0.2);
+      \fill[orange,opacity=0.7,path fading=beam fading,transform canvas={rotate=40}]
+      (-2, -0.2) rectangle (2, 0.2);
+    }
+    \visible<2-3>{
+      \fill [blue,path fading=glow fading] (0,0) circle (0.08);
+    }
+  \end{tikzpicture}
+\end{frame}
+
 \end{document}

### 2016-05-22 presentations/damop-2016/plot.jl
[presentations/damop-2016] AC -> modulated

@@ -22,9 +22,9 @@ close()
 
 figure()
 errorbar(data[:, 1], data[:, 2], data[:, 3],
-         label="DC,\$\\lambda=970nm\$", fmt="o-", linewidth=3, markersize=8)
+         label="\$\\lambda=970nm\$", fmt="o-", linewidth=3, markersize=8)
 errorbar(data2[:, 1], data2[:, 2], data2[:, 3],
-         label="DC,\$\\lambda=935nm\$", fmt="o-", linewidth=3, markersize=8)
+         label="\$\\lambda=935nm\$", fmt="o-", linewidth=3, markersize=8)
 ylim([0, 30000])
 legend()
 grid()
@@ -36,11 +36,11 @@ close()
 
 figure()
 errorbar(data[:, 1], data[:, 2], data[:, 3],
-         label="DC,\$\\lambda=970nm\$", fmt="o-", linewidth=3, markersize=8)
+         label="\$\\lambda=970nm\$", fmt="o-", linewidth=3, markersize=8)
 errorbar(data2[:, 1], data2[:, 2], data2[:, 3],
-         label="DC,\$\\lambda=935nm\$", fmt="o-", linewidth=3, markersize=8)
+         label="\$\\lambda=935nm\$", fmt="o-", linewidth=3, markersize=8)
 errorbar(data3[:, 1], data3[:, 2], data3[:, 3],
-         label="AC,\$\\lambda=970nm\$", fmt="o-", linewidth=3, markersize=8)
+         label="\$\\lambda=970nm\$\n(modulated)", fmt="o-", linewidth=3, markersize=8)
 ylim([0, 30000])
 legend()
 grid()

### 2016-11-01 experiments/na_loading/process.jl
[experiments/na_loading] loading scan

@@ -1,0 +1,112 @@
+#!/usr/bin/julia
+
+using PyPlot
+using NaCsData
+
+matplotlib["rcParams"][:update](Dict("font.size" => 30,
+                                     "font.weight" => "bold"))
+matplotlib[:rc]("xtick", labelsize=25)
+matplotlib[:rc]("ytick", labelsize=25)
+
+const params, ratios, uncs = NaCsData.calc_survival(ARGS[1])
+
+const freqs = linspace(-5e6, -30e6, 11)
+const base_amps = [0, 0.685, 1.32, 1.82, 2.36, 2.75, 3.24,
+                   3.75, 4.29, 4.83, 5.30, 5.84, 6.41]
+const amp_scals = [6.62, 6.56, 6.40, 6.32, 6.21, 5.98,
+                   5.70, 5.40, 5.01, 4.46, 3.97] / 6.40
+const nfreqs = length(freqs)
+const namps = length(base_amps)
+const all_freqs = Vector{Float64}(nfreqs * namps)
+const all_amps = Vector{Float64}(nfreqs * namps)
+
+for i in 1:nfreqs
+    local i
+    local idx_offset = (i - 1) * namps
+    local freq = freqs[i]
+    local amp_scal = amp_scals[i]
+    for j in 1:namps
+        local j
+        idx = j + idx_offset
+        all_freqs[idx] = freq
+        all_amps[idx] = base_amps[j] * amp_scal
+    end
+end
+
+const ratios_matrix = reshape(ratios[:, 1], namps, nfreqs)
+
+# The following is a hacky 2D interpolation implementation since I can't
+# get any non-hacky one to work quickly.....
+# It split the 2D surface into triangles and do linear interpolation in each
+# triangle.
+function dist_to_line(p1, p2, xy)
+    x1, y1 = p1
+    x2, y2 = p2
+    x0, y0 = xy
+    y21 = y2 - y1
+    x21 = x2 - x1
+    return abs(y21 * x0 - x21 * y0 + x2 * y1 - y2 * x1) / sqrt(y21^2 + x21^2)
+end
+
+function calc_val(f, a)
+    fi = (f - first(freqs)) / step(freqs)
+    fi < 0 && return NaN
+    fi_lo = floor(Int, fi) + 1
+    fi_hi = fi_lo + 1
[…]

### 2017-03-24 experiments/misc/plot_20170319_213303.jl
[experiments/misc] Before cooling only plot

@@ -60,3 +60,12 @@ xlabel("\$\\delta\$/MHz")
 savefig("$(prefix)_r3.png", bbox_inches="tight", transparent=true)
 savefig("$(prefix)_r3.svg", bbox_inches="tight", transparent=true)
 close()
+
+figure()
+plot_params(Params4, Idx4, fmt="ro-")
+grid()
+ylim([0, 1])
+xlabel("\$\\delta\$/MHz")
+savefig("$(prefix)_r3_before.png", bbox_inches="tight", transparent=true)
+savefig("$(prefix)_r3_before.svg", bbox_inches="tight", transparent=true)
+close()

### 2017-03-24 experiments/misc/plot_20170324_010638.jl
[experiments/misc] 3D cooling sidebands

@@ -1,0 +1,80 @@
+#!/usr/bin/julia
+
+push!(LOAD_PATH, joinpath(@__DIR__, "../../lib"))
+
+using NaCsData
+using PyPlot
+matplotlib["rcParams"][:update](Dict("font.size" => 20,
+                                     "font.weight" => "bold"))
+matplotlib[:rc]("xtick", labelsize=15)
+matplotlib[:rc]("ytick", labelsize=15)
+
+const params, ratios, uncs = NaCsData.calc_survival(ARGS[1])
+
+Params1 = [linspace(-18.93, -18.71, 12); linspace(-18.125, -17.425, 29)] - 0.075;
+Params2 = [linspace(-18.87, -19.07, 11); linspace(-17.925, -17.1, 34)] - 0.075;
+Params3 = [linspace(-18.54, -18.57, 16); linspace(-18.40, -18.43, 16)];
+Params4 = linspace(-18.4, -18, 81);
+
+offset1 = length(Params1)
+offset2 = offset1 + length(Params2)
+offset3 = offset2 + length(Params3)
+offset4 = offset3 + length(Params4)
+
+Idx1 = [1:offset1;]
+Idx2 = [(offset1 + 1):offset2;]
+Idx3 = [(offset2 + 1):offset3;]
+Idx4 = [(offset3 + 1):offset4;]
+
+function plot_params(Params, Idx; kws...)
+    perm = sortperm(Params)
+    Params = Params[perm]
+    Idx = Idx[perm]
+    Ratios = ratios[Idx, 2]
+    Uncs = uncs[Idx, 2]
+    errorbar(Params, Ratios, Uncs; kws...)
+end
+
+const prefix = ARGS[2]
+
+figure()
+plot_params(Params1, Idx1, fmt="bo-")
+grid()
+ylim([0, ylim()[2]])
+title("Axis 2 (Radial)")
+xlabel("\$\\delta\$/MHz")
+savefig("$(prefix)_r2.png", bbox_inches="tight", transparent=true)
+savefig("$(prefix)_r2.svg", bbox_inches="tight", transparent=true)
+close()
+
+figure()
+plot_params(Params2, Idx2, fmt="bo-")
+grid()
+ylim([0, ylim()[2]])
+title("Axis 3 (Radial)")
+xlabel("\$\\delta\$/MHz")
+savefig("$(prefix)_r3.png", bbox_inches="tight", transparent=true)
[…]

### 2017-04-08 presentations/na_cool_paper/sequence.tex
[presentations/na_cool_paper] sequence plot

\documentclass{standalone}
\usepackage{tikz}
\usetikzlibrary{decorations.pathreplacing}
\usepackage{graphicx}
\begin{document}
\begin{tikzpicture}
  % 0.0 - 1.5 axial
  % 1.5 - 2.0 OP
  % 2.0 - 3.5 axial
  % 3.5 - 4.0 OP
  % 4.0 - 5.0 radial 2
  % 5.0 - 5.5 OP
  % 5.5 - 7.0 axial
  % 7.0 - 7.5 OP
  % 7.5 - 9.0 axial
  % 9.0 - 9.5 OP
  % 9.5 - 10.5 radial 3
  % 10.5 - 11.0 OP

  \foreach \i in {2.0, 4.0, 5.5, 7.5, 9.5, 11.0, 13.0, 15.0, 16.5, 18.5, 20.5} {
    \draw[gray!20, line width=1.5] (\i, 1.5) -- (\i, -6);
  }

  %% Axial
  \foreach \i in {0, 5.5, 11.0, 16.5} {
    \fill[blue!30]
    plot[draw,samples=200,domain=\i:{\i+1.5},variable=\x] ({\x}, {sin((\x-\i) * 120)^4})
    -- cycle;
    \fill[blue!30]
    plot[draw,samples=200,domain={\i+2.0}:{\i+3.5},variable=\x] ({\x}, {sin((\x-\i-2.0) * 120)^4})
    -- cycle;
    \draw[line width=1,blue] plot[domain=\i:{\i+1.5},variable=\x]
    ({\x}, {sin((\x-\i) * 120)^4}) -- (\i+2.0, 0)
    plot[domain={\i+2.0}:{\i+3.5},variable=\x]
    ({\x}, {sin((\x-\i-2.0) * 120)^4})-- (\i+5.5, 0);
  }
  \path (0, 0.5) node[left,blue,align=center] {\textbf{Axis 1}\\\textit{Axial}};

  %% Radial 2
  \foreach \i in {0, 11.0} {
    \fill[red!30]
    plot[draw,samples=200,domain={\i+4.0}:{\i+5.0},variable=\x] ({\x}, {1.5*sin((\x-\i-4.0) * 180)^4 - 2})
    -- cycle;
    \draw[line width=1,red] (\i, -2) -- plot[domain={\i+4.0}:{\i+5.0},variable=\x]
    ({\x}, {1.5*sin((\x-\i-4.0) * 180)^4 - 2}) -- (\i+11.0, -2);
  }
  \path (0, -1.5) node[left,red,align=center] {\textbf{Axis 2}\\\textit{Radial}};

  %% Radial 3
  \foreach \i in {0, 11.0} {
    \fill[black!30]
    plot[draw,samples=200,domain={\i+9.5}:{\i+10.5},variable=\x] ({\x}, {1.5*sin((\x-\i-9.5) * 180)^4 - 4})
    -- cycle;
    \draw[line width=1,black] (\i, -4) -- plot[domain={\i+9.5}:{\i+10.5},variable=\x]
    ({\x}, {1.5*sin((\x-\i-9.5) * 180)^4 - 4}) -- (\i+11.0, -4);
  }
  \path (0, -3.5) node[left,black,align=center] {\textbf{Axis 3}\\\textit{Radial}};

  \foreach \i in {0, 5.5, 11.0, 16.5} {
    \filldraw[fill=orange!30,draw=orange,line width=1.5]
    (\i+1.5, -6) -- (\i+1.5, -4.5) -- (\i+2.0, -4.5) -- (\i+2.0, -6) -- cycle;
    \filldraw[fill=orange!30,draw=orange,line width=1.5]
    (\i+3.5, -6) -- (\i+3.5, -4.5) -- (\i+4.0, -4.5) -- (\i+4.0, -6) -- cycle;
    \filldraw[fill=orange!30,draw=orange,line width=1.5]
    (\i+5.0, -6) -- (\i+5.0, -4.5) -- (\i+5.5, -4.5) -- (\i+5.5, -6) -- cycle;
  }
  \path (0, -5.5) node[left,orange,align=center] {\textbf{Optical}\\\textbf{pumping}};
  \draw[line width=2,orange,->] (0,-6) -- (23,-6) node[right, below] {\scalebox{2}{$t$}};
  \draw[decoration={brace,mirror,raise=3pt, amplitude=10pt},decorate,line width=2]
  (0,-6) -- node[below=15pt] {\scalebox{1.5}{One cooling cycle}} (11,-6);
\end{tikzpicture}
\end{document}

### 2017-04-13 calculations/raman-scatter/raman-scatter.jl
[calculations/raman-scatter] Fix typo.....

@@ -82,7 +82,7 @@ function propagate(ϕ, δt, nstep, Γ, i1, i2, Ω, nstate, rates, buff1, rd)
         @fastmath factor = 1 / 2 / sqrt(s)
         s = 0 # normalization
         @simd for j in 1:nstate
-            v = ϕ[j] * (1 - rates[j] * factor * δt)
+            v = ϕ[j] * (1 - rates[j] * δt) * factor
             s += abs2(v)
             ϕ[j] = v
         end

### 2017-04-14 calculations/raman-scatter/raman-scatter.jl
[calculations/raman-scatter] fastmath

@@ -87,8 +87,8 @@ function propagate_2states_underdamp(params::RabiDecayParams{T}, tmax, rd) where
     absΔ = abs(params.Δ)
     exp_lo = r / params.Ω / (params.Ω + absΔ)
     exp_hi = r / params.Ω / (params.Ω - absΔ)
-    tlo::T = -log(exp_hi) / params.Γ
-    thi::T = -log(exp_lo) / params.Γ
+    @fastmath tlo::T = -log(exp_hi) / params.Γ
+    @fastmath thi::T = -log(exp_lo) / params.Γ
     if !(tlo > 0)
         tlo = 0
     end

### 2017-04-14 calculations/raman-scatter/raman-scatter.jl
[calculations/raman-scatter] comparing

@@ -199,6 +199,27 @@ function propagate_underdamp(Ω::T, Γ::AbstractMatrix{T},
     return flipped ? (zero(T), one(T)) : (one(T), zero(T))
 end
 
+function average_underdamp(Ω::T, Γ::AbstractMatrix{T},
+                           rates::AbstractVector{T}, tmax, n, rd) where T
+    sumϕ = zeros(T, 2)
+    sumϕ² = zeros(T, 2)
+    @inbounds for i in 1:n
+        ψ = propagate_underdamp(Ω, Γ, rates, tmax, rd)
+        for j in 1:2
+            ψi = abs2(ψ[j])
+            sumϕ[j] += ψi
+            sumϕ²[j] += ψi^2
+        end
+    end
+    @inbounds for i in 1:2
+        avgϕi = sumϕ[i] / n
+        avgϕ²i = sumϕ²[i] / n
+        sumϕ[i] = avgϕi
+        sumϕ²[i] = (avgϕ²i - avgϕi^2) / sqrt(n - 1)
+    end
+    return sumϕ, sumϕ²
+end
+
 # Propagate the state `ϕ` by `nstep` number of time steps each of length `δt`
 # The decay matrix is `Γ`, the element `(i,j)` of this matrix represents the decay rate
 # from state `j` to state `i`.
@@ -213,11 +234,11 @@ function propagate(ϕ, δt, nstep, Γ, i1, i2, Ω, nstate, rates, buff1, rd)
     end
 
     # Half step
-    @fastmath sinΩt_2 = sin(Ω * δt / 2)
-    @fastmath cosΩt_2 = cos(Ω * δt / 2)
+    @fastmath sinΩt_2 = sin(Ω * δt / 4)
+    @fastmath cosΩt_2 = cos(Ω * δt / 4)
     # Full step
-    @fastmath sinΩt = sin(Ω * δt)
-    @fastmath cosΩt = cos(Ω * δt)
+    @fastmath sinΩt = sin(Ω * δt / 2)
+    @fastmath cosΩt = cos(Ω * δt / 2)
     # Decay rate
     T = real(eltype(ϕ))
     s::T = 0
@@ -324,8 +345,7 @@ function average(ϕ0, δt, nstep, Γ, i1, i2, Ω, n, rates, rd)
 end
 
 
-# ϕ = [1.0, 0.0]
-# δt = 1e-7
+ϕ = [1.0, 0.0]
 Γ = [0 3e4
       2e4 0]
 rates = Vector{eltype(Γ)}(2)
[…]

### 2017-04-15 calculations/raman-scatter/raman-scatter.jl
[calculations/raman-scatter] Performance optimization other comparisons

@@ -56,45 +56,49 @@ function propagate_2states_underdamp(params::RabiDecayParams{T}, tmax, rd) where
     # Now find the t for which `ψ^2(t) * Ω′² = r`.
     # First check if `ψ^2(tmax) * Ω′² > r`
     t::T = tmax
-    Ω′t = params.Ω′ * t
-    @fastmath sinΩ′t = sin(Ω′t)
-    @fastmath cosΩ′t = cos(Ω′t)
-    @fastmath expΓt = exp(-params.Γ * t)
-    ψ² = -expΓt * muladd(params.ΔΩ′, sinΩ′t, muladd(params.Δ², cosΩ′t, -params.Ω²))
-    if ψ² > r
-        # No decay happened, return the wave function at tmax
-        Ω′t_2 = Ω′t / 2
-        @fastmath sinΩ′t_2 = sin(Ω′t_2)
-        @fastmath cosΩ′t_2 = cos(Ω′t_2)
-        ψ1 = muladd(params.Ω′, cosΩ′t_2, -params.Δ * sinΩ′t_2)
-        ψ2 = params.Ω * sinΩ′t_2
-        @fastmath factor = sqrt(expΓt / ψ²)
-        return t, 0, (ψ1 * factor, ψ2 * factor)
-    end
     # Tolerance
     yδ = max(T(2e-7), eps(T) * 10) * params.Ω′²
-    # Find the root using a combination of newton's method and bisecting.
-    # The bisection is to avoid newton's method overshotting since the function we want
-    # to solve is known to have partial oscillation.
-    if r - ψ² <= yδ
-        @goto ret
-    end
     if params.Ω′² - r <= yδ
         return zero(T), 1, (one(T), zero(T))
     end
+    Ω′t::T = 0
+    sinΩ′t::T = 0
+    cosΩ′t::T = 0
+    expΓt::T = 0
+    ψ²::T = 0
     # ψ² * Ω′² is bound between exp(-Γt) * Ω * (Ω ± Δ)
     # Use this to compute a better bounds
     absΔ = abs(params.Δ)
     exp_lo = r / params.Ω / (params.Ω + absΔ)
+    @fastmath thi::T = -log(exp_lo) / params.Γ
+    if !(thi < t)
+        thi = t
+        Ω′t = params.Ω′ * t
+        @fastmath sinΩ′t = sin(Ω′t)
+        @fastmath cosΩ′t = cos(Ω′t)
[…]

### 2017-04-16 calculations/multistate-op/plot.jl
[calculations/multistate-op] Move some functions to lib

@@ -14,7 +14,11 @@ function plot_f12(rates, tscale)
     τ_max = max(τ, τ_f1)
     ts = linspace(0, τ_max * tscale, 100)
     f1 = gen_model(rates, init).(ts)
+    A = rates_to_A(rates)
+    full_f = t->expm(A * t) * init
+    full_phi = full_f.(ts)
     plot(ts, f1)
+    plot(ts, full_phi)
     ylim(0, 1)
     maxt = maximum(ts)
     xlim(0, maxt)
@@ -24,14 +28,14 @@ end
 
 figure()
 title("F2 Counter OP")
-plot_f12(rates_f2_counterop, 10)
+plot_f12(rates_f2_counterop, 100)
 figure()
 title("F2 Co-prop")
-plot_f12(rates_f2_coprop, 10)
+plot_f12(rates_f2_coprop, 100)
 figure()
 title("F1 Up/Down")
-plot_f12(rates_f1_up, 10)
+plot_f12(rates_f1_up, 100)
 figure()
 title("F1 Co-prop")
-plot_f12(rates_f1_coprop, 10)
+plot_f12(rates_f1_coprop, 100)
 show()

### 2017-04-16 calculations/multistate-op/script.jl

@@ -1,63 +1,9 @@
 #!/usr/bin/julia
 
-import GSL
-
-function coupling_LS(L1x2::Integer, L2x2::Integer, J1x2::Integer, J2x2::Integer, Ix2::Integer,
-                     F1x2::Integer, F2x2::Integer, mF1x2::Integer, mF2x2::Integer)::Float64
-    if abs(L1x2 - L2x2) != 2
-        return 0
-    elseif abs(J1x2 - L1x2) != 1 || abs(J2x2 - L2x2) != 1
-        throw(ArgumentError("Illegal J"))
-    elseif !(abs(J1x2 - Ix2) <= F1x2 <= J1x2 + Ix2 && abs(J2x2 - Ix2) <= F2x2 <= J2x2 + Ix2)
-        throw(ArgumentError("Illegal F"))
-    elseif (F1x2 + J1x2 + Ix2) % 2 != 0 || (F2x2 + J2x2 + Ix2) % 2 != 0
-        throw(ArgumentError("Illegal F"))
-    elseif !((F1x2 - F2x2) in (-2, 0, 2) && (mF1x2 - mF2x2) in (-2, 0, 2))
-        return 0
-    end
-    qx2 = mF1x2 - mF2x2
-    m1powx2 = F2x2 + mF1x2 - 2
-    factor = sqrt(F1x2 + 1) * GSL.sf_coupling_3j(F2x2, 2, F1x2, mF2x2, qx2, -mF1x2)
-    m1powx2 += F2x2 + J1x2 + 2 + Ix2
-    factor *= sqrt((F2x2 + 1) * (J1x2 + 1)) * GSL.sf_coupling_6j(J1x2, J2x2, 2, F2x2, F1x2, Ix2)
-    m1powx2 += J2x2 + L1x2 + 2 + 1
-    factor *= sqrt((J2x2 + 1) * (L1x2 + 1)) * GSL.sf_coupling_6j(L1x2, L2x2, 2, J2x2, J1x2, 1)
-    if m1powx2 % 4 == 2
-        factor = -factor
-    end
-    return factor
-end
-
-coupling_D(D2::Bool, Ix2, F1x2, F2x2, mF1x2, mF2x2) =
-    coupling_LS(0, 2, 1, D2 ? 3 : 1, Ix2, F1x2, F2x2, mF1x2, mF2x2)
+using NaCsCalc.Atomic: coupling_D_raman
 
[…]

### 2017-04-16 lib/NaCsCalc/src/NaCsCalc.jl

@@ -7,5 +7,6 @@ module NaCsCalc
 include("utils.jl")
 include("trap.jl")
 include("format.jl")
+include("atomic.jl")
 
 end

### 2017-04-16 lib/NaCsCalc/src/atomic.jl

@@ -1,0 +1,76 @@
+#!/usr/bin/julia
+
+module Atomic
+
+import GSL
+
+"""
+    coupling_LS(L1x2, L2x2, J1x2, J2x2, Ix2, F1x2, F2x2, mF1x2, mF2x2)
+
+Compute the relative matrix element between two states (`F1`, `mF1`) and (`F2`, `mF2`)
+relative to the reduced matrix element on two `L` states for a single electron atom
+in the LS coupling regime (i.e. Hydrogen or Alkali-like).
+The `I` for the atom and `L`, `J`, `F` and `mF` for the two states are given in their value
+multiplying by two so they are all integers.
+"""
+function coupling_LS(L1x2::Integer, L2x2::Integer, J1x2::Integer, J2x2::Integer, Ix2::Integer,
+                     F1x2::Integer, F2x2::Integer, mF1x2::Integer, mF2x2::Integer)::Float64
+    if abs(L1x2 - L2x2) != 2
+        return 0
+    elseif abs(J1x2 - L1x2) != 1 || abs(J2x2 - L2x2) != 1
+        throw(ArgumentError("Illegal J"))
+    elseif !(abs(J1x2 - Ix2) <= F1x2 <= J1x2 + Ix2 && abs(J2x2 - Ix2) <= F2x2 <= J2x2 + Ix2)
+        throw(ArgumentError("Illegal F"))
+    elseif (F1x2 + J1x2 + Ix2) % 2 != 0 || (F2x2 + J2x2 + Ix2) % 2 != 0
+        throw(ArgumentError("Illegal F"))
+    elseif !((F1x2 - F2x2) in (-2, 0, 2) && (mF1x2 - mF2x2) in (-2, 0, 2))
+        return 0
+    end
+    qx2 = mF1x2 - mF2x2
+    m1powx2 = F2x2 + mF1x2 - 2
+    factor = sqrt(F1x2 + 1) * GSL.sf_coupling_3j(F2x2, 2, F1x2, mF2x2, qx2, -mF1x2)
+    m1powx2 += F2x2 + J1x2 + 2 + Ix2
+    factor *= sqrt((F2x2 + 1) * (J1x2 + 1)) * GSL.sf_coupling_6j(J1x2, J2x2, 2, F2x2, F1x2, Ix2)
+    m1powx2 += J2x2 + L1x2 + 2 + 1
[…]

### 2017-04-16 lib/NaCsSim/src/decay_rabi.jl
[lib/NaCsSim] Rename

@@ -50,7 +50,7 @@ struct RabiDecayParams{T}
     end
 end
 
-function propagate_2states_underdamp(params::RabiDecayParams{T}, tmax, rd) where T
+function propagate_step_underdamp(params::RabiDecayParams{T}, tmax, rd) where T
     r = T(rand(rd)) * params.Ω′²
     # Now find the t for which `ψ^2(t) * Ω′² = r`.
     # First check if `ψ^2(tmax) * Ω′² > r`
@@ -154,7 +154,7 @@ function propagate_2states_underdamp(params::RabiDecayParams{T}, tmax, rd) where
     return t, rtotal * rand(rd) < r2 ? 2 : 1, (one(T), zero(T))
 end
 
-function propagate_2states_overdamp(params::RabiDecayParams{T}, tmax, rd) where T
+function propagate_step_overdamp(params::RabiDecayParams{T}, tmax, rd) where T
     r0 = T(rand(rd))
     # Now find the t for which `ψ^2(t) = r0`.
     t::T = tmax
@@ -263,7 +263,7 @@ function propagate_2states_overdamp(params::RabiDecayParams{T}, tmax, rd) where 
 end
 
 """
-    propagate_2states(params::RabiDecayParams, tmax, rd) -> (t, i, ψ)
+    propagate_step(params::RabiDecayParams, tmax, rd) -> (t, i, ψ)
 
 The atom start in state 1 and is doing Rabi flopping with (angular) Rabi frequency `Ω`
 to state 2. The state 1(2) has a decay rate of `Γ₁`(`Γ₂`). Propagate this system under the
@@ -274,10 +274,10 @@ If a decay has happend, `t` is the decay time. `i` (either `1` or `2`) is the st
 the decay occurs. `ψ` is unused.
 If no decay happens, `t == tmax`, `i == 0`, `ψ` is a tuple of the wavefunctions
 """
-@inline propagate_2states(params::RabiDecayParams, tmax, rd) = if params.overdamp
-    propagate_2states_overdamp(params, tmax, rd)
+@inline propagate_step(params::RabiDecayParams, tmax, rd) = if params.overdamp
+    propagate_step_overdamp(params, tmax, rd)
 else
-    propagate_2states_underdamp(params, tmax, rd)
+    propagate_step_underdamp(params, tmax, rd)
 end
 
 """
[…]

### 2017-04-16 calculations/multistate-op/script.jl
[calculations/multistate-op] move more to the lib

@@ -1,56 +1,19 @@
 #!/usr/bin/julia
 
-using NaCsCalc.Atomic: coupling_D_raman
+using NaCsCalc.Atomic: all_scatter_D
 
-function na_scattering_d2(F1::Integer, F2::Integer, mF1::Integer, mF2::Integer, pol::Integer)
-    return coupling_D_raman(true, 3, F1 * 2, F2 * 2, mF1 * 2, mF2 * 2, pol)
-end
+const δf1 = -25.0e9
+const δf2 = -25.0e9 - 1.77e9
+const rlof_f1 = (61.542e6 / (δf1 - 1.107266e9))^2
+const rlof_f2 = (61.542e6 / (δf2 - 1.107266e9))^2
+const rhif_f1 = (61.542e6 / (δf1 + 664.360e6))^2
+const rhif_f2 = (61.542e6 / (δf2 + 664.360e6))^2
 
-function na_scattering_d2_rate(F1::Integer, F2::Integer, mF1::Integer, mF2::Integer,
-                               pol::NTuple{3,Real}, δc::Real)
-    if F1 == 1
-        δ = δc + 664.360e6
-    else
-        δ = δc - 1.107266e9
-    end
-    rate = 0.0
-    for i in 1:3
-        p = pol[i]
-        if p == 0
-            continue
-        end
-        rate += na_scattering_d2(F1, F2, mF1, mF2, i - 2)^2 * p
-    end
-    return rate * (61.542e6 / δ)^2
-end
-
-const states = Tuple{Int,Int}[]
-for i in -2:2
-    push!(states, (2, i))
-end
-for i in -1:1
-    push!(states, (1, i))
-end
-const nstates = length(states)
-
-function gen_rates(pol, δ)
-    rates = Matrix{Float64}(nstates, nstates)
-    @inbounds for i in 1:nstates
-        state1 = states[i]
-        for j in 1:nstates
-            state2 = states[j]
-            rates[j, i] = na_scattering_d2_rate(state1[1], state2[1],
-                                                state1[2], state2[2], pol, δ)
-        end
-    end
-    return rates
-end
-
-const rates_f1_up = gen_rates((0.25, 0.5, 0.25), -25.0e9)
+const rates_f1_up = all_scatter_D(true, 3, (0.25, 0.5, 0.25), rhif_f1, rlof_f1)
[…]

### 2017-04-16 lib/NaCsCalc/src/atomic.jl

@@ -73,4 +73,47 @@ function coupling_D_raman(D2::Bool, Ix2::Integer, F1x2::Integer, F2x2::Integer,
     return cpl
 end
 
+function scatter_D(D2::Bool, Ix2::Integer, F1x2::Integer, F2x2::Integer,
+                   mF1x2::Integer, mF2x2::Integer, pol::NTuple{3,Real})
+    rate = 0.0
+    for i in 1:3
+        p = pol[i]
+        if p == 0
+            continue
+        end
+        rate += abs2(coupling_D_raman(D2, Ix2, F1x2, F2x2, mF1x2, mF2x2, i - 2)) * p
+    end
+    return rate
+end
+
+function all_scatter_D(D2::Bool, Ix2, pol, rhi, rlo)
+    # Order: F high->low; mF low->high
+    idx_to_state = function (idx)
+        local Fx2, mFx2, r
+        if idx > Ix2 + 2
+            # low F
+            idx -= Ix2 + 2
+            Fx2 = Ix2 - 1
+            mFx2 = idx * 2 - Ix2 - 1
+            r = rlo
+        else
+            # high F
+            Fx2 = Ix2 + 1
+            mFx2 = idx * 2 - Ix2 - 3
+            r = rhi
+        end
+        return r, Fx2, mFx2
+    end
+    nstates = (Ix2 + 1) * 2
+    rates = Matrix{Float64}(nstates, nstates)
+    @inbounds for i in 1:nstates
+        r, F1x2, mF1x2 = idx_to_state(i)
+        for j in 1:nstates
+            _, F2x2, mF2x2 = idx_to_state(j)
+            rates[j, i] = scatter_D(D2, Ix2, F1x2, F2x2, mF1x2, mF2x2, pol) * r
+        end
+    end
+    return rates
+end
+
 end

### 2017-04-16 calculations/multistate-op/script.jl
[calculations/multistate-op] path handling

@@ -1,5 +1,6 @@
 #!/usr/bin/julia
 
+push!(LOAD_PATH, joinpath(@__DIR__, "../../lib"))
 using NaCsCalc.Atomic: all_scatter_D
 
 const δf1 = -25.0e9

### 2017-04-18 presentations/2017-04-19_itamp/present.tex
[presentations/2017-04-19_itamp] WIP slides

\documentclass{beamer}
\mode<presentation>{
  \usetheme{Boadilla}
  \usefonttheme[onlylarge]{structurebold}
  \usefonttheme[stillsansseriflarge]{serif}
  \setbeamerfont*{frametitle}{size=\normalsize,series=\bfseries}
  % \setbeamertemplate{navigation symbols}{}
  \setbeamercovered{transparent}
}
\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage{times}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{esint}
\usepackage{hyperref}
\usepackage{tikz}
\usepackage{xkeyval}
\usepackage{xargs}
\usepackage{verbatim}
\usepackage{listings}
\usepackage{multimedia}
\usepackage{bm}
\usetikzlibrary{
  arrows,
  calc,
  decorations.pathmorphing,
  decorations.pathreplacing,
  decorations.markings,
  fadings,
  positioning,
  shapes
}

\mode<handout>{
  \usepackage{pgfpages}
  \pgfpagesuselayout{4 on 1}[a4paper,landscape,border shrink=5mm]
  \setbeamercolor{background canvas}{bg=black!10}
}

\newcommand\pgfmathsinandcos[3]{%
  \pgfmathsetmacro#1{sin(#3)}%
  \pgfmathsetmacro#2{cos(#3)}%
}
\newcommand\LongitudePlane[3][current plane]{%
  \pgfmathsinandcos\sinEl\cosEl{#2} % elevation
  \pgfmathsinandcos\sint\cost{#3} % azimuth
  \tikzset{#1/.estyle={cm={\cost,\sint*\sinEl,0,\cosEl,(0,0)}}}
}
\newcommand\LatitudePlane[3][current plane]{%
  \pgfmathsinandcos\sinEl\cosEl{#2} % elevation
  \pgfmathsinandcos\sint\cost{#3} % latitude
  \pgfmathsetmacro\yshift{\cosEl*\sint}
  \tikzset{#1/.estyle={cm={\cost,0,0,\cost*\sinEl,(0,\yshift)}}} %
}
\newcommand\DrawLongitudeCircle[2][1]{
  \LongitudePlane{\angEl}{#2}
  \tikzset{current plane/.prefix style={scale=#1}}
  % angle of "visibility"
  \pgfmathsetmacro\angVis{atan(sin(#2)*cos(\angEl)/sin(\angEl))} %
  \draw[current plane] (\angVis:1) arc (\angVis:\angVis+180:1);
  \draw[current plane,dashed] (\angVis-180:1) arc (\angVis-180:\angVis:1);
}
\newcommand\DrawLatitudeCircleArrow[2][1]{
  \LatitudePlane{\angEl}{#2}
  \tikzset{current plane/.prefix style={scale=#1}}
  \pgfmathsetmacro\sinVis{sin(#2)/cos(#2)*sin(\angEl)/cos(\angEl)}
  % angle of "visibility"
  \pgfmathsetmacro\angVis{asin(min(1,max(\sinVis,-1)))}
  \draw[current plane,decoration={markings, mark=at position 0.6 with {\arrow{<}}},postaction={decorate},line width=.6mm] (\angVis:1) arc (\angVis:-\angVis-180:1);
  \draw[current plane,dashed,line width=.6mm] (180-\angVis:1) arc (180-\angVis:\angVis:1);
}
\newcommand\DrawLatitudeCircle[2][1]{
  \LatitudePlane{\angEl}{#2}
  \tikzset{current plane/.prefix style={scale=#1}}
  \pgfmathsetmacro\sinVis{sin(#2)/cos(#2)*sin(\angEl)/cos(\angEl)}
  % angle of "visibility"
  \pgfmathsetmacro\angVis{asin(min(1,max(\sinVis,-1)))}
  \draw[current plane] (\angVis:1) arc (\angVis:-\angVis-180:1);
  \draw[current plane,dashed] (180-\angVis:1) arc (180-\angVis:\angVis:1);
}
\newcommand\coil[1]{
  {\rh * cos(\t * pi r)}, {\apart * (2 * #1 + \t) + \rv * sin(\t * pi r)}
}
\makeatletter
\define@key{DrawFromCenter}{style}[{->}]{
  \tikzset{DrawFromCenterPlane/.style={#1}}
}
\define@key{DrawFromCenter}{r}[1]{
  \def\@R{#1}
}
\define@key{DrawFromCenter}{center}[(0, 0)]{
  \def\@Center{#1}
}
\define@key{DrawFromCenter}{theta}[0]{
  \def\@Theta{#1}
}
\define@key{DrawFromCenter}{phi}[0]{
  \def\@Phi{#1}
}
\presetkeys{DrawFromCenter}{style, r, center, theta, phi}{}
\newcommand*\DrawFromCenter[1][]{
  \setkeys{DrawFromCenter}{#1}{
    \pgfmathsinandcos\sint\cost{\@Theta}
    \pgfmathsinandcos\sinp\cosp{\@Phi}
    \pgfmathsinandcos\sinA\cosA{\angEl}
    \pgfmathsetmacro\DX{\@R*\cost*\cosp}
    \pgfmathsetmacro\DY{\@R*(\cost*\sinp*\sinA+\sint*\cosA)}
    \draw[DrawFromCenterPlane] \@Center -- ++(\DX, \DY);
  }
}
\newcommand*\DrawFromCenterText[2][]{
  \setkeys{DrawFromCenter}{#1}{
    \pgfmathsinandcos\sint\cost{\@Theta}
    \pgfmathsinandcos\sinp\cosp{\@Phi}
    \pgfmathsinandcos\sinA\cosA{\angEl}
    \pgfmathsetmacro\DX{\@R*\cost*\cosp}
    \pgfmathsetmacro\DY{\@R*(\cost*\sinp*\sinA+\sint*\cosA)}
    \draw[DrawFromCenterPlane] \@Center -- ++(\DX, \DY) node {#2};
  }
}
\makeatother

% not mandatory, but I though it was better to set it blank
\setbeamertemplate{headline}{}
\def\beamer@entrycode{\vspace{-\headheight}}

\tikzstyle{snakearrow} = [decorate, decoration={pre length=0.2cm,
  post length=0.2cm, snake, amplitude=.4mm,
  segment length=2mm},thick, ->]

%% document-wide tikz options and styles

\tikzset{%
  % >=latex, % option for nice arrows
  inner sep=0pt,%
  outer sep=2pt,%
  mark coordinate/.style={inner sep=0pt,outer sep=0pt,minimum size=3pt,
    fill=black,circle}%
}
\tikzset{
  % Define standard arrow tip
  >=stealth',
  % Define style for boxes
  punkt/.style={
    rectangle,
    rounded corners,
    draw=black, very thick,
    text width=8em,
    minimum height=2.5em,
    text centered},
}
\makeatletter
\newbox\@backgroundblock
\newenvironment{backgroundblock}[2]{%
  \global\setbox\@backgroundblock=\vbox\bgroup%
  \unvbox\@backgroundblock%
  \vbox to0pt\bgroup\vskip#2\hbox to0pt\bgroup\hskip#1\relax%
}{\egroup\egroup\egroup}
\addtobeamertemplate{background}{\box\@backgroundblock}{}
\makeatother

% \def\timeleft{15:00->14:55}

\title[Na ground state cooling]{Raman sideband cooling of single sodium atom to 3D ground state}
\date{April 19, 2017}
\author{Yichao Yu}
\institute{Ni Group/Harvard}

\begin{document}

\begin{frame}{}
  \titlepage
\end{frame}

% \begin{frame}{}
%   \tableofcontents
% \end{frame}

\begin{frame}{}
  \begin{center}
    \begin{tikzpicture}
      \visible<1> {
        \path (0, 0) node
        {\includegraphics[width=10cm]{../2015-05-05_cua/overall_full_min.png}};
      }
      \visible<2-> {
        \path (0, 0) node
        {\includegraphics[width=10cm]{../2015-05-05_cua/overall_trap_min.png}};
      }
      \visible<3-> {
        \path (3, -3) node
        {\includegraphics[width=3cm]{../../experiments/nacs_atoms/imgs/single_viridis.png}};
      }
    \end{tikzpicture}
  \end{center}
\end{frame}

\begin{frame}{Raman sideband cooling of Sodium}
  \begin{columns}
    \column{6.5cm}
    \includegraphics[width=6cm]{Na_RSC_schematic.pdf}
    \column{5cm}
    \visible<2->{
      \begin{block}{Difficulties}
        \begin{itemize}
        \item High initial temperature ($40\mu K$)
        \item<3-> High recoil heating
        \end{itemize}
      \end{block}
    }
  \end{columns}
\end{frame}

\begin{frame}{Cooling sequence}
  \tikzfading[name=fade img right,
  left color=transparent!90, right color=transparent!0]
  \begin{tikzpicture}[scale=0.75]
    % 0.0 - 1.5 axial
    % 1.5 - 2.0 OP
    % 2.0 - 3.5 axial
    % 3.5 - 4.0 OP
    % 4.0 - 5.0 radial 2
    % 5.0 - 5.5 OP
    % 5.5 - 7.0 axial
    % 7.0 - 7.5 OP
    % 7.5 - 9.0 axial
    % 9.0 - 9.5 OP
    % 9.5 - 10.5 radial 3
    % 10.5 - 11.0 OP

    %% Pulse mark
    \foreach \i in {2.0, 4.0, 5.5, 7.5, 9.5, 11.0, 13.0, 15.0, 16.5, 18.5, 20.5} {
      \draw[gray!20, line width=1.5] (\i, 1.8) -- (\i, -6.0);
    }

    %% Axial
    \foreach \i in {0, 5.5, 11.0, 16.5} {
      \fill[blue!30]
      plot[draw,samples=200,domain=\i:{\i+1.5},variable=\x] ({\x}, {sin((\x-\i) * 120)^4})
      -- cycle;
      \path (\i+1, 1) node[above,blue,align=center] {$n$-th\\order};
      \fill[blue!30]
      plot[draw,samples=200,domain={\i+2.0}:{\i+3.5},variable=\x] ({\x}, {sin((\x-\i-2.0) * 120)^4})
      -- cycle;
      \path (\i+3, 1) node[above,blue,align=center] {$(n-1)$-th\\order};
      \draw[line width=1,blue] plot[domain=\i:{\i+1.5},variable=\x]
      ({\x}, {sin((\x-\i) * 120)^4}) -- (\i+2.0, 0)
      plot[domain={\i+2.0}:{\i+3.5},variable=\x]
      ({\x}, {sin((\x-\i-2.0) * 120)^4})-- (\i+5.5, 0);
    }
    \path (0, 0.5) node[left,blue,align=center] {\textbf{Axis 1}\\\textit{Axial}};

    %% Radial 2
    \foreach \i in {0, 11.0} {
      \fill[red!30]
      plot[draw,samples=200,domain={\i+4.0}:{\i+5.0},variable=\x] ({\x}, {1.5*sin((\x-\i-4.0) * 180)^4 - 2})
      -- cycle;
      \draw[line width=1,red] (\i, -2) -- plot[domain={\i+4.0}:{\i+5.0},variable=\x]
      ({\x}, {1.5*sin((\x-\i-4.0) * 180)^4 - 2}) -- (\i+11.0, -2);
    }
    \path (0, -1.5) node[left,red,align=center] {\textbf{Axis 2}\\\textit{Radial}};

    %% Radial 3
    \foreach \i in {0, 11.0} {
      \fill[black!30]
      plot[draw,samples=200,domain={\i+9.5}:{\i+10.5},variable=\x] ({\x}, {1.5*sin((\x-\i-9.5) * 180)^4 - 4})
      -- cycle;
      \draw[line width=1,black] (\i, -4) -- plot[domain={\i+9.5}:{\i+10.5},variable=\x]
      ({\x}, {1.5*sin((\x-\i-9.5) * 180)^4 - 4}) -- (\i+11.0, -4);
    }
    \path (0, -3.5) node[left,black,align=center] {\textbf{Axis 3}\\\textit{Radial}};

    %% OP
    \foreach \i in {0, 5.5, 11.0, 16.5} {
      \filldraw[fill=orange!30,draw=orange,line width=1.5]
      (\i+1.5, -6) -- (\i+1.5, -4.5) -- (\i+2.0, -4.5) -- (\i+2.0, -6) -- cycle;
      \filldraw[fill=orange!30,draw=orange,line width=1.5]
      (\i+3.5, -6) -- (\i+3.5, -4.5) -- (\i+4.0, -4.5) -- (\i+4.0, -6) -- cycle;
      \filldraw[fill=orange!30,draw=orange,line width=1.5]
      (\i+5.0, -6) -- (\i+5.0, -4.5) -- (\i+5.5, -4.5) -- (\i+5.5, -6) -- cycle;
    }
    \path (0, -5.5) node[left,orange,align=center] {\textbf{Optical}\\\textbf{pumping}};
    \draw[line width=2,orange] (0,-6) -- (23,-6);

    %% Cycle mark
    \draw[decoration={brace,mirror,raise=3pt, amplitude=10pt},decorate,line width=2]
    (0,-6) -- node[below=15pt] {\scalebox{1.5}{One cooling cycle}} (11,-6);

    \fill[white,path fading=fade img right] (11, -7) rectangle (14.5, 2.5);
    \fill[white,path fading=fade img right] (11, -7) rectangle (14.5, 2.5);
    \fill[white] (14.5, 2.5) rectangle (23, -7);

    \draw[line width=2,orange,->] (0,-6) -- (12,-6) node[right, below] {\scalebox{2}{$t$}};
  \end{tikzpicture}
\end{frame}

\begin{frame}{Raman sidebands}
  \begin{tikzpicture}
    \visible<1-2> {
      \path (1.75, 4) node {
        \includegraphics[width=8.5cm]{../../experiments/misc/imgs/data_spectrum_20170409_a1_before.png}
      };
      \path (0, 0) node {
        \includegraphics[width=5cm]{../../experiments/misc/imgs/data_spectrum_20170409_r2_before.png}
      };
      \path (6, 0) node {
        \includegraphics[width=5cm]{../../experiments/misc/imgs/data_spectrum_20170409_r3_before.png}
      };
      \visible<2> {
        \draw[red, <-, line width=1.5] (-1.4, 4.5) -- (-1.2, 5.2)
        node[above right] {1st order heating};
        \draw[<-, line width=1.5] (-0.7, 4.2) -- (-0.5, 4.8) node[above right] {Carrier};
        \draw[black!40!green, <-, line width=1.5] (0.05, 4.2) -- (0.2, 4.6)
        node[right] {1st order cooling};
        \draw[blue, <-, line width=1.5] (0.8, 3.9) -- (1.2, 4.1)
        node[right] {2nd order cooling};
        \path[magenta] (2, 3.5) node[right] {And higher orders{$\cdots$}};

        \draw[<-, line width=1.5] (-0.35, 0) -- (0, 0.8) node[right] {Carrier};

        \draw[<-, line width=1.5] (5.67, 0.1) -- (6, 0.8) node[right] {Carrier};
      }
    }
    \visible<3-> {
      \path (1.75, 4) node {
        \includegraphics[width=8.5cm]{../../experiments/misc/imgs/data_spectrum_20170409_a1.png}
      };
      \path (0, 0) node {
        \includegraphics[width=5cm]{../../experiments/misc/imgs/data_spectrum_20170409_r2.png}
      };
      \path (6, 0) node {
        \includegraphics[width=5cm]{../../experiments/misc/imgs/data_spectrum_20170409_r3.png}
      };
    }
    \visible<4-> {
      \path[blue] (2, 4.6) node[fill=white,opacity=0.6,text opacity=1,align=center]
      {$\bm{P_{ground\ state}}$\\$\bm{93.1(2.5)\%}$};
      \path[blue] (2, 0.1) node[fill=white,opacity=0.6,text opacity=1,align=center]
      {$\bm{P_{ground\ state}}$\\$\bm{91.9(2.3)\%}$};
      \path[blue] (8, 0.1) node[fill=white,opacity=0.6,text opacity=1,align=center]
      {$\bm{P_{ground\ state}}$\\$\bm{92.9(2.5)\%}$};
      \fill[white,path fading=fade img right] (4, 2.1) rectangle (7, 6);
      \fill[white,path fading=fade img right] (4, 2.1) rectangle (7, 6);
      \fill[white,path fading=fade img right] (4, 2.1) rectangle (7, 6);
      \path (4, 4) node[fill=blue!80!white,opacity=0.8,text opacity=1,
      text=white!85!yellow,right,align=center,
      rounded corners=0.2cm,inner sep=0.2cm] {
        \textbf{3D ground state:} $79.5(3.6)\%$\\
        \textbf{Loss after cooling:} $15\%$\\\\
        \textbf{Total 3D ground state}\\
        \textbf{preparation fidelity}\\
        $67.6(3.1)\%$
      };
    }
  \end{tikzpicture}
\end{frame}

\begin{frame}{Status}
  \begin{columns}
    \column{5cm}
    \begin{itemize}
    \item Radial-only cooling
    \item<2-> Axial-only cooling
    \item<3-> 3D cooling\\
      (Survival: $\approx 89\%$)
    \end{itemize}
    \vspace{0.5cm}
    \visible<3>{
      \includegraphics[width=5cm]{../../experiments/misc/imgs/data_20170324_010638_a1.png}
    }
    \column{6cm}
    \begin{center}
      \vspace{-1cm}
    \end{center}
  \end{columns}
\end{frame}

\begin{frame}{}
\end{frame}

\begin{frame}{Axial matrix element}
  \begin{center}
    \includegraphics[width=5cm]{../../calculations/sideband_strength/imgs/coupling.png}
    \includegraphics[width=6.5cm]{{../../calculations/sideband_strength/imgs/coupling_0.46_0-6}.png}
  \end{center}
\end{frame}

\begin{frame}{Radial matrix element}
  \begin{center}
    \includegraphics[width=6.5cm]{{../../calculations/sideband_strength/imgs/coupling_0.35_0-2}.png}
  \end{center}
\end{frame}

\end{document}

### 2017-04-18 presentations/2017-04-19_itamp/present.tex
[presentations/2017-04-19_itamp] WIP slides

@@
       \path (4, 4) node[fill=blue!80!white,opacity=0.8,text opacity=1,
-      text=white!85!yellow,right,align=center,
+      text=white!90!yellow,right,align=center,
       rounded corners=0.2cm,inner sep=0.2cm] {
@@
 
-\begin{frame}{Status}
-  \begin{columns}
-    \column{5cm}
+\begin{frame}{Rabi flopping (radial)}
+  \begin{center}
+    \visible<+->{
+      \includegraphics[width=10cm]{../../experiments/rabi_flop/imgs/fit_20170409_r2_0_ba.png}\\
+    }
+    \visible<+->{
+      Good agreement between spectrum and Rabi flopping data.
+    }
+  \end{center}
+\end{frame}
+
+\begin{frame}{Rabi flopping (axial)}
+  \begin{center}
+    \includegraphics[width=10cm]{../../experiments/rabi_flop/imgs/fit_20170409_a1_p1_ba.png}\\
+    Decoherence caused by magnetic field fluctuation.
+  \end{center}
+\end{frame}
+
+\begin{frame}{}
+  \begin{block}{Conclusion}
+    $67.6(3.1)\%$ ground state preparation fidelity {\small ($79.5(3.6)\%$ without loss)}
+  \end{block}
+  \vspace{1cm}
+  \begin{block}{Improvements}
     \begin{itemize}
-    \item Radial-only cooling
-    \item<2-> Axial-only cooling
-    \item<3-> 3D cooling\\
-      (Survival: $\approx 89\%$)
+    \item Reduce off-resonance scattering from Raman beams
+    \item Reduce magnetic field fluctuation
+    \item Reduce loss during cooling
     \end{itemize}
-    \vspace{0.5cm}
-    \visible<3>{
-      \includegraphics[width=5cm]{../../experiments/misc/imgs/data_20170324_010638_a1.png}
-    }
-    \column{6cm}
-    \begin{center}
-      \vspace{-1cm}
-    \end{center}
-  \end{columns}
+  \end{block}
 \end{frame}
@@
   \begin{center}
-    \includegraphics[width=5cm]{../../calculations/sideband_strength/imgs/coupling.png}
-    \includegraphics[width=6.5cm]{{../../calculations/sideband_strength/imgs/coupling_0.46_0-6}.png}
+    \includegraphics[width=6.5cm]{{../../calculations/sideband_strength/imgs/coupling_0.43_0-6}.png}
   \end{center}
@@
 
-\begin{frame}{Radial matrix element}
+\begin{frame}{Radial 2 matrix element}
   \begin{center}
@@
 
+\begin{frame}{Radial 3 matrix element}
+  \begin{center}
+    \includegraphics[width=6.5cm]{{../../calculations/sideband_strength/imgs/coupling_0.29_0-2}.png}
+  \end{center}
+\end{frame}
+
 \end{document}

### 2017-04-19 presentations/2017-04-19_itamp/present.tex
[presentations/2017-04-19_itamp] Wave function comparison slide
[presentations/2017-04-19_itamp] Add lab member name
[presentations/2017-04-19_itamp] no legend axial plot

@@
 \usepackage{bm}
+\usepackage{siunitx}
 \usetikzlibrary{
@@
 \date{April 19, 2017}
-\author{Yichao Yu}
+\author[Yichao Yu]{Yichao Yu\\
+  \vspace{0.5cm}
+  {\footnotesize Lee Liu, Dr. Nick Hutzler,\\
+    Jessie Zhang, Dr. Jon Hood}}
 \institute{Ni Group/Harvard}
@@
       }
+    \end{tikzpicture}
+  \end{center}
+\end{frame}
+
+\begin{frame}{Wave function size}
+  \begin{center}
+    \begin{tikzpicture}
+      \shade[ball color=blue!90] (0, 0) circle (0.45);
+      \shade[ball color=orange!90] (0.4, 0.2) circle (0.3);
+      \draw[<->,line width=1] (-0.45, 0.4) -- (0.35, 0.8);
+      \path (-0.05, 0.6) node[rotate=26.565,above=2pt] {$4a_0$};
+      \path (0.2, -2) node[below] {\textbf{Molecule}};
+
+      \draw[line width=1] plot[samples=200,domain=-2:2,variable=\x] ({\x + 6}, {(\x)^2 * 0.8 - 1.5});
+      \draw[line width=2,orange!90!black]
+      plot[samples=200,domain=-2:2,variable=\x] ({\x + 6}, {exp(-(\x)^2 * 1.3) - 0.988});
+      \draw[line width=0.8] (6 - 0.8, -0.988) -- (6 + 0.8, -0.988);
+      \draw[<->,line width=1] (6 - 1, 0.3) -- (6 + 1, 0.3);
+      \path (6, 0.3) node[above] {$1000a_0$};
+      \path (6, -2) node[below] {\textbf{Atom}};
     \end{tikzpicture}
@@
   \begin{center}
-    \includegraphics[width=10cm]{../../experiments/rabi_flop/imgs/fit_20170409_a1_p1_ba.png}\\
+    \includegraphics[height=4.8cm]{../../experiments/rabi_flop/imgs/fit_20170409_a1_0_ba_nol.png}
+    \includegraphics[height=4.8cm]{../../experiments/rabi_flop/imgs/fit_20170409_a1_p1_ba_nol.png}\\
     Decoherence caused by magnetic field fluctuation.

### 2017-04-19 experiments/rabi_flop/fit_20170409.jl

@@ -287,8 +287,10 @@ maybe_save("$(prefix)_r2_p1_ba")
 const τ_a1 = 60.1833e-6
 const p_a1 = [0.92, 0.08, 0.0]
 
-figure()
 ts_a1_0 = linspace(0, 300e-6, 201)
+ts_a1_p1 = linspace(0, 450e-6, 201)
+
+figure()
 plot_f1(f_a1, ts_a1_0, 2π / τ_a1 * (meles_a1_0[1:3] * meles_r3_0[1:3]'),
         p_a1 * p_r3', color="darkslateblue", label="Fit")
 plot_data(data_after_a1_0, 1 / 0.85, fmt="bo", label="With RSC")
@@ -303,7 +305,19 @@ grid()
 maybe_save("$(prefix)_a1_0_ba")
 
 figure()
-ts_a1_p1 = linspace(0, 450e-6, 201)
+plot_f1(f_a1, ts_a1_0, 2π / τ_a1 * (meles_a1_0[1:3] * meles_r3_0[1:3]'),
+        p_a1 * p_r3', color="darkslateblue", label="Fit")
+plot_data(data_after_a1_0, 1 / 0.85, fmt="bo", label="With RSC")
+plot_data(data_before_a1_0, 1 / 0.95, fmt="ro-", label="No RSC")
+ylim([0, 1])
+xlim([ts_a1_0[1] * 1e6, ts_a1_0[end] * 1e6])
+xlabel("Time (\$\\mu s\$)")
+ylabel("Normalized survival")
+title("Axis 1 (axial) carrier")
+grid()
+maybe_save("$(prefix)_a1_0_ba_nol")
+
+figure()
 plot_f1(f_a1, ts_a1_p1, 2π / τ_a1 * (meles_a1_p1[1:3] * meles_r3_0[1:3]'),
         p_a1 * p_r3', color="darkslateblue", label="Fit")
 plot_data(data_after_a1_p1, 1 / 0.85, fmt="bo", label="With RSC")
@@ -316,5 +330,18 @@ title("Axis 1 (axial) heating")
 legend(bbox_to_anchor=(1.05, 1), loc=2, borderaxespad=0.0)
 grid()
 maybe_save("$(prefix)_a1_p1_ba")
+
+figure()
+plot_f1(f_a1, ts_a1_p1, 2π / τ_a1 * (meles_a1_p1[1:3] * meles_r3_0[1:3]'),
[…]

### 2017-04-19 presentations/2017-04-19_itamp/present.tex
[presentations/2017-04-19_itamp] no before axial plot

@@
   \begin{center}
-    \includegraphics[height=4.8cm]{../../experiments/rabi_flop/imgs/fit_20170409_a1_0_ba_nol.png}
-    \includegraphics[height=4.8cm]{../../experiments/rabi_flop/imgs/fit_20170409_a1_p1_ba_nol.png}\\
+    \includegraphics[height=4.8cm]{../../experiments/rabi_flop/imgs/fit_20170409_a1_0_nol.png}
+    \includegraphics[height=4.8cm]{../../experiments/rabi_flop/imgs/fit_20170409_a1_p1_nol.png}\\
     Decoherence caused by magnetic field fluctuation.

### 2017-04-19 experiments/rabi_flop/fit_20170409.jl

@@ -308,14 +308,13 @@ figure()
 plot_f1(f_a1, ts_a1_0, 2π / τ_a1 * (meles_a1_0[1:3] * meles_r3_0[1:3]'),
         p_a1 * p_r3', color="darkslateblue", label="Fit")
 plot_data(data_after_a1_0, 1 / 0.85, fmt="bo", label="With RSC")
-plot_data(data_before_a1_0, 1 / 0.95, fmt="ro-", label="No RSC")
 ylim([0, 1])
 xlim([ts_a1_0[1] * 1e6, ts_a1_0[end] * 1e6])
 xlabel("Time (\$\\mu s\$)")
 ylabel("Normalized survival")
 title("Axis 1 (axial) carrier")
 grid()
-maybe_save("$(prefix)_a1_0_ba_nol")
+maybe_save("$(prefix)_a1_0_nol")
 
 figure()
 plot_f1(f_a1, ts_a1_p1, 2π / τ_a1 * (meles_a1_p1[1:3] * meles_r3_0[1:3]'),
@@ -335,13 +334,12 @@ figure()
 plot_f1(f_a1, ts_a1_p1, 2π / τ_a1 * (meles_a1_p1[1:3] * meles_r3_0[1:3]'),
         p_a1 * p_r3', color="darkslateblue", label="Fit")
 plot_data(data_after_a1_p1, 1 / 0.85, fmt="bo", label="With RSC")
-plot_data(data_before_a1_p1, 1 / 0.95, fmt="ro-", label="No RSC")
 ylim([0, 1])
 xlim([ts_a1_p1[1] * 1e6, ts_a1_p1[end] * 1e6])
 xlabel("Time (\$\\mu s\$)")
 ylabel("Normalized survival")
 title("Axis 1 (axial) heating")
 grid()
-maybe_save("$(prefix)_a1_p1_ba_nol")
+maybe_save("$(prefix)_a1_p1_nol")
 
 maybe_show()

### 2017-04-19 presentations/2017-04-19_itamp/present.tex
[presentations/2017-04-19_itamp] Tweaks after practice talk

@@
 
-\title[Na ground state cooling]{Raman sideband cooling of single sodium atom to 3D ground state}
+\title[Na ground state cooling]{Raman sideband cooling of a single sodium atom to 3D ground state}
 \date{April 19, 2017}
@@
         {\includegraphics[width=10cm]{../2015-05-05_cua/overall_trap_min.png}};
-      }
-      \visible<3-> {
         \path (3, -3) node
@@
 
-\begin{frame}{Wave function size}
+\begin{frame}{Wave function size mismatch}
   \begin{center}
@@
     \end{tikzpicture}
+    \vspace{1cm}
+    \begin{block}{Goal of cooling}
+      \begin{itemize}
+      \item Single initial state
+      \item Shrink wavefunction size
+      \end{itemize}
+    \end{block}
   \end{center}
@@
         \item High initial temperature ($40\mu K$)
-        \item<3-> High recoil heating
+        \item<3-> High recoil heating\\
+          {\footnotesize (High Lamb Dicke parameter)}
         \end{itemize}
@@
 
-\begin{frame}{Cooling sequence}
-  \tikzfading[name=fade img right,
-  left color=transparent!90, right color=transparent!0]
-  \begin{tikzpicture}[scale=0.75]
-    % 0.0 - 1.5 axial
-    % 1.5 - 2.0 OP
-    % 2.0 - 3.5 axial
-    % 3.5 - 4.0 OP
-    % 4.0 - 5.0 radial 2
-    % 5.0 - 5.5 OP
-    % 5.5 - 7.0 axial
-    % 7.0 - 7.5 OP
-    % 7.5 - 9.0 axial
-    % 9.0 - 9.5 OP
-    % 9.5 - 10.5 radial 3
-    % 10.5 - 11.0 OP
-
-    %% Pulse mark
-    \foreach \i in {2.0, 4.0, 5.5, 7.5, 9.5, 11.0, 13.0, 15.0, 16.5, 18.5, 20.5} {
-      \draw[gray!20, line width=1.5] (\i, 1.8) -- (\i, -6.0);
+\begin{frame}{Raman sidebands}
+  \begin{center}
+    \begin{tikzpicture}
+      \visible<1> {
+        \path (0, 0) node {
+          \includegraphics[width=10cm]{../../experiments/misc/imgs/data_spectrum_20170409_r2_before.png}
+        };
+        \draw[<-, line width=1.5] (-0.7, 0) -- (0, 1.6) node[right] {\Large Carrier};
       }
-
-    %% Axial
-    \foreach \i in {0, 5.5, 11.0, 16.5} {
-      \fill[blue!30]
-      plot[draw,samples=200,domain=\i:{\i+1.5},variable=\x] ({\x}, {sin((\x-\i) * 120)^4})
-      -- cycle;
-      \path (\i+1, 1) node[above,blue,align=center] {$n$-th\\order};
-      \fill[blue!30]
-      plot[draw,samples=200,domain={\i+2.0}:{\i+3.5},variable=\x] ({\x}, {sin((\x-\i-2.0) * 120)^4})
-      -- cycle;
-      \path (\i+3, 1) node[above,blue,align=center] {$(n-1)$-th\\order};
-      \draw[line width=1,blue] plot[domain=\i:{\i+1.5},variable=\x]
-      ({\x}, {sin((\x-\i) * 120)^4}) -- (\i+2.0, 0)
-      plot[domain={\i+2.0}:{\i+3.5},variable=\x]
-      ({\x}, {sin((\x-\i-2.0) * 120)^4})-- (\i+5.5, 0);
+      \visible<2> {
+        \path (0, 0) node {
+          \includegraphics[width=10cm]{../../experiments/misc/imgs/data_spectrum_20170409_r2.png}
+        };
       }
-    \path (0, 0.5) node[left,blue,align=center] {\textbf{Axis 1}\\\textit{Axial}};
-
-    %% Radial 2
-    \foreach \i in {0, 11.0} {
-      \fill[red!30]
-      plot[draw,samples=200,domain={\i+4.0}:{\i+5.0},variable=\x] ({\x}, {1.5*sin((\x-\i-4.0) * 180)^4 - 2})
-      -- cycle;
-      \draw[line width=1,red] (\i, -2) -- plot[domain={\i+4.0}:{\i+5.0},variable=\x]
-      ({\x}, {1.5*sin((\x-\i-4.0) * 180)^4 - 2}) -- (\i+11.0, -2);
+      \visible<3> {
+        \path (0, 0) node {
+          \includegraphics[width=10cm]{../../experiments/misc/imgs/data_spectrum_20170409_r3.png}
+        };
       }
-    \path (0, -1.5) node[left,red,align=center] {\textbf{Axis 2}\\\textit{Radial}};
-
-    %% Radial 3
-    \foreach \i in {0, 11.0} {
-      \fill[black!30]
-      plot[draw,samples=200,domain={\i+9.5}:{\i+10.5},variable=\x] ({\x}, {1.5*sin((\x-\i-9.5) * 180)^4 - 4})
-      -- cycle;
-      \draw[line width=1,black] (\i, -4) -- plot[domain={\i+9.5}:{\i+10.5},variable=\x]
-      ({\x}, {1.5*sin((\x-\i-9.5) * 180)^4 - 4}) -- (\i+11.0, -4);
-    }
-    \path (0, -3.5) node[left,black,align=center] {\textbf{Axis 3}\\\textit{Radial}};
-
-    %% OP
-    \foreach \i in {0, 5.5, 11.0, 16.5} {
-      \filldraw[fill=orange!30,draw=orange,line width=1.5]
-      (\i+1.5, -6) -- (\i+1.5, -4.5) -- (\i+2.0, -4.5) -- (\i+2.0, -6) -- cycle;
-      \filldraw[fill=orange!30,draw=orange,line width=1.5]
-      (\i+3.5, -6) -- (\i+3.5, -4.5) -- (\i+4.0, -4.5) -- (\i+4.0, -6) -- cycle;
-      \filldraw[fill=orange!30,draw=orange,line width=1.5]
-      (\i+5.0, -6) -- (\i+5.0, -4.5) -- (\i+5.5, -4.5) -- (\i+5.5, -6) -- cycle;
-    }
-    \path (0, -5.5) node[left,orange,align=center] {\textbf{Optical}\\\textbf{pumping}};
-    \draw[line width=2,orange] (0,-6) -- (23,-6);
-
-    %% Cycle mark
-    \draw[decoration={brace,mirror,raise=3pt, amplitude=10pt},decorate,line width=2]
-    (0,-6) -- node[below=15pt] {\scalebox{1.5}{One cooling cycle}} (11,-6);
-
-    \fill[white,path fading=fade img right] (11, -7) rectangle (14.5, 2.5);
-    \fill[white,path fading=fade img right] (11, -7) rectangle (14.5, 2.5);
-    \fill[white] (14.5, 2.5) rectangle (23, -7);
-
-    \draw[line width=2,orange,->] (0,-6) -- (12,-6) node[right, below] {\scalebox{2}{$t$}};
     \end{tikzpicture}
+  \end{center}
 \end{frame}
@@
 \begin{frame}{Raman sidebands}
-  \begin{tikzpicture}
-    \visible<1-2> {
-      \path (1.75, 4) node {
-        \includegraphics[width=8.5cm]{../../experiments/misc/imgs/data_spectrum_20170409_a1_before.png}
+  \begin{center}
+    \begin{tikzpicture}[scale=1.41176]
+      \visible<1> {
+        \path (0, 0) node {
+          \includegraphics[width=12cm]{../../experiments/misc/imgs/data_spectrum_20170409_a1_before.png}
         };
+        \draw[red, <-, line width=1.5] (-3.15, 0.5) -- (-2.95, 1.2)
+        node[above right] {\Large 1st order heating};
+        \draw[<-, line width=1.5] (-2.45, 0.2) -- (-2.25, 0.8) node[above right] {\Large Carrier};
+        \draw[black!40!green, <-, line width=1.5] (-1.7, 0.2) -- (-1.55, 0.6)
+        node[right] {\Large 1st order cooling};
+        \draw[blue, <-, line width=1.5] (-0.95, -0.1) -- (-0.55, 0.1)
+        node[right] {\Large 2nd order cooling};
+        \path[magenta] (0.25, -0.5) node[right] {\Large And higher orders{$\cdots$}};
+      }
+      \visible<2-> {
         \path (0, 0) node {
-        \includegraphics[width=5cm]{../../experiments/misc/imgs/data_spectrum_20170409_r2_before.png}
+          \includegraphics[width=12cm]{../../experiments/misc/imgs/data_spectrum_20170409_a1.png}
         };
-      \path (6, 0) node {
-        \includegraphics[width=5cm]{../../experiments/misc/imgs/data_spectrum_20170409_r3_before.png}
+      }
+      \visible<3-> {
+        \fill[white,opacity=0.95] (-4.2, -2.5) rectangle (5, 2.5);
+        \path (0, 1) node[align=center]
+        {
+          \begin{tabular}{|c|c|}
+            \hline
+            \textbf{Axis}&\textbf{Ground state probability}\\\hline
+            1 (Axial)&93.1(2.5)\%\\\hline
+            2 (Radial)&91.9(2.3)\%\\\hline
+            3 (Radial)&92.9(2.5)\%\\\hline
+          \end{tabular}
         };
-      \visible<2> {
-        \draw[red, <-, line width=1.5] (-1.4, 4.5) -- (-1.2, 5.2)
-        node[above right] {1st order heating};
-        \draw[<-, line width=1.5] (-0.7, 4.2) -- (-0.5, 4.8) node[above right] {Carrier};
-        \draw[black!40!green, <-, line width=1.5] (0.05, 4.2) -- (0.2, 4.6)
-        node[right] {1st order cooling};
-        \draw[blue, <-, line width=1.5] (0.8, 3.9) -- (1.2, 4.1)
-        node[right] {2nd order cooling};
-        \path[magenta] (2, 3.5) node[right] {And higher orders{$\cdots$}};
-
-        \draw[<-, line width=1.5] (-0.35, 0) -- (0, 0.8) node[right] {Carrier};
-
-        \draw[<-, line width=1.5] (5.67, 0.1) -- (6, 0.8) node[right] {Carrier};
+        \visible<4-> {
+          \path (0, -1) node[align=center]
+          {
+            \textbf{3D ground state:} $79.5(3.6)\%$\\
+            \textbf{Loss after cooling:} $15\%$\\\\
+            \textbf{Total 3D ground state preparation fidelity:} $67.6(3.1)\%$
+          };
         }
       }
-    \visible<3-> {
-      \path (1.75, 4) node {
-        \includegraphics[width=8.5cm]{../../experiments/misc/imgs/data_spectrum_20170409_a1.png}
-      };
-      \path (0, 0) node {
-        \includegraphics[width=5cm]{../../experiments/misc/imgs/data_spectrum_20170409_r2.png}
-      };
-      \path (6, 0) node {
-        \includegraphics[width=5cm]{../../experiments/misc/imgs/data_spectrum_20170409_r3.png}
-      };
-    }
-    \visible<4-> {
-      \path[blue] (2, 4.6) node[fill=white,opacity=0.6,text opacity=1,align=center]
-      {$\bm{P_{ground\ state}}$\\$\bm{93.1(2.5)\%}$};
-      \path[blue] (2, 0.1) node[fill=white,opacity=0.6,text opacity=1,align=center]
-      {$\bm{P_{ground\ state}}$\\$\bm{91.9(2.3)\%}$};
-      \path[blue] (8, 0.1) node[fill=white,opacity=0.6,text opacity=1,align=center]
-      {$\bm{P_{ground\ state}}$\\$\bm{92.9(2.5)\%}$};
-      \fill[white,path fading=fade img right] (4, 2.1) rectangle (7, 6);
-      \fill[white,path fading=fade img right] (4, 2.1) rectangle (7, 6);
-      \fill[white,path fading=fade img right] (4, 2.1) rectangle (7, 6);
-      \path (4, 4) node[fill=blue!80!white,opacity=0.8,text opacity=1,
-      text=white!90!yellow,right,align=center,
-      rounded corners=0.2cm,inner sep=0.2cm] {
-        \textbf{3D ground state:} $79.5(3.6)\%$\\
-        \textbf{Loss after cooling:} $15\%$\\\\
-        \textbf{Total 3D ground state}\\
-        \textbf{preparation fidelity}\\
-        $67.6(3.1)\%$
-      };
-    }
     \end{tikzpicture}
+  \end{center}
 \end{frame}
@@
     \visible<+->{
-      Good agreement between spectrum and Rabi flopping data.
+      Good agreement in ground state probability between spectrum and Rabi flopping data.
     }
@@
     \includegraphics[height=4.8cm]{../../experiments/rabi_flop/imgs/fit_20170409_a1_0_nol.png}
-    \includegraphics[height=4.8cm]{../../experiments/rabi_flop/imgs/fit_20170409_a1_p1_nol.png}\\
-    Decoherence caused by magnetic field fluctuation.
+    \includegraphics[height=4.8cm]{../../experiments/rabi_flop/imgs/fit_20170409_a1_p1_nol.png}
   \end{center}

### 2017-05-21 presentations/na_cool_paper/paper.tex
[presentations/na_cool_paperf pre-first draft]

\documentclass[aps,twocolumn,secnumarabic,balancelastpage,amsmath,amssymb,nofootinbib]{revtex4}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{chapterbib}
\usepackage{color}
\usepackage{graphics}
\usepackage[pdftex]{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{epsf}
\usepackage{bm}
\usepackage{tikz}
\usepackage{asymptote}
\usepackage{thumbpdf}
\usepackage{bbm}
\usepackage{amscd}
\usepackage{units}
\usepackage{textcomp}
\usepackage[utf8x]{inputenc}
\usepackage{feyn}
\usepackage{feynmp}
\usepackage[colorlinks=true]{hyperref}
\newcommand{\drelectron}[1]{\node at #1 [circle, draw, inner sep=0pt, minimum size=1pt] {\_}}

\newcommand{\ud}{\mathrm{d}}
\newcommand{\ue}{\mathrm{e}}
\newcommand{\ui}{\mathrm{i}}
\newcommand{\res}{\mathrm{Res}}
\newcommand{\Tr}{\mathrm{Tr}}
\newcommand{\dsum}{\displaystyle\sum}
\newcommand{\dprod}{\displaystyle\prod}
\newcommand{\dlim}{\displaystyle\lim}
\newcommand{\dint}{\displaystyle\int}
\newcommand{\fsno}[1]{{\!\not\!{#1}}}
\newcommand{\eqar}[1]
{
  \begin{align*}
    #1
  \end{align*}
}
\newcommand{\eqarn}[1]
{
  \begin{align}
    #1
  \end{align}
}
\newcommand{\texp}[2]{\ensuremath{{#1}\times10^{#2}}}
\newcommand{\dexp}[2]{\ensuremath{{#1}\cdot10^{#2}}}
\newcommand{\eval}[2]{{\left.{#1}\right|_{#2}}}
\newcommand{\paren}[1]{{\left({#1}\right)}}
\newcommand{\lparen}[1]{{\left({#1}\right.}}
\newcommand{\rparen}[1]{{\left.{#1}\right)}}
\newcommand{\abs}[1]{{\left|{#1}\right|}}
\newcommand{\sqr}[1]{{\left[{#1}\right]}}
\newcommand{\crly}[1]{{\left\{{#1}\right\}}}
\newcommand{\angl}[1]{{\left\langle{#1}\right\rangle}}
\newcommand{\tpdiff}[4][{}]{{\paren{\frac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}}_{#4}}}
\newcommand{\tpsdiff}[4][{}]{{\paren{\frac{\partial^{#1}}{\partial {#3}{}^{#1}}{#2}}_{#4}}}
\newcommand{\pdiff}[3][{}]{{\frac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}}}
\newcommand{\diff}[3][{}]{{\frac{\ud^{#1} {#2}}{\ud {#3}{}^{#1}}}}
\newcommand{\psdiff}[3][{}]{{\frac{\partial^{#1}}{\partial {#3}{}^{#1}} {#2}}}
\newcommand{\sdiff}[3][{}]{{\frac{\ud^{#1}}{\ud {#3}{}^{#1}} {#2}}}
\newcommand{\tpddiff}[4][{}]{{\left(\dfrac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}\right)_{#4}}}
\newcommand{\tpsddiff}[4][{}]{{\paren{\dfrac{\partial^{#1}}{\partial {#3}{}^{#1}}{#2}}_{#4}}}
\newcommand{\pddiff}[3][{}]{{\dfrac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}}}
\newcommand{\ddiff}[3][{}]{{\dfrac{\ud^{#1} {#2}}{\ud {#3}{}^{#1}}}}
\newcommand{\psddiff}[3][{}]{{\frac{\partial^{#1}}{\partial{}^{#1} {#3}} {#2}}}
\newcommand{\sddiff}[3][{}]{{\frac{\ud^{#1}}{\ud {#3}{}^{#1}} {#2}}}

\begin{document}
\tikzstyle{every picture}+=[remember picture]
\title{}
\author{}
\date{\today}
\affiliation{Harvard Department of Physics}

\begin{abstract}
\end{abstract}

\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section*{Introduction}

Why do we need to cool (for STIRAP/transfer to molecular state)\\

* Pure initial state\\
* Small wavefunction span\\

\begin{figure}
  \includegraphics[width=8cm]{imgs/Na_RSC_schematic.pdf}\\
  \includegraphics[width=8cm]{sequence.pdf}
  \caption{(A) Beam diretions and polarizations
    (B) Energy diagram. D1 OP
    (C) Sequence description}
  \label{f-setup}
\end{figure}

We achieve the high ground state preparation fidelity needed for molecule formation
using Raman sideband cooling. We use multiple pairs of beams to drive Raman transitions that
couples to different axis of the trap. The configuration of these beams and the relative position
to the tweezer trap and optical pumping beam is shown in figure \ref{f-setup}B.
The Raman sideband cooling consists of multiple cycles of laser pulses.
Each cycle starts with the Sodium atom in the $|F=2, m_F=-2\rangle$
ground electronic state and a certain vibration level $n$.
In the first step, a Raman pulse drives a transition on the motional sideband to lower
the vibrational state to $n-\Delta n$ while also changing the internal state
to $|F=1, m_F=-1\rangle$. In the second step, which finishes the cooling cycle,
an optical pumping pulse bring the atom back to the $|F=2, m_F=-2\rangle$ state to take away
the entropy. The optical pumping step may also change the vibrational level of the atom which
will cause heating. The possiblity for this to happen for an atom in the vibrational level $n$
is proportional to the effective Lamb-Dicke parameter $\eta^{eff}=\sqrt{n}\eta$ where $\eta=???$ is the Lamb-Dicke parameter.

Therefore, in order to perform Raman sideband cooling efficiently and minimize the heating during the optical pumping, we need to have a low initial temperature and a small Lamb-Dicke parameter. Comparing to previous realizations of Raman sideband cooling on heavier neutral alkali atoms like Rubidium[?] and Cesium[?], a few properties of Sodium makes this harder to achieve. Due to the unresolved(?) hyperfine structure in the $3^2P_{3/2}$ manifold, the sub-doppler cooling in Sodium is less efficient and we starts the Raman sideband cooling with a initial temperature of $40\mu K$, compare to $??\mu K$ for Cesium. Since the Lamb-Dicke parameter $\eta$ is inversely proportional to $\sqrt{m}$, it is also larger due for Sodium. With $45mW$ of power (??limited by trap switching??) at the focus of the trap, we measured a trapping frequency of $\{\omega_1,\omega_2,\omega_3\}/2\pi = \{67, 420, 580\} kHz$ which corresponds to an optical pumping Lamb-Dicke parameters of $\{\eta_{OP1},\eta_{OP2},\eta_{OP3}\} = \{???, ???, ???\}$. As a result, there is a very high probability of heating during the optical pumping step in the initial part of the cooling sequence.
This can be seen in figure [?], showing the probability distribution
of $n$ after optical pumping when the atom starts with different initial state. The probability
of staying in the same state drops very quickly as $n$ increases.

In additional to the high $\eta_{OP}$ for optical pumping, the Lamb-Dicke parameter for the Raman
transition $\eta_{Raman}$ is also very high on all three axis. For our geometry, we have $\{\eta_{Raman1},\eta_{Raman2},\eta_{Raman3}\} = \{???, ???, ???\}$.
The high $\eta_{Raman}$ means the sideband strength will not simple be proportional to $\sqrt{n}$ as it would be in the Lamb-Dicke regime. Instead, the sideband strength as a function of vibrational level $n$ in the axial direction is shown in figure [?].
Since the usual sideband thermometry, which measures $n/(n + 1)$ based on the ratio between heating and cooling sidebands, relies on the $\sqrt{n}$ scaling of the coupling strength, it breaks down
in our setup, making it harder to determing the temperature of the atom accurately. The strength
of the $-1$ order sideband also shows multiple points where the coupling strengh is very closed to
$0$, which means we cannot use this sideband to efficiently cool atom that is in those states.

Finally, the large number of populated vibrational level also means that the atom explores a larger percentage of the trap and is therefore more sensitive to trap anharmonicity.
This sets a lower limit on the minimum Raman Rabi frequency we can use in order to drive all
vibrational states efficiently.

% * Loose confinement
% ** More heating
% ** Complex sideband spectrum
% ** Matrix element minimum
% * Trap depth limit due to switching
% * High occupation
% ** Need more cooling
% ** Trap anharmonicity

\begin{figure*}
  \includegraphics[width=8cm]{../../calculations/sideband_strength/imgs/coupling_0.46_0-6.png}
  \includegraphics[width=8cm]{../../calculations/sideband_strength/imgs/coupling_0.61_op-pi.png}
  \caption{(A) Matrix elements as a function of $n$ and $\Delta n$ (showing complex dependency and zeros) (B) State changing probability. Large and increases as $n$ gets larger}
  \label{f-ld}
\end{figure*}

Fortunately, the features that make cooling Sodium challenging also provide us unique tools to
overcome these difficulties. As shown in figure [???], the high $\eta_{Raman}$ also causes the
coupling to higher order sideband during the Raman transition to be stronger,
especially for high vibrational states. This enables us to drive on high order Raman sidebands
to remove more vibrational energy in a single cooling pulse.
Since the heating from optical pumping is also worse for high vibrational states,
cooling on the high order sidebands can greately suppress the high heating during optical pumping.
The sideband strength for different orders are also oscillating out of phase, so we can generally
use a different sideband order to address vibrational states that cannot be efficiently addressed
by one sideband order.

% * Loose confinement
% ** Use higher orders to cool

Taking all the features of our system into account, we use a Monte-Carlo similation to verify
the validity of our method and explore the large parameter space for the cooling sequence.
In the simulation, we can observe the high heating rate due to the high Lamb-Dicke parameters
and confirm that high order of Raman sideband can be used to suppress this effect and reduces
the vibrational energy of the atom faster.
We also use the simulation to find a robust cooling strategy. As shown in figure (?),
we found that instead of cooling on only one sideband order at a time, it is generally more
efficient to alternate the cooling pulse between two neighboring orders. A cooling sequence
like this minimizes the accumulation of atom in a state not addressed by a particular sideband order.

For the more tightly confined radial directions, we starts the cooling with $\{\bar n_2, \bar n_3\}=????, ????$. The sideband spectra of the initial distribution is shown in figure (?) where we can clearly see the first order heating, first order cooling and second order cooling sidebands. After applying about 1000 cooling pulses cooling in all three dimentions starting with cooling on the radial second order, the Raman spectrum with the same parameter is shown in figure (?), where both cooling orders are suppressed. We can estimate the ground state probability in each direction based on the height of the first order cooling and heating sideband and the absence of the second order cooling sideband to be $......$. Due to the complexity of the sideband structure, we also use the Rabi flopping on the carrier and heating sideband as a independent measurement of the ground state population and gets $......$, showing good agreement between the two methods.

\begin{figure*}
  \includegraphics[width=8cm]{imgs/spectrum_r.png}
  \includegraphics[width=8cm]{../../experiments/rabi_flop/imgs/fit_20170409_r2_0_ba.png}
  \caption{(A) (B)}
  \label{f-radial}
\end{figure*}

As mentioned previously, the axial direction is much less confined and therefore has a much higher
effective Lamb-Dicke parameter of $\sqrt{n}\eta_{Raman1}\approx2.4$. The Raman spectrum before applying Raman sideban cooling is shown in figure (???) where we can see clearly resolved Raman cooling sidebands up to the 8th order suggesting that we have many vibrational states populated in this direction.

\begin{figure*}
  \includegraphics[width=8cm]{imgs/spectrum_a1.png}
  \includegraphics[width=8cm]{../../experiments/rabi_flop/imgs/fit_20170409_a1_0_ba.png}
  \caption{(A) (B)}
  \label{f-axial}
\end{figure*}
% Fig4 Axial

% \section{Conclusion}

% Missing:
% ?? Switching helps OP fidelity
% ?? off-resonant scattering
% ?? D1 OP
% ?? Switching improves

\bibliography{paper}
\end{document}

### 2017-05-21 presentations/na_cool_paper/sequence.tex
[presentations/na_cool_paper] add axial order label and tweezer switching (????)
[presentations/na_cool_paper] better sequence plot

@@
-\documentclass{standalone}
+\documentclass[border=0pt]{standalone}
 \usepackage{tikz}
-\usetikzlibrary{decorations.pathreplacing}
+\usetikzlibrary{decorations.pathreplacing,
+  fadings
+}
+\tikzfading[name=fade img right,left color=transparent!100, right color=transparent!0]
+\tikzfading[name=fade img left,right color=transparent!100, left color=transparent!0]
 \usepackage{graphicx}
@@
 \begin{tikzpicture}
-  % 0.0 - 1.5 axial
-  % 1.5 - 2.0 OP
-  % 2.0 - 3.5 axial
-  % 3.5 - 4.0 OP
-  % 4.0 - 5.0 radial 2
-  % 5.0 - 5.5 OP
-  % 5.5 - 7.0 axial
-  % 7.0 - 7.5 OP
-  % 7.5 - 9.0 axial
-  % 9.0 - 9.5 OP
-  % 9.5 - 10.5 radial 3
-  % 10.5 - 11.0 OP
+  % 0.0 - 1.6 axial (1.6)
+  % 1.6 - 1.9 OP (0.3)
+  % 1.9 - 2.5 radial 2 (0.6)
+  % 2.5 - 2.8 OP (0.3)
+  % 2.8 - 4.4 axial (1.6)
+  % 4.4 - 4.7 OP (0.3)
+  % 4.7 - 5.3 radial 3 (0.6)
+  % 5.3 - 5.6 OP (0.3)
+  % 5.6 - 7.2 axial (1.6)
+  % 7.2 - 7.5 OP (0.3)
+  % 7.5 - 8.1 radial 2 (0.6)
+  % 8.1 - 8.4 OP (0.3)
+  % 8.4 - 10.0 axial (1.6)
+  % 10.0 - 10.3 OP (0.3)
+  % 10.3 - 10.9 radial 3 (0.6)
+  % 10.9 - 11.2 OP (0.3)
 
-  \foreach \i in {2.0, 4.0, 5.5, 7.5, 9.5, 11.0, 13.0, 15.0, 16.5, 18.5, 20.5} {
-    \draw[gray!20, line width=1.5] (\i, 1.5) -- (\i, -6);
+  \begin{scope}
+    \clip (4.6, -6.5) rectangle (17.8, 3.5);
+    %% Pulse mark
+    \foreach \i in {0,...,7} {
+      \draw[gray!20, line width=2] (2.8*\i, 1.8) -- (2.8*\i, -6.0);
+      \draw[gray!20, line width=2] (2.8*\i+1.9, 1.8) -- (2.8*\i+1.9, -6.0);
+    }
+
+    %% Tweezer
+    \draw[line width=1.5,purple] (0, 2) -- (22.4, 2);
+    \foreach \i in {0,...,99} {
+      \filldraw[line width=1,purple] (\i*22.4/100, 2) rectangle (\i*22.4/100+0.06, 3.5);
     }
@@
     %% Axial
-  \foreach \i in {0, 5.5, 11.0, 16.5} {
+    \foreach \i in {0,...,7} {
       \fill[blue!30]
-    plot[draw,samples=200,domain=\i:{\i+1.5},variable=\x] ({\x}, {sin((\x-\i) * 120)^4})
+      plot[draw,samples=200,domain={2.8*\i}:{2.8*\i+1.6},variable=\x] ({\x}, {sin((\x-2.8*\i) * 112.5)^4})
       -- cycle;
-    \fill[blue!30]
-    plot[draw,samples=200,domain={\i+2.0}:{\i+3.5},variable=\x] ({\x}, {sin((\x-\i-2.0) * 120)^4})
-    -- cycle;
-    \draw[line width=1,blue] plot[domain=\i:{\i+1.5},variable=\x]
-    ({\x}, {sin((\x-\i) * 120)^4}) -- (\i+2.0, 0)
-    plot[domain={\i+2.0}:{\i+3.5},variable=\x]
-    ({\x}, {sin((\x-\i-2.0) * 120)^4})-- (\i+5.5, 0);
+      \draw[line width=1,blue] plot[domain={2.8*\i}:{2.8*\i+1.6},variable=\x]
+      ({\x}, {sin((\x-2.8*\i) * 112.5)^4}) -- (2.8*\i + 2.8, 0);
     }
-  \path (0, 0.5) node[left,blue,align=center] {\textbf{Axis 1}\\\textit{Axial}};
+    \foreach \i in {0,...,3} {
+      \path (5.6*\i + 0.8, 1) node[above,blue,align=center] {$n$-th\\order};
+      \path (5.6*\i + 3.6, 1) node[above,blue,align=center] {$(n-1)$-th\\order};
+    }
 
     %% Radial 2
-  \foreach \i in {0, 11.0} {
+    \foreach \i in {0,...,3} {
       \fill[red!30]
-    plot[draw,samples=200,domain={\i+4.0}:{\i+5.0},variable=\x] ({\x}, {1.5*sin((\x-\i-4.0) * 180)^4 - 2})
+      plot[draw,samples=200,domain={5.6*\i+1.9}:{5.6*\i+2.5},variable=\x] ({\x}, {1.5*sin((\x-5.6*\i-1.9) * 300)^4 - 2})
       -- cycle;
-    \draw[line width=1,red] (\i, -2) -- plot[domain={\i+4.0}:{\i+5.0},variable=\x]
-    ({\x}, {1.5*sin((\x-\i-4.0) * 180)^4 - 2}) -- (\i+11.0, -2);
+      \draw[line width=1,red] (5.6*\i, -2) -- plot[domain={5.6*\i+1.9}:{5.6*\i+2.5},variable=\x]
+      ({\x}, {1.5*sin((\x-5.6*\i-1.9) * 300)^4 - 2}) -- (5.6*\i+5.6, -2);
     }
-  \path (0, -1.5) node[left,red,align=center] {\textbf{Axis 2}\\\textit{Radial}};
 
     %% Radial 3
-  \foreach \i in {0, 11.0} {
+    \foreach \i in {0,...,3} {
       \fill[black!30]
-    plot[draw,samples=200,domain={\i+9.5}:{\i+10.5},variable=\x] ({\x}, {1.5*sin((\x-\i-9.5) * 180)^4 - 4})
+      plot[draw,samples=200,domain={5.6*\i+4.7}:{5.6*\i+5.3},variable=\x] ({\x}, {1.5*sin((\x-5.6*\i-4.7) * 300)^4 - 4})
       -- cycle;
-    \draw[line width=1,black] (\i, -4) -- plot[domain={\i+9.5}:{\i+10.5},variable=\x]
-    ({\x}, {1.5*sin((\x-\i-9.5) * 180)^4 - 4}) -- (\i+11.0, -4);
+      \draw[line width=1,black] (5.6*\i, -4) -- plot[domain={5.6*\i+4.7}:{5.6*\i+5.3},variable=\x]
+      ({\x}, {1.5*sin((\x-5.6*\i-4.7) * 300)^4 - 4}) -- (5.6*\i+5.6, -4);
     }
-  \path (0, -3.5) node[left,black,align=center] {\textbf{Axis 3}\\\textit{Radial}};
 
-  \foreach \i in {0, 5.5, 11.0, 16.5} {
-    \filldraw[fill=orange!30,draw=orange,line width=1.5]
-    (\i+1.5, -6) -- (\i+1.5, -4.5) -- (\i+2.0, -4.5) -- (\i+2.0, -6) -- cycle;
-    \filldraw[fill=orange!30,draw=orange,line width=1.5]
-    (\i+3.5, -6) -- (\i+3.5, -4.5) -- (\i+4.0, -4.5) -- (\i+4.0, -6) -- cycle;
-    \filldraw[fill=orange!30,draw=orange,line width=1.5]
-    (\i+5.0, -6) -- (\i+5.0, -4.5) -- (\i+5.5, -4.5) -- (\i+5.5, -6) -- cycle;
+    %% OP
+    \foreach \i in {0,...,7} {
+      \filldraw[fill=orange!30,draw=orange,line width=1.2]
+      (2.8*\i+1.58, -6) rectangle (2.8*\i+1.91, -4.5);
+      \filldraw[fill=orange!30,draw=orange,line width=1.2]
+      (2.8*\i+2.48, -6) rectangle (2.8*\i+2.81, -4.5);
     }
-  \path (0, -5.5) node[left,orange,align=center] {\textbf{Optical}\\\textbf{pumping}};
-  \draw[line width=2,orange,->] (0,-6) -- (23,-6) node[right, below] {\scalebox{2}{$t$}};
+    \draw[line width=2,orange] (0,-6) -- (22.4,-6);
+
+    \fill[white,path fading=fade img right] (16.8, -7) rectangle (17.81, 4);
+    \fill[white,path fading=fade img right] (16.8, -7) rectangle (17.81, 4);
+    \fill[white,path fading=fade img right] (16.8, -7) rectangle (17.81, 4);
+
+    \fill[white,path fading=fade img left] (5.6, -7) rectangle (4.59, 4);
+    \fill[white,path fading=fade img left] (5.6, -7) rectangle (4.59, 4);
+    \fill[white,path fading=fade img left] (5.6, -7) rectangle (4.59, 4);
+  \end{scope}
+
+  \path (4.95, 2.3) node[left,purple,align=center] {\textbf{Tweezer}};
+  \path (4.8, 0.5) node[left,blue,align=center] {\textbf{Axis 1}\\\textit{Axial}};
+  \path (4.8, -1.5) node[left,red,align=center] {\textbf{Axis 2}\\\textit{Radial}};
+  \path (4.8, -3.5) node[left,black,align=center] {\textbf{Axis 3}\\\textit{Radial}};
+  \path (5.1, -5.5) node[left,orange,align=center] {\textbf{Optical}\\\textbf{pumping}};
+  \draw[line width=2,orange,->] (5.6,-6) -- (17.8,-6) node[right, below] {\scalebox{2}{$t$}};
+
+  %% Cycle mark
   \draw[decoration={brace,mirror,raise=3pt, amplitude=10pt},decorate,line width=2]
-  (0,-6) -- node[below=15pt] {\scalebox{1.5}{One cooling cycle}} (11,-6);
+  (5.6,-6) -- node[below=15pt] {\scalebox{1.5}{One cooling cycle}} (16.8,-6);
+
+  %% Sub figure label
+  \path (3.8,2.5) node[above=8pt] {\scalebox{1.2}{(C)}};
 \end{tikzpicture}

### 2017-05-21 presentations/na_cool_paper/sequence.tex
[presentations/na_cool_paper] better sequence plot

@@
     \foreach \i in {0,...,3} {
-      \path (5.6*\i + 0.8, 1) node[above,blue,align=center] {$n$-th\\order};
-      \path (5.6*\i + 3.6, 1) node[above,blue,align=center] {$(n-1)$-th\\order};
+      \path (5.6*\i + 0.8, 1) node[above,blue,align=center] {\textbf{$n$-th}\\\textbf{order}};
+      \path (5.6*\i + 3.6, 1) node[above,blue,align=center] {\textbf{$(n-1)$-th}\\\textbf{order}};
     }
@@
     \draw[line width=2,orange] (0,-6) -- (22.4,-6);
-
-    \fill[white,path fading=fade img right] (16.8, -7) rectangle (17.81, 4);
-    \fill[white,path fading=fade img right] (16.8, -7) rectangle (17.81, 4);
-    \fill[white,path fading=fade img right] (16.8, -7) rectangle (17.81, 4);
-
-    \fill[white,path fading=fade img left] (5.6, -7) rectangle (4.59, 4);
-    \fill[white,path fading=fade img left] (5.6, -7) rectangle (4.59, 4);
-    \fill[white,path fading=fade img left] (5.6, -7) rectangle (4.59, 4);
   \end{scope}
 
-  \path (4.95, 2.3) node[left,purple,align=center] {\textbf{Tweezer}};
+  \fill[white,path fading=fade img right] (16.8, -6.6) rectangle (17.81, 3.51);
+  \fill[white,path fading=fade img right] (16.8, -6.6) rectangle (17.81, 3.51);
+  \fill[white,path fading=fade img right] (16.8, -6.6) rectangle (17.81, 3.51);
+
+  \fill[white,path fading=fade img left] (5.6, -6.6) rectangle (4.59, 3.51);
+  \fill[white,path fading=fade img left] (5.6, -6.6) rectangle (4.59, 3.51);
+  \fill[white,path fading=fade img left] (5.6, -6.6) rectangle (4.59, 3.51);
+
+  \path (5.0, 2.3) node[left,purple,align=center] {\textbf{Tweezer}};
   \path (4.8, 0.5) node[left,blue,align=center] {\textbf{Axis 1}\\\textit{Axial}};
@@
   \path (4.8, -3.5) node[left,black,align=center] {\textbf{Axis 3}\\\textit{Radial}};
-  \path (5.1, -5.5) node[left,orange,align=center] {\textbf{Optical}\\\textbf{pumping}};
+  \path (5.15, -5.5) node[left,orange,align=center] {\textbf{Optical}\\\textbf{pumping}};
   \draw[line width=2,orange,->] (5.6,-6) -- (17.8,-6) node[right, below] {\scalebox{2}{$t$}};

### 2017-05-21 presentations/na_cool_paper/paper.tex
[presentations/na_cool_paper] WIP text

@@
-\documentclass[aps,twocolumn,secnumarabic,balancelastpage,amsmath,amssymb,nofootinbib]{revtex4}
+\documentclass[aps,prl,twocolumn,groupedaddress]{revtex4-1}
+% \documentclass[aps,twocolumn,secnumarabic,balancelastpage,amsmath,amssymb,nofootinbib]{revtex4-1}
 \usepackage{amsmath}
@@
 \tikzstyle{every picture}+=[remember picture]
-\title{}
-\author{}
+\title{Raman sideband cooling of single Na atoms to 3D motional ground state}
+\author{....}
 \date{\today}
@@
 \begin{abstract}
+  We report Raman sideband cooling of a single neutral Sodium atom to its three-dimensional
+  vibrational ground state in an optical tweezer.
+  Despite having a very large Lamb-Dicke parameter, high initial temperature and
+  large differential AC Stark shift in the excited state,
+  after applying a cooling sequence for a hundred milliseconds,
+  we observed a ground state preparation fidelity of $70\%$ using sideband thermometry.
+  We demonstrated that Raman sideband cooling to vibrational ground state is applicable to
+  systems where tight confinement or low initial cooling is hard to achieve.
+  For example, the result provides new opportunities to achieve much lower temperatures
+  in cold molecules with direct laser cooling.
 \end{abstract}
@@
 \maketitle
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \section*{Introduction}
 
@@
 
-\begin{figure}
-  \includegraphics[width=8cm]{imgs/Na_RSC_schematic.pdf}\\
-  \includegraphics[width=8cm]{sequence.pdf}
-  \caption{(A) Beam diretions and polarizations
-    (B) Energy diagram. D1 OP
-    (C) Sequence description}
-  \label{f-setup}
-\end{figure}
+\begin{figure*}
+  \includegraphics[height=7cm]{imgs/Na_RSC_schematic.pdf}
+  \includegraphics[height=7cm]{sequence.pdf}
+  \caption{(A) Energy diagram. D1 OP
+    (B) Beam diretions and polarizations
+    (C) Sequence description
+    \label{f-setup}}
+\end{figure*}
 
 We achieve the high ground state preparation fidelity needed for molecule formation
-using Raman sideband cooling. We use multiple pairs of beams to drive Raman transitions that
-couples to different axis of the trap. The configuration of these beams and the relative position
-to the tweezer trap and optical pumping beam is shown in figure \ref{f-setup}B.
-The Raman sideband cooling consists of multiple cycles of laser pulses.
-Each cycle starts with the Sodium atom in the $|F=2, m_F=-2\rangle$
+using Raman sideband cooling. The process consists of multiple cycles of laser pulses
+to manipulate the internal and vibrational state of the atom.
+Figure \ref{f-setup}A shows the schematic of the energy levels and the cooling sequence
+in our setup.
+Each cooling cycle starts with the Sodium atom in the $|F=2, m_F=-2\rangle$
 ground electronic state and a certain vibration level $n$.
@@
 the vibrational state to $n-\Delta n$ while also changing the internal state
-to $|F=1, m_F=-1\rangle$. In the second step, which finishes the cooling cycle,
+to $|F=1, m_F=-1\rangle$.
+In the second step, which finishes the cooling cycle,
 an optical pumping pulse bring the atom back to the $|F=2, m_F=-2\rangle$ state to take away
-the entropy. The optical pumping step may also change the vibrational level of the atom which
+the entropy.
+The geometry of the relavant beams and their polarizations is showed in figure \ref{f-setup}B.
+The optical tweezer has one weakly confined axial direction (axis $1$) and
+two more strongly confined radial directions (axis $2$ and $3$).
+Multiple pairs of beams are used to drive the Raman transition during cooling in order to
+isolate and maximize the coupling to different trap axis.
+
+The optical pumping step may also change the vibrational level of the atom which
 will cause heating. The possiblity for this to happen for an atom in the vibrational level $n$
-is proportional to the effective Lamb-Dicke parameter $\eta^{eff}=\sqrt{n}\eta$ where $\eta=???$ is the Lamb-Dicke parameter.
+is proportional to the effective Lamb-Dicke parameter $\eta^{eff}=\sqrt{n}\eta$ where $\eta=???$ is the Lamb-Dicke parameter.\\
 
@@
 of $n$ after optical pumping when the atom starts with different initial state. The probability
-of staying in the same state drops very quickly as $n$ increases.
+of staying in the same state drops very quickly as $n$ increases.\\
 
@@
 of the $-1$ order sideband also shows multiple points where the coupling strengh is very closed to
-$0$, which means we cannot use this sideband to efficiently cool atom that is in those states.
+$0$, which means we cannot use this sideband to efficiently cool atom that is in those states.\\
 
@@
 This sets a lower limit on the minimum Raman Rabi frequency we can use in order to drive all
-vibrational states efficiently.
+vibrational states efficiently.\\
 
@@
 
-\begin{figure*}
-  \includegraphics[width=8cm]{../../calculations/sideband_strength/imgs/coupling_0.46_0-6.png}
-  \includegraphics[width=8cm]{../../calculations/sideband_strength/imgs/coupling_0.61_op-pi.png}
-  \caption{(A) Matrix elements as a function of $n$ and $\Delta n$ (showing complex dependency and zeros) (B) State changing probability. Large and increases as $n$ gets larger}
-  \label{f-ld}
-\end{figure*}
+\begin{figure}
+  \includegraphics[width=9cm]{../../calculations/sideband_strength/imgs/coupling_0.46_0-6.png}
+  \includegraphics[width=9cm]{../../calculations/sideband_strength/imgs/coupling_0.61_op-pi.png}
+  \caption{(A) Matrix elements as a function of $n$ and $\Delta n$ (showing complex dependency and zeros) (B) State changing probability. Large and increases as $n$ gets larger
+    \label{f-ld}}
+\end{figure}
 
@@
 use a different sideband order to address vibrational states that cannot be efficiently addressed
-by one sideband order.
+by one sideband order.\\
 
@@
 efficient to alternate the cooling pulse between two neighboring orders. A cooling sequence
-like this minimizes the accumulation of atom in a state not addressed by a particular sideband order.
-
-For the more tightly confined radial directions, we starts the cooling with $\{\bar n_2, \bar n_3\}=????, ????$.
-The sideband spectra of the initial distribution is shown in figure (?) where we can clearly see the first order heating, first order cooling and second order cooling sidebands.
-After applying about 1000 cooling pulses cooling in all three dimentions starting with cooling on the radial second order, the Raman spectrum with the same parameter is shown in figure (?), where both cooling orders are suppressed.
-We can estimate the ground state probability in each direction based on the height of the first order cooling and heating sideband and the absence of the second order cooling sideband to be $......$.
-Due to the complexity of the sideband structure, we also use the Rabi flopping on the carrier and heating sideband as a independent measurement of the ground state population and gets $......$, showing good agreement between the two methods.
+like this minimizes the accumulation of atom in a state not addressed by a particular sideband order.\\
 
@@
   \includegraphics[width=8cm]{../../experiments/rabi_flop/imgs/fit_20170409_r2_0_ba.png}
-  \caption{(A) (B)}
-  \label{f-radial}
+  \caption{(A) (B) \label{f-radial}}
+\end{figure*}
+
+For the more tightly confined radial directions, we starts the cooling with $\{\bar n_2, \bar n_3\}=????, ????$.
+The sideband spectra of the initial distribution is shown in figure \ref{f-radial}A where we can clearly see the first order heating, first order cooling and second order cooling sidebands.
+After applying about 1000 cooling pulses cooling in all three dimentions starting with cooling on the radial second order, the Raman spectrum with the same parameter is shown in figure \ref{f-radial}B, where both cooling orders are suppressed.
+We can estimate the ground state probability in each direction based on the height of the first order cooling and heating sideband and the absence of the second order cooling sideband to be $......$.
+Due to the complexity of the sideband structure, we also use the Rabi flopping on the carrier and heating sideband as a independent measurement of the ground state population and gets $......$, showing good agreement between the two methods.
+(?????
+figure \ref{f-radial}C and \ref{f-radial}D)\\
+
+\begin{figure*}
+  \includegraphics[width=8cm]{imgs/spectrum_a1.png}
+  \includegraphics[width=8cm]{../../experiments/rabi_flop/imgs/fit_20170409_a1_0_ba.png}
+  \caption{(A) (B) \label{f-axial}}
 \end{figure*}
@@
 effective Lamb-Dicke parameter of $\sqrt{n}\eta_{Raman1}\approx2.4$.
-The Raman spectrum before applying Raman sideban cooling is shown in figure (???) where we can see clearly resolved Raman cooling sidebands up to the 8th order suggesting that we have many vibrational states populated in this direction.
+The Raman spectrum before applying Raman sideban cooling is shown in figure \ref{f-axial}A where we can see clearly resolved Raman cooling sidebands up to the 8th order suggesting that we have many vibrational states populated in this direction.\\
 
-\begin{figure*}
-  \includegraphics[width=8cm]{imgs/spectrum_a1.png}
-  \includegraphics[width=8cm]{../../experiments/rabi_flop/imgs/fit_20170409_a1_0_ba.png}
-  \caption{(A) (B)}
-  \label{f-axial}
-\end{figure*}
-% Fig4 Axial
-
-% \section{Conclusion}
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
+\ \\
 
@@
 \end{document}
+
+% Generalization to other systems (properties that are shared with "more real" systems)
+% Inharmonicity -> gaussian beam. -> importance to use short/strong pulses.

### 2017-05-22 presentations/na_cool_paper/paper.tex
[presentations/na_cool_paper] WIP

@@
 \tikzstyle{every picture}+=[remember picture]
-\title{Raman sideband cooling of single Na atoms to 3D motional ground state}
+\title{Raman sideband cooling of single Na atoms to 3D vibrational ground state}
 \author{....}
@@
 \begin{figure*}
-  \includegraphics[height=7cm]{imgs/Na_RSC_schematic.pdf}
-  \includegraphics[height=7cm]{sequence.pdf}
+  \includegraphics[height=6.5cm]{imgs/Na_RSC_schematic.pdf}
+  \includegraphics[height=6.5cm]{sequence.pdf}
   \caption{(A) Energy diagram. D1 OP
@@
 using Raman sideband cooling. The process consists of multiple cycles of laser pulses
-to manipulate the internal and vibrational state of the atom.
+to manipulate the internal and vibrational states of the atoms.
 Figure \ref{f-setup}A shows the schematic of the energy levels and the cooling sequence
@@
 Each cooling cycle starts with the Sodium atom in the $|F=2, m_F=-2\rangle$
-ground electronic state and a certain vibration level $n$.
-In the first step, a Raman pulse drives a transition on the motional sideband to lower
-the vibrational state to $n-\Delta n$ while also changing the internal state
-to $|F=1, m_F=-1\rangle$.
+ground electronic state and a certain vibration state $n$.
+In the first step, a Raman pulse drives a transition to the vibrational state $n-\Delta n$
+to reduce the vibrational energy while also changing the internal state to $|F=1, m_F=-1\rangle$.
 In the second step, which finishes the cooling cycle,
 an optical pumping pulse bring the atom back to the $|F=2, m_F=-2\rangle$ state to take away
-the entropy.
-The geometry of the relavant beams and their polarizations is showed in figure \ref{f-setup}B.
+the entropy. The second step could also change the vibrational state of the atoms which
+could cause heating. The possiblity for this to happen for an atom in the vibrational level $n$
+is approximately proportional to the effective Lamb-Dicke parameter
+$\eta^{OP}_{eff}=\sqrt{2n+1}\eta^{OP}$ where $\eta^{OP}=???$ is the Lamb-Dicke parameter for
+optical pumping.
+The geometry of the relavant beams (???and their polarizations) is showed in figure \ref{f-setup}B.
 The optical tweezer has one weakly confined axial direction (axis $1$) and
@@
 
-The optical pumping step may also change the vibrational level of the atom which
-will cause heating. The possiblity for this to happen for an atom in the vibrational level $n$
-is proportional to the effective Lamb-Dicke parameter $\eta^{eff}=\sqrt{n}\eta$ where $\eta=???$ is the Lamb-Dicke parameter.\\
+Although Raman sideband cooling to vibrational ground state has already been successfully
+implemented on neutral atoms in other experiments using heavier species like Rubidium [????]
+and Cesium [????], such experiments generally use good polarization gradient cooling
+and a tight confinement to achieve a small Lamb-Dicke parameter and effective Lamb-Dicke parameter.
+However, this regime is harder to achieve with Sodium atoms, creating additional challenges for
+us to realize ground state cooling. On the other hand, since these conditions can also be difficult
+to meet for other interesting systemd like directly laser cooled molecules, the techniques we
+use to overcome these challenges could be useful for a wider variety of systems.
 
-Therefore, in order to perform Raman sideband cooling efficiently and minimize the heating during the optical pumping, we need to have a low initial temperature and a small Lamb-Dicke parameter.
-Comparing to previous realizations of Raman sideband cooling on heavier neutral alkali atoms like Rubidium[?] and Cesium[?], a few properties of Sodium makes this harder to achieve.
-Due to the unresolved(?) hyperfine structure in the $3^2P_{3/2}$ manifold, the sub-doppler cooling in Sodium is less efficient and we starts the Raman sideband cooling with a initial temperature of $40\mu K$, compare to $??\mu K$ for Cesium.
-Since the Lamb-Dicke parameter $\eta$ is inversely proportional to $\sqrt{m}$, it is also larger due for Sodium.
-With $45mW$ of power (??limited by trap switching??) at the focus of the trap, we measured a trapping frequency of $\{\omega_1,\omega_2,\omega_3\}/2\pi = \{67, 420, 580\} kHz$ which corresponds to an optical pumping Lamb-Dicke parameters of $\{\eta_{OP1},\eta_{OP2},\eta_{OP3}\} = \{???, ???, ???\}$.
-As a result, there is a very high probability of heating during the optical pumping step in the initial part of the cooling sequence.
-This can be seen in figure [?], showing the probability distribution
-of $n$ after optical pumping when the atom starts with different initial state. The probability
-of staying in the same state drops very quickly as $n$ increases.\\
+\begin{figure}
+  \includegraphics[width=9cm]{../../calculations/sideband_strength/imgs/coupling_0.46_0-6.png}
+  \includegraphics[width=7cm]{imgs/heating_op.png}
+  \caption{(A) Matrix elements as a function of $n$ and $\Delta n$ (showing complex dependency and zeros) (B) State changing probability. Large and increases as $n$ gets larger
+    \label{f-ld}}
+\end{figure}
 
-In additional to the high $\eta_{OP}$ for optical pumping, the Lamb-Dicke parameter for the Raman
-transition $\eta_{Raman}$ is also very high on all three axis. For our geometry, we have $\{\eta_{Raman1},\eta_{Raman2},\eta_{Raman3}\} = \{???, ???, ???\}$.
-The high $\eta_{Raman}$ means the sideband strength will not simple be proportional to $\sqrt{n}$ as it would be in the Lamb-Dicke regime.
-Instead, the sideband strength as a function of vibrational level $n$ in the axial direction is shown in figure [?].
-Since the usual sideband thermometry, which measures $n/(n + 1)$ based on the ratio between heating and cooling sidebands, relies on the $\sqrt{n}$ scaling of the coupling strength, it breaks down
-in our setup, making it harder to determing the temperature of the atom accurately. The strength
-of the $-1$ order sideband also shows multiple points where the coupling strengh is very closed to
-$0$, which means we cannot use this sideband to efficiently cool atom that is in those states.\\
+As mentioned previously, in order to perform Raman sideband cooling efficiently and
+minimize the heating during the optical pumping, we need to have a low initial temperature and
+a small Lamb-Dicke parameter. However, since the Lamb-Dicke parameter $\eta$ is inversely
+proportional to $\sqrt{m}$ (???) where $m$ is the mass of the atom, it is larger for Sodium
+given the same trap depth (???). With $45mW$ of power at the focus of the trap,
+we measured a trapping frequency of $\{\omega_1,\omega_2,\omega_3\}/2\pi = \{67, 420, 580\}\ \text{kHz}$
+which corresponds to optical pumping Lamb-Dicke parameters of
+$\{\eta^{OP}_1,\eta^{OP}_2,\eta^{OP}_3\} = \{???, ???, ???\}$.
+Moreover, due to the unresolved(?) hyperfine structure in the $3^2P_{3/2}$ manifold,
+the sub-doppler cooling in Sodium is also less efficient and we start the
+Raman sideband cooling with a initial temperature of $40\mu K$. Combined with the high Lamb-Dicke
+parameters, this gives us a initial effective optical pumping Lamb-Dicke parameters of
+$\{\eta^{OP}_{1eff},\eta^{OP}_{2eff},\eta^{OP}_{3eff}\} = \{???, ???, ???\}$
+As a result, there is a very high probability of heating during the optical pumping step
+(figure \ref{f-ld}B) causing a $30\%$ average heating probability during optical pumping
+in the weakly confined axial direction. Fortunately, the high Lamb-Dicke parameters also
+provide us tools to overcome this issue. From our geometry, the Lamb-Dicke parameters for
+Raman transitions are $\{\eta^R_{1},\eta^R_{2},\eta^R_{3}\} = \{???, ???, ???\}$. As shown in
+figure \ref{f-ld}A, the high Raman Lamb-Dicke parameters causes a strong coupling to higher orders
+of cooling sidebands, especially for high vibrational states.
+This enables us to cool atoms in high vibrational states by driving on high order Raman sidebands,
+removing more vibrational energy in a single cooling pulse and offsetting the effect of
+strong heating. Since the heating probability is higher for high vibrational states,
+cooling on these high order sidebands can greately suppress the high heating during
+optical pumping during the initial cooling. Since the coupling strength of different orders
+do not reach their minimums at the same time, using multiple orders of vibrational sidebands
+for cooling also avoids accumulation of population near the coupling minimum of a particular
+order, which improves the overall efficiency of the cooling process.
 
-Finally, the large number of populated vibrational level also means that the atom explores a larger percentage of the trap and is therefore more sensitive to trap anharmonicity.
-This sets a lower limit on the minimum Raman Rabi frequency we can use in order to drive all
-vibrational states efficiently.\\
+In additional to improving the cooling efficiency, the large Raman Lamb-Dicke parameters $\eta^R$
+also creates difficulties for measuring the temperature. Traditional sideband thermometry uses
+the ratio of the cooling and heating sidebands to measure $\bar n / (\bar n + 1)$, which relies
+on the coupling strength to be proportional to $\sqrt{n}$. However, since we are not in the
+Lamb-Dicke regime, the coupling strength diviates from this simple scaling rule quickly as already
+shown in figure \ref{f-ld}A, causing the normal sideband thermometry to break down.
+In order to solve this problem, when the atom temperature is still high,
+we measure the heights of multiple sidebands to make sure no population is hidden at the
+minimum of one sideband order. And when the atom is cooled down, we estimate the temperature
+and ground state population under the assumption that only a few states are populated.
+This result is then varified using independent measure of Rabi flopping on the carrier and heating
+sidebands since they provide more information about the distribution of coupling strength.
+
+Another issue caused by the high initial temperature is trap anharmonicity.
+Although the potential near the center of a focused Gaussian beam can be approximated
+by a harmonic trap, when a large number of levels are populated due to high initial temperature
+the anharmonicity of the trap can lead to broadening of the sideband and the decrease of
+the sideband signal. In our setup, this effect limits the Rabi frequency of the Raman pulse
+on the radial sidebands to be no lower than tens of kilo-Hertz in order to drive atoms in
+different vibrational states equally.
+
+Finally, another important feature of our setup is the strong AC starck shift in the excited state.
+The deep trap that is needed to trap and image single Sodium atom creates a light shift on the
+
+the deep trap needed to ...
+also creates a large differential ..., which makes it impossible to load ....
+The same effect also happens on OP causing not only ...
+but also ....
+due to the breakdown of excited state HF structure....
+We use switching....
 
@@
 % ** Trap anharmonicity
-
-\begin{figure}
-  \includegraphics[width=9cm]{../../calculations/sideband_strength/imgs/coupling_0.46_0-6.png}
-  \includegraphics[width=9cm]{../../calculations/sideband_strength/imgs/coupling_0.61_op-pi.png}
-  \caption{(A) Matrix elements as a function of $n$ and $\Delta n$ (showing complex dependency and zeros) (B) State changing probability. Large and increases as $n$ gets larger
-    \label{f-ld}}
-\end{figure}
-
-Fortunately, the features that make cooling Sodium challenging also provide us unique tools to
-overcome these difficulties. As shown in figure [???], the high $\eta_{Raman}$ also causes the
-coupling to higher order sideband during the Raman transition to be stronger,
-especially for high vibrational states. This enables us to drive on high order Raman sidebands
-to remove more vibrational energy in a single cooling pulse.
-Since the heating from optical pumping is also worse for high vibrational states,
-cooling on the high order sidebands can greately suppress the high heating during optical pumping.
-The sideband strength for different orders are also oscillating out of phase, so we can generally
-use a different sideband order to address vibrational states that cannot be efficiently addressed
-by one sideband order.\\
 

### 2017-05-23 presentations/na_cool_paper/paper.tex
[presentations/na_cool_paper] minor update

@@
 
-Finally, another important feature of our setup is the strong AC starck shift in the excited state.
-The deep trap that is needed to trap and image single Sodium atom creates a light shift on the
+<WIP>
 
-the deep trap needed to ...
-also creates a large differential ..., which makes it impossible to load ....
-The same effect also happens on OP causing not only ...
-but also ....
-due to the breakdown of excited state HF structure....
-We use switching....
+Finally, the deep trap that is needed to trap and image single Sodium atom also creates
+a very large AC Stark shift in the excited state.
 
-% * Loose confinement
-% ** More heating
-% ** Complex sideband spectrum
-% ** Matrix element minimum
-% * Trap depth limit due to switching
-% * High occupation
-% ** Need more cooling
-% ** Trap anharmonicity
-
-% * Loose confinement
-% ** Use higher orders to cool
+% impossible to load without switching
+% The same effect also happens on OP causing
+% *   cannot address atom in different position at the same time
+% *   breakdown of excited state HF structure
+% use switching
 

### 2017-05-25 presentations/na_cool_paper/paper.tex
[presentations/na_cool_paper] spell check

@@
   \caption{(A) Energy diagram. D1 OP
-    (B) Beam diretions and polarizations
+    (B) Beam directions and polarizations
     (C) Sequence description
@@
 the entropy. The second step could also change the vibrational state of the atoms which
-could cause heating. The possiblity for this to happen for an atom in the vibrational level $n$
+could cause heating. The possibility for this to happen for an atom in the vibrational level $n$
 is approximately proportional to the effective Lamb-Dicke parameter
@@
 optical pumping.
-The geometry of the relavant beams (???and their polarizations) is showed in figure \ref{f-setup}B.
+The geometry of the relevant beams (???and their polarizations) is showed in figure \ref{f-setup}B.
 The optical tweezer has one weakly confined axial direction (axis $1$) and
@@
 us to realize ground state cooling. On the other hand, since these conditions can also be difficult
-to meet for other interesting systemd like directly laser cooled molecules, the techniques we
+to meet for other interesting systems like directly laser cooled molecules, the techniques we
 use to overcome these challenges could be useful for a wider variety of systems.
@@
 Moreover, due to the unresolved(?) hyperfine structure in the $3^2P_{3/2}$ manifold,
-the sub-doppler cooling in Sodium is also less efficient and we start the
+the sub-Doppler cooling in Sodium is also less efficient and we start the
 Raman sideband cooling with a initial temperature of $40\mu K$. Combined with the high Lamb-Dicke
@@
 strong heating. Since the heating probability is higher for high vibrational states,
-cooling on these high order sidebands can greately suppress the high heating during
+cooling on these high order sidebands can greatly suppress the high heating during
 optical pumping during the initial cooling. Since the coupling strength of different orders
@@
 on the coupling strength to be proportional to $\sqrt{n}$. However, since we are not in the
-Lamb-Dicke regime, the coupling strength diviates from this simple scaling rule quickly as already
+Lamb-Dicke regime, the coupling strength deviates from this simple scaling rule quickly as already
 shown in figure \ref{f-ld}A, causing the normal sideband thermometry to break down.
@@
 and ground state population under the assumption that only a few states are populated.
-This result is then varified using independent measure of Rabi flopping on the carrier and heating
+This result is then verified using independent measure of Rabi flopping on the carrier and heating
 sidebands since they provide more information about the distribution of coupling strength.
@@
 
-Taking all the features of our system into account, we use a Monte-Carlo similation to verify
+Taking all the features of our system into account, we use a Monte-Carlo simulation to verify
 the validity of our method and explore the large parameter space for the cooling sequence.
@@
 The sideband spectra of the initial distribution is shown in figure \ref{f-radial}A where we can clearly see the first order heating, first order cooling and second order cooling sidebands.
-After applying about 1000 cooling pulses cooling in all three dimentions starting with cooling on the radial second order, the Raman spectrum with the same parameter is shown in figure \ref{f-radial}B, where both cooling orders are suppressed.
+After applying about 1000 cooling pulses cooling in all three dimensions starting with cooling on the radial second order, the Raman spectrum with the same parameter is shown in figure \ref{f-radial}B, where both cooling orders are suppressed.
 We can estimate the ground state probability in each direction based on the height of the first order cooling and heating sideband and the absence of the second order cooling sideband to be $......$.
@@
 effective Lamb-Dicke parameter of $\sqrt{n}\eta_{Raman1}\approx2.4$.
-The Raman spectrum before applying Raman sideban cooling is shown in figure \ref{f-axial}A where we can see clearly resolved Raman cooling sidebands up to the 8th order suggesting that we have many vibrational states populated in this direction.\\
+The Raman spectrum before applying Raman sideband cooling is shown in figure \ref{f-axial}A where we can see clearly resolved Raman cooling sidebands up to the 8th order suggesting that we have many vibrational states populated in this direction.\\
 

### 2017-05-25 presentations/na_cool_paper/paper.tex
[presentations/na_cool_paper] Remove some unused packages

@@
 \usepackage[pdftex]{graphicx}
-\usepackage{grffile}
-\usepackage{longtable}
-\usepackage{epsf}
-\usepackage{bm}
-\usepackage{tikz}
-\usepackage{asymptote}
-\usepackage{thumbpdf}
-\usepackage{bbm}
-\usepackage{amscd}
-\usepackage{units}
-\usepackage{textcomp}
 \usepackage[utf8x]{inputenc}
-\usepackage{feyn}
-\usepackage{feynmp}
 \usepackage[colorlinks=true]{hyperref}
-\newcommand{\drelectron}[1]{\node at #1 [circle, draw, inner sep=0pt, minimum size=1pt] {\_}}
 
@@
 \newcommand{\fsno}[1]{{\!\not\!{#1}}}
-\newcommand{\eqar}[1]
-{
-  \begin{align*}
-    #1
-  \end{align*}
-}
-\newcommand{\eqarn}[1]
-{
-  \begin{align}
-    #1
-  \end{align}
-}
 \newcommand{\texp}[2]{\ensuremath{{#1}\times10^{#2}}}
@@
 \begin{document}
-\tikzstyle{every picture}+=[remember picture]
 \title{Raman sideband cooling of single Na atoms to 3D vibrational ground state}
@@
 \maketitle
+
+% Here's why single atom is great.
+
+% Here's how you do it, sodium is hard.
 
@@
 \begin{figure}
-  \includegraphics[width=9cm]{../../calculations/sideband_strength/imgs/coupling_0.46_0-6.png}
-  \includegraphics[width=7cm]{imgs/heating_op.png}
+  \includegraphics[width=4cm]{imgs/coupling_ax.png}
+  \includegraphics[width=4cm]{imgs/heating_op.png}
   \caption{(A) Matrix elements as a function of $n$ and $\Delta n$ (showing complex dependency and zeros) (B) State changing probability. Large and increases as $n$ gets larger
@@
 effective Lamb-Dicke parameter of $\sqrt{n}\eta_{Raman1}\approx2.4$.
-The Raman spectrum before applying Raman sideband cooling is shown in figure \ref{f-axial}A where we can see clearly resolved Raman cooling sidebands up to the 8th order suggesting that we have many vibrational states populated in this direction.\\
-
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
-\ \\
+The Raman spectrum before applying Raman sideband cooling is shown in figure \ref{f-axial}A where we can see clearly resolved Raman cooling sidebands up to the 8th order suggesting that we have many vibrational states populated in this direction.
 

### 2017-05-25 presentations/na_cool_paper/paper.tex
[presentations/na_cool_paper] sync changes from dropbox

@@
 \begin{document}
-\title{Raman sideband cooling of single Na atoms to 3D vibrational ground state}
-\author{....}
+\title{Motional Quantum Ground-State Cooing of a Single Sodium Atom}
+\author{Yichao Yu}
+\author{Nicholas R. Hutzler}
+\author{Jessie T. Zhang}
+\author{Lee R. Liu}
+\author{Kang-Kuen Ni}
+\email{ni@chemistry.harvard.edu}
+\affiliation{Department of Chemistry and Chemical Biology, Harvard University, Cambridge, Massachusetts, 02138, USA}
+\affiliation{Department of Physics, Harvard University, Cambridge, Massachusetts, 02138, USA}
+\affiliation{Harvard-MIT Center for Ultracold Atoms, Cambridge, Massachusetts, 02138, USA}
+
 \date{\today}
-\affiliation{Harvard Department of Physics}
 
 \begin{abstract}
+  % (add a general sentence on the importance or motivation of the work)
+  % Controlling quantum motion of...
+  % (state the challenge), (Give the result and brief solutions), (outlook)
   We report Raman sideband cooling of a single neutral Sodium atom to its three-dimensional
-  vibrational ground state in an optical tweezer.
+  motional ground state in an optical tweezer.
   Despite having a very large Lamb-Dicke parameter, high initial temperature and

### 2017-05-26 presentations/na_cool_paper/paper.tex
[presentations/na_cool_paper] include figures that needs to be changed in the same directory under imgs/temp
[presentations/na_cool_paper] Fix figure 1

@@
 \begin{figure*}
-  \includegraphics[height=6.5cm]{imgs/Na_RSC_schematic.pdf}
-  \includegraphics[height=6.5cm]{sequence.pdf}
+  \includegraphics[height=6cm]{imgs/Na_RSC_schematic.pdf}
+  \includegraphics[height=5cm]{sequence.pdf}
   \caption{(A) Energy diagram. D1 OP
@@
 
-<WIP>
-
 Finally, the deep trap that is needed to trap and image single Sodium atom also creates
-a very large AC Stark shift in the excited state.
-
-% impossible to load without switching
-% The same effect also happens on OP causing
-% *   cannot address atom in different position at the same time
-% *   breakdown of excited state HF structure
-% use switching
+a very large AC Stark shift in the excited state. For the trap depth we are using, the
+light shift in the center of the trap is as large as $300MHz$.
+In additional to creating a large and position dependent detuning for the optical pumping light,
+it also mixes the excited state state hyperfine levels,
+affecting the branching ratio and increasing the number of photons needed during optical pumping.
+Similar to our loading and imaging process [???], we solve this issue by switching the
+trapping light at $3MHz$ during the whole cooling sequence.
+Due to the large light shift, the optical pumping is effectively off when the trap light is on.
+Since the atom can only be addressed by the optical pumping light when the trap light is off,
+the effect of light shift on optical pumping fidelity is suppressed.
 
@@
   \includegraphics[width=8cm]{imgs/spectrum_r.png}
-  \includegraphics[width=8cm]{../../experiments/rabi_flop/imgs/fit_20170409_r2_0_ba.png}
+  \includegraphics[width=8cm]{imgs/temp/fit_20170409_r2_0_ba.png}
   \caption{(A) (B) \label{f-radial}}
@@
   \includegraphics[width=8cm]{imgs/spectrum_a1.png}
-  \includegraphics[width=8cm]{../../experiments/rabi_flop/imgs/fit_20170409_a1_0_ba.png}
+  \includegraphics[width=8cm]{imgs/temp/fit_20170409_a1_0_ba.png}
   \caption{(A) (B) \label{f-axial}}
@@
 effective Lamb-Dicke parameter of $\sqrt{n}\eta_{Raman1}\approx2.4$.
-The Raman spectrum before applying Raman sideband cooling is shown in figure \ref{f-axial}A where we can see clearly resolved Raman cooling sidebands up to the 8th order suggesting that we have many vibrational states populated in this direction.
+The Raman spectrum before applying Raman sideband cooling is shown in figure \ref{f-axial}A where we can see clearly resolved Raman cooling sidebands up to the eighth order suggesting that we have many vibrational states populated in this direction.
 

### 2017-05-26 presentations/na_cool_paper/sequence.tex
[presentations/na_cool_paper] Fix figure 1

@@
   \begin{scope}
-    \clip (4.6, -6.5) rectangle (17.8, 3.5);
+    \clip (4.6, -2.1) rectangle (17.8, 3.5);
     %% Pulse mark
     \foreach \i in {0,...,7} {
-      \draw[gray!20, line width=2] (2.8*\i, 1.8) -- (2.8*\i, -6.0);
-      \draw[gray!20, line width=2] (2.8*\i+1.9, 1.8) -- (2.8*\i+1.9, -6.0);
+      \draw[gray!20, line width=2] (2.8*\i, 1.5) -- (2.8*\i, -2.0);
+      \draw[gray!20, line width=2] (2.8*\i+1.9, 1.5) -- (2.8*\i+1.9, -2.0);
     }
@@
     %% Tweezer
-    \draw[line width=1.5,purple] (0, 2) -- (22.4, 2);
+    \draw[line width=1.5,purple] (0, 2.4) -- (22.4, 2.4);
     \foreach \i in {0,...,99} {
-      \filldraw[line width=1,purple] (\i*22.4/100, 2) rectangle (\i*22.4/100+0.06, 3.5);
+      \filldraw[line width=1,purple] (\i*22.4/100, 2.4) rectangle (\i*22.4/100+0.06, 3.5);
     }
@@
     }
+    \path[blue] (2.8*2+0.8, 0) node[below,align=center] {\textbf{Axis 1}\\\textit{Axial}};
     \foreach \i in {0,...,3} {
@@
       \fill[red!30]
-      plot[draw,samples=200,domain={5.6*\i+1.9}:{5.6*\i+2.5},variable=\x] ({\x}, {1.5*sin((\x-5.6*\i-1.9) * 300)^4 - 2})
+      plot[draw,samples=200,domain={5.6*\i+1.9}:{5.6*\i+2.5},variable=\x] ({\x}, {1.5*sin((\x-5.6*\i-1.9) * 300)^4})
       -- cycle;
-      \draw[line width=1,red] (5.6*\i, -2) -- plot[domain={5.6*\i+1.9}:{5.6*\i+2.5},variable=\x]
-      ({\x}, {1.5*sin((\x-5.6*\i-1.9) * 300)^4 - 2}) -- (5.6*\i+5.6, -2);
+      \draw[line width=1,red] (5.6*\i, 0) -- plot[domain={5.6*\i+1.9}:{5.6*\i+2.5},variable=\x]
+      ({\x}, {1.5*sin((\x-5.6*\i-1.9) * 300)^4}) -- (5.6*\i+5.6, 0);
     }
+    \path[red] (5.6*1+2.2, 1.5) node[above,align=center] {\textbf{Axis 2}\\\textit{Radial}};
 
@@
       \fill[black!30]
-      plot[draw,samples=200,domain={5.6*\i+4.7}:{5.6*\i+5.3},variable=\x] ({\x}, {1.5*sin((\x-5.6*\i-4.7) * 300)^4 - 4})
+      plot[draw,samples=200,domain={5.6*\i+4.7}:{5.6*\i+5.3},variable=\x] ({\x}, {1.5*sin((\x-5.6*\i-4.7) * 300)^4})
       -- cycle;
-      \draw[line width=1,black] (5.6*\i, -4) -- plot[domain={5.6*\i+4.7}:{5.6*\i+5.3},variable=\x]
-      ({\x}, {1.5*sin((\x-5.6*\i-4.7) * 300)^4 - 4}) -- (5.6*\i+5.6, -4);
+      \draw[line width=1,black] (5.6*\i, 0) -- plot[domain={5.6*\i+4.7}:{5.6*\i+5.3},variable=\x]
+      ({\x}, {1.5*sin((\x-5.6*\i-4.7) * 300)^4}) -- (5.6*\i+5.6, 0);
     }
+    \path[black] (5.6*1+5.0, 1.5) node[above,align=center] {\textbf{Axis 3}\\\textit{Radial}};
 
@@
       \filldraw[fill=orange!30,draw=orange,line width=1.2]
-      (2.8*\i+1.58, -6) rectangle (2.8*\i+1.91, -4.5);
+      (2.8*\i+1.58, -2) rectangle (2.8*\i+1.91, -0.7);
       \filldraw[fill=orange!30,draw=orange,line width=1.2]
-      (2.8*\i+2.48, -6) rectangle (2.8*\i+2.81, -4.5);
+      (2.8*\i+2.48, -2) rectangle (2.8*\i+2.81, -0.7);
     }
-    \draw[line width=2,orange] (0,-6) -- (22.4,-6);
+    \draw[line width=2,orange] (0,-2) -- (22.4,-2);
   \end{scope}
 
-  \fill[white,path fading=fade img right] (16.8, -6.6) rectangle (17.81, 3.51);
-  \fill[white,path fading=fade img right] (16.8, -6.6) rectangle (17.81, 3.51);
-  \fill[white,path fading=fade img right] (16.8, -6.6) rectangle (17.81, 3.51);
+  \fill[white,path fading=fade img right] (16.8, -2.2) rectangle (17.81, 3.51);
+  \fill[white,path fading=fade img right] (16.8, -2.2) rectangle (17.81, 3.51);
+  \fill[white,path fading=fade img right] (16.8, -2.2) rectangle (17.81, 3.51);
 
-  \fill[white,path fading=fade img left] (5.6, -6.6) rectangle (4.59, 3.51);
-  \fill[white,path fading=fade img left] (5.6, -6.6) rectangle (4.59, 3.51);
-  \fill[white,path fading=fade img left] (5.6, -6.6) rectangle (4.59, 3.51);
+  \fill[white,path fading=fade img left] (5.6, -2.2) rectangle (4.59, 3.51);
+  \fill[white,path fading=fade img left] (5.6, -2.2) rectangle (4.59, 3.51);
+  \fill[white,path fading=fade img left] (5.6, -2.2) rectangle (4.59, 3.51);
 
   \path (5.0, 2.3) node[left,purple,align=center] {\textbf{Tweezer}};
-  \path (4.8, 0.5) node[left,blue,align=center] {\textbf{Axis 1}\\\textit{Axial}};
-  \path (4.8, -1.5) node[left,red,align=center] {\textbf{Axis 2}\\\textit{Radial}};
-  \path (4.8, -3.5) node[left,black,align=center] {\textbf{Axis 3}\\\textit{Radial}};
-  \path (5.15, -5.5) node[left,orange,align=center] {\textbf{Optical}\\\textbf{pumping}};
-  \draw[line width=2,orange,->] (5.6,-6) -- (17.8,-6) node[right, below] {\scalebox{2}{$t$}};
+  \path (4.8, 0.5) node[left,align=center] {\textbf{Raman}};
+  \path (5.15, -1.5) node[left,orange,align=center] {\textbf{Optical}\\\textbf{pumping}};
+  \draw[line width=2,orange,->] (5.6,-2) -- (17.8,-2) node[right, below] {\scalebox{2}{$t$}};
 
@@
   \draw[decoration={brace,mirror,raise=3pt, amplitude=10pt},decorate,line width=2]
-  (5.6,-6) -- node[below=15pt] {\scalebox{1.5}{One cooling cycle}} (16.8,-6);
+  (5.6,-2) -- node[below=15pt] {\scalebox{1.5}{One cooling cycle}} (16.8,-2);
 

### 2017-05-26 presentations/na_cool_paper/plot_raman.jl
[presentations/na_cool_paper] Update axial raman coupling figure

@@ -21,10 +21,6 @@ function plot_sidebands(ns, Δns, η)
     for Δn in Δns
         plot(ns, abs.(Trap.sideband.(ns, ns .+ Δn, η)), ".-", label="\$\\Delta n=$(Δn)\$")
     end
-    xlim([0, xlim()[2]])
-    ylim([0, 1])
-    legend()
-    grid()
 end
 
 function maybe_save(name)
@@ -42,9 +38,17 @@ function maybe_show()
 end
 
 figure()
-plot_sidebands(0:50, -1:-1:-4, η_ax)
+plot_sidebands(0:70, -1:-1:-5, η_ax)
+xlim([0, 70])
+ylim([0, 0.79])
+grid()
 xlabel("Vibrational state")
 ylabel("\$|\\langle n |e^{ikr}| n + \\Delta n \\rangle|\$")
+text(0, 0.65, "\$\\left|\\Delta n\\right|\\!\\!=\\!\\!1\$", color="C0")
+text(9, 0.55, "\$\\left|\\Delta n\\right|\\!\\!=\\!\\!2\$", color="C1")
+text(21, 0.47, "\$\\left|\\Delta n\\right|\\!\\!=\\!\\!3\$", color="C2")
+text(36, 0.44, "\$\\left|\\Delta n\\right|\\!\\!=\\!4\$", color="C3")
+text(53, 0.42, "\$\\left|\\Delta n\\right|\\!\\!=\\!5\$", color="C4")
 maybe_save(joinpath(@__DIR__, "imgs/coupling_ax"))
 
 maybe_show()

### 2017-05-26 presentations/na_cool_paper/paper.tex
[presentations/na_cool_paper]
* vibrational -> motional
* move figures
* more radial results

@@
   we observed a ground state preparation fidelity of $70\%$ using sideband thermometry.
-  We demonstrated that Raman sideband cooling to vibrational ground state is applicable to
+  We demonstrated that Raman sideband cooling to motional ground state is applicable to
   systems where tight confinement or low initial cooling is hard to achieve.
@@
 \maketitle
+
+\begin{figure*}
+  \includegraphics[height=6cm]{imgs/Na_RSC_schematic.pdf}
+  \includegraphics[height=5cm]{sequence.pdf}
+  \caption{(A) Energy diagram. D1 OP
+    (B) Beam directions and polarizations
+    (C) Sequence description
+    \label{f-setup}}
+\end{figure*}
+\begin{figure}
+  \includegraphics[width=4cm]{imgs/coupling_ax.png}
+  \includegraphics[width=4cm]{imgs/heating_op.png}
+  \caption{(A) Matrix elements as a function of $n$ and $\Delta n$ (showing complex dependency and zeros) (B) State changing probability. Large and increases as $n$ gets larger
+    \label{f-ld}}
+\end{figure}
+\begin{figure*}
+  \includegraphics[width=8cm]{imgs/spectrum_r.png}
+  \includegraphics[width=8cm]{imgs/temp/fit_20170409_r2_0_ba.png}
+  \caption{(A) (B) \label{f-radial}}
+\end{figure*}
+\begin{figure*}
+  \includegraphics[width=8cm]{imgs/spectrum_a1.png}
+  \includegraphics[width=8cm]{imgs/temp/fit_20170409_a1_0_ba.png}
+  \caption{(A) (B) \label{f-axial}}
+\end{figure*}
 
@@
 
-\begin{figure*}
-  \includegraphics[height=6cm]{imgs/Na_RSC_schematic.pdf}
-  \includegraphics[height=5cm]{sequence.pdf}
-  \caption{(A) Energy diagram. D1 OP
-    (B) Beam directions and polarizations
-    (C) Sequence description
-    \label{f-setup}}
-\end{figure*}
-
 We achieve the high ground state preparation fidelity needed for molecule formation
 using Raman sideband cooling. The process consists of multiple cycles of laser pulses
-to manipulate the internal and vibrational states of the atoms.
+to manipulate the internal and motional states of the atoms.
 Figure \ref{f-setup}A shows the schematic of the energy levels and the cooling sequence
@@
 ground electronic state and a certain vibration state $n$.
-In the first step, a Raman pulse drives a transition to the vibrational state $n-\Delta n$
-to reduce the vibrational energy while also changing the internal state to $|F=1, m_F=-1\rangle$.
+In the first step, a Raman pulse drives a transition to the motional state $n-\Delta n$
+to reduce the motional energy while also changing the internal state to $|F=1, m_F=-1\rangle$.
 In the second step, which finishes the cooling cycle,
 an optical pumping pulse bring the atom back to the $|F=2, m_F=-2\rangle$ state to take away
-the entropy. The second step could also change the vibrational state of the atoms which
-could cause heating. The possibility for this to happen for an atom in the vibrational level $n$
+the entropy. The second step could also change the motional state of the atoms which
+could cause heating. The possibility for this to happen for an atom in the motional level $n$
 is approximately proportional to the effective Lamb-Dicke parameter
@@
 
-Although Raman sideband cooling to vibrational ground state has already been successfully
+Although Raman sideband cooling to motional ground state has already been successfully
 implemented on neutral atoms in other experiments using heavier species like Rubidium [????]
@@
 
-\begin{figure}
-  \includegraphics[width=4cm]{imgs/coupling_ax.png}
-  \includegraphics[width=4cm]{imgs/heating_op.png}
-  \caption{(A) Matrix elements as a function of $n$ and $\Delta n$ (showing complex dependency and zeros) (B) State changing probability. Large and increases as $n$ gets larger
-    \label{f-ld}}
-\end{figure}
-
 As mentioned previously, in order to perform Raman sideband cooling efficiently and
@@
 proportional to $\sqrt{m}$ (???) where $m$ is the mass of the atom, it is larger for Sodium
-given the same trap depth (???). With $45mW$ of power at the focus of the trap,
-we measured a trapping frequency of $\{\omega_1,\omega_2,\omega_3\}/2\pi = \{67, 420, 580\}\ \text{kHz}$
+given the same trap depth (???).
+With $45mW$ of power at the focus of the trap, we measured a trapping frequency of
+$\{\omega_1,\omega_2,\omega_3\}/2\pi = \{67, 420, 580\}\ \text{kHz}$
 which corresponds to optical pumping Lamb-Dicke parameters of
@@
 figure \ref{f-ld}A, the high Raman Lamb-Dicke parameters causes a strong coupling to higher orders
-of cooling sidebands, especially for high vibrational states.
-This enables us to cool atoms in high vibrational states by driving on high order Raman sidebands,
-removing more vibrational energy in a single cooling pulse and offsetting the effect of
-strong heating. Since the heating probability is higher for high vibrational states,
+of cooling sidebands, especially for high motional states.
+This enables us to cool atoms in high motional states by driving on high order Raman sidebands,
+removing more motional energy in a single cooling pulse and offsetting the effect of
+strong heating. Since the heating probability is higher for high motional states,
 cooling on these high order sidebands can greatly suppress the high heating during
 optical pumping during the initial cooling. Since the coupling strength of different orders
-do not reach their minimums at the same time, using multiple orders of vibrational sidebands
+do not reach their minimums at the same time, using multiple orders of motional sidebands
 for cooling also avoids accumulation of population near the coupling minimum of a particular
@@
 on the radial sidebands to be no lower than tens of kilo-Hertz in order to drive atoms in
-different vibrational states equally.
+different motional states equally.
 
@@
 Taking all the features of our system into account, we use a Monte-Carlo simulation to verify
-the validity of our method and explore the large parameter space for the cooling sequence.
+the validity of our method.
 In the simulation, we can observe the high heating rate due to the high Lamb-Dicke parameters
-and confirm that high order of Raman sideband can be used to suppress this effect and reduces
-the vibrational energy of the atom faster.
-We also use the simulation to find a robust cooling strategy. As shown in figure (?),
+and confirm that by using high order Raman sideband transition in the cooling sequence we can
+suppress this effect and reduces the motional energy of the atom faster.
+The simulation is also used to guide the optimization of the cooling sequence by exploring the
+large parameter space and finding a robust cooling strategy. As shown in figure (?),
 we found that instead of cooling on only one sideband order at a time, it is generally more
-efficient to alternate the cooling pulse between two neighboring orders. A cooling sequence
-like this minimizes the accumulation of atom in a state not addressed by a particular sideband order.\\
+efficient to alternate the cooling pulse between two neighboring orders (axial) or pulse lengths.
+A cooling sequence like this minimizes the accumulation of atom in a state not addressed by a
+particular Raman pulse parameter.
 
-\begin{figure*}
-  \includegraphics[width=8cm]{imgs/spectrum_r.png}
-  \includegraphics[width=8cm]{imgs/temp/fit_20170409_r2_0_ba.png}
-  \caption{(A) (B) \label{f-radial}}
-\end{figure*}
-
-For the more tightly confined radial directions, we starts the cooling with $\{\bar n_2, \bar n_3\}=????, ????$.
-The sideband spectra of the initial distribution is shown in figure \ref{f-radial}A where we can clearly see the first order heating, first order cooling and second order cooling sidebands.
-After applying about 1000 cooling pulses cooling in all three dimensions starting with cooling on the radial second order, the Raman spectrum with the same parameter is shown in figure \ref{f-radial}B, where both cooling orders are suppressed.
-We can estimate the ground state probability in each direction based on the height of the first order cooling and heating sideband and the absence of the second order cooling sideband to be $......$.
-Due to the complexity of the sideband structure, we also use the Rabi flopping on the carrier and heating sideband as a independent measurement of the ground state population and gets $......$, showing good agreement between the two methods.
-(?????
-figure \ref{f-radial}C and \ref{f-radial}D)\\
-
-\begin{figure*}
-  \includegraphics[width=8cm]{imgs/spectrum_a1.png}
-  \includegraphics[width=8cm]{imgs/temp/fit_20170409_a1_0_ba.png}
-  \caption{(A) (B) \label{f-axial}}
-\end{figure*}
+For the more tightly confined radial directions,
+we starts the cooling with $\{\bar n_2, \bar n_3\}=????, ????$.
+The radial sideband spectra of the initial distribution is shown in figure \ref{f-radial}A
+where we can clearly see the first order heating, first order cooling and
+second order cooling sidebands.
+After applying about 1000 cooling pulses cooling in all three dimensions
+starting with cooling on the radial second order,
+the Raman spectrum with the same parameter is shown in figure \ref{f-radial}B,
+where the first and second order cooling sidebands on both axis are suppressed.
+Given the absence of the second order cooling sideband,
+we can estimate the ground state probability in each direction based on the height of
+the first order cooling and heating sideband to be $????$ and $????$.
+Due to the complexity of the sideband structure,
+we measured the Rabi flopping on the carrier and heating sideband before and after cooling
+(\ref{f-radial}C and \ref{f-radial}D)
+as a independent way to obtain the population in different motional states.
+Fitting the Rabi flopping data give a ground state probability of $????$ and $????$,
+showing good agreement between the two methods.
 
 As mentioned previously, the axial direction is much less confined and therefore has a much higher
-effective Lamb-Dicke parameter of $\sqrt{n}\eta_{Raman1}\approx2.4$.
-The Raman spectrum before applying Raman sideband cooling is shown in figure \ref{f-axial}A where we can see clearly resolved Raman cooling sidebands up to the eighth order suggesting that we have many vibrational states populated in this direction.
+effective Lamb-Dicke parameter of $\eta^{OP}_{eff1}\approx3.3$.
+The Raman spectrum before applying Raman sideband cooling is shown in figure \ref{f-axial}A where we can see clearly resolved Raman cooling sidebands up to the eighth order suggesting that we have many motional states populated in this direction.
 
 % Missing:
-% ?? Switching helps OP fidelity
-% ?? off-resonant scattering
 % ?? D1 OP
-% ?? Switching improves
 

### 2017-05-26 lib/NaCsSim/src/samplers.jl
[lib] unfinished comment....

@@ -80,7 +80,7 @@ function emission(::Type{T}, isσ::Bool, rng) where T<:AbstractFloat
     # The (real) solution is
     # `cosθ = x + 1 / x` where `x = ∛(2√(v² - v) - 2v + 1)` for π light and
     # `cosθ = x - 1 / x` where `x = ∛(√(16v² - 16v + 5) + 4v - 2)` for σ± light
-    # Note that the `x` for
+    # Note that the `x` for π polarization is complex
     v = T(rand(rng)) # This is faster than `rand(T)`....
     φ = T(rand(rng)) * T(2π)
     if isσ

### 2017-05-26 presentations/na_cool_paper/plot_op_combine.jl
[presentations/na_cool_paper] Fix OP heating figure

@@ -15,23 +15,75 @@ const m_Na = 23e-3 / 6.02e23
 const η_ax = Trap.η(m_Na, 67e3, 2π / 589e-9)
 const η_ra = Trap.η(m_Na, 580e3, 2π / 589e-9)
 
-function op_coupling_kernel(n1, n2, η::T, θ::T, ϕ::T, isσ) where T
-    sinθ, cosθ = @fastmath sincos(θ)
-    η_eff = @fastmath η * cosθ * sin(ϕ)
-    factor = if isσ
-        T(3 / (2π)) * sinθ^3
+"""
+    emission(v, isσ::Bool) -> (sinθ, cosθ)
+
+Given an uniform distribution in `[0, 1]` of `v` this function will return a distribution
+of `cosθ` that matches a dipole emission pattern (the type of the transition is determined by
+`isσ`).
+"""
+function emission_angle(v::T, isσ::Bool) where T<:AbstractFloat
+    # Returns `cosθ`. The caller should be ready to handle `|cosθ| > 1`
+    # The PDFs of the `θ` distribution are
+    # `3 / 4 * (1 - cos²θ) * sinθ` for π light and
+    # `3 / 8 * (1 + cos²θ) * sinθ` for σ± light
+    # The corresponding CDFs are
+    # `1 / 4 * (3cosθ - cos³θ) + 1 / 2` for π light and
+    # `1 / 8 * (3cosθ + cos³θ) + 1 / 2` for σ± light
+    # For a random number `v` we need to solve
+    # `3cosθ - cos³θ = 4v - 2` for π light and
+    # `3cosθ + cos³θ = 8v - 4` for σ± light
+    # The (real) solution is
+    # `cosθ = x + 1 / x` where `x = ∛(2√(v² - v) - 2v + 1)` for π light and
+    # `cosθ = x - 1 / x` where `x = ∛(√(16v² - 16v + 5) + 4v - 2)` for σ± light
+    # Note that the `x` for π polarization is complex
+    if isσ
+        y = muladd(v, 4, -2)
+        x = @fastmath cbrt(sqrt(muladd(y, y, 1)) + y)
+        return x - 1 / x
     else
-        T(3 / (4π)) * (1 + cosθ^2) * sinθ
+        θ′ = @fastmath acos(muladd(T(-2), v, T(1)))
+        cosθ = @fastmath cos(muladd(θ′, T(1 / 3), - T(2π / 3))) * 2
[…]

### 2017-05-26 presentations/na_cool_paper/paper.tex
[presentations/na_cool_paper] Combine figure 2

@@
 \begin{figure*}
-  \includegraphics[height=6cm]{imgs/Na_RSC_schematic.pdf}
-  \includegraphics[height=5cm]{sequence.pdf}
+  \includegraphics[height=5.2cm]{imgs/Na_RSC_schematic.pdf}
+  \includegraphics[height=4.5cm]{sequence.pdf}
   \caption{(A) Energy diagram. D1 OP
@@
 \begin{figure}
-  \includegraphics[width=4cm]{imgs/coupling_ax.png}
-  \includegraphics[width=4cm]{imgs/heating_op.png}
+  \includegraphics[width=8.5cm]{imgs/fig2_raman_op.png}
   \caption{(A) Matrix elements as a function of $n$ and $\Delta n$ (showing complex dependency and zeros) (B) State changing probability. Large and increases as $n$ gets larger
@@
 
-As mentioned previously, the axial direction is much less confined and therefore has a much higher
+The axial direction is much less confined and therefore has a much higher
 effective Lamb-Dicke parameter of $\eta^{OP}_{eff1}\approx3.3$.

### 2017-05-26 presentations/na_cool_paper/plot_raman.jl

@@ -1,54 +1,0 @@
-#!/usr/bin/julia
-
-push!(LOAD_PATH, joinpath(@__DIR__, "../../lib"))
-
-import NaCsCalc.Utils: interactive
-import NaCsCalc: Trap
-using PyPlot
-
-PyPlot.matplotlib["rcParams"][:update](Dict("font.size" => 20))
-PyPlot.matplotlib[:rc]("xtick", labelsize=15)
-PyPlot.matplotlib[:rc]("ytick", labelsize=15)
-
-const m_Na = 23e-3 / 6.02e23
-const η_ax = Trap.η(m_Na, 67e3, 2π / 589e-9) / √(2)
-const η_rad1 = Trap.η(m_Na, 420e3, 2π / 589e-9) * √(2)
-const η_rad2 = Trap.η(m_Na, 580e3, 2π / 589e-9) * √(2)
-
-# const colors = ["k", "r", "y", "g", "c", "b", "m"]
-const colors = ["C0", "C1", "C2", "C3", "C4", "C5", "C6"]
-function plot_sidebands(ns, Δns, η)
-    for Δn in Δns
-        plot(ns, abs.(Trap.sideband.(ns, ns .+ Δn, η)), ".-", label="\$\\Delta n=$(Δn)\$")
-    end
-end
-
-function maybe_save(name)
-    if !interactive()
-        savefig("$name.png"; bbox_inches="tight", transparent=true)
-        savefig("$name.svg", bbox_inches="tight", transparent=true)
-        close()
-    end
-end
-
-function maybe_show()
-    if interactive()
-        show()
-    end
-end
-
-figure()
-plot_sidebands(0:70, -1:-1:-5, η_ax)
-xlim([0, 70])
-ylim([0, 0.79])
-grid()
-xlabel("Vibrational state")
-ylabel("\$|\\langle n |e^{ikr}| n + \\Delta n \\rangle|\$")
-text(0, 0.65, "\$\\left|\\Delta n\\right|\\!\\!=\\!\\!1\$", color="C0")
-text(9, 0.55, "\$\\left|\\Delta n\\right|\\!\\!=\\!\\!2\$", color="C1")
-text(21, 0.47, "\$\\left|\\Delta n\\right|\\!\\!=\\!\\!3\$", color="C2")
-text(36, 0.44, "\$\\left|\\Delta n\\right|\\!\\!=\\!4\$", color="C3")
[…]

### 2017-05-26 presentations/na_cool_paper/plot_raman_op.jl

@@ -2,8 +2,8 @@
 
 push!(LOAD_PATH, joinpath(@__DIR__, "../../lib"))
 
-import NaCsCalc: Trap
 import NaCsCalc.Utils: interactive
+import NaCsCalc: Trap
 using Cubature
 using PyPlot
 
@@ -12,8 +12,9 @@ PyPlot.matplotlib[:rc]("xtick", labelsize=15)
 PyPlot.matplotlib[:rc]("ytick", labelsize=15)
 
 const m_Na = 23e-3 / 6.02e23
-const η_ax = Trap.η(m_Na, 67e3, 2π / 589e-9)
-const η_ra = Trap.η(m_Na, 580e3, 2π / 589e-9)
+const η_ax = Trap.η(m_Na, 67e3, 2π / 589e-9) / √(2)
+const η_ra1 = Trap.η(m_Na, 430e3, 2π / 589e-9)
+const η_ra2 = Trap.η(m_Na, 590e3, 2π / 589e-9)
 
 """
     emission(v, isσ::Bool) -> (sinθ, cosθ)
@@ -53,7 +54,7 @@ end
 
 Given an uniform distribution in `[0, 1]` of `v` and an uniform distribution in `[0, π]` of φ
 this function will return the distribution of matrix element of matrix element between `n1`
-and `n2` vibrational states after one photon scattering.
+and `n2` motional states after one photon scattering.
 
 The polarization of the emission is determined by `isσ`.
 The overlap between the axis and the drive beam direction is `cosθ_dri`.
@@ -74,13 +75,13 @@ end
 
 function op_heating_ax(n1, n2, η::T, isσ) where T
     hcubature(x->op_coupling(n1, n2, η, T(x[1]), T(x[2]), isσ, T(0), (T(1), T(0))),
-              [0.0, 0.0], [1.0, π], abstol=1e-5)[1]
+              [0.0, 0.0], [1.0, π], abstol=1e-6)[1]
 end
 
 function op_heating_ra(n1, n2, η::T, isσ) where T
     hcubature(x->op_coupling(n1, n2, η, T(x[1]), T(x[2]), isσ,
                              sqrt(T(0.5)), (sqrt(T(0.5)), sqrt(T(0.5)))),
-              [0.0, 0.0], [1.0, π], abstol=1e-5)[1]
+              [0.0, 0.0], [1.0, π], abstol=1e-6)[1]
 end
 
[…]

### 2017-05-26 presentations/na_cool_paper/paper.tex
[presentations/na_cool_paper] figure 2 caption, fix axial op heating plot (wrong Lamb-Dicke parameter), add subfigure label

@@
 \end{figure*}
-\begin{figure}
+\begin{figure}[b]
   \includegraphics[width=8.5cm]{imgs/fig2_raman_op.png}
-  \caption{(A) Matrix elements as a function of $n$ and $\Delta n$ (showing complex dependency and zeros) (B) State changing probability. Large and increases as $n$ gets larger
+  \caption{Matrix elements and heating probabilities as a function of motional state.
+    The range plotted covers $99\%$ of the initial thermal distribution.
+    (A) Matrix elements for Raman transition in the axial direction showing diviation from
+    $\sqrt{n}$ scaling and multiple minimums for different sideband orders.
+    (B) Heating probability during the optical pumping step for all three axis.
+    Due to the large Lamb-Dicke parameter,
+    there is a high probability of heating especially in the axial direction.
     \label{f-ld}}

### 2017-05-26 presentations/na_cool_paper/plot_raman_op.jl

@@ -13,6 +13,7 @@ PyPlot.matplotlib[:rc]("ytick", labelsize=15)
 
 const m_Na = 23e-3 / 6.02e23
 const η_ax = Trap.η(m_Na, 67e3, 2π / 589e-9) / √(2)
+const η_ax_op = Trap.η(m_Na, 67e3, 2π / 589e-9)
 const η_ra1 = Trap.η(m_Na, 430e3, 2π / 589e-9)
 const η_ra2 = Trap.η(m_Na, 590e3, 2π / 589e-9)
 
@@ -104,8 +105,8 @@ function op_heating_all(cb::Function, sz1, sz2, η::T, isσ) where T
     res
 end
 
-const coupling_ax = (op_heating_all(op_heating_ax, 100, 100, Float32(η_ax), false) *
-                     op_heating_all(op_heating_ax, 100, 100, Float32(η_ax), true))
+const coupling_ax = (op_heating_all(op_heating_ax, 100, 100, Float32(η_ax_op), false) *
+                     op_heating_all(op_heating_ax, 100, 100, Float32(η_ax_op), true))
 const coupling_ra1 = (op_heating_all(op_heating_ra, 30, 30, Float32(η_ra1), false) *
                       op_heating_all(op_heating_ra, 30, 30, Float32(η_ra1), true))
 const coupling_ra2 = (op_heating_all(op_heating_ra, 30, 30, Float32(η_ra2), false) *
@@ -160,6 +161,7 @@ text(9, 0.55, "\$\\left|\\Delta n\\right|\\!\\!=\\!\\!2\$", color="C1")
 text(21, 0.47, "\$\\left|\\Delta n\\right|\\!\\!=\\!\\!3\$", color="C2")
 text(36, 0.44, "\$\\left|\\Delta n\\right|\\!\\!=\\!4\$", color="C3")
 text(53, 0.42, "\$\\left|\\Delta n\\right|\\!\\!=\\!5\$", color="C4")
+text(60, 0.632, "(A)")
 setp(ax1[:get_xticklabels](), visible=false)
 
 ax2 = subplot(212)
@@ -167,9 +169,10 @@ subplots_adjust(hspace=0)
 plot(0:nmax, p_heat(coupling_ax, nmax + 1), label="Axial")
 plot(0:nmax_r, p_heat(coupling_ra1, nmax_r + 1), label="Radial (axis 2)")
[…]

### 2017-05-26 presentations/na_cool_paper/plot_raman_op.jl
[presentations/na_cool_paper] PDF figure

@@ -127,6 +127,7 @@ end
 
 function maybe_save(name)
     if !interactive()
+        savefig("$name.pdf"; bbox_inches="tight", transparent=true)
         savefig("$name.png"; bbox_inches="tight", transparent=true)
         savefig("$name.svg", bbox_inches="tight", transparent=true)
         close()

### 2017-05-28 presentations/na_cool_paper/paper.tex
[presentations/na_cool_paper] PDF figure
[presentations/na_cool_paper] Introductions

@@
   % Controlling quantum motion of...
-  % (state the challenge), (Give the result and brief solutions), (outlook)
+  % (state the challenge),
+  % (Give the result and brief solutions),
+  % (outlook)
   We report Raman sideband cooling of a single neutral Sodium atom to its three-dimensional
@@
 \begin{figure}[b]
-  \includegraphics[width=8.5cm]{imgs/fig2_raman_op.png}
+  \includegraphics[width=8.5cm]{imgs/fig2_raman_op.pdf}
   \caption{Matrix elements and heating probabilities as a function of motional state.
@@
 
-% Here's why single atom is great.
+Single neutral atoms trapped in optical tweezers provide a promising system
+for various applications including quantum information, quantum chemistry
+and quantum simulation of many-body systems.
+The interaction between different sites can be controlled by creating Rydberg excitation
+or by creating dipolar molecules from two trapped atoms.
+Combined with the ability to move, detect and manipulate individual sites,
+arrays of optical tweezers can be used to prepare complex interacting system
+with high fidelity.
+In order to achieve long coherence time and full quantum control of the system needed for
+these applications,
+it is usually necessary to control the thermal motion of the atoms by cooling to the
+three dimensional motional ground state in the optical tweezer,
+which has already been demonstrated with heavy alkali atoms including rubidium and cesium.
+However, some of the important properties of previous experiements,
+for example low initial temperature and small Lamb-Dicke parameter,
+may not be easily achievable for other systems and
+the versatility of this approach requires being able to perform ground motional state cooling
+in the more general case. In this letter, we present our work on cooling single sodium atoms
+trapped in optical tweezers to the motional ground state with Raman sideband cooling.
+Dispite having a large Lamb-Dicke parameter and high initial temperature,
+by utilizing several new cooling techniques and a well optimized cooling sequence,
+we are able to achieve a ground state probability of $80\%$.
 
-% Here's how you do it, sodium is hard.
-
-Why do we need to cool (for STIRAP/transfer to molecular state)\\
-
-* Pure initial state\\
-* Small wavefunction span\\
-
-We achieve the high ground state preparation fidelity needed for molecule formation
-using Raman sideband cooling. The process consists of multiple cycles of laser pulses
-to manipulate the internal and motional states of the atoms.
+The Raman sideband cooling we used to achieve the high ground state preparation fidelity
+consists of multiple cycles of laser pulses to manipulate the internal and
+motional states of the atoms.
 Figure \ref{f-setup}A shows the schematic of the energy levels and the cooling sequence
@@
 by a harmonic trap, when a large number of levels are populated due to high initial temperature
-the anharmonicity of the trap can lead to broadening of the sideband and the decrease of
+the anharmonicity of the trap can lead to broadening of the sideband and decrease of
 the sideband signal. In our setup, this effect limits the Rabi frequency of the Raman pulse
@@
 
-The axial direction is much less confined and therefore has a much higher
-effective Lamb-Dicke parameter of $\eta^{OP}_{eff1}\approx3.3$.
-The Raman spectrum before applying Raman sideband cooling is shown in figure \ref{f-axial}A where we can see clearly resolved Raman cooling sidebands up to the eighth order suggesting that we have many motional states populated in this direction.
+The axial direction is much less confined and therefore has a much higher initial effective
+Lamb-Dicke parameter of $\eta^{OP}_{eff1}\approx3.3$.
+
+Figure \ref{f-axial}A shows the Raman spectrum in the axial direction before applying Raman sideband cooling where we can see clearly resolved Raman cooling sidebands up to the eighth order suggesting that we have many motional states populated in this direction.
+
+Limitation
 
@@
 % ?? D1 OP
+% ?? Blackman pulse
 
@@
 \end{document}
-
-% Generalization to other systems (properties that are shared with "more real" systems)
-% Inharmonicity -> gaussian beam. -> importance to use short/strong pulses.

### 2017-05-28 presentations/na_cool_paper/paper.tex
[presentations/na_cool_paper] axial results

@@
 Lamb-Dicke parameter of $\eta^{OP}_{eff1}\approx3.3$.
-
-Figure \ref{f-axial}A shows the Raman spectrum in the axial direction before applying Raman sideband cooling where we can see clearly resolved Raman cooling sidebands up to the eighth order suggesting that we have many motional states populated in this direction.
-
-Limitation
+The line in figure \ref{f-axial}A shows the Raman spectrum in the axial direction
+before applying Raman sideband cooling where we can see clearly resolved Raman cooling sidebands
+up to the eighth order suggesting that we have many motional states populated in this direction.
+Therefore, we starts our cooling sequence by driving Raman transitions on the eighth order axial
+cooling sideband. After applying the cooling sequence identical to the one we use to cool
+the radial directions, the spectrum is shown as the blue line in figure \ref{f-axial}A.
+All of the high order ($\geqslant2$) axial cooling sidebands disappeared and the first order
+cooling sideband is also strongly suppressed.
+The ground state probability calculated from this spectrum is $????$.
+We can also use Rabi flopping on the carrier and heating sideband to varify this result
+similar to the radial direction. In this case, we see very good agreement on the carrier
+(figure \ref{f-axial}B) but there is additional decoherence on the axial first order
+heating sideband (figure \ref{f-axial}C).
+We believe this decoherence is caused by technical noise in our setup which
+produces the strongest effect on this transition due to its slow Rabi frequency.
+The decoherence time scale agree with the magnetic field fluctuation we measured which produces
+a Zeeman shift of around $5kHz$.
 

### 2017-05-28 presentations/na_cool_paper/paper.tex
[presentations/na_cool_paper] conclusion

@@
   % (outlook)
-  We report Raman sideband cooling of a single neutral Sodium atom to its three-dimensional
+  We report Raman sideband cooling of a single neutral sodium atom to its three-dimensional
   motional ground state in an optical tweezer.
@@
 in our setup.
-Each cooling cycle starts with the Sodium atom in the $|F=2, m_F=-2\rangle$
+Each cooling cycle starts with the sodium atom in the $|F=2, m_F=-2\rangle$
 ground electronic state and a certain vibration state $n$.
@@
 and a tight confinement to achieve a small Lamb-Dicke parameter and effective Lamb-Dicke parameter.
-However, this regime is harder to achieve with Sodium atoms, creating additional challenges for
+However, this regime is harder to achieve with sodium atoms, creating additional challenges for
 us to realize ground state cooling. On the other hand, since these conditions can also be difficult
@@
 a small Lamb-Dicke parameter. However, since the Lamb-Dicke parameter $\eta$ is inversely
-proportional to $\sqrt{m}$ (???) where $m$ is the mass of the atom, it is larger for Sodium
+proportional to $\sqrt{m}$ (???) where $m$ is the mass of the atom, it is larger for sodium
 given the same trap depth (???).
@@
 Moreover, due to the unresolved(?) hyperfine structure in the $3^2P_{3/2}$ manifold,
-the sub-Doppler cooling in Sodium is also less efficient and we start the
+the sub-Doppler cooling in sodium is also less efficient and we start the
 Raman sideband cooling with a initial temperature of $40\mu K$. Combined with the high Lamb-Dicke
@@
 
-Finally, the deep trap that is needed to trap and image single Sodium atom also creates
+Finally, the deep trap that is needed to trap and image single sodium atom also creates
 a very large AC Stark shift in the excited state. For the trap depth we are using, the
@@
 
+Combining the axial and radial cooling results, we have achieved a ground state probability of
+$....$. We believe this is currently limited by off-resonant scattering from the Raman beams
+and the resonance shift caused by magnetic field fluctuation.
+Improvements on these should improve the cooling performance even further.
+
 % Missing:

### 2017-05-28 presentations/na_cool_paper/paper.tex
[presentations/na_cool_paper] Caption 1

@@
   \includegraphics[height=4.5cm]{sequence.pdf}
-  \caption{(A) Energy diagram. D1 OP
-    (B) Beam directions and polarizations
-    (C) Sequence description
+  \caption{(A) Energy levels and schematics of Raman sideband cooling.
+    The Raman transitions has a one photon detuning $\Delta=25GHz$ from the D2 line.
+    We use D1 light with $\sigma^-$ polarization to repump atom out of $|F=2,m_F=-1\rangle$
+    state to minimize heating on the atom in $|F=2,m_F=-2\rangle$ state.
+    (B) Geometry and polarizations of the Raman and optical pumping beams relative to the
+    optical tweezer and bias magnetic field.
+    (C) Schematics of the cooling sequence. The tweezer is switching at $3MHz$ to
+    reduce light shift during optical pumping. Each cooling cycle consists of $8$ pulses.
+    The four axial pulses are addressing two neighboring cooling orders.
+    The two pulses in each radial directions are either addressing two neighbering cooling orders
+    or having different length on the first order when most of the population are below $n=3$
+    towards then end of the cooling sequence.
     \label{f-setup}}

### 2017-05-29 presentations/na_cool_paper/plot_spectrum.jl
[presentations/na_cool_paper] Figure 3ab, 4ab

@@ -6,8 +6,7 @@ using NaCsCalc.Utils: interactive
 using NaCsData
 using PyPlot
 using DataStructures
-matplotlib["rcParams"][:update](Dict("font.size" => 20,
-                                     "font.weight" => "bold"))
+matplotlib["rcParams"][:update](Dict("font.size" => 20))
 matplotlib[:rc]("xtick", labelsize=15)
 matplotlib[:rc]("ytick", labelsize=15)
 
@@ -84,6 +83,7 @@ end
 
 function maybe_save(name)
     if !interactive()
+        savefig("$name.pdf"; bbox_inches="tight", transparent=true)
         savefig("$name.png"; bbox_inches="tight", transparent=true)
         savefig("$name.svg", bbox_inches="tight", transparent=true)
         close()
@@ -115,14 +115,14 @@ data_nocool_a1_hi = [NaCsData.map_params(to_sideband(-18.5015), split_a[:nocool_
 data_cool_a1 =  NaCsData.map_params(to_sideband(-18.488), split_d[3])
 data_cool_a1_hi =  NaCsData.map_params(to_sideband(-18.488), split_c[4])
 
-fig = figure(figsize=[1.5, 1] * 4.8)
+fig = figure(figsize=[1.6, 1] * 4.8)
 
 # Without cooling
 ax1 = subplot(211)
 # Radial 2
-plot_data(data_nocool_r2[1], 1, fmt="ro-", label="Axis 2")
-plot_data(data_nocool_r2[2], 1, fmt="ro-")
-plot_data(data_nocool_r2[3], 1, fmt="ro-")
+plot_data(data_nocool_r2[1], 1, fmt="C3o-", label="Axis 2")
+plot_data(data_nocool_r2[2], 1, fmt="C3o-")
+plot_data(data_nocool_r2[3], 1, fmt="C3o-")
 # Radial 3
 plot_data(data_nocool_r3[1], 1, fmt="ko-", label="Axis 3")
 plot_data(data_nocool_r3[2], 1, fmt="ko-")
@@ -132,6 +132,7 @@ grid()
 ylim([0, 1])
 xlim([-700, 1400])
 legend()
+text(-660, 0.8, "(A)")
 setp(ax1[:get_xticklabels](), visible=false)
 
 # With cooling
[…]

### 2017-05-29 presentations/na_cool_paper/paper.tex
[presentations/na_cool_paper] Figure 3ab, 4ab
[presentations/na_cool_paper] Figure 3cd, 4cd

@@
     optical tweezer and bias magnetic field.
-    (C) Schematics of the cooling sequence. The tweezer is switching at $3MHz$ to
+    (C) Schematics of the cooling sequence. The tweezer is switching at $3\text{MHz}$ to
     reduce light shift during optical pumping. Each cooling cycle consists of $8$ pulses.
@@
 \begin{figure*}
-  \includegraphics[width=8cm]{imgs/spectrum_r.png}
-  \includegraphics[width=8cm]{imgs/temp/fit_20170409_r2_0_ba.png}
+  \includegraphics[height=4cm]{imgs/spectrum_r.pdf}
+  \includegraphics[height=4cm]{imgs/rabi_flop_r3_0.png}
+  \includegraphics[height=4cm]{imgs/rabi_flop_r3_p1.png}
   \caption{(A) (B) \label{f-radial}}
@@
 \begin{figure*}
-  \includegraphics[width=8cm]{imgs/spectrum_a1.png}
-  \includegraphics[width=8cm]{imgs/temp/fit_20170409_a1_0_ba.png}
+  \includegraphics[height=4cm]{imgs/spectrum_a1.pdf}
+  \includegraphics[height=4cm]{imgs/rabi_flop_a1_0.png}
+  \includegraphics[height=4cm]{imgs/rabi_flop_a1_p1.png}
   \caption{(A) (B) \label{f-axial}}
@@
 With $45mW$ of power at the focus of the trap, we measured a trapping frequency of
-$\{\omega_1,\omega_2,\omega_3\}/2\pi = \{67, 420, 580\}\ \text{kHz}$
+$\{\omega_1,\omega_2,\omega_3\}/2\pi = \{67, 420, 580\}\ \text{\text{kHz}}$
 which corresponds to optical pumping Lamb-Dicke parameters of
@@
 a very large AC Stark shift in the excited state. For the trap depth we are using, the
-light shift in the center of the trap is as large as $300MHz$.
+light shift in the center of the trap is as large as $300\text{MHz}$.
 In additional to creating a large and position dependent detuning for the optical pumping light,
@@
 Similar to our loading and imaging process [???], we solve this issue by switching the
-trapping light at $3MHz$ during the whole cooling sequence.
+trapping light at $3\text{MHz}$ during the whole cooling sequence.
 Due to the large light shift, the optical pumping is effectively off when the trap light is on.
@@
 cooling sideband. After applying the cooling sequence identical to the one we use to cool
-the radial directions, the spectrum is shown as the blue line in figure \ref{f-axial}A.
+the radial directions, the spectrum is shown in figure \ref{f-axial}B.
 All of the high order ($\geqslant2$) axial cooling sidebands disappeared and the first order
@@
 The decoherence time scale agree with the magnetic field fluctuation we measured which produces
-a Zeeman shift of around $5kHz$.
+a Zeeman shift of around $5\text{kHz}$.
 

### 2017-05-29 presentations/na_cool_paper/plot_rabi_flop.jl

@@ -1,0 +1,296 @@
+#!/usr/bin/julia
+
+# Compute Rabi flopping with the present of decay terms
+# The Hamiltonian is assumed to be time independent and the Rabi drive is on-resonance
+
+push!(LOAD_PATH, joinpath(@__DIR__, "../../lib"))
+using NaCsCalc.Utils: binomial_estimate, thread_rng, interactive
+using NaCsCalc.Atomic: all_scatter_D
+import NaCsCalc: Trap
+using NaCsSim.DecayRabi: propagate_multistates, average_multistates, Γ_to_rates
+using NaCsData
+using DataStructures
+using PyPlot
+matplotlib["rcParams"][:update](Dict("font.size" => 20))
+matplotlib[:rc]("xtick", labelsize=15)
+matplotlib[:rc]("ytick", labelsize=15)
+
+# Scattering rates
+const δf1 = -25.0e9
+const δf2 = -25.0e9 - 1.77e9
+const rlof_f1 = (61.542e6 / (δf1 - 1.107266e9))^2
+const rlof_f2 = (61.542e6 / (δf2 - 1.107266e9))^2
+const rhif_f1 = (61.542e6 / (δf1 + 664.360e6))^2
+const rhif_f2 = (61.542e6 / (δf2 + 664.360e6))^2
+
+const rates_f1_coprop = all_scatter_D(true, 3, (0.5, 0.0, 0.5), rhif_f1, rlof_f1)
+const rates_f1_up = all_scatter_D(true, 3, (0.25, 0.5, 0.25), rhif_f1, rlof_f1)
+const rates_f1_down = all_scatter_D(true, 3, (0.25, 0.5, 0.25), rhif_f1, rlof_f1)
+const rates_f2_coprop = all_scatter_D(true, 3, (0.25, 0.5, 0.25), rhif_f2, rlof_f2)
+const rates_f2_counterop = all_scatter_D(true, 3, (0.1, 0.0, 0.9), rhif_f2, rlof_f2)
+
+rates_f1_coprop .*= 4.46e8
+rates_f2_coprop .*= 4.1e8
+rates_f1_up .*= 1.05e9
+rates_f1_down .*= 8.2e8
+rates_f2_counterop .*= 3.25e9
+
+const rates_r3 = rates_f1_down + rates_f2_counterop
+const rates_r2 = rates_f1_up + rates_f2_counterop
[…]

### 2017-05-29 presentations/na_cool_paper/paper.tex
[presentations/na_cool_paper] pdf figures

@@
   \includegraphics[height=4cm]{imgs/spectrum_r.pdf}
-  \includegraphics[height=4cm]{imgs/rabi_flop_r3_0.png}
-  \includegraphics[height=4cm]{imgs/rabi_flop_r3_p1.png}
+  \includegraphics[height=4cm]{imgs/rabi_flop_r3_0.pdf}
+  \includegraphics[height=4cm]{imgs/rabi_flop_r3_p1.pdf}
   \caption{(A) (B) \label{f-radial}}
@@
   \includegraphics[height=4cm]{imgs/spectrum_a1.pdf}
-  \includegraphics[height=4cm]{imgs/rabi_flop_a1_0.png}
-  \includegraphics[height=4cm]{imgs/rabi_flop_a1_p1.png}
+  \includegraphics[height=4cm]{imgs/rabi_flop_a1_0.pdf}
+  \includegraphics[height=4cm]{imgs/rabi_flop_a1_p1.pdf}
   \caption{(A) (B) \label{f-axial}}

### 2017-05-29 presentations/na_cool_paper/paper.tex
[presentations/na_cool_paper] caption 3 and 4

@@
 \begin{figure*}
-  \includegraphics[height=4cm]{imgs/spectrum_r.pdf}
-  \includegraphics[height=4cm]{imgs/rabi_flop_r3_0.pdf}
-  \includegraphics[height=4cm]{imgs/rabi_flop_r3_p1.pdf}
-  \caption{(A) (B) \label{f-radial}}
-\end{figure*}
-\begin{figure*}
-  \includegraphics[height=4cm]{imgs/spectrum_a1.pdf}
-  \includegraphics[height=4cm]{imgs/rabi_flop_a1_0.pdf}
-  \includegraphics[height=4cm]{imgs/rabi_flop_a1_p1.pdf}
-  \caption{(A) (B) \label{f-axial}}
+  \includegraphics[height=4.3cm]{imgs/spectrum_r.pdf}
+  \includegraphics[height=4.3cm]{imgs/rabi_flop_r3_0.pdf}
+  \includegraphics[height=4.3cm]{imgs/rabi_flop_r3_p1.pdf}
+  \caption{Radial Raman sideband spectrum of first order heating, first order cooling and
+    second order cooling (A) before and (B) after Raman sideband cooling.
+    Rabi flopping on axis 3 (C) carrier and (D) first order heating sideband
+    after cooling.
+    Solid lines in (C) and (D) are theoretical fit with a ground state probability of $????\%$.
+    Horizontal dashed lines in (A) to (D) are total survival and detection efficiency.
+    \label{f-radial}}
 \end{figure*}
@@
 showing good agreement between the two methods.
+\begin{figure*}
+  \includegraphics[height=4.3cm]{imgs/spectrum_a1.pdf}
+  \includegraphics[height=4.3cm]{imgs/rabi_flop_a1_0.pdf}
+  \includegraphics[height=4.3cm]{imgs/rabi_flop_a1_p1.pdf}
+  \caption{Axial Raman sideban spectrum from first order heating to eighth order cooling
+    (A) before and (B) after Raman sideband cooling.
+    Rabi flopping on axial (C) carrier and (D) first order heating sideband
+    after cooling.
+    Solid lines in (C) and (D) are theoretical fit with a ground state probability of $????\%$.
+    Horizontal dashed lines in (C) and (D) are total survival and detection efficiency.
+    \label{f-axial}}
+\end{figure*}
 

### 2017-05-29 presentations/na_cool_paper/paper.tex
[presentations/na_cool_paper] typos

@@
     The four axial pulses are addressing two neighboring cooling orders.
-    The two pulses in each radial directions are either addressing two neighbering cooling orders
+    The two pulses in each radial directions are either addressing two neighboring cooling orders
     or having different length on the first order when most of the population are below $n=3$
@@
     The range plotted covers $99\%$ of the initial thermal distribution.
-    (A) Matrix elements for Raman transition in the axial direction showing diviation from
+    (A) Matrix elements for Raman transition in the axial direction showing deviation from
     $\sqrt{n}$ scaling and multiple minimums for different sideband orders.
@@
 which has already been demonstrated with heavy alkali atoms including rubidium and cesium.
-However, some of the important properties of previous experiements,
+However, some of the important properties of previous experiments,
 for example low initial temperature and small Lamb-Dicke parameter,
@@
 trapped in optical tweezers to the motional ground state with Raman sideband cooling.
-Dispite having a large Lamb-Dicke parameter and high initial temperature,
+Despite having a large Lamb-Dicke parameter and high initial temperature,
 by utilizing several new cooling techniques and a well optimized cooling sequence,
@@
   \includegraphics[height=4.3cm]{imgs/rabi_flop_a1_p1.pdf}
-  \caption{Axial Raman sideban spectrum from first order heating to eighth order cooling
+  \caption{Axial Raman sideband spectrum from first order heating to eighth order cooling
     (A) before and (B) after Raman sideband cooling.
@@
 The ground state probability calculated from this spectrum is $????$.
-We can also use Rabi flopping on the carrier and heating sideband to varify this result
+We can also use Rabi flopping on the carrier and heating sideband to verify this result
 similar to the radial direction. In this case, we see very good agreement on the carrier

### 2017-06-09 presentations/grc-2017/plot_rabi_flop.jl
[presentations/grc-2017] Replot axial Rabi with comparison between with and without decoherence

@@ -286,7 +286,9 @@ maybe_save("$(prefix)_a1_0")
 
 figure(figsize=[1.4, 1] * 4.8)
 plot_f1(f_a1, ts_a1_p1, 2π / τ_a1 * (meles_a1_p1[1:3] * meles_r3_0[1:3]'),
-        p_a1 * p_r3', δΩ_a1, color="darkslateblue", label="Fit")
+        p_a1 * p_r3', 0, color="darkslateblue", label="Fit")
+plot_f1(f_a1, ts_a1_p1, 2π / τ_a1 * (meles_a1_p1[1:3] * meles_r3_0[1:3]'),
+        p_a1 * p_r3', δΩ_a1, color="g", label="Decohere")
 plot_data(data_after_a1_p1, 1, fmt="bo", label="With RSC")
 plot_data(data_before_a1_p1, 1, fmt="ro-", label="No RSC")
 ylim([0, 1])
@@ -294,7 +296,7 @@ xlim([ts_a1_p1[1] * 1e6, ts_a1_p1[end] * 1e6])
 xlabel("Time (\$\\mu s\$)")
 ylabel("Normalized survival")
 title("Axis 1 (axial) heating")
-legend(loc=1)
+legend(loc=1, ncol=2, mode="expand")
 grid()
 maybe_save("$(prefix)_a1_p1")
 

### 2017-07-31 presentations/2017-08-02_shutdown/checklist.tex
[presentations/2017-08-02_shutdown] WIP shutdown list

\documentclass[10pt,fleqn,twocolumn]{article}
% \usepackage[journal=rsc]{chemstyle}
% \usepackage{mhchem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{esint}
\usepackage{bbm}
\usepackage{amscd}
\usepackage{picinpar}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{tikz-3dplot}
\usepackage{indentfirst}
\usepackage{wrapfig}
\usepackage{units}
\usepackage{textcomp}
\usepackage[utf8x]{inputenc}
% \usepackage{feyn}
\usepackage{feynmp}
\usepackage{xkeyval}
\usepackage{xargs}
\usepackage{verbatim}
\usepackage{pgfplots}
\usepackage{hyperref}
\usetikzlibrary{
  arrows,
  calc,
  decorations.pathmorphing,
  decorations.pathreplacing,
  decorations.markings,
  fadings,
  positioning,
  shapes
}

\DeclareGraphicsRule{*}{mps}{*}{}
\newcommand{\ud}{\mathrm{d}}
\newcommand{\ue}{\mathrm{e}}
\newcommand{\ui}{\mathrm{i}}
\newcommand{\res}{\mathrm{Res}}
\newcommand{\Tr}{\mathrm{Tr}}
\newcommand{\dsum}{\displaystyle\sum}
\newcommand{\dprod}{\displaystyle\prod}
\newcommand{\dlim}{\displaystyle\lim}
\newcommand{\dint}{\displaystyle\int}
\newcommand{\fsno}[1]{{\!\not\!{#1}}}
\newcommand{\eqar}[1]
{
  \begin{align*}
    #1
  \end{align*}
}
\newcommand{\texp}[2]{\ensuremath{{#1}\times10^{#2}}}
\newcommand{\dexp}[2]{\ensuremath{{#1}\cdot10^{#2}}}
\newcommand{\eval}[2]{{\left.{#1}\right|_{#2}}}
\newcommand{\paren}[1]{{\left({#1}\right)}}
\newcommand{\lparen}[1]{{\left({#1}\right.}}
\newcommand{\rparen}[1]{{\left.{#1}\right)}}
\newcommand{\abs}[1]{{\left|{#1}\right|}}
\newcommand{\sqr}[1]{{\left[{#1}\right]}}
\newcommand{\crly}[1]{{\left\{{#1}\right\}}}
\newcommand{\angl}[1]{{\left\langle{#1}\right\rangle}}
\newcommand{\tpdiff}[4][{}]{{\paren{\frac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}}_{#4}}}
\newcommand{\tpsdiff}[4][{}]{{\paren{\frac{\partial^{#1}}{\partial {#3}{}^{#1}}{#2}}_{#4}}}
\newcommand{\pdiff}[3][{}]{{\frac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}}}
\newcommand{\diff}[3][{}]{{\frac{\ud^{#1} {#2}}{\ud {#3}{}^{#1}}}}
\newcommand{\psdiff}[3][{}]{{\frac{\partial^{#1}}{\partial {#3}{}^{#1}} {#2}}}
\newcommand{\sdiff}[3][{}]{{\frac{\ud^{#1}}{\ud {#3}{}^{#1}} {#2}}}
\newcommand{\tpddiff}[4][{}]{{\left(\dfrac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}\right)_{#4}}}
\newcommand{\tpsddiff}[4][{}]{{\paren{\dfrac{\partial^{#1}}{\partial {#3}{}^{#1}}{#2}}_{#4}}}
\newcommand{\pddiff}[3][{}]{{\dfrac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}}}
\newcommand{\ddiff}[3][{}]{{\dfrac{\ud^{#1} {#2}}{\ud {#3}{}^{#1}}}}
\newcommand{\psddiff}[3][{}]{{\frac{\partial^{#1}}{\partial{}^{#1} {#3}} {#2}}}
\newcommand{\sddiff}[3][{}]{{\frac{\ud^{#1}}{\ud {#3}{}^{#1}} {#2}}}
\usepackage{fancyhdr}
\usepackage{multirow}
\usepackage{fontenc}
% \usepackage{tipa}
\usepackage{ulem}
\usepackage{color}
\usepackage{cancel}
\newcommand{\hcancel}[2][black]{\setbox0=\hbox{#2}%
  \rlap{\raisebox{.45\ht0}{\textcolor{#1}{\rule{\wd0}{1pt}}}}#2}
\pagestyle{fancy}
\setlength{\headheight}{67pt}
\fancyhead{}
\fancyfoot{}
\fancyfoot[C]{\thepage}
\fancyhead[R]{}
\renewcommand{\footruleskip}{0pt}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0pt}

\newcommand\pgfmathsinandcos[3]{%
  \pgfmathsetmacro#1{sin(#3)}%
  \pgfmathsetmacro#2{cos(#3)}%
}
\newcommand\LongitudePlane[3][current plane]{%
  \pgfmathsinandcos\sinEl\cosEl{#2} % elevation
  \pgfmathsinandcos\sint\cost{#3} % azimuth
  \tikzset{#1/.estyle={cm={\cost,\sint*\sinEl,0,\cosEl,(0,0)}}}
}
\newcommand\LatitudePlane[3][current plane]{%
  \pgfmathsinandcos\sinEl\cosEl{#2} % elevation
  \pgfmathsinandcos\sint\cost{#3} % latitude
  \pgfmathsetmacro\yshift{\cosEl*\sint}
  \tikzset{#1/.estyle={cm={\cost,0,0,\cost*\sinEl,(0,\yshift)}}} %
}
\newcommand\DrawLongitudeCircle[2][1]{
  \LongitudePlane{\angEl}{#2}
  \tikzset{current plane/.prefix style={scale=#1}}
  % angle of "visibility"
  \pgfmathsetmacro\angVis{atan(sin(#2)*cos(\angEl)/sin(\angEl))} %
  \draw[current plane] (\angVis:1) arc (\angVis:\angVis+180:1);
  \draw[current plane,dashed] (\angVis-180:1) arc (\angVis-180:\angVis:1);
}
\newcommand\DrawLatitudeCircleArrow[2][1]{
  \LatitudePlane{\angEl}{#2}
  \tikzset{current plane/.prefix style={scale=#1}}
  \pgfmathsetmacro\sinVis{sin(#2)/cos(#2)*sin(\angEl)/cos(\angEl)}
  % angle of "visibility"
  \pgfmathsetmacro\angVis{asin(min(1,max(\sinVis,-1)))}
  \draw[current plane,decoration={markings, mark=at position 0.6 with {\arrow{<}}},postaction={decorate},line width=.6mm] (\angVis:1) arc (\angVis:-\angVis-180:1);
  \draw[current plane,dashed,line width=.6mm] (180-\angVis:1) arc (180-\angVis:\angVis:1);
}
\newcommand\DrawLatitudeCircle[2][1]{
  \LatitudePlane{\angEl}{#2}
  \tikzset{current plane/.prefix style={scale=#1}}
  \pgfmathsetmacro\sinVis{sin(#2)/cos(#2)*sin(\angEl)/cos(\angEl)}
  % angle of "visibility"
  \pgfmathsetmacro\angVis{asin(min(1,max(\sinVis,-1)))}
  \draw[current plane] (\angVis:1) arc (\angVis:-\angVis-180:1);
  \draw[current plane,dashed] (180-\angVis:1) arc (180-\angVis:\angVis:1);
}
\newcommand\coil[1]{
  {\rh * cos(\t * pi r)}, {\apart * (2 * #1 + \t) + \rv * sin(\t * pi r)}
}
\makeatletter
\define@key{DrawFromCenter}{style}[{->}]{
  \tikzset{DrawFromCenterPlane/.style={#1}}
}
\define@key{DrawFromCenter}{r}[1]{
  \def\@R{#1}
}
\define@key{DrawFromCenter}{center}[(0, 0)]{
  \def\@Center{#1}
}
\define@key{DrawFromCenter}{theta}[0]{
  \def\@Theta{#1}
}
\define@key{DrawFromCenter}{phi}[0]{
  \def\@Phi{#1}
}
\presetkeys{DrawFromCenter}{style, r, center, theta, phi}{}
\newcommand*\DrawFromCenter[1][]{
  \setkeys{DrawFromCenter}{#1}{
    \pgfmathsinandcos\sint\cost{\@Theta}
    \pgfmathsinandcos\sinp\cosp{\@Phi}
    \pgfmathsinandcos\sinA\cosA{\angEl}
    \pgfmathsetmacro\DX{\@R*\cost*\cosp}
    \pgfmathsetmacro\DY{\@R*(\cost*\sinp*\sinA+\sint*\cosA)}
    \draw[DrawFromCenterPlane] \@Center -- ++(\DX, \DY);
  }
}
\newcommand*\DrawFromCenterText[2][]{
  \setkeys{DrawFromCenter}{#1}{
    \pgfmathsinandcos\sint\cost{\@Theta}
    \pgfmathsinandcos\sinp\cosp{\@Phi}
    \pgfmathsinandcos\sinA\cosA{\angEl}
    \pgfmathsetmacro\DX{\@R*\cost*\cosp}
    \pgfmathsetmacro\DY{\@R*(\cost*\sinp*\sinA+\sint*\cosA)}
    \draw[DrawFromCenterPlane] \@Center -- ++(\DX, \DY) node {#2};
  }
}
\makeatother
\tikzstyle{snakearrow} = [decorate, decoration={pre length=0.2cm,
  post length=0.2cm, snake, amplitude=.4mm,
  segment length=2mm},thick, ->]
%% document-wide tikz options and styles
\tikzset{%
  >=latex, % option for nice arrows
  inner sep=0pt,%
  outer sep=2pt,%
  mark coordinate/.style={inner sep=0pt,outer sep=0pt,minimum size=3pt,
    fill=black,circle}%
}
\addtolength{\hoffset}{-1.3cm}
\addtolength{\voffset}{-2cm}
\addtolength{\textwidth}{3cm}
\addtolength{\textheight}{2.5cm}
\renewcommand{\footskip}{10pt}
\setlength{\headwidth}{\textwidth}
\setlength{\headsep}{20pt}
\setlength{\marginparwidth}{0pt}

\makeatletter
\newcommand\ColorBox[2]{
  \begin{tikzpicture}
    \fill[#1] (0, 0) rectangle (\f@size/25, \f@size/25);
    \path (\f@size/50, \f@size/50) node[color=black!15] {\small #2};
  \end{tikzpicture}
}
\newcommand\DevBoxes{{\Large\ColorBox{color=red!50}{Off}\!\!\ColorBox{color=green!50}{On}}}
\newcommand\OffBox{{\normalsize\ColorBox{color=orange!50}{}}}
\newcommand\OnBox{{\normalsize\ColorBox{color=cyan!50}{}}}
\makeatother

\newcommand\DevHeader[1]{{\Large\DevBoxes\textbf{#1}\\}}
\def\arraystretch{2}

\parindent=0pt
\title{Checklist}
\date{August 2nd, 2017}
\begin{document}

\begin{itemize}
\item\DevHeader{1.0 Camera}
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Switch off
  \item\OffBox Switch off chiller
  \item\OffBox Unplug camera power (zip tie to camera)
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug in camera power
  \item\OnBox Switch on chiller
  \item\OnBox Switch on
  \end{itemize}
\item\DevHeader{1.5 Camera}
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Switch off
  \item\OffBox Switch off chiller
  \item\OffBox Unplug camera power (zip tie to camera)
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug in camera power
  \item\OnBox Switch on chiller
  \item\OnBox Switch on
  \end{itemize}
\item\DevHeader{Tweezer 1 computer}
  \textbf{Check following devices}
  \begin{itemize}
  \item\OnBox Thorlabs cameras
  \item\OnBox Na Raman amplifier
  \end{itemize}
\item\DevHeader{Tweezer 2 computer}
  \textbf{Check following devices}
  \begin{itemize}
  \item\OnBox Andor camera
  \end{itemize}
\item\DevHeader{Tweezer 3 computer}
  \textbf{Check following devices}
  \begin{itemize}
  \item\OnBox Software radio
  \end{itemize}
\item\DevHeader{Tweezer 4 computer}
  \textbf{Check following devices}
  \begin{itemize}
  \item\OnBox Andor camera
  \item\OnBox Thorlabs camera
  \end{itemize}
\item\DevHeader{1.0 Cs MOT PLL}
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug all signals (zip tie together)
  \item\OffBox Unplug 15V and 5V powers (zip tie together)
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plugin 15V and 5V powers
  \item\OnBox Plugin all signals
  \item\OnBox Apply settings according to note on Generic tab, Equipment Settings.
  \end{itemize}
\item\DevHeader{1.0 Cs Raman PLL}
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug all signals (zip tie together)
  \item\OffBox Unplug 15V and 5V powers (zip tie together)
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plugin 15V and 5V powers
  \item\OnBox Plugin all signals
  \item\OnBox Apply settings according to note on Generic tab, Equipment Settings.
  \end{itemize}
\item\DevHeader{1.5 Cs MOT PLL}
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug all signals (zip tie together)
  \item\OffBox Unplug 15V and 5V powers (zip tie together)
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plugin 15V and 5V powers
  \item\OnBox Plugin all signals
  \item\OnBox Apply settings ???
  \end{itemize}
\item\DevHeader{1.5 Feshbach coils}
  \textbf{Before power shutdown}
  \begin{itemize}
  \item\OffBox Wrap exposed part in napkins to prevent condensations
  \end{itemize}
\item\DevHeader{1.5 IGBT}
  \textbf{Before power shutdown}
  \begin{itemize}
  \item\OffBox Wrap exposed part in napkins to prevent condensations
  \end{itemize}
\item\DevHeader{1.0 computer control box}
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox (Do following three steps quickly)
  \item\OffBox Turn off the box by flipping the switch on the front side of the box
  \item\OffBox Unplug the high voltage (48V) power supply (circular plug)
    on the front side of the box. Then unplug the power supply itself fromm the outlet.
  \item\OffBox Unplug the 12V board power supply.
    (L.T.E. one with a rectangular connector in the front)
  \item\OffBox Unplug USB power on the front side near the fan.
  \item\OffBox Zip tie the three unpluged powers to the computer control box.
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Connect to 3.5G Windfrek clock generator from Tweezer1.
    Set frequency to 3.5G and amplitude to max.
  \item\OnBox (Remove power connection zip ties and) Plug in USB power supply.
  \item\OnBox (Do following three steps quickly)
  \item\OnBox Plug in the 12V board power supply.
  \item\OnBox Plug in high voltage power supply.
  \item\OnBox Turn on the power switch of the box. The fans should start spinning.
  \end{itemize}
\item\DevHeader{1.5 computer control box}
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox (Do following three steps quickly)
  \item\OffBox Turn off the box by flipping the switch on the front side of the box
  \item\OffBox Unplug the high voltage (48V) power supply (circular plug)
    on the left side of the box. Then unplug the power supply itself fromm the outlet.
  \item\OffBox Unplug the 12V board power supply.
    (L.T.E. one with a rectangular connector in the front)
  \item\OffBox Unplug USB power on the front side near the fan.
  \item\OffBox Zip tie the three unpluged powers to the computer control box.
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Connect to 3.5G Windfrek clock generator from Tweezer1.
    Set frequency to 3.5G and amplitude to max.
  \item\OnBox (Remove power connection zip ties and) Plug in USB power supply.
  \item\OnBox (Do following three steps quickly)
  \item\OnBox Plug in the 12V board power supply.
  \item\OnBox Plug in high voltage power supply. The fans should start spinning.
  \item\OnBox Turn on the power switch of the box.
  \end{itemize}
\item\DevHeader{Cs 1.0 MOT home built temperature servo}
  \textbf{1st level above Cs tweezer/MOT lasers}\\
  Switch off/on the front switch
\item\DevHeader{Benchtop power supply}
  \textbf{1st level above Cs tweezer/MOT lasers}\\
  Record voltage/current values:\\
  \begin{tabular}{|c|c|}
    \hline
    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
    Left Current&\\\hline
    Right Voltage&\\\hline
    Right Current&\\\hline
  \end{tabular}\\
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug loads
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Turn off the power supply
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into the wall
  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
  \item\OnBox Plug the load back in
  \end{itemize}
\item\DevHeader{1st version Till's current controller for Cs MOT}
  \textbf{1st level above Cs tweezer/MOT lasers}\\
  Record current value:\\
  \begin{tabular}{|c|c|}
    \hline
    Current&\hphantom{\hspace{3.5cm}}\\\hline
  \end{tabular}\\
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off
  \item\OffBox Unplug power (zip tie to controller)
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug in power
  \item\OnBox Turn on
  \end{itemize}
\item\DevHeader{Homebuilt $\pm15,5$V power supply}
  \textbf{2nd level above Cs tweezer/MOT lasers}\\
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug load
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Switch off on the back
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Switch on
  \item\OnBox Plug the load back in
  \end{itemize}
\end{itemize}

\end{document}

### 2017-08-01 presentations/2017-08-02_shutdown/checklist.tex
[presentations/2017-08-02_shutdown] WIP shutdown list

@@
 }
-\newcommand\DevBoxes{{\Large\ColorBox{color=red!50}{Off}\!\!\ColorBox{color=green!50}{On}}}
+\newcommand\DevBoxes{\mbox{{\Large\ColorBox{color=red!50}{Off}\!\!\ColorBox{color=green!50}{On}}}}
 \newcommand\OffBox{{\normalsize\ColorBox{color=orange!50}{}}}
@@
   Record voltage/current values:\\
+
   \begin{tabular}{|c|c|}
@@
   \end{tabular}\\
+
   \textbf{Turn off check list}
@@
   Record current value:\\
+
   \begin{tabular}{|c|c|}
@@
   \end{itemize}
+\item\DevHeader{Cs 1.0 MOT lock box}
+  \textbf{1st level above Cs MOT lasers}
+  \begin{itemize}
+  \item\OffBox Make sure the laser is unlocked.
+  \end{itemize}
+\item\DevHeader{Novatech function generator}
+  \textbf{1st level above Cs MOT lasers}
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Save settings
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Restore settings
+  \end{itemize}\vspace{1cm}
+\item\DevHeader{New Focus Cs Raman lasers drivers (2x)}
+  \textbf{1st level above Cs Raman lasers}\\
+  Record Temperature, Current, Piezo voltage\\
+  Temperature is accessible in the menu under system status\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    F3 Current&\hphantom{\hspace{3.5cm}}\\\hline
+    F3 Piezo Voltage&\\\hline
+    F3 Temperature&\\\hline
+    F4 Current&\\\hline
+    F4 Piezo Voltage&\\\hline
+    F4 Temperature&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off
+  \item\OffBox Unplug power
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug in power
+  \item\OnBox (Turn on)
+  \end{itemize}
+\item\DevHeader{Benchtop power supply}
+  \textbf{1st level next to Cs Raman driver}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    Current&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug loads
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Turn off the power supply
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
+  \item\OnBox Plug the load back in
+  \end{itemize}
+\item\DevHeader{Homebuilt $24$V power supply}
+  \textbf{2nd level above Cs Raman lasers}\\
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug load
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Switch off on the back
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Switch on
+  \item\OnBox Plug the load back in
+  \end{itemize}
+\item\DevHeader{SRS shutter driver}
+  \textbf{1st level above Cs Raman lasers}\\
+  Switch off/on with the switch on the back.
+\item\DevHeader{New Focus lock box for Cs Raman}
+  \textbf{1st level above Cs Raman lasers}\\
+  Unplug power.
+\item\DevHeader{Timebase driver for Na Raman and Na D2 (x2)}
+  \textbf{1st level above Na Raman and D2 seed lasers}\\
+  Record current and T1 settings\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Raman Current&\hphantom{\hspace{3.5cm}}\\\hline
+    Raman T1&\\\hline
+    MOT Current&\hphantom{\hspace{3.5cm}}\\\hline
+    MOT T1&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off
+  \item\OffBox Unplug power
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug in power
+  \item\OnBox Turn on
+  \item\OnBox Set current/temperature.
+  \item\OnBox Enable T1 survo
+  \item\OnBox Turn on current
+  \end{itemize}
+\item\DevHeader{Thorlabs temperature controller for Na Raman doubler}
+  \textbf{1st level above Na Raman and D2 seed lasers}\\
+  Record temperature settings\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Setpoint&\hphantom{\hspace{3.5cm}}\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off
+  \item\OffBox Unplug power
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug in power
+  \item\OnBox Check temperature setting
+  \item\OnBox Turn on
+  \end{itemize}
 \end{itemize}

### 2017-08-01 presentations/2017-08-02_shutdown/checklist.tex
[presentations/2017-08-02_shutdown] improve format

@@
 
+\newcommand\DevDef[2]{
+  \begin{minipage}{\linewidth}
+    \begin{itemize}
+    \item\DevHeader{#1}
+      #2
+    \end{itemize}
+    \vspace{0.8cm}
+  \end{minipage}
+}
+
 \parindent=0pt
@@
 
-\begin{itemize}
-\item\DevHeader{1.0 Camera}
+\DevDef{1.0 Camera}{
   \textbf{Turn off check list}
@@
   \end{itemize}
-\item\DevHeader{1.5 Camera}
+}
+\DevDef{1.5 Camera}{
   \textbf{Turn off check list}
@@
   \end{itemize}
-\item\DevHeader{Tweezer 1 computer}
+}
+\DevDef{Tweezer 1 computer}{
   \textbf{Check following devices}
@@
   \end{itemize}
-\item\DevHeader{Tweezer 2 computer}
+}
+\DevDef{Tweezer 2 computer}{
   \textbf{Check following devices}
@@
   \end{itemize}
-\item\DevHeader{Tweezer 3 computer}
+}
+\DevDef{Tweezer 3 computer}{
   \textbf{Check following devices}
@@
   \end{itemize}
-\item\DevHeader{Tweezer 4 computer}
+}
+\DevDef{Tweezer 4 computer}{
   \textbf{Check following devices}
@@
   \end{itemize}
-\item\DevHeader{1.0 Cs MOT PLL}
+}
+\DevDef{1.0 Cs MOT PLL}{
   \textbf{Turn off check list}
@@
   \end{itemize}
-\item\DevHeader{1.0 Cs Raman PLL}
+}
+\DevDef{1.0 Cs Raman PLL}{
   \textbf{Turn off check list}
@@
   \end{itemize}
-\item\DevHeader{1.5 Cs MOT PLL}
+}
+\DevDef{1.5 Cs MOT PLL}{
   \textbf{Turn off check list}
@@
   \end{itemize}
-\item\DevHeader{1.5 Feshbach coils}
+}
+\DevDef{1.5 Feshbach coils}{
   \textbf{Before power shutdown}
@@
   \end{itemize}
-\item\DevHeader{1.5 IGBT}
+}
+\DevDef{1.5 IGBT}{
   \textbf{Before power shutdown}
@@
   \end{itemize}
-\item\DevHeader{1.0 computer control box}
+}
+\DevDef{1.0 computer control box}{
   \textbf{Turn off check list}
@@
   \end{itemize}
-\item\DevHeader{1.5 computer control box}
+}
+\DevDef{1.5 computer control box}{
   \textbf{Turn off check list}
@@
   \end{itemize}
-\item\DevHeader{Cs 1.0 MOT home built temperature servo}
+}
+\DevDef{Cs 1.0 MOT home built temperature servo}{
   \textbf{1st level above Cs tweezer/MOT lasers}\\
   Switch off/on the front switch
-\item\DevHeader{Benchtop power supply}
+}
+\DevDef{Benchtop power supply}{
   \textbf{1st level above Cs tweezer/MOT lasers}\\
@@
   \end{itemize}
-\item\DevHeader{1st version Till's current controller for Cs MOT}
+}
+\DevDef{1st version Till's current controller for Cs MOT}{
   \textbf{1st level above Cs tweezer/MOT lasers}\\
@@
   \end{itemize}
-\item\DevHeader{Homebuilt $\pm15,5$V power supply}
+}
+\DevDef{Homebuilt $\pm15,5$V power supply}{
   \textbf{2nd level above Cs tweezer/MOT lasers}\\
@@
   \end{itemize}
-\item\DevHeader{Cs 1.0 MOT lock box}
+}
+\DevDef{Cs 1.0 MOT lock box}{
   \textbf{1st level above Cs MOT lasers}
@@
   \end{itemize}
-\item\DevHeader{Novatech function generator}
+}
+\DevDef{Novatech function generator}{
   \textbf{1st level above Cs MOT lasers}
@@
   \end{itemize}\vspace{1cm}
-\item\DevHeader{New Focus Cs Raman lasers drivers (2x)}
+}
+\DevDef{New Focus Cs Raman lasers drivers (2x)}{
   \textbf{1st level above Cs Raman lasers}\\
@@
   \end{itemize}
-\item\DevHeader{Benchtop power supply}
+}
+\DevDef{Benchtop power supply}{
   \textbf{1st level next to Cs Raman driver}\\
@@
   \end{itemize}
-\item\DevHeader{Homebuilt $24$V power supply}
+}
+\DevDef{Homebuilt $24$V power supply}{
   \textbf{2nd level above Cs Raman lasers}\\
@@
   \end{itemize}
-\item\DevHeader{SRS shutter driver}
+}
+\DevDef{SRS shutter driver}{
   \textbf{1st level above Cs Raman lasers}\\
   Switch off/on with the switch on the back.
-\item\DevHeader{New Focus lock box for Cs Raman}
+}
+\DevDef{New Focus lock box for Cs Raman}{
   \textbf{1st level above Cs Raman lasers}\\
   Unplug power.
-\item\DevHeader{Timebase driver for Na Raman and Na D2 (x2)}
+}
+\DevDef{Timebase driver for Na Raman and Na D2 (x2)}{
   \textbf{1st level above Na Raman and D2 seed lasers}\\
@@
   \end{itemize}
-\item\DevHeader{Thorlabs temperature controller for Na Raman doubler}
+}
+\DevDef{Thorlabs temperature controller for Na Raman doubler}{
   \textbf{1st level above Na Raman and D2 seed lasers}\\
@@
   \end{itemize}
-\end{itemize}
+}
 

### 2017-08-01 presentations/2017-08-02_shutdown/checklist.tex
[presentations/2017-08-02_shutdown] WIP spliting list

@@
 }
+\newcommand\Person[1]{
+\clearpage
+\section{#1}
+\fancyhead[R]{#1}
+\setcounter{page}{1}
+For shutting off, go through the checklist in the following order
+\begin{itemize}
+\item\OffBox Turn off equipments
+\item\OffBox Turn off power supplies
+\item\OffBox Turn off computers
+\end{itemize}
+Wait before everyone else finish their corresponding steps before starting the next one.\\
+For powering up, go through the checklist in the following order
+\begin{itemize}
+\item\OnBox Turn on computers
+\item\OnBox Turn on power supplies
+\item\OnBox Turn on equipments
+\item\OnBox Check computer connection to devices
+\end{itemize}
+Also wait before everyone else finish their corresponding steps before starting the next one.
+}
 
@@
 
-\DevDef{1.0 Camera}{
+\Person{Yichao}
+\section{Equipments}
+\section{Power supplies}
+\section{Computers}
+\Person{Jon}
+\section{Equipments}
+\section{Power supplies}
+\section{Computers}
+\Person{Lee}
+\section{Equipments}
+\section{Power supplies}
+\section{Computers}
+\Person{Jessie}
+\section{Equipments}
+\section{Power supplies}
+\section{Computers}
+\Person{Frederic}
+\section{Equipments}
+\section{Power supplies}
+\section{Computers}
+
+\DevDef{Andor Camera for 1.0}{
   \textbf{Turn off check list}
@@
 }
-\DevDef{1.5 Camera}{
+\DevDef{Andor Camera for 1.5}{
   \textbf{Turn off check list}
@@
 }
-\DevDef{1.0 Cs MOT PLL}{
+\DevDef{PLL for 1.0 Cs MOT}{
   \textbf{Turn off check list}
@@
 }
-\DevDef{1.0 Cs Raman PLL}{
+\DevDef{PLL for 1.0 Cs Raman}{
   \textbf{Turn off check list}
@@
 }
-\DevDef{1.5 Cs MOT PLL}{
+\DevDef{PLL for 1.5 Cs MOT}{
   \textbf{Turn off check list}
@@
 }
-\DevDef{1.0 computer control box}{
+\DevDef{Computer control box for 1.0}{
   \textbf{Turn off check list}
@@
 }
-\DevDef{1.5 computer control box}{
+\DevDef{Computer control box for 1.5}{
   \textbf{Turn off check list}
@@
 }
-\DevDef{Cs 1.0 MOT home built temperature servo}{
+\DevDef{Homebuilt temperature servo for Cs 1.0 MOT}{
   \textbf{1st level above Cs tweezer/MOT lasers}\\
@@
   \item\OnBox Restore settings
-  \end{itemize}\vspace{1cm}
+  \end{itemize}
 }
@@
 }
-\DevDef{SRS shutter driver}{
+\DevDef{SRS shutter driver for Cs}{
   \textbf{1st level above Cs Raman lasers}\\
@@
   Unplug power.
+}
+\DevDef{Benchtop power supply for Cs Raman locking}{
+  \textbf{2nd level above Cs Raman lockbox}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    Current&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug loads
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Turn off the power supply
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
+  \item\OnBox Plug the load back in
+  \end{itemize}
 }
@@
 }
+\DevDef{Homebuilt lockbox for Na D2}{
+  \textbf{1st level above Na seed}\\
+  \textbf{Turn on-off together with the adjustable high voltage power supply above}\\
+  Record high voltage power supply output
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unlock
+  \item\OffBox Turn down the voltage of the high voltage power supply to 0
+  \item\OffBox Unplug high voltage power on lockbox (zip tie)
+  \item\OffBox Unplug 15V from lockbox (zip tie)
+  \item\OffBox Turn off high voltage power supply
+  \item\OffBox Unplug high voltage power supply from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug high voltage power supply into the wall
+  \item\OnBox Turn on high voltage power supply (make sure the output is 0)
+  \item\OnBox Plug in 15V to lockbox
+  \item\OnBox Plug in high voltage to lockbox
+  \item\OnBox Turn up the voltage of the high voltage power supply
+  \item\OnBox Check HV output
+  \end{itemize}
+}
+\DevDef{Oscilloscope for Na D2 lock}{
+  \textbf{1st level above Na Raman amplifier}
+  \begin{itemize}
+  \item\OffBox Unplug from wall
+  \end{itemize}
+}
+\DevDef{MPB Raman amplifier}{
+  \textbf{1st level above Na MOT beam path}\\
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Power off
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into wall
+  \item\OnBox Power on
+  \end{itemize}
+}
+\DevDef{Variac for Na cell}{
+  \textbf{Above Na D2 beam path}\\
+  Record temperature and voltage settings\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    Temperature&\hphantom{\hspace{3.5cm}}\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn voltage to 0
+  \item\OffBox Switch off
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into wall
+  \item\OnBox Switch on
+  \item\OnBox Turn the voltage up \textbf{SLOWLY} and monitor the temperature at the same time.
+  \end{itemize}
+}
+\DevDef{SRS shutter driver for Na}{
+  \textbf{1st level above Na D2 beam path, below Variac}\\
+  Switch off/on with the switch on the back.
+}
+\DevDef{Benchtop power supply}{
+  \textbf{2nd level above Na Variac}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    Left Current&\\\hline
+    Right Voltage&\\\hline
+    Right Current&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug loads
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Turn off the power supply
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+\DevDef{Homebuilt lockbox for Na D1}{
+  \textbf{1st level above Na D2 beam path}\\
+  \textbf{Turn on-off together with the fixed high voltage power supply above}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unlock
+  \item\OffBox Unplug high voltage power on lockbox (zip tie)
+  \item\OffBox Unplug 15V from lockbox (zip tie)
+  \item\OffBox Unplug high voltage power supply from walls
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug high voltage power supply into the wall
+  \item\OnBox Plug in 15V to lockbox
+  \item\OnBox Plug in high voltage to lockbox
+  \item\OnBox Check HV output
+  \end{itemize}
+}
+\DevDef{Thorlabs temperature controller for Na D1 doubler}{
+  \textbf{1st level above Na D1}\\
+  Record temperature settings\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Setpoint&\hphantom{\hspace{3.5cm}}\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off
+  \item\OffBox Unplug power
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug in power
+  \item\OnBox Check temperature setting
+  \item\OnBox Turn on
+  \end{itemize}
+}
+\DevDef{Thorlabs temperature controller for Na D1 seed}{
+  \textbf{1st level above Na D1 seed}\\
+  Record temperature settings\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Setpoint&\hphantom{\hspace{3.5cm}}\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off
+  \item\OffBox Unplug power
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug in power
+  \item\OnBox Check temperature setting
+  \item\OnBox Turn on
+  \end{itemize}
+}
+\DevDef{Thorlabs current controller for Na D1 seed}{
+  \textbf{1st level above Na D1 seed}\\
+  Record current settings\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Current&\hphantom{\hspace{3.5cm}}\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off
+  \item\OffBox Unplug power
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug in power
+  \item\OnBox Check current setting
+  \item\OnBox Turn on
+  \end{itemize}
+}
+\DevDef{Benchtop power supply}{
+  \textbf{2nd level above Na D1 seed controllers}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    Left Current&\\\hline
+    Right Voltage&\\\hline
+    Right Current&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug loads
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Turn off the power supply
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+\DevDef{Homebuilt $24$V power supply}{
+  \textbf{2nd level above Cs tweezer controllers}\\
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug load
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Switch off on the back
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Switch on
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+\DevDef{Benchtop power supply}{
+  \textbf{2nd level above Cs tweezer, right of 24V power supply}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    Left Current&\\\hline
+    Right Voltage&\\\hline
+    Right Current&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug loads
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Turn off the power supply
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+\DevDef{Homebuilt temperature servo for Cs tweezer}{
+  \textbf{1st level above Cs tweezer}\\
+  Switch off/on the front switch
+}
+\DevDef{2nd version Till's current controller for Cs Tweezer}{
+  \textbf{1st level above Cs tweezer}\\
+  Record current value:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Current&\hphantom{\hspace{3.5cm}}\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off
+  \item\OffBox Unplug power (zip tie to controller)
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug in power
+  \item\OnBox Turn on
+  \end{itemize}
+}
+\DevDef{Thorlabs current controller}{
+  \textbf{1st level below Cs tweezer driver}\\
+  Unused\\
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off
+  \item\OffBox Unplug power
+  \end{itemize}
+}
+\DevDef{Thorlabs temperature controller for Cs tweezer}{
+  \textbf{1st level above Cs tweezer}\\
+  Record temperature settings\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Setpoint&\hphantom{\hspace{3.5cm}}\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off
+  \item\OffBox Unplug power
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug in power
+  \item\OnBox Check temperature setting
+  \item\OnBox Turn on
+  \end{itemize}
+}
+\DevDef{Intensity servo for Cs}{
+  \textbf{1st level above Cs tweezer}\\
+  Unplug power
+}
+\DevDef{Benchtop power supply}{
+  \textbf{1st level above Cs tweezer}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    Left Current&\\\hline
+    Right Voltage&\\\hline
+    Right Current&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug loads
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Turn off the power supply
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+%% Machine table facing laser table (south)
+\DevDef{2nd version Till's current controller for Cs 1.5 (x2)}{
+  \textbf{1st level above 1.5 Cs MOT}\\
+  Record current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Top Current&\hphantom{\hspace{3.5cm}}\\\hline
+    Bottom Current&\hphantom{\hspace{3.5cm}}\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off
+  \item\OffBox Unplug power (zip tie to controller)
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug in power
+  \item\OnBox Turn on
+  \end{itemize}
+}
+\DevDef{Thorlabs current controller}{
+  \textbf{1st level below Cs 1.5 MOT drivers}\\
+  Unused\\
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off
+  \item\OffBox Unplug power
+  \end{itemize}
+}
+\DevDef{Benchtop power supply}{
+  \textbf{2nd level above Cs 1.5 MOT controllers}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    Left Current&\\\hline
+    Right Voltage&\\\hline
+    Right Current&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug loads
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Turn off the power supply
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+\DevDef{Homebuilt $24$V power supply}{
+  \textbf{2nd level above Cs 1.5 MOT controllers}\\
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug load
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Switch off on the back
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Switch on
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+\DevDef{Homebuilt temperature servo for Cs 1.5 MOT (x2)}{
+  \textbf{1st level above Cs 1.5 MOT}\\
+  Switch off/on the front switch
+}
+\DevDef{Oscilloscope for Cs 1.5 MOT lock}{
+  \textbf{1st level above Cs 1.5 MOT}
+  \begin{itemize}
+  \item\OffBox Unplug from wall
+  \end{itemize}
+}
+\DevDef{Homebuilt lockbox for Cs 1.5 MOT}{
+  \textbf{1st level above Cs 1.5 MOT}\\
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unlock
+  \item\OffBox Unplug 15V from lockbox (zip tie)
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug in 15V to lockbox
+  \end{itemize}
+}
+\DevDef{Function generator for Cs MOT 1.5 lockbox}{
+  \textbf{1st level under Cs MOT 1.5 lockbox}
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Record settings
+  \item\OffBox Turn off
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into wall
+  \item\OnBox Turn on
+  \item\OnBox Restore settings
+  \end{itemize}
+}
+\DevDef{Benchtop power supply (x2)}{
+  \textbf{1st level above Na 1.5 bean path}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    Left Current&\\\hline
+    Right Voltage&\\\hline
+    Right Current&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug loads
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Turn off the power supply
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+\DevDef{Homebuilt $\pm15,5$V power supply}{
+  \textbf{2nd level above Na 1.5 beam path}\\
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug load
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Switch off on the back
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Switch on
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+\DevDef{HV amplifiers for 1.0 piezo mirrors}{
+  \textbf{Above the space beween Na 1.5 beam path and NaCs 1.5 chamber}\\
+  \textbf{Turn on-off together with the function generator below
+    and the high voltage power supply on the left}\\
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off the function generator
+  \item\OffBox Unplug function generator output (zip tie and label)
+  \item\OffBox Unplug HV power supply from the wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plugin HV power supply to the wall
+  \item\OnBox Plugin function generator output
+  \item\OnBox Turn on the function generator
+  \end{itemize}
+}
+\DevDef{Benchtop power supply (x2)}{
+  \textbf{2nd level above piezo mirror electronics}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    Left Current&\\\hline
+    Right Voltage&\\\hline
+    Right Current&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug loads
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Turn off the power supply
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+\DevDef{Pump}{
+  \textbf{1st level above NaCs 1.0 chamber}\\
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off
+  \item\OffBox Unplug from walls
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into wall
+  \item\OnBox Turn on (should be enough)
+  \end{itemize}
+}
+\DevDef{Benchtop power supply}{
+  \textbf{2nd level above NaCs 1.0 chamber}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    Left Current&\\\hline
+    Right Voltage&\\\hline
+    Right Current&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug loads
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Turn off the power supply
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+% Machine table facing the wall (north)
+\DevDef{Homebuilt $24$V power supply}{
+  \textbf{2nd level above NaCs 1.0 chamber, facing the drawers/wall}\\
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug load
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Switch off on the back
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Switch on
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+\DevDef{Benchtop power supply for dispensers}{
+  \textbf{1st level above NaCs 1.0 chamber}\\
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug loads
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Turn off the power supply
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+\DevDef{Quantel Laser}{
+  \textbf{1st level in the middle, facing 1.5 table}\\
+  Ask Frederic.
+  \vspace{1cm}
+}
+\DevDef{Intensity servo for Na}{
+  \textbf{1st level above Na tweezer, below 1.0 computer control box}\\
+  Unplug power
+}
+\DevDef{Benchtop power supply for 1.5 computer control clock}{
+  \textbf{2nd level next to 1.5 computer control box}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    Current&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug loads
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Turn off the power supply
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+\DevDef{1st version Till's current controller for butterfly laser}{
+  \textbf{1st level above TiSapph}\\
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off
+  \item\OffBox Unplug power (zip tie to controller)
+  \end{itemize}
+}
+\DevDef{Homebuilt temperature servo for butterfly laser}{
+  \textbf{1st level above TiSapph}\\
+  Switch off/on the front switch
+}
+\DevDef{Homebuilt $\pm15,5$V power supply}{
+  \textbf{2nd level above TiSapph}\\
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug load
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Switch off on the back
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Switch on
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+\DevDef{TiSapph}{
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off pump, unplug from wall
+  \item\OffBox Turn off controller, unplug from wall
+  \item\OffBox Turn off chiller, unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into wall, turn on chiller
+  \item\OnBox Plug into wall, turn on controller
+  \item\OnBox Plug into wall, turn on pump
+  \end{itemize}
+}
+\DevDef{Agilent function generator for Na 1.0 switching}{
+  \textbf{1st level above TiSapph facing computers}\\
+  Record parameters:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Ch1 Hi&\hphantom{\hspace{3.5cm}}\\\hline
+    Ch1 Lo&\\\hline
+    Ch2 Hi&\\\hline
+    Ch2 Lo&\\\hline
+  \end{tabular}\\
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into wall
+  \item\OnBox Turn on
+  \item\OnBox Set frequency, duty cycle, high/low voltages
+  \item\OnBox Set switching phase back
+  \end{itemize}
+}
+% 1.5 Rack
+\DevDef{HV amplifiers for 1.5 piezo mirrors}{
+  \textbf{Top level of 1.5 rack}\\
+  \textbf{Turn on-off together with the function generator below
+    and the high voltage power supply above the 1.0 machine table}\\
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off the function generator
+  \item\OffBox Unplug function generator output (zip tie and label)
+  \item\OffBox Unplug HV power supply from the wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plugin HV power supply to the wall
+  \item\OnBox Plugin function generator output
+  \item\OnBox Turn on the function generator
+  \end{itemize}
+}
+\DevDef{Benchtop power supply}{
+  \textbf{2nd level (from the top) 1.5 Rack. Next to coil servo}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    Left Current&\\\hline
+    Right Voltage&\\\hline
+    Right Current&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug loads
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Turn off the power supply
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+\DevDef{Benchtop power supply}{
+  \textbf{Bottom level 1.5 Rack. Next to pump}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    Current&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug loads
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Turn off the power supply
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+\DevDef{Pump}{
+  \textbf{Bottom level 1.5 Rack}\\
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off
+  \item\OffBox Unplug from walls
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into wall
+  \item\OnBox Turn on (should be enough)
+  \end{itemize}
+}
+\DevDef{Cooling water}{
+  Valves to close/reopen:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    \OnBox\OffBox&\hphantom{\hspace{5cm}}\\\hline
+    \OnBox\OffBox&\hphantom{\hspace{5cm}}\\\hline
+    \OnBox\OffBox&\hphantom{\hspace{5cm}}\\\hline
+    \OnBox\OffBox&\hphantom{\hspace{5cm}}\\\hline
+    \OnBox\OffBox&\hphantom{\hspace{5cm}}\\\hline
+    \OnBox\OffBox&\hphantom{\hspace{5cm}}\\\hline
+    \OnBox\OffBox&\hphantom{\hspace{5cm}}\\\hline
+    \OnBox\OffBox&\hphantom{\hspace{5cm}}\\\hline
+    \OnBox\OffBox&\hphantom{\hspace{5cm}}\\\hline
+    \OnBox\OffBox&\hphantom{\hspace{5cm}}\\\hline
+    \OnBox\OffBox&\hphantom{\hspace{5cm}}\\\hline
+    \OnBox\OffBox&\hphantom{\hspace{5cm}}\\\hline
+  \end{tabular}\\
+}
 

### 2017-08-01 presentations/2017-08-02_shutdown/checklist.tex
[presentations/2017-08-02_shutdown] personal checklist

@@
 \clearpage
-\section{#1}
+\section*{#1}
 \fancyhead[R]{#1}
 \setcounter{page}{1}
+\setcounter{subsection}{0}
 For shutting off, go through the checklist in the following order
@@
 }
+\renewcommand{\thesubsection}{\arabic{subsection}}
 
@@
 \Person{Yichao}
-\section{Equipments}
-\section{Power supplies}
-\section{Computers}
-\Person{Jon}
-\section{Equipments}
-\section{Power supplies}
-\section{Computers}
-\Person{Lee}
-\section{Equipments}
-\section{Power supplies}
-\section{Computers}
-\Person{Jessie}
-\section{Equipments}
-\section{Power supplies}
-\section{Computers}
-\Person{Frederic}
-\section{Equipments}
-\section{Power supplies}
-\section{Computers}
-
-\DevDef{Andor Camera for 1.0}{
-  \textbf{Turn off check list}
-  \begin{itemize}
+\subsection{Equipments}
+\DevDef{Thorlabs temperature controller for Na Raman doubler}{
+  \textbf{1st level above Na Raman and D2 seed lasers}\\
+  Record temperature settings\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Setpoint&\hphantom{\hspace{3.5cm}}\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off
+  \item\OffBox Unplug power
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug in power
+  \item\OnBox Check temperature setting
+  \item\OnBox Turn on
+  \end{itemize}
+}
+\DevDef{Timebase driver for Na Raman and Na D2 (x2)}{
+  \textbf{1st level above Na Raman and D2 seed lasers}\\
+  Record current and T1 settings\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Raman Current&\hphantom{\hspace{3.5cm}}\\\hline
+    Raman T1&\\\hline
+    MOT Current&\hphantom{\hspace{3.5cm}}\\\hline
+    MOT T1&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off
+  \item\OffBox Unplug power
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug in power
+  \item\OnBox Turn on
+  \item\OnBox Set current/temperature.
+  \item\OnBox Enable T1 survo
+  \item\OnBox Turn on current
+  \end{itemize}
+}
+\DevDef{Oscilloscope for Na D2 lock}{
+  \textbf{1st level above Na Raman amplifier}
+  \begin{itemize}
+  \item\OffBox Unplug from wall
+  \end{itemize}
+}
+\DevDef{MPB Raman amplifier}{
+  \textbf{1st level above Na MOT beam path}\\
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Power off
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into wall
+  \item\OnBox Power on
+  \end{itemize}
+}
+\DevDef{Homebuilt lockbox for Na D2}{
+  \textbf{1st level above Na seed}\\
+  \textbf{Turn on-off together with the adjustable high voltage power supply above}\\
+  Record high voltage power supply output
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unlock
+  \item\OffBox Turn down the voltage of the high voltage power supply to 0
+  \item\OffBox Unplug high voltage power on lockbox (zip tie)
+  \item\OffBox Unplug 15V from lockbox (zip tie)
+  \item\OffBox Turn off high voltage power supply
+  \item\OffBox Unplug high voltage power supply from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug high voltage power supply into the wall
+  \item\OnBox Turn on high voltage power supply (make sure the output is 0)
+  \item\OnBox Plug in 15V to lockbox
+  \item\OnBox Plug in high voltage to lockbox
+  \item\OnBox Turn up the voltage of the high voltage power supply
+  \item\OnBox Check HV output
+  \end{itemize}
+}
+\DevDef{SRS shutter driver for Na}{
+  \textbf{1st level above Na D2 beam path, below Variac}\\
+  Switch off/on with the switch on the back.
+}
+\DevDef{Variac for Na cell}{
+  \textbf{Above Na D2 beam path}\\
+  Record temperature and voltage settings\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    Temperature&\hphantom{\hspace{3.5cm}}\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn voltage to 0
   \item\OffBox Switch off
-  \item\OffBox Switch off chiller
-  \item\OffBox Unplug camera power (zip tie to camera)
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug in camera power
-  \item\OnBox Switch on chiller
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into wall
   \item\OnBox Switch on
-  \end{itemize}
-}
-\DevDef{Andor Camera for 1.5}{
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Switch off
-  \item\OffBox Switch off chiller
-  \item\OffBox Unplug camera power (zip tie to camera)
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug in camera power
-  \item\OnBox Switch on chiller
+  \item\OnBox Turn the voltage up \textbf{SLOWLY} and monitor the temperature at the same time.
+  \end{itemize}
+}
+\DevDef{Homebuilt lockbox for Na D1}{
+  \textbf{1st level above Na D2 beam path}\\
+  \textbf{Turn on-off together with the fixed high voltage power supply above}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unlock
+  \item\OffBox Unplug high voltage power on lockbox (zip tie)
+  \item\OffBox Unplug 15V from lockbox (zip tie)
+  \item\OffBox Unplug high voltage power supply from walls
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug high voltage power supply into the wall
+  \item\OnBox Plug in 15V to lockbox
+  \item\OnBox Plug in high voltage to lockbox
+  \item\OnBox Check HV output
+  \end{itemize}
+}
+\DevDef{Thorlabs temperature controller for Na D1 doubler}{
+  \textbf{1st level above Na D1}\\
+  Record temperature settings\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Setpoint&\hphantom{\hspace{3.5cm}}\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off
+  \item\OffBox Unplug power
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug in power
+  \item\OnBox Check temperature setting
+  \item\OnBox Turn on
+  \end{itemize}
+}
+\DevDef{Thorlabs temperature controller for Na D1 seed}{
+  \textbf{1st level above Na D1 seed}\\
+  Record temperature settings\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Setpoint&\hphantom{\hspace{3.5cm}}\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off
+  \item\OffBox Unplug power
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug in power
+  \item\OnBox Check temperature setting
+  \item\OnBox Turn on
+  \end{itemize}
+}
+\DevDef{Thorlabs current controller for Na D1 seed}{
+  \textbf{1st level above Na D1 seed}\\
+  Record current settings\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Current&\hphantom{\hspace{3.5cm}}\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off
+  \item\OffBox Unplug power
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug in power
+  \item\OnBox Check current setting
+  \item\OnBox Turn on
+  \end{itemize}
+}
+\subsection{Power supplies}
+\DevDef{Benchtop power supply}{
+  \textbf{2nd level above Na Variac}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    Left Current&\\\hline
+    Right Voltage&\\\hline
+    Right Current&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug loads
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Turn off the power supply
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+\DevDef{Homebuilt $24$V power supply}{
+  \textbf{2nd level above Cs tweezer controllers}\\
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug load
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Switch off on the back
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
   \item\OnBox Switch on
-  \end{itemize}
-}
-\DevDef{Tweezer 1 computer}{
-  \textbf{Check following devices}
-  \begin{itemize}
-  \item\OnBox Thorlabs cameras
-  \item\OnBox Na Raman amplifier
-  \end{itemize}
-}
-\DevDef{Tweezer 2 computer}{
-  \textbf{Check following devices}
-  \begin{itemize}
-  \item\OnBox Andor camera
-  \end{itemize}
-}
-\DevDef{Tweezer 3 computer}{
-  \textbf{Check following devices}
-  \begin{itemize}
-  \item\OnBox Software radio
-  \end{itemize}
-}
-\DevDef{Tweezer 4 computer}{
-  \textbf{Check following devices}
-  \begin{itemize}
-  \item\OnBox Andor camera
-  \item\OnBox Thorlabs camera
-  \end{itemize}
-}
-\DevDef{PLL for 1.0 Cs MOT}{
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug all signals (zip tie together)
-  \item\OffBox Unplug 15V and 5V powers (zip tie together)
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plugin 15V and 5V powers
-  \item\OnBox Plugin all signals
-  \item\OnBox Apply settings according to note on Generic tab, Equipment Settings.
-  \end{itemize}
-}
-\DevDef{PLL for 1.0 Cs Raman}{
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug all signals (zip tie together)
-  \item\OffBox Unplug 15V and 5V powers (zip tie together)
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plugin 15V and 5V powers
-  \item\OnBox Plugin all signals
-  \item\OnBox Apply settings according to note on Generic tab, Equipment Settings.
-  \end{itemize}
-}
-\DevDef{PLL for 1.5 Cs MOT}{
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug all signals (zip tie together)
-  \item\OffBox Unplug 15V and 5V powers (zip tie together)
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plugin 15V and 5V powers
-  \item\OnBox Plugin all signals
-  \item\OnBox Apply settings ???
-  \end{itemize}
-}
-\DevDef{1.5 Feshbach coils}{
-  \textbf{Before power shutdown}
-  \begin{itemize}
-  \item\OffBox Wrap exposed part in napkins to prevent condensations
-  \end{itemize}
-}
-\DevDef{1.5 IGBT}{
-  \textbf{Before power shutdown}
-  \begin{itemize}
-  \item\OffBox Wrap exposed part in napkins to prevent condensations
-  \end{itemize}
-}
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+\DevDef{Benchtop power supply}{
+  \textbf{2nd level above Na D1 seed controllers}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    Left Current&\\\hline
+    Right Voltage&\\\hline
+    Right Current&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug loads
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Turn off the power supply
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+\DevDef{Benchtop power supply}{
+  \textbf{2nd level above Cs tweezer, right of 24V power supply}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    Left Current&\\\hline
+    Right Voltage&\\\hline
+    Right Current&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug loads
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Turn off the power supply
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+\DevDef{Benchtop power supply}{
+  \textbf{1st level above Cs tweezer}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    Left Current&\\\hline
+    Right Voltage&\\\hline
+    Right Current&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug loads
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Turn off the power supply
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+\subsection{Computers}
 \DevDef{Computer control box for 1.0}{
@@
 }
+\Person{Jon}
+\subsection{Equipments}
+\DevDef{Agilent function generator for Na 1.0 switching}{
+  \textbf{1st level above TiSapph facing computers}\\
+  Record parameters:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Ch1 Hi&\hphantom{\hspace{3.5cm}}\\\hline
+    Ch1 Lo&\\\hline
+    Ch2 Hi&\\\hline
+    Ch2 Lo&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into wall
+  \item\OnBox Turn on
+  \item\OnBox Set frequency, duty cycle, high/low voltages
+  \item\OnBox Set switching phase back
+  \end{itemize}
+}
+\DevDef{2nd version Till's current controller for Cs 1.5 (x2)}{
+  \textbf{1st level above 1.5 Cs MOT}\\
+  Record current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Top Current&\hphantom{\hspace{3.5cm}}\\\hline
+    Bottom Current&\hphantom{\hspace{3.5cm}}\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off
+  \item\OffBox Unplug power (zip tie to controller)
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug in power
+  \item\OnBox Turn on
+  \end{itemize}
+}
+\DevDef{Thorlabs current controller}{
+  \textbf{1st level below Cs 1.5 MOT drivers}\\
+  Unused\\
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off
+  \item\OffBox Unplug power
+  \end{itemize}
+}
+\DevDef{Homebuilt temperature servo for Cs 1.5 MOT (x2)}{
+  \textbf{1st level above Cs 1.5 MOT}\\
+  Switch off/on the front switch
+}
+\DevDef{Oscilloscope for Cs 1.5 MOT lock}{
+  \textbf{1st level above Cs 1.5 MOT}
+  \begin{itemize}
+  \item\OffBox Unplug from wall
+  \end{itemize}
+}
+\DevDef{Homebuilt lockbox for Cs 1.5 MOT}{
+  \textbf{1st level above Cs 1.5 MOT}\\
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unlock
+  \item\OffBox Unplug 15V from lockbox (zip tie)
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug in 15V to lockbox
+  \end{itemize}
+}
+\DevDef{Function generator for Cs MOT 1.5 lockbox}{
+  \textbf{1st level under Cs MOT 1.5 lockbox}
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Record settings
+  \item\OffBox Turn off
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into wall
+  \item\OnBox Turn on
+  \item\OnBox Restore settings
+  \end{itemize}
+}
+\DevDef{HV amplifiers for 1.0 piezo mirrors}{
+  \textbf{Above the space beween Na 1.5 beam path and NaCs 1.5 chamber}\\
+  \textbf{Turn on-off together with the function generator below
+    and the high voltage power supply on the left}\\
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off the function generator
+  \item\OffBox Unplug function generator output (zip tie and label)
+  \item\OffBox Unplug HV power supply from the wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plugin HV power supply to the wall
+  \item\OnBox Plugin function generator output
+  \item\OnBox Turn on the function generator
+  \end{itemize}
+}
+\DevDef{Pump}{
+  \textbf{1st level above NaCs 1.0 chamber}\\
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off
+  \item\OffBox Unplug from walls
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into wall
+  \item\OnBox Turn on (should be enough)
+  \end{itemize}
+}
+\DevDef{Andor Camera for 1.0}{
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Switch off
+  \item\OffBox Switch off chiller
+  \item\OffBox Unplug camera power (zip tie to camera)
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug in camera power
+  \item\OnBox Switch on chiller
+  \item\OnBox Switch on
+  \end{itemize}
+}
+\subsection{Power supplies}
+\DevDef{Benchtop power supply}{
+  \textbf{2nd level above Cs 1.5 MOT controllers}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    Left Current&\\\hline
+    Right Voltage&\\\hline
+    Right Current&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug loads
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Turn off the power supply
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+\DevDef{Homebuilt $24$V power supply}{
+  \textbf{2nd level above Cs 1.5 MOT controllers}\\
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug load
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Switch off on the back
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Switch on
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+\DevDef{Benchtop power supply (x2)}{
+  \textbf{1st level above Na 1.5 bean path}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    Left Current&\\\hline
+    Right Voltage&\\\hline
+    Right Current&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug loads
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Turn off the power supply
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+\DevDef{Homebuilt $\pm15,5$V power supply}{
+  \textbf{2nd level above Na 1.5 beam path}\\
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug load
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Switch off on the back
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Switch on
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+\DevDef{Benchtop power supply (x2)}{
+  \textbf{2nd level above piezo mirror electronics}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    Left Current&\\\hline
+    Right Voltage&\\\hline
+    Right Current&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug loads
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Turn off the power supply
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+\DevDef{Benchtop power supply}{
+  \textbf{2nd level above NaCs 1.0 chamber}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    Left Current&\\\hline
+    Right Voltage&\\\hline
+    Right Current&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug loads
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Turn off the power supply
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+\subsection{Computers}
+\DevDef{Tweezer 2 computer}{
+  \textbf{Check following devices}
+  \begin{itemize}
+  \item\OnBox Andor camera
+  \end{itemize}
+}
+\DevDef{Tweezer 3 computer}{
+  \textbf{Check following devices}
+  \begin{itemize}
+  \item\OnBox Software radio
+  \end{itemize}
+}
+\Person{Lee}
+\subsection{Equipments}
+\DevDef{PLL for 1.0 Cs MOT}{
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug all signals (zip tie together)
+  \item\OffBox Unplug 15V and 5V powers (zip tie together)
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plugin 15V and 5V powers
+  \item\OnBox Plugin all signals
+  \item\OnBox Apply settings according to note on Generic tab, Equipment Settings.
+  \end{itemize}
+}
+\DevDef{PLL for 1.0 Cs Raman}{
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug all signals (zip tie together)
+  \item\OffBox Unplug 15V and 5V powers (zip tie together)
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plugin 15V and 5V powers
+  \item\OnBox Plugin all signals
+  \item\OnBox Apply settings according to note on Generic tab, Equipment Settings.
+  \end{itemize}
+}
+\DevDef{Homebuilt temperature servo for Cs 1.0 MOT}{
+  \textbf{1st level above Cs tweezer/MOT lasers}\\
+  Switch off/on the front switch
+}
+\DevDef{1st version Till's current controller for Cs MOT}{
+  \textbf{1st level above Cs tweezer/MOT lasers}\\
+  Record current value:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Current&\hphantom{\hspace{3.5cm}}\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off
+  \item\OffBox Unplug power (zip tie to controller)
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug in power
+  \item\OnBox Turn on
+  \end{itemize}
+}
+\DevDef{Cs 1.0 MOT lock box}{
+  \textbf{1st level above Cs MOT lasers}
+  \begin{itemize}
+  \item\OffBox Make sure the laser is unlocked.
+  \end{itemize}
+}
+\DevDef{Novatech function generator}{
+  \textbf{1st level above Cs MOT lasers}
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Save settings
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Restore settings
+  \end{itemize}
+}
+\DevDef{New Focus Cs Raman lasers drivers (2x)}{
+  \textbf{1st level above Cs Raman lasers}\\
+  Record Temperature, Current, Piezo voltage\\
+  Temperature is accessible in the menu under system status\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    F3 Current&\hphantom{\hspace{3.5cm}}\\\hline
+    F3 Piezo Voltage&\\\hline
+    F3 Temperature&\\\hline
+    F4 Current&\\\hline
+    F4 Piezo Voltage&\\\hline
+    F4 Temperature&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off
+  \item\OffBox Unplug power
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug in power
+  \item\OnBox (Turn on)
+  \end{itemize}
+}
+\DevDef{SRS shutter driver for Cs}{
+  \textbf{1st level above Cs Raman lasers}\\
+  Switch off/on with the switch on the back.
+}
+\DevDef{New Focus lock box for Cs Raman}{
+  \textbf{1st level above Cs Raman lasers}\\
+  Unplug power.
+}
+\DevDef{Homebuilt temperature servo for Cs tweezer}{
+  \textbf{1st level above Cs tweezer}\\
+  Switch off/on the front switch
+}
+\DevDef{2nd version Till's current controller for Cs Tweezer}{
+  \textbf{1st level above Cs tweezer}\\
+  Record current value:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Current&\hphantom{\hspace{3.5cm}}\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off
+  \item\OffBox Unplug power (zip tie to controller)
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug in power
+  \item\OnBox Turn on
+  \end{itemize}
+}
+\DevDef{Thorlabs current controller}{
+  \textbf{1st level below Cs tweezer driver}\\
+  Unused\\
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off
+  \item\OffBox Unplug power
+  \end{itemize}
+}
+\DevDef{Thorlabs temperature controller for Cs tweezer}{
+  \textbf{1st level above Cs tweezer}\\
+  Record temperature settings\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Setpoint&\hphantom{\hspace{3.5cm}}\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off
+  \item\OffBox Unplug power
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug in power
+  \item\OnBox Check temperature setting
+  \item\OnBox Turn on
+  \end{itemize}
+}
+\DevDef{Intensity servo for Cs}{
+  \textbf{1st level above Cs tweezer}\\
+  Unplug power
+}
+\subsection{Power supplies}
+\DevDef{Benchtop power supply}{
+  \textbf{1st level above Cs tweezer/MOT lasers}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    Left Current&\\\hline
+    Right Voltage&\\\hline
+    Right Current&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug loads
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Turn off the power supply
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+\DevDef{Homebuilt $\pm15,5$V power supply}{
+  \textbf{2nd level above Cs tweezer/MOT lasers}\\
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug load
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Switch off on the back
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Switch on
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+\DevDef{Benchtop power supply}{
+  \textbf{1st level next to Cs Raman driver}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    Current&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug loads
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Turn off the power supply
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+\DevDef{Homebuilt $24$V power supply}{
+  \textbf{2nd level above Cs Raman lasers}\\
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug load
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Switch off on the back
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Switch on
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+\DevDef{Benchtop power supply for Cs Raman locking}{
+  \textbf{2nd level above Cs Raman lockbox}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    Current&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug loads
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Turn off the power supply
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+\subsection{Computers}
+\DevDef{Tweezer 1 computer}{
+  \textbf{Check following devices}
+  \begin{itemize}
+  \item\OnBox Thorlabs cameras
+  \item\OnBox Na Raman amplifier
+  \end{itemize}
+}
+\Person{Jessie}
+\subsection{Equipments}
+\DevDef{TiSapph}{
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off pump, unplug from wall
+  \item\OffBox Turn off controller, unplug from wall
+  \item\OffBox Turn off chiller, unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into wall, turn on chiller
+  \item\OnBox Plug into wall, turn on controller
+  \item\OnBox Plug into wall, turn on pump
+  \end{itemize}
+}
+\DevDef{Quantel Laser}{
+  \textbf{1st level in the middle, facing 1.5 table}\\
+  Ask Frederic.
+  \vspace{1cm}
+}
+\DevDef{Intensity servo for Na}{
+  \textbf{1st level above Na tweezer, below 1.0 computer control box}\\
+  Unplug power
+}
+\DevDef{1st version Till's current controller for butterfly laser}{
+  \textbf{1st level above TiSapph}\\
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off
+  \item\OffBox Unplug power (zip tie to controller)
+  \end{itemize}
+}
+\DevDef{Homebuilt temperature servo for butterfly laser}{
+  \textbf{1st level above TiSapph}\\
+  Switch off/on the front switch
+}
+\DevDef{PLL for 1.5 Cs MOT}{
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug all signals (zip tie together)
+  \item\OffBox Unplug 15V and 5V powers (zip tie together)
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plugin 15V and 5V powers
+  \item\OnBox Plugin all signals
+  \item\OnBox Apply settings ???
+  \end{itemize}
+}
+\subsection{Power supplies}
+\DevDef{Homebuilt $24$V power supply}{
+  \textbf{2nd level above NaCs 1.0 chamber, facing the drawers/wall}\\
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug load
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Switch off on the back
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Switch on
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+\DevDef{Benchtop power supply for dispensers}{
+  \textbf{1st level above NaCs 1.0 chamber}\\
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug loads
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Turn off the power supply
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+\DevDef{Benchtop power supply for 1.5 computer control clock}{
+  \textbf{2nd level next to 1.5 computer control box}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    Current&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug loads
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Turn off the power supply
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+\DevDef{Homebuilt $\pm15,5$V power supply}{
+  \textbf{2nd level above TiSapph}\\
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug load
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Switch off on the back
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Switch on
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+\subsection{Computers}
 \DevDef{Computer control box for 1.5}{
@@
 }
-\DevDef{Homebuilt temperature servo for Cs 1.0 MOT}{
-  \textbf{1st level above Cs tweezer/MOT lasers}\\
-  Switch off/on the front switch
-}
-\DevDef{Benchtop power supply}{
-  \textbf{1st level above Cs tweezer/MOT lasers}\\
-  Record voltage/current values:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-    Left Current&\\\hline
-    Right Voltage&\\\hline
-    Right Current&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug loads
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Turn off the power supply
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{1st version Till's current controller for Cs MOT}{
-  \textbf{1st level above Cs tweezer/MOT lasers}\\
-  Record current value:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Current&\hphantom{\hspace{3.5cm}}\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug power (zip tie to controller)
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug in power
-  \item\OnBox Turn on
-  \end{itemize}
-}
-\DevDef{Homebuilt $\pm15,5$V power supply}{
-  \textbf{2nd level above Cs tweezer/MOT lasers}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug load
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Switch off on the back
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
+\Person{Frederic}
+\subsection{Equipments}
+\DevDef{Andor Camera for 1.5}{
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Switch off
+  \item\OffBox Switch off chiller
+  \item\OffBox Unplug camera power (zip tie to camera)
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug in camera power
+  \item\OnBox Switch on chiller
   \item\OnBox Switch on
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Cs 1.0 MOT lock box}{
-  \textbf{1st level above Cs MOT lasers}
-  \begin{itemize}
-  \item\OffBox Make sure the laser is unlocked.
-  \end{itemize}
-}
-\DevDef{Novatech function generator}{
-  \textbf{1st level above Cs MOT lasers}
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Save settings
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Restore settings
-  \end{itemize}
-}
-\DevDef{New Focus Cs Raman lasers drivers (2x)}{
-  \textbf{1st level above Cs Raman lasers}\\
-  Record Temperature, Current, Piezo voltage\\
-  Temperature is accessible in the menu under system status\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    F3 Current&\hphantom{\hspace{3.5cm}}\\\hline
-    F3 Piezo Voltage&\\\hline
-    F3 Temperature&\\\hline
-    F4 Current&\\\hline
-    F4 Piezo Voltage&\\\hline
-    F4 Temperature&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug power
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug in power
-  \item\OnBox (Turn on)
-  \end{itemize}
-}
-\DevDef{Benchtop power supply}{
-  \textbf{1st level next to Cs Raman driver}\\
-  Record voltage/current values:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-    Current&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug loads
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Turn off the power supply
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Homebuilt $24$V power supply}{
-  \textbf{2nd level above Cs Raman lasers}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug load
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Switch off on the back
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Switch on
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{SRS shutter driver for Cs}{
-  \textbf{1st level above Cs Raman lasers}\\
-  Switch off/on with the switch on the back.
-}
-\DevDef{New Focus lock box for Cs Raman}{
-  \textbf{1st level above Cs Raman lasers}\\
-  Unplug power.
-}
-\DevDef{Benchtop power supply for Cs Raman locking}{
-  \textbf{2nd level above Cs Raman lockbox}\\
-  Record voltage/current values:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-    Current&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug loads
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Turn off the power supply
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Timebase driver for Na Raman and Na D2 (x2)}{
-  \textbf{1st level above Na Raman and D2 seed lasers}\\
-  Record current and T1 settings\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Raman Current&\hphantom{\hspace{3.5cm}}\\\hline
-    Raman T1&\\\hline
-    MOT Current&\hphantom{\hspace{3.5cm}}\\\hline
-    MOT T1&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug power
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug in power
-  \item\OnBox Turn on
-  \item\OnBox Set current/temperature.
-  \item\OnBox Enable T1 survo
-  \item\OnBox Turn on current
-  \end{itemize}
-}
-\DevDef{Thorlabs temperature controller for Na Raman doubler}{
-  \textbf{1st level above Na Raman and D2 seed lasers}\\
-  Record temperature settings\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Setpoint&\hphantom{\hspace{3.5cm}}\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug power
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug in power
-  \item\OnBox Check temperature setting
-  \item\OnBox Turn on
-  \end{itemize}
-}
-\DevDef{Homebuilt lockbox for Na D2}{
-  \textbf{1st level above Na seed}\\
-  \textbf{Turn on-off together with the adjustable high voltage power supply above}\\
-  Record high voltage power supply output
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unlock
-  \item\OffBox Turn down the voltage of the high voltage power supply to 0
-  \item\OffBox Unplug high voltage power on lockbox (zip tie)
-  \item\OffBox Unplug 15V from lockbox (zip tie)
-  \item\OffBox Turn off high voltage power supply
-  \item\OffBox Unplug high voltage power supply from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug high voltage power supply into the wall
-  \item\OnBox Turn on high voltage power supply (make sure the output is 0)
-  \item\OnBox Plug in 15V to lockbox
-  \item\OnBox Plug in high voltage to lockbox
-  \item\OnBox Turn up the voltage of the high voltage power supply
-  \item\OnBox Check HV output
-  \end{itemize}
-}
-\DevDef{Oscilloscope for Na D2 lock}{
-  \textbf{1st level above Na Raman amplifier}
-  \begin{itemize}
-  \item\OffBox Unplug from wall
-  \end{itemize}
-}
-\DevDef{MPB Raman amplifier}{
-  \textbf{1st level above Na MOT beam path}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Power off
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into wall
-  \item\OnBox Power on
-  \end{itemize}
-}
-\DevDef{Variac for Na cell}{
-  \textbf{Above Na D2 beam path}\\
-  Record temperature and voltage settings\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-    Temperature&\hphantom{\hspace{3.5cm}}\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn voltage to 0
-  \item\OffBox Switch off
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into wall
-  \item\OnBox Switch on
-  \item\OnBox Turn the voltage up \textbf{SLOWLY} and monitor the temperature at the same time.
-  \end{itemize}
-}
-\DevDef{SRS shutter driver for Na}{
-  \textbf{1st level above Na D2 beam path, below Variac}\\
-  Switch off/on with the switch on the back.
-}
-\DevDef{Benchtop power supply}{
-  \textbf{2nd level above Na Variac}\\
-  Record voltage/current values:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-    Left Current&\\\hline
-    Right Voltage&\\\hline
-    Right Current&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug loads
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Turn off the power supply
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Homebuilt lockbox for Na D1}{
-  \textbf{1st level above Na D2 beam path}\\
-  \textbf{Turn on-off together with the fixed high voltage power supply above}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unlock
-  \item\OffBox Unplug high voltage power on lockbox (zip tie)
-  \item\OffBox Unplug 15V from lockbox (zip tie)
-  \item\OffBox Unplug high voltage power supply from walls
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug high voltage power supply into the wall
-  \item\OnBox Plug in 15V to lockbox
-  \item\OnBox Plug in high voltage to lockbox
-  \item\OnBox Check HV output
-  \end{itemize}
-}
-\DevDef{Thorlabs temperature controller for Na D1 doubler}{
-  \textbf{1st level above Na D1}\\
-  Record temperature settings\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Setpoint&\hphantom{\hspace{3.5cm}}\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug power
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug in power
-  \item\OnBox Check temperature setting
-  \item\OnBox Turn on
-  \end{itemize}
-}
-\DevDef{Thorlabs temperature controller for Na D1 seed}{
-  \textbf{1st level above Na D1 seed}\\
-  Record temperature settings\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Setpoint&\hphantom{\hspace{3.5cm}}\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug power
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug in power
-  \item\OnBox Check temperature setting
-  \item\OnBox Turn on
-  \end{itemize}
-}
-\DevDef{Thorlabs current controller for Na D1 seed}{
-  \textbf{1st level above Na D1 seed}\\
-  Record current settings\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Current&\hphantom{\hspace{3.5cm}}\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug power
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug in power
-  \item\OnBox Check current setting
-  \item\OnBox Turn on
-  \end{itemize}
-}
-\DevDef{Benchtop power supply}{
-  \textbf{2nd level above Na D1 seed controllers}\\
-  Record voltage/current values:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-    Left Current&\\\hline
-    Right Voltage&\\\hline
-    Right Current&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug loads
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Turn off the power supply
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Homebuilt $24$V power supply}{
-  \textbf{2nd level above Cs tweezer controllers}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug load
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Switch off on the back
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Switch on
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Benchtop power supply}{
-  \textbf{2nd level above Cs tweezer, right of 24V power supply}\\
-  Record voltage/current values:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-    Left Current&\\\hline
-    Right Voltage&\\\hline
-    Right Current&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug loads
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Turn off the power supply
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Homebuilt temperature servo for Cs tweezer}{
-  \textbf{1st level above Cs tweezer}\\
-  Switch off/on the front switch
-}
-\DevDef{2nd version Till's current controller for Cs Tweezer}{
-  \textbf{1st level above Cs tweezer}\\
-  Record current value:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Current&\hphantom{\hspace{3.5cm}}\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug power (zip tie to controller)
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug in power
-  \item\OnBox Turn on
-  \end{itemize}
-}
-\DevDef{Thorlabs current controller}{
-  \textbf{1st level below Cs tweezer driver}\\
-  Unused\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug power
-  \end{itemize}
-}
-\DevDef{Thorlabs temperature controller for Cs tweezer}{
-  \textbf{1st level above Cs tweezer}\\
-  Record temperature settings\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Setpoint&\hphantom{\hspace{3.5cm}}\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug power
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug in power
-  \item\OnBox Check temperature setting
-  \item\OnBox Turn on
-  \end{itemize}
-}
-\DevDef{Intensity servo for Cs}{
-  \textbf{1st level above Cs tweezer}\\
-  Unplug power
-}
-\DevDef{Benchtop power supply}{
-  \textbf{1st level above Cs tweezer}\\
-  Record voltage/current values:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-    Left Current&\\\hline
-    Right Voltage&\\\hline
-    Right Current&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug loads
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Turn off the power supply
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-%% Machine table facing laser table (south)
-\DevDef{2nd version Till's current controller for Cs 1.5 (x2)}{
-  \textbf{1st level above 1.5 Cs MOT}\\
-  Record current values:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Top Current&\hphantom{\hspace{3.5cm}}\\\hline
-    Bottom Current&\hphantom{\hspace{3.5cm}}\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug power (zip tie to controller)
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug in power
-  \item\OnBox Turn on
-  \end{itemize}
-}
-\DevDef{Thorlabs current controller}{
-  \textbf{1st level below Cs 1.5 MOT drivers}\\
-  Unused\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug power
-  \end{itemize}
-}
-\DevDef{Benchtop power supply}{
-  \textbf{2nd level above Cs 1.5 MOT controllers}\\
-  Record voltage/current values:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-    Left Current&\\\hline
-    Right Voltage&\\\hline
-    Right Current&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug loads
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Turn off the power supply
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Homebuilt $24$V power supply}{
-  \textbf{2nd level above Cs 1.5 MOT controllers}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug load
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Switch off on the back
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Switch on
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Homebuilt temperature servo for Cs 1.5 MOT (x2)}{
-  \textbf{1st level above Cs 1.5 MOT}\\
-  Switch off/on the front switch
-}
-\DevDef{Oscilloscope for Cs 1.5 MOT lock}{
-  \textbf{1st level above Cs 1.5 MOT}
-  \begin{itemize}
-  \item\OffBox Unplug from wall
-  \end{itemize}
-}
-\DevDef{Homebuilt lockbox for Cs 1.5 MOT}{
-  \textbf{1st level above Cs 1.5 MOT}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unlock
-  \item\OffBox Unplug 15V from lockbox (zip tie)
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug in 15V to lockbox
-  \end{itemize}
-}
-\DevDef{Function generator for Cs MOT 1.5 lockbox}{
-  \textbf{1st level under Cs MOT 1.5 lockbox}
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Record settings
-  \item\OffBox Turn off
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into wall
-  \item\OnBox Turn on
-  \item\OnBox Restore settings
-  \end{itemize}
-}
-\DevDef{Benchtop power supply (x2)}{
-  \textbf{1st level above Na 1.5 bean path}\\
-  Record voltage/current values:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-    Left Current&\\\hline
-    Right Voltage&\\\hline
-    Right Current&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug loads
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Turn off the power supply
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Homebuilt $\pm15,5$V power supply}{
-  \textbf{2nd level above Na 1.5 beam path}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug load
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Switch off on the back
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Switch on
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{HV amplifiers for 1.0 piezo mirrors}{
-  \textbf{Above the space beween Na 1.5 beam path and NaCs 1.5 chamber}\\
-  \textbf{Turn on-off together with the function generator below
-    and the high voltage power supply on the left}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off the function generator
-  \item\OffBox Unplug function generator output (zip tie and label)
-  \item\OffBox Unplug HV power supply from the wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plugin HV power supply to the wall
-  \item\OnBox Plugin function generator output
-  \item\OnBox Turn on the function generator
-  \end{itemize}
-}
-\DevDef{Benchtop power supply (x2)}{
-  \textbf{2nd level above piezo mirror electronics}\\
-  Record voltage/current values:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-    Left Current&\\\hline
-    Right Voltage&\\\hline
-    Right Current&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug loads
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Turn off the power supply
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Pump}{
-  \textbf{1st level above NaCs 1.0 chamber}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug from walls
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into wall
-  \item\OnBox Turn on (should be enough)
-  \end{itemize}
-}
-\DevDef{Benchtop power supply}{
-  \textbf{2nd level above NaCs 1.0 chamber}\\
-  Record voltage/current values:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-    Left Current&\\\hline
-    Right Voltage&\\\hline
-    Right Current&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug loads
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Turn off the power supply
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-% Machine table facing the wall (north)
-\DevDef{Homebuilt $24$V power supply}{
-  \textbf{2nd level above NaCs 1.0 chamber, facing the drawers/wall}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug load
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Switch off on the back
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Switch on
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Benchtop power supply for dispensers}{
-  \textbf{1st level above NaCs 1.0 chamber}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug loads
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Turn off the power supply
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Quantel Laser}{
-  \textbf{1st level in the middle, facing 1.5 table}\\
-  Ask Frederic.
-  \vspace{1cm}
-}
-\DevDef{Intensity servo for Na}{
-  \textbf{1st level above Na tweezer, below 1.0 computer control box}\\
-  Unplug power
-}
-\DevDef{Benchtop power supply for 1.5 computer control clock}{
-  \textbf{2nd level next to 1.5 computer control box}\\
-  Record voltage/current values:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-    Current&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug loads
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Turn off the power supply
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{1st version Till's current controller for butterfly laser}{
-  \textbf{1st level above TiSapph}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug power (zip tie to controller)
-  \end{itemize}
-}
-\DevDef{Homebuilt temperature servo for butterfly laser}{
-  \textbf{1st level above TiSapph}\\
-  Switch off/on the front switch
-}
-\DevDef{Homebuilt $\pm15,5$V power supply}{
-  \textbf{2nd level above TiSapph}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug load
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Switch off on the back
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Switch on
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{TiSapph}{
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off pump, unplug from wall
-  \item\OffBox Turn off controller, unplug from wall
-  \item\OffBox Turn off chiller, unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into wall, turn on chiller
-  \item\OnBox Plug into wall, turn on controller
-  \item\OnBox Plug into wall, turn on pump
-  \end{itemize}
-}
-\DevDef{Agilent function generator for Na 1.0 switching}{
-  \textbf{1st level above TiSapph facing computers}\\
-  Record parameters:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Ch1 Hi&\hphantom{\hspace{3.5cm}}\\\hline
-    Ch1 Lo&\\\hline
-    Ch2 Hi&\\\hline
-    Ch2 Lo&\\\hline
-  \end{tabular}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into wall
-  \item\OnBox Turn on
-  \item\OnBox Set frequency, duty cycle, high/low voltages
-  \item\OnBox Set switching phase back
-  \end{itemize}
-}
-% 1.5 Rack
-\DevDef{HV amplifiers for 1.5 piezo mirrors}{
-  \textbf{Top level of 1.5 rack}\\
-  \textbf{Turn on-off together with the function generator below
-    and the high voltage power supply above the 1.0 machine table}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off the function generator
-  \item\OffBox Unplug function generator output (zip tie and label)
-  \item\OffBox Unplug HV power supply from the wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plugin HV power supply to the wall
-  \item\OnBox Plugin function generator output
-  \item\OnBox Turn on the function generator
-  \end{itemize}
-}
-\DevDef{Benchtop power supply}{
-  \textbf{2nd level (from the top) 1.5 Rack. Next to coil servo}\\
-  Record voltage/current values:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-    Left Current&\\\hline
-    Right Voltage&\\\hline
-    Right Current&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug loads
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Turn off the power supply
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Benchtop power supply}{
-  \textbf{Bottom level 1.5 Rack. Next to pump}\\
-  Record voltage/current values:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-    Current&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug loads
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Turn off the power supply
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Pump}{
-  \textbf{Bottom level 1.5 Rack}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug from walls
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into wall
-  \item\OnBox Turn on (should be enough)
+  \end{itemize}
+}
+\DevDef{1.5 Feshbach coils}{
+  \textbf{Before power shutdown}
+  \begin{itemize}
+  \item\OffBox Wrap exposed part in napkins to prevent condensations
+  \end{itemize}
+}
+\DevDef{1.5 IGBT}{
+  \textbf{Before power shutdown}
+  \begin{itemize}
+  \item\OffBox Wrap exposed part in napkins to prevent condensations
   \end{itemize}
@@
 }
+\DevDef{HV amplifiers for 1.5 piezo mirrors}{
+  \textbf{Top level of 1.5 rack}\\
+  \textbf{Turn on-off together with the function generator below
+    and the high voltage power supply above the 1.0 machine table}\\
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off the function generator
+  \item\OffBox Unplug function generator output (zip tie and label)
+  \item\OffBox Unplug HV power supply from the wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plugin HV power supply to the wall
+  \item\OnBox Plugin function generator output
+  \item\OnBox Turn on the function generator
+  \end{itemize}
+}
+\DevDef{Pump}{
+  \textbf{Bottom level 1.5 Rack}\\
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off
+  \item\OffBox Unplug from walls
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into wall
+  \item\OnBox Turn on (should be enough)
+  \end{itemize}
+}
+\subsection{Power supplies}
+\DevDef{Benchtop power supply}{
+  \textbf{2nd level (from the top) 1.5 Rack. Next to coil servo}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    Left Current&\\\hline
+    Right Voltage&\\\hline
+    Right Current&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug loads
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Turn off the power supply
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+\DevDef{Benchtop power supply}{
+  \textbf{Bottom level 1.5 Rack. Next to pump}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    Current&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug loads
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Turn off the power supply
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+\subsection{Computers}
+\DevDef{Tweezer 4 computer}{
+  \textbf{Check following devices}
+  \begin{itemize}
+  \item\OnBox Andor camera
+  \item\OnBox Thorlabs camera
+  \end{itemize}
+}
 

### 2017-08-01 presentations/2017-08-02_shutdown/checklist.tex
[presentations/2017-08-02_shutdown] Format update and include location notes

@@
 \documentclass[10pt,fleqn,twocolumn]{article}
-% \usepackage[journal=rsc]{chemstyle}
-% \usepackage{mhchem}
 \usepackage{amsmath}
@@
 \usepackage{fontenc}
+\usepackage{titlesec}
 % \usepackage{tipa}
@@
 \usepackage{cancel}
+
 \newcommand{\hcancel}[2][black]{\setbox0=\hbox{#2}%
@@
 \pagestyle{fancy}
-\setlength{\headheight}{67pt}
+% \setlength{\headheight}{60pt}
 \fancyhead{}
@@
 \renewcommand{\footrulewidth}{0pt}
+\titlespacing{\subsection}{0pt}{\parskip}{-\parskip}
 
@@
 \newcommand\DevDef[2]{
-  \begin{minipage}{\linewidth}
+  \begin{minipage}[t]{\linewidth}
     \begin{itemize}
@@
 \end{itemize}
-Also wait before everyone else finish their corresponding steps before starting the next one.
+Also wait before everyone else finish their corresponding steps before starting the next one.\\
+
 }
@@
 \Person{Yichao}
+\textbf{\Large
+  Equipments and power supplies are mostly located around the laser table on the library side.
+}\\
 \subsection{Equipments}
@@
   \item\OnBox Plug the load back in
+  \end{itemize}
+}
+\DevDef{UPS}{
+  \textbf{2nd level above laser table}\\
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall
+  \item\OnBox Turn on
   \end{itemize}
@@
 \Person{Jon}
+\textbf{\Large
+  Equipments and power supplies are mostly located around the machine table facing the laser table
+  or the computer area.
+}\\
 \subsection{Equipments}
@@
 \Person{Lee}
+\textbf{\Large
+  Equipments and power supplies are mostly located around the laser table
+  on the computer area side.
+}\\
 \subsection{Equipments}
@@
 \Person{Jessie}
+\textbf{\Large
+  Equipments and power supplies are mostly located around the machine table facing the 1.5 table.
+}\\
 \subsection{Equipments}
@@
 \Person{Frederic}
+\textbf{\Large
+  Equipments and power supplies are mostly on the 1.5 rack.
+}\\
 \subsection{Equipments}

### 2017-08-01 presentations/2017-08-02_shutdown/checklist.tex
[presentations/2017-08-02_shutdown] More format tweaks

--- 2017-08-01 presentations/2017-08-02_shutdown/checklist.tex
@@
     \fill[#1] (0, 0) rectangle (\f@size/25, \f@size/25);
+    \draw[color=gray!80] (0, 0) rectangle (\f@size/25, \f@size/25);
     \path (\f@size/50, \f@size/50) node[color=black!15] {\small #2};
@@
 }
-\newcommand\DevBoxes{\mbox{{\Large\ColorBox{color=red!50}{Off}\!\!\ColorBox{color=green!50}{On}}}}
-\newcommand\OffBox{{\normalsize\ColorBox{color=orange!50}{}}}
-\newcommand\OnBox{{\normalsize\ColorBox{color=cyan!50}{}}}
+\newcommand\DevBoxes{\mbox{{\Large\ColorBox{color=red!35}{Off}\!\!\ColorBox{color=green!35}{On}}}}
+\newcommand\OffBox{{\normalsize\ColorBox{color=orange!40}{}}}
+\newcommand\OnBox{{\normalsize\ColorBox{color=cyan!40}{}}}
 \makeatother
@@
 }
-\newcommand\Person[1]{
+\newcommand\Person[2]{
 \clearpage
@@
 \end{itemize}
-Also wait before everyone else finish their corresponding steps before starting the next one.
+Also wait before everyone else finish their corresponding steps before starting the next one.\\
+
+\textbf{\Large #2}
+\vfill
 }
@@
 
-\Person{Yichao}
+\Person{Yichao}{
+  Equipments and power supplies are mostly located around the laser table on the library side.
+}
 \subsection{Equipments}
@@
 }
-\Person{Jon}
+\Person{Jon}{
+  Equipments and power supplies are mostly located around the machine table facing the laser table
+  or the computer area.
+}
 \subsection{Equipments}
@@
 }
-\Person{Lee}
+\Person{Lee}{
+  Equipments and power supplies are mostly located around the laser table
+  on the computer area side.
+}
 \subsection{Equipments}
@@
 }
-\Person{Jessie}
+\Person{Jessie}{
+  Equipments and power supplies are mostly located around the machine table facing the 1.5 table.
+}
 \subsection{Equipments}
@@
 }
-\Person{Frederic}
+\Person{Frederic}{
+  Equipments and power supplies are mostly on the 1.5 rack.
+}
 \subsection{Equipments}

### 2017-08-01 presentations/2017-08-02_shutdown/checklist.tex
"Peer review ;-p"

@@
 \Person{Yichao}{
-  Equipments and power supplies are mostly located around the laser table on the library side.
+  Equipments and power supplies are mostly located around the laser table on the library side.\\
+  Check Lee's part after everything are off.
 }
@@
   Equipments and power supplies are mostly located around the machine table facing the laser table
-  or the computer area.
+  or the computer area.\\
+  Check Jessie's part after everything are off.
 }
@@
   Equipments and power supplies are mostly located around the laser table
-  on the computer area side.
+  on the computer area side.\\
+  Check Yichao's part after everything are off.
 }
@@
 \Person{Jessie}{
-  Equipments and power supplies are mostly located around the machine table facing the 1.5 table.
+  Equipments and power supplies are mostly located around the machine table facing the 1.5 table.\\
+  Check Frederic's part after everything are off.
 }
@@
 \Person{Frederic}{
-  Equipments and power supplies are mostly on the 1.5 rack.
+  Equipments and power supplies are mostly on the 1.5 rack.\\
+  Check Jon's part after everything are off.
 }

### 2017-08-07 presentations/qual/plot_raman_op.jl
[presentations/qual] Move figures, Raman challenges

@@ -1,0 +1,179 @@
+#!/usr/bin/julia
+
+push!(LOAD_PATH, joinpath(@__DIR__, "../../lib"))
+
+import NaCsCalc.Utils: interactive
+import NaCsCalc: Trap
+using Cubature
+using PyPlot
+
+PyPlot.matplotlib["rcParams"][:update](Dict("font.size" => 20))
+PyPlot.matplotlib[:rc]("xtick", labelsize=15)
+PyPlot.matplotlib[:rc]("ytick", labelsize=15)
+
+const m_Na = 23e-3 / 6.02e23
+const η_ax = Trap.η(m_Na, 67e3, 2π / 589e-9) / √(2)
+const η_ax_op = Trap.η(m_Na, 67e3, 2π / 589e-9)
+const η_ra1 = Trap.η(m_Na, 430e3, 2π / 589e-9)
+const η_ra2 = Trap.η(m_Na, 590e3, 2π / 589e-9)
+
+"""
+    emission(v, isσ::Bool) -> (sinθ, cosθ)
+
+Given an uniform distribution in `[0, 1]` of `v` this function will return a distribution
+of `cosθ` that matches a dipole emission pattern (the type of the transition is determined by
+`isσ`).
+"""
+function emission_angle(v::T, isσ::Bool) where T<:AbstractFloat
+    # Returns `cosθ`. The caller should be ready to handle `|cosθ| > 1`
+    # The PDFs of the `θ` distribution are
+    # `3 / 4 * (1 - cos²θ) * sinθ` for π light and
+    # `3 / 8 * (1 + cos²θ) * sinθ` for σ± light
+    # The corresponding CDFs are
+    # `1 / 4 * (3cosθ - cos³θ) + 1 / 2` for π light and
+    # `1 / 8 * (3cosθ + cos³θ) + 1 / 2` for σ± light
+    # For a random number `v` we need to solve
+    # `3cosθ - cos³θ = 4v - 2` for π light and
+    # `3cosθ + cos³θ = 8v - 4` for σ± light
+    # The (real) solution is
+    # `cosθ = x + 1 / x` where `x = ∛(2√(v² - v) - 2v + 1)` for π light and
+    # `cosθ = x - 1 / x` where `x = ∛(√(16v² - 16v + 5) + 4v - 2)` for σ± light
+    # Note that the `x` for π polarization is complex
+    if isσ
+        y = muladd(v, 4, -2)
[…]

### 2017-08-07 presentations/qual/sequence.tex
[presentations/qual] Sequence

--- 2017-05-26 presentations/na_cool_paper/sequence.tex
@@
   \begin{scope}
-    \clip (4.6, -2.1) rectangle (17.8, 3.5);
+    \clip (4.6, -3.1) rectangle (17.8, 3.5);
     %% Pulse mark
@@
     }
-    \path[blue] (2.8*2+0.8, 0) node[below,align=center] {\textbf{Axis 1}\\\textit{Axial}};
+    \path[blue] (2.8*2+0.8, 1) node[above,align=center] {\textit{Axial $z$}};
     \foreach \i in {0,...,3} {
-      \path (5.6*\i + 0.8, 1) node[above,blue,align=center] {\textbf{$n$-th}\\\textbf{order}};
-      \path (5.6*\i + 3.6, 1) node[above,blue,align=center] {\textbf{$(n-1)$-th}\\\textbf{order}};
+      \path (5.6*\i + 0.8, -0.3) node[below,blue,align=center] {\textbf{$m$-th}\\\textbf{order}};
+      \path (5.6*\i + 3.6, -0.3) node[below,blue,align=center] {\textbf{$(\!m-1\!)$-th}\\\textbf{order}};
     }
@@
     }
-    \path[red] (5.6*1+2.2, 1.5) node[above,align=center] {\textbf{Axis 2}\\\textit{Radial}};
+    \path[red] (5.6*1+2.2, 1.5) node[above,align=center] {\textit{Radial $x$}};
+    \path[red] (5.6*1+2.1, 0.05) node[below,align=center] {\textbf{pulse $1$}};
+    \path[red] (5.6*2+2.1, 0.05) node[below,align=center] {\textbf{pulse $2$}};
 
@@
     }
-    \path[black] (5.6*1+5.0, 1.5) node[above,align=center] {\textbf{Axis 3}\\\textit{Radial}};
+    \path[black] (5.6*1+5.0, 1.5) node[above,align=center] {\textit{Radial $y$}};
+    \path[black] (5.6*1+5.2, 0.05) node[below,align=center] {\textbf{pulse $1$}};
+    \path[black] (5.6*2+5.2, 0.05) node[below,align=center] {\textbf{pulse $2$}};
 
@@
       \filldraw[fill=orange!30,draw=orange,line width=1.2]
-      (2.8*\i+1.58, -2) rectangle (2.8*\i+1.91, -0.7);
+      (2.8*\i+1.58, -3) rectangle (2.8*\i+1.91, -1.5);
       \filldraw[fill=orange!30,draw=orange,line width=1.2]
-      (2.8*\i+2.48, -2) rectangle (2.8*\i+2.81, -0.7);
+      (2.8*\i+2.48, -3) rectangle (2.8*\i+2.81, -1.5);
     }
-    \draw[line width=2,orange] (0,-2) -- (22.4,-2);
+    \draw[line width=2,orange] (0,-3) -- (22.4,-3);
   \end{scope}
 
-  \fill[white,path fading=fade img right] (16.8, -2.2) rectangle (17.81, 3.51);
-  \fill[white,path fading=fade img right] (16.8, -2.2) rectangle (17.81, 3.51);
-  \fill[white,path fading=fade img right] (16.8, -2.2) rectangle (17.81, 3.51);
+  \fill[white,path fading=fade img right] (16.8, -3.2) rectangle (17.81, 3.51);
+  \fill[white,path fading=fade img right] (16.8, -3.2) rectangle (17.81, 3.51);
+  \fill[white,path fading=fade img right] (16.8, -3.2) rectangle (17.81, 3.51);
 
-  \fill[white,path fading=fade img left] (5.6, -2.2) rectangle (4.59, 3.51);
-  \fill[white,path fading=fade img left] (5.6, -2.2) rectangle (4.59, 3.51);
-  \fill[white,path fading=fade img left] (5.6, -2.2) rectangle (4.59, 3.51);
+  \fill[white,path fading=fade img left] (5.6, -3.2) rectangle (4.59, 3.51);
+  \fill[white,path fading=fade img left] (5.6, -3.2) rectangle (4.59, 3.51);
+  \fill[white,path fading=fade img left] (5.6, -3.2) rectangle (4.59, 3.51);
 
@@
   \path (4.8, 0.5) node[left,align=center] {\textbf{Raman}};
-  \path (5.15, -1.5) node[left,orange,align=center] {\textbf{Optical}\\\textbf{pumping}};
-  \draw[line width=2,orange,->] (5.6,-2) -- (17.8,-2) node[right, below] {\scalebox{2}{$t$}};
+  \path (5.15, -2.4) node[left,orange,align=center] {\textbf{Optical}\\\textbf{pumping}};
+  \draw[line width=2,orange,->] (5.6,-3) -- (17.8,-3) node[right, below] {\scalebox{2}{$t$}};
 
@@
   \draw[decoration={brace,mirror,raise=3pt, amplitude=10pt},decorate,line width=2]
-  (5.6,-2) -- node[below=15pt] {\scalebox{1.5}{One cooling cycle}} (16.8,-2);
-
-  %% Sub figure label
-  \path (3.8,2.5) node[above=8pt] {\scalebox{1.2}{(C)}};
+  (5.6,-3) -- node[below=15pt] {\scalebox{1.5}{One cooling cycle}} (16.8,-3);
 \end{tikzpicture}

### 2017-08-07 presentations/qual/plot_raman_op.jl
[presentations/qual] Fix plot, add simulation result

@@ -156,10 +156,10 @@ text(49, 0.10, "\$n_{init}\\!\\!=\\!\\!55\$", color="C7")
 grid()
 xlim([0, nmax])
 ylim([0, 0.9])
-title("Raman matrix elements")
+title("Motional state branching ratios")
 ylabel("Probability")
 xlabel("Motional state \$n\$")
-maybe_save(joinpath(@__DIR__, "imgs/mele_raman"))
+maybe_save(joinpath(@__DIR__, "imgs/op_branching"))
 
 figure(figsize=[1.5, 0.9] * 4.8)
 plot_sidebands(0:nmax, -1:-1:-5, η_ax)
@@ -171,9 +171,9 @@ text(9, 0.50, "\$\\Delta n\\!\\!=\\!\\!\\!-\\!2\$", color="C1")
 text(21, 0.445, "\$\\Delta n\\!\\!=\\!\\!\\!-\\!3\$", color="C2")
 text(36, 0.41, "\$\\Delta n\\!\\!=\\!\\!\\!-\\!4\$", color="C3")
 text(53, 0.39, "\$\\Delta n\\!\\!=\\!\\!\\!-\\!5\$", color="C4")
-title("Motional state branching ratios")
 xlabel("Motional state \$n\$")
 ylabel("\$|\\langle n |e^{ikr}| n + \\Delta n \\rangle|\$")
-maybe_save(joinpath(@__DIR__, "imgs/op_branching"))
+title("Raman matrix elements")
+maybe_save(joinpath(@__DIR__, "imgs/mele_raman"))
 
 maybe_show()

### 2017-08-08 presentations/qual/sequence.tex
[presentations/qual] Smooth out sequence plot

@@
       -- cycle;
-      \draw[line width=1,blue] plot[domain={2.8*\i}:{2.8*\i+1.6},variable=\x]
+      \draw[line width=1,blue] plot[smooth,domain={2.8*\i}:{2.8*\i+1.6},variable=\x]
       ({\x}, {sin((\x-2.8*\i) * 112.5)^4}) -- (2.8*\i + 2.8, 0);
@@
       -- cycle;
-      \draw[line width=1,red] (5.6*\i, 0) -- plot[domain={5.6*\i+1.9}:{5.6*\i+2.5},variable=\x]
+      \draw[line width=1,red] (5.6*\i, 0) -- plot[smooth,domain={5.6*\i+1.9}:{5.6*\i+2.5},variable=\x]
       ({\x}, {1.5*sin((\x-5.6*\i-1.9) * 300)^4}) -- (5.6*\i+5.6, 0);
@@
       -- cycle;
-      \draw[line width=1,black] (5.6*\i, 0) -- plot[domain={5.6*\i+4.7}:{5.6*\i+5.3},variable=\x]
+      \draw[line width=1,black] (5.6*\i, 0) -- plot[smooth,domain={5.6*\i+4.7}:{5.6*\i+5.3},variable=\x]
       ({\x}, {1.5*sin((\x-5.6*\i-4.7) * 300)^4}) -- (5.6*\i+5.6, 0);

### 2017-08-10 presentations/qual/plot_raman_op.jl
[presentations/qual] Finish setup / difficulty slide

@@ -7,7 +7,7 @@ import NaCsCalc: Trap
 using Cubature
 using PyPlot
 
-PyPlot.matplotlib["rcParams"][:update](Dict("font.size" => 20))
+PyPlot.matplotlib["rcParams"][:update](Dict("font.size" => 25))
 PyPlot.matplotlib[:rc]("xtick", labelsize=15)
 PyPlot.matplotlib[:rc]("ytick", labelsize=15)
 
@@ -112,10 +112,10 @@ const coupling_ra1 = (op_heating_all(op_heating_ra, 30, 30, Float32(η_ra1), fal
 const coupling_ra2 = (op_heating_all(op_heating_ra, 30, 30, Float32(η_ra2), false) *
                       op_heating_all(op_heating_ra, 30, 30, Float32(η_ra2), true))
 
-function plot_op_sidebands(n1s, n2s, coupling)
+function plot_op_sidebands(n1s, n2s, coupling; kws...)
     for i in 1:length(n2s)
         n2 = n2s[i]
-        plot(n1s, coupling[n2 + 1, n1s + 1], ".-")
+        plot(n1s, coupling[n2 + 1, n1s + 1], ".-"; kws...)
     end
 end
 
@@ -146,13 +146,13 @@ end
 figure(figsize=[1.5, 0.9] * 4.8)
 plot_op_sidebands(0:nmax, [0, 1, 2, 5, 10, 20, 35, 55], coupling_ax)
 text(0.5, 0.8, "\$n_{init}\\!\\!=\\!\\!0\$", color="C0")
-text(1, 0.53, "\$n_{init}\\!\\!=\\!\\!1\$", color="C1")
-text(2, 0.40, "\$n_{init}\\!\\!=\\!\\!2\$", color="C2")
-text(3, 0.28, "\$n_{init}\\!\\!=\\!\\!5\$", color="C3")
-text(7, 0.20, "\$n_{init}\\!\\!=\\!\\!10\$", color="C4")
-text(19.5, 0.14, "\$n_{init}\\!\\!=\\!\\!20\$", color="C5")
-text(33, 0.12, "\$n_{init}\\!\\!=\\!\\!35\$", color="C6")
-text(49, 0.10, "\$n_{init}\\!\\!=\\!\\!55\$", color="C7")
[…]

### 2017-08-10 experiments/rnr/utils.jl
Fix ntuple depwarn

@@ -39,7 +39,7 @@ end
 end
 
 @inline pdf_rnr{N}(kT::Number, t, ωs::NTuple{N}, Es::NTuple{N}) =
-    pdf_rnr(ntuple(i->kT, Val{N}), t, ωs, Es)
+    pdf_rnr(ntuple(i->kT, Val(N)), t, ωs, Es)
 
 function pdf_rnr_polar(kT, t, ωs, Er, θ, ϕ)
     sinθ = @fastmath sin(θ)

### 2017-08-10 lib/NaCsSim/src/system.jl

@@ -521,7 +521,7 @@ function (::HyperFineMeasure{N})(res::Vector{Int}, state::StateC, extern_state, 
 end
 function Setup.finalize_measure(::HyperFineMeasure{N}, m, n) where {N}
     total = m[N + 1]
-    return (ntuple(i->binomial_unc(m[i], total), Val{N}),
+    return (ntuple(i->binomial_unc(m[i], total), Val(N)),
             binomial_unc(total, n))
 end
 function Setup.abort_measure(::HyperFineMeasure, res::Vector{Int}, n)

### 2017-08-10 lib/NaCsSim/test/runtests.jl

@@ -41,7 +41,7 @@ function op_pulse(t, γ1, γ2, γ2′=0.01f0 * γ2, ηs=η_op, ηdri=η_op_dri)
     System.OP{Float32}(t, branching, ηs, ηdri, isσ)
 end
 function raman_pulse(ax, order, t, Γ)
-    ns = ntuple(i->i == ax ? -order : 0, Val{3})
+    ns = ntuple(i->i == ax ? -order : 0, Val(3))
     System.Raman{Float32,1,3}(t, 1, η_ramans[ax], ns, sz, Γ)
 end
 

### 2017-08-10 calculations/sideband/sideband.jl
[calculations/sideband] save simulation result

@@ -81,7 +81,7 @@ end
 
 plot_hf(params, res) = plot_hf(params, collect(res))
 
-function plot_hf{T<:Tuple}(params, res::Vector{T})
+function plot_hf(params, res::Vector{T}) where {T<:Tuple}
     figure()
     for i in 1:nfields(T)
         hf = [r[i].a for r in res]
@@ -114,6 +114,57 @@ const xname = Ref("")
 function plot_hook()
     xlabel(xname[])
 end
+
+
+
+function get_ground_state(res)
+    [r.a for r in res], [r.s for r in res]
+end
+
+function get_total(res)
+    [1 - t.a for t in res], [t.s for t in res]
+end
+
+function get_nbars(res)
+    nbarx_res = (nr[1] for nr in res)
+    nbary_res = (nr[2] for nr in res)
+    nbarz_res = (nr[3] for nr in res)
+
+    nbarx = [n.a for n in nbarx_res]
+    nbarx_unc = [n.s for n in nbarx_res]
+    nbary = [n.a for n in nbary_res]
+    nbary_unc = [n.s for n in nbary_res]
+    nbarz = [n.a for n in nbarz_res]
+    nbarz_unc = [n.s for n in nbarz_res]
+
+    return nbarx, nbarx_unc, nbary, nbary_unc, nbarz, nbarz_unc
+end
+
+get_hf(res) = get_hf(collect(res))
+
+Base.@pure Nx2(N::Int) = N * 2
+
+function get_hf(res::Vector{T}) where {N,T<:NTuple{N,Any}}
+    return ntuple(i->i % 2 == 1 ? [r[(i + 1) ÷ 2].a for r in res] : [r[i ÷ 2].s for r in res],
+                  Val(Nx2(N)))
+end
+
+function save_result(params, res, fname)
+    data = (get_ground_state((r[2] for r in res))...,
+            get_total((r[1][2] for r in res))...,
+            get_nbars((r[1][1] for r in res))...,
+            get_hf((r[3][1] for r in res))...)
+    open("$fname.csv", "w") do fh
+        for i in 1:length(params)
+            print(fh, params[i])
+            for a in data
+                print(fh, ",", a[i])
+            end
+            println(fh)
+        end
+    end
+end
+
 
 function threadmap(f, arg)
     # A really simple work queue
@@ -295,7 +346,7 @@ gen_f2op_spec(p, pol) =
 #     F1 Down 1.000 + F2 counterop 1.000: Ω = 2π / 11.45us
[…]

### 2017-08-10 presentations/qual/plot_sim_combined.jl
[presentations/qual] Fix scattering rate. Update simulation figures.

@@ -1,0 +1,58 @@
+#!/usr/bin/julia
+
+# Parameter, P_ground, σ(P_ground), loss, σ(loss),
+# nbar_x, σ(nbar_x), nbar_y, σ(nbar_y), nbar_z, σ(nbar_z), hf1, σ(hf1), ..., hf8, σ(hf8)
+
+push!(LOAD_PATH, joinpath(@__DIR__, "../../lib"))
+
+import NaCsCalc.Utils: interactive
+using PyPlot
+
+PyPlot.matplotlib["rcParams"][:update](Dict("font.size" => 25))
+PyPlot.matplotlib[:rc]("xtick", labelsize=15)
+PyPlot.matplotlib[:rc]("ytick", labelsize=15)
+
+function maybe_save(name)
+    if !interactive()
+        savefig("$name.pdf"; bbox_inches="tight", transparent=true)
+        savefig("$name.png"; bbox_inches="tight", transparent=true)
+        savefig("$name.svg"; bbox_inches="tight", transparent=true)
+        close()
+    end
+end
+
+function maybe_show()
+    if interactive()
+        show()
+    end
+end
+
+const datadir = joinpath(@__DIR__, "../../calculations/sideband/data")
+const data_with_scatter = readcsv(joinpath(datadir, "qual_with_scatter.csv"), Float64)
+const data_no_scatter = readcsv(joinpath(datadir, "qual_no_scatter.csv"), Float64)
+
+figure()
+errorbar(data_with_scatter[:, 1], data_with_scatter[:, 2], data_with_scatter[:, 3],
+         label="With scatter", color="C1")
+errorbar(data_no_scatter[:, 1], data_no_scatter[:, 2], data_no_scatter[:, 3],
+         label="Without scatter", color="C0")
+xlim([0, maximum(data_no_scatter[:, 1])])
+ylim([0, 1])
+xlabel("Cooling Cycle")
+ylabel("Probability")
+legend(fontsize=18, loc=4)
+grid()
+maybe_save(joinpath(@__DIR__, "imgs/simcool_real"))
+
+figure()
+errorbar(data_no_scatter[:, 1], data_no_scatter[:, 2], data_no_scatter[:, 3],
+         label="Without scatter", color="C0")
+xlim([0, maximum(data_no_scatter[:, 1])])
+ylim([0, 1])
+xlabel("Cooling Cycle")
+ylabel("Probability")
[…]

### 2017-08-10 presentations/qual/plot_spectrum.jl
[presentations/qual] Use new images for Raman spectra

@@ -1,0 +1,206 @@
+#!/usr/bin/julia
+
+push!(LOAD_PATH, joinpath(@__DIR__, "../../lib"))
+
+using NaCsCalc.Utils: interactive
+using NaCsData
+using PyPlot
+using DataStructures
+matplotlib["rcParams"][:update](Dict("font.size" => 20))
+matplotlib[:rc]("xtick", labelsize=15)
+matplotlib[:rc]("ytick", labelsize=15)
+
+const iname_a = joinpath(@__DIR__, "../../experiments/misc/data/data_20170402_205344.csv")
+const iname_b = joinpath(@__DIR__, "../../experiments/misc/data/data_20170404_133229.csv")
+const iname_c = joinpath(@__DIR__, "../../experiments/misc/data/data_20170409_005850.csv")
+const iname_d = joinpath(@__DIR__, "../../experiments/misc/data/data_20170409_082523.csv")
+
+const data_a = NaCsData.load_count_csv(iname_a)
+const data_b = NaCsData.load_count_csv(iname_b)
+const data_c = NaCsData.load_count_csv(iname_c)
+const data_d = NaCsData.load_count_csv(iname_d)
+
+const spec_a = OrderedDict(
+    # With cooling +-1
+    :cool_pm1=>((linspace(-18.985, -18.785, 11), linspace(-18.15, -17.95, 11)),
+                (linspace(-18.945, -19.145, 11), linspace(-18.00, -17.75, 11)),
+                (linspace(-18.545, -18.585, 11), linspace(-18.415, -18.455, 11))),
+    # Without cooling +-1, -2
+    :nocool_pm12=>((linspace(-18.985, -18.785, 11), linspace(-18.15, -17.95, 11),
+                    linspace(-17.53, -17.745, 11)),
+                   (linspace(-18.945, -19.145, 11), linspace(-18.00, -17.75, 11),
+                    linspace(-17.14, -17.44, 11)),
+                   (linspace(-18.545, -18.585, 11), linspace(-18.415, -18.455, 11),
+                    linspace(-18.35, -18.39, 11))),
+    # Without cooling carrier
+    :nocool_0=>(linspace(-18.335, -18.58, 11),
+                linspace(-18.31, -18.61, 11),
[…]

### 2017-08-11 presentations/qual/plot_rabi_flop.jl
[presentations/qual] Remove subfigure label from rabi flopping plots

@@ -1,0 +1,362 @@
+#!/usr/bin/julia
+
+# Compute Rabi flopping with the present of decay terms
+# The Hamiltonian is assumed to be time independent and the Rabi drive is on-resonance
+
+push!(LOAD_PATH, joinpath(@__DIR__, "../../lib"))
+using NaCsCalc.Utils: binomial_estimate, thread_rng, interactive
+using NaCsCalc.Atomic: all_scatter_D
+import NaCsCalc: Trap
+using NaCsSim.DecayRabi: propagate_multistates, average_multistates, Γ_to_rates
+using NaCsData
+using DataStructures
+using PyPlot
+matplotlib["rcParams"][:update](Dict("font.size" => 20))
+matplotlib[:rc]("xtick", labelsize=15)
+matplotlib[:rc]("ytick", labelsize=15)
+
+# Scattering rates
+const δf1 = -25.0e9
+const δf2 = -25.0e9 - 1.77e9
+const rlof_f1 = (61.542e6 / (δf1 - 1.107266e9))^2
+const rlof_f2 = (61.542e6 / (δf2 - 1.107266e9))^2
+const rhif_f1 = (61.542e6 / (δf1 + 664.360e6))^2
+const rhif_f2 = (61.542e6 / (δf2 + 664.360e6))^2
+
+const rates_f1_coprop = all_scatter_D(true, 3, (0.5, 0.0, 0.5), rhif_f1, rlof_f1)
+const rates_f1_up = all_scatter_D(true, 3, (0.25, 0.5, 0.25), rhif_f1, rlof_f1)
+const rates_f1_down = all_scatter_D(true, 3, (0.25, 0.5, 0.25), rhif_f1, rlof_f1)
+const rates_f2_coprop = all_scatter_D(true, 3, (0.25, 0.5, 0.25), rhif_f2, rlof_f2)
+const rates_f2_counterop = all_scatter_D(true, 3, (0.1, 0.0, 0.9), rhif_f2, rlof_f2)
+
+rates_f1_coprop .*= 4.46e8
+rates_f2_coprop .*= 4.1e8
+rates_f1_up .*= 1.05e9
+rates_f1_down .*= 8.2e8
+rates_f2_counterop .*= 3.25e9
+
+const rates_r3 = rates_f1_down + rates_f2_counterop
+const rates_r2 = rates_f1_up + rates_f2_counterop
[…]

### 2017-08-11 presentations/qual/plot_raman_op.jl
[presentations/qual] Use a more representitive n_init as the first OP branching ratio to show

@@ -177,8 +177,8 @@ title("Raman matrix elements")
 maybe_save(joinpath(@__DIR__, "imgs/mele_raman"))
 
 figure(figsize=[1.5, 0.9] * 4.8)
-plot_op_sidebands(0:nmax, [35], coupling_ax, color="C6")
-text(32, 0.13, "\$n_{init}\\!\\!=\\!\\!35\$", color="C6")
+plot_op_sidebands(0:nmax, [20], coupling_ax, color="C5")
+text(15, 0.16, "\$n_{init}\\!\\!=\\!\\!20\$", color="C5")
 grid()
 xlim([0, nmax])
 ylim([0, 0.9])

### 2017-10-17 presentations/2017-10-17_julia-mv/present.tex
[presentations/2017-10-17_julia-mv] WIP

--- 2017-04-19 presentations/2017-04-19_itamp/present.tex
@@
 \usepackage{multimedia}
-\usepackage{bm}
-\usepackage{siunitx}
 \usetikzlibrary{
@@
 
-% \def\timeleft{15:00->14:55}
-
-\title[Na ground state cooling]{Raman sideband cooling of a single sodium atom to 3D ground state}
-\date{April 19, 2017}
-\author[Yichao Yu]{Yichao Yu\\
-  \vspace{0.5cm}
-  {\footnotesize Lee Liu, Dr. Nick Hutzler,\\
-    Jessie Zhang, Dr. Jon Hood}}
-\institute{Ni Group/Harvard}
+\title{Function multiversioning in system image}
+\subtitle{All about vector registers}
+\date{Oct. 16, 2017}
+\author{Yichao Yu}
+\institute{Harvard}
 
@@
 
-% \begin{frame}{}
-%   \tableofcontents
-% \end{frame}
-
 \begin{frame}{}
   \begin{center}
+    \includegraphics[width=11cm]{imgs/pr21849.png}
+  \end{center}
+\end{frame}
+
+% Probably more techincal and low level than many other talks
+% So let's set the base line
+% By Jameson
+
+% With that in mind, feel free to ask questions.
+
+% I'll talk less about this PR specifically,
+% but more about the general issue when dealing with code compiled for different architectures.
+
+\begin{frame}{Goal}
+  \visible<+-> {
+    \begin{block}{Amount of implementation details}
+      \begin{itemize}
+      \item<+-> Just enough to make Jeff happy
+      \item<+-> Without losing the audience
+      \item<+-> With a single version of the talk \textbf{(Important!)}
+      \end{itemize}
+    \end{block}
+  }
+\end{frame}
+
+% Story
+% * openlibm performance issue
+
+\begin{frame}{How did it all begin}
   \begin{tikzpicture}
-      \visible<1> {
-        \path (0, 0) node
-        {\includegraphics[width=10cm]{../2015-05-05_cua/overall_full_min.png}};
+    \node at (0, 0) {\includegraphics[width=11cm]{imgs/issue17395.png}};
+    \visible<2>{
+      \fill[white,opacity=0.85] (5.5, 3.9) rectangle (-5.5, -3.9);
+      \node[fill=red!20!white,thick,rounded corners=.3cm,inner sep=8pt] at (-4, 2) (S1) {Startup};
+      \node[fill=red!20!white,thick,rounded corners=.3cm,inner sep=8pt] at (2, 2) (S2) {Slow loop};
+
+      \node[fill=green!20!white,thick,rounded corners=.3cm,inner sep=8pt] at (-4, -2) (F2) {Magic};
+      \node[fill=green!20!white,thick,rounded corners=.3cm,inner sep=8pt] at (2, -2) (F3) {Fast loop};
+      \draw[->, line width=1.4] (S1) edge (S2) (S2) edge (F2) (F2) edge (F3);
+
+      \node at (3, 0) (L0) {Same code};
+
+      \draw[->, gray, line width=1] (L0) edge (S2);
+      \draw[->, gray, line width=1] (L0) edge (F3);
+
+      \draw[<-, line width=1.4] (S2.north) arc(190:-80:0.9);
+      \draw[<-, line width=1.4] (F3.south) arc(-190:80:0.9);
     }
+  \end{tikzpicture}
+\end{frame}
+
+\begin{frame}{Register size}
+  \begin{center}
+    \begin{tikzpicture}
+      \node at (-4, 2) (ax) {\textbf{ax}};
+      \node at (-2, 2) (eax) {\textbf{eax}};
+      \node at (0, 2) (rax) {\textbf{rax}};
+
+      \node at (0, 1.3) (mmx0) {\textbf{mmx0}};
+      \node at (2, 1.3) (xmm0) {\textbf{xmm0}};
+      \node at (4, 1.3) (ymm0) {\textbf{ymm0}};
+      \node at (6, 1.3) (zmm0) {\textbf{zmm0}};
+
+      \draw[->, line width=1, gray] (ax) edge (eax);
+      \draw[->, line width=1, gray] (eax) edge (rax);
+      \draw[->, line width=1, gray] (mmx0) edge (xmm0);
+      \draw[->, line width=1, gray] (xmm0) edge (ymm0);
+      \draw[->, line width=1, gray] (ymm0) edge (zmm0);
+
       \visible<2-> {
-        \path (0, 0) node
-        {\includegraphics[width=10cm]{../2015-05-05_cua/overall_trap_min.png}};
-        \path (3, -3) node
-        {\includegraphics[width=3cm]{../../experiments/nacs_atoms/imgs/single_viridis.png}};
+        \node[right] at (-4, 0) (A) {More/larger registers};
+        \node[right] at (2, 0) (B) {More states to manage};
+        \draw[->, line width=1, gray] (A) edge (B);
+      }
+      \visible<3-> {
+        \node[right] at (-4, -0.7) {(Intel got something wrong almost everytime)};
       }
@@
 
-\begin{frame}{Wave function size mismatch}
-  \begin{center}
-    \begin{tikzpicture}
-      \shade[ball color=blue!90] (0, 0) circle (0.45);
-      \shade[ball color=orange!90] (0.4, 0.2) circle (0.3);
-      \draw[<->,line width=1] (-0.45, 0.4) -- (0.35, 0.8);
-      \path (-0.05, 0.6) node[rotate=26.565,above=2pt] {$4a_0$};
-      \path (0.2, -2) node[below] {\textbf{Molecule}};
-
-      \draw[line width=1] plot[samples=200,domain=-2:2,variable=\x] ({\x + 6}, {(\x)^2 * 0.8 - 1.5});
-      \draw[line width=2,orange!90!black]
-      plot[samples=200,domain=-2:2,variable=\x] ({\x + 6}, {exp(-(\x)^2 * 1.3) - 0.988});
-      \draw[line width=0.8] (6 - 0.8, -0.988) -- (6 + 0.8, -0.988);
-      \draw[<->,line width=1] (6 - 1, 0.3) -- (6 + 1, 0.3);
-      \path (6, 0.3) node[above] {$1000a_0$};
-      \path (6, -2) node[below] {\textbf{Atom}};
-    \end{tikzpicture}
-    \vspace{1cm}
-    \begin{block}{Goal of cooling}
-      \begin{itemize}
-      \item Single initial state
-      \item Shrink wavefunction size
-      \end{itemize}
-    \end{block}
-  \end{center}
-\end{frame}
-
-\begin{frame}{Raman sideband cooling of Sodium}
-  \begin{columns}
-    \column{6.5cm}
-    \includegraphics[width=6cm]{Na_RSC_schematic.pdf}
-    \column{5cm}
-    \visible<2->{
-      \begin{block}{Difficulties}
-        \begin{itemize}
-        \item High initial temperature ($40\mu K$)
-        \item<3-> High recoil heating\\
-          {\footnotesize (High Lamb Dicke parameter)}
-        \end{itemize}
-      \end{block}
-    }
-  \end{columns}
-\end{frame}
-
-\begin{frame}{Raman sidebands}
-  \begin{center}
-    \begin{tikzpicture}
-      \visible<1> {
-        \path (0, 0) node {
-          \includegraphics[width=10cm]{../../experiments/misc/imgs/data_spectrum_20170409_r2_before.png}
-        };
-        \draw[<-, line width=1.5] (-0.7, 0) -- (0, 1.6) node[right] {\Large Carrier};
-      }
-      \visible<2> {
-        \path (0, 0) node {
-          \includegraphics[width=10cm]{../../experiments/misc/imgs/data_spectrum_20170409_r2.png}
-        };
-      }
-      \visible<3> {
-        \path (0, 0) node {
-          \includegraphics[width=10cm]{../../experiments/misc/imgs/data_spectrum_20170409_r3.png}
-        };
-      }
-    \end{tikzpicture}
-  \end{center}
-\end{frame}
-
-\begin{frame}{Raman sidebands}
-  \begin{center}
-    \begin{tikzpicture}[scale=1.41176]
-      \visible<1> {
-        \path (0, 0) node {
-          \includegraphics[width=12cm]{../../experiments/misc/imgs/data_spectrum_20170409_a1_before.png}
-        };
-        \draw[red, <-, line width=1.5] (-3.15, 0.5) -- (-2.95, 1.2)
-        node[above right] {\Large 1st order heating};
-        \draw[<-, line width=1.5] (-2.45, 0.2) -- (-2.25, 0.8) node[above right] {\Large Carrier};
-        \draw[black!40!green, <-, line width=1.5] (-1.7, 0.2) -- (-1.55, 0.6)
-        node[right] {\Large 1st order cooling};
-        \draw[blue, <-, line width=1.5] (-0.95, -0.1) -- (-0.55, 0.1)
-        node[right] {\Large 2nd order cooling};
-        \path[magenta] (0.25, -0.5) node[right] {\Large And higher orders{$\cdots$}};
-      }
-      \visible<2-> {
-        \path (0, 0) node {
-          \includegraphics[width=12cm]{../../experiments/misc/imgs/data_spectrum_20170409_a1.png}
-        };
-      }
-      \visible<3-> {
-        \fill[white,opacity=0.95] (-4.2, -2.5) rectangle (5, 2.5);
-        \path (0, 1) node[align=center]
-        {
-          \begin{tabular}{|c|c|}
-            \hline
-            \textbf{Axis}&\textbf{Ground state probability}\\\hline
-            1 (Axial)&93.1(2.5)\%\\\hline
-            2 (Radial)&91.9(2.3)\%\\\hline
-            3 (Radial)&92.9(2.5)\%\\\hline
-          \end{tabular}
-        };
-        \visible<4-> {
-          \path (0, -1) node[align=center]
-          {
-            \textbf{3D ground state:} $79.5(3.6)\%$\\
-            \textbf{Loss after cooling:} $15\%$\\\\
-            \textbf{Total 3D ground state preparation fidelity:} $67.6(3.1)\%$
-          };
-        }
-      }
-    \end{tikzpicture}
-  \end{center}
-\end{frame}
-
-\begin{frame}{Rabi flopping (radial)}
-  \begin{center}
-    \visible<+->{
-      \includegraphics[width=10cm]{../../experiments/rabi_flop/imgs/fit_20170409_r2_0_ba.png}\\
-    }
-    \visible<+->{
-      Good agreement in ground state probability between spectrum and Rabi flopping data.
-    }
-  \end{center}
-\end{frame}
-
-\begin{frame}{Rabi flopping (axial)}
-  \begin{center}
-    \includegraphics[height=4.8cm]{../../experiments/rabi_flop/imgs/fit_20170409_a1_0_nol.png}
-    \includegraphics[height=4.8cm]{../../experiments/rabi_flop/imgs/fit_20170409_a1_p1_nol.png}
-  \end{center}
-\end{frame}
-
-\begin{frame}{}
-  \begin{block}{Conclusion}
-    $67.6(3.1)\%$ ground state preparation fidelity {\small ($79.5(3.6)\%$ without loss)}
-  \end{block}
-  \vspace{1cm}
-  \begin{block}{Improvements}
-    \begin{itemize}
-    \item Reduce off-resonance scattering from Raman beams
-    \item Reduce magnetic field fluctuation
-    \item Reduce loss during cooling
-    \end{itemize}
-  \end{block}
-\end{frame}
-
-\begin{frame}{}
-\end{frame}
-
-\begin{frame}{Axial matrix element}
-  \begin{center}
-    \includegraphics[width=6.5cm]{{../../calculations/sideband_strength/imgs/coupling_0.43_0-6}.png}
-  \end{center}
-\end{frame}
-
-\begin{frame}{Radial 2 matrix element}
-  \begin{center}
-    \includegraphics[width=6.5cm]{{../../calculations/sideband_strength/imgs/coupling_0.35_0-2}.png}
-  \end{center}
-\end{frame}
-
-\begin{frame}{Radial 3 matrix element}
-  \begin{center}
-    \includegraphics[width=6.5cm]{{../../calculations/sideband_strength/imgs/coupling_0.29_0-2}.png}
-  \end{center}
-\end{frame}
-
 \end{document}

### 2017-10-17 presentations/2017-10-17_julia-mv/present.tex
[presentations/2017-10-17_julia-mv] done?

@@
 
-% Story
-% * openlibm performance issue
+% openlibm performance issue
+% Not only does this trigger the chain of events that led me to implement this PR
+% but it's also another example of interaction between code compiled for different archs.
+
+% Processors shouldn't remember the history and decide how fast to run
+% Except that it does....
 
@@
 \end{frame}
+
+% Larger address space / more data simultaneously
+% Issue caused by mixing YMM aware Glibc code and legacy code using XMM in openlibm.
 
@@
 
+\begin{frame}{Compile openlibm for AVX (ymm registers)}
+  \begin{itemize}
+  \item<+-> GCC function attribute \textit{target\_clone}\\
+    \ldots specify that a function be cloned into multiple versions
+    compiled with different target options \ldots It also creates a resolver function (\ldots)
+    that dynamically selects a clone suitable for current architecture \ldots\\\vspace{0.5cm}
+  \item<+-> Has bug on current GCC versions so not usable in openlibm.\\
+    But it's a good start.
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Why function multiversioning}
+  \begin{itemize}
+  \item<+-> For code in the system image\\\vspace{0.1cm}
+  \item<+-> For JIT code\\\vspace{0.1cm}
+    \visible<+->{JIT features > system image features}\\\vspace{0.1cm}
+    \visible<+->{JIT register size == system register size}
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Cloning}
+  \begin{center}
+    \begin{tikzpicture}
+      \node[fill=red!20!white,thick,rounded corners=.3cm,inner sep=8pt] at (-5, 2) (f0) {test\_f};
+      \node[fill=red!20!white,thick,rounded corners=.3cm,inner sep=8pt] at (0, 2) (g0) {test\_g};
+      \node[fill=red!20!white,thick,rounded corners=.3cm,inner sep=8pt] at (5, 2) (h0) {test\_h};
+      \draw[->, line width=1.4] (g0) edge (f0);
+      \visible<1> {
+        \draw[->, line width=1.4] (h0) edge (g0);
+      }
+
+      \visible<2-> {
+        \node[fill=green!20!white,thick,rounded corners=.3cm,inner sep=8pt] at (-5, -2) (f1) {test\_f.clone};
+        \node[fill=green!20!white,thick,rounded corners=.3cm,inner sep=8pt] at (0, -2) (g1) {test\_g.clone};
+        \draw[->, line width=1.4] (g1) edge (f1);
+      }
+      \visible<2> {
+        \draw[->, red, line width=1.4] (h0) edge (g0);
+      }
+
+      \visible<3> {
+        \node[fill=orange!20!white,thick,rounded corners=.3cm,inner sep=8pt] at (1, 0) (gg) {test\_g.slot};
+        \draw[->, blue, line width=1.4] (h0) edge (gg);
+        \draw[->, dashed, line width=1.4] (gg) edge (g0);
+        \draw[->, dashed, line width=1.4] (gg) edge (g1);
+      }
+    \end{tikzpicture}
+  \end{center}
+\end{frame}
+
+\begin{frame}{Next step}
+  \begin{block}{}
+    \begin{itemize}
+    \item<+-> Expose user API\\\vspace{0.2cm}
+      \begin{itemize}
+      \item<+-> Platform agnostic, e.g. ``fma''\\\vspace{0.2cm}
+      \item<+-> Platform specific, e.g. ``x86::avx2''\\\vspace{0.2cm}
+      \end{itemize}\\\vspace{0.2cm}
+    \item<+-> Make use of this in other part of runtime\\\vspace{0.2cm}
+      \visible<+->{crc32c, PLT, \ldots}
+    \end{itemize}
+  \end{block}
+\end{frame}
+
+\begin{frame}{}
+\end{frame}
+
 \end{document}

### 2018-02-18 notes/capacitor_size.tex
[notes] why F is a big unit

--- 2017-08-01 presentations/2017-08-02_shutdown/checklist.tex
@@
-\documentclass[10pt,fleqn,twocolumn]{article}
+\documentclass[10pt,fleqn]{article}
+% \usepackage[journal=rsc]{chemstyle}
+% \usepackage{mhchem}
 \usepackage{amsmath}
@@
 \usepackage{fontenc}
-\usepackage{titlesec}
 % \usepackage{tipa}
@@
 \usepackage{cancel}
-
 \newcommand{\hcancel}[2][black]{\setbox0=\hbox{#2}%
@@
 \pagestyle{fancy}
-% \setlength{\headheight}{60pt}
+\setlength{\headheight}{67pt}
 \fancyhead{}
@@
 \renewcommand{\footrulewidth}{0pt}
-\titlespacing{\subsection}{0pt}{\parskip}{-\parskip}
 
@@
 \setlength{\marginparwidth}{0pt}
-
-\makeatletter
-\newcommand\ColorBox[2]{
-  \begin{tikzpicture}
-    \fill[#1] (0, 0) rectangle (\f@size/25, \f@size/25);
-    \path (\f@size/50, \f@size/50) node[color=black!15] {\small #2};
-  \end{tikzpicture}
-}
-\newcommand\DevBoxes{\mbox{{\Large\ColorBox{color=red!50}{Off}\!\!\ColorBox{color=green!50}{On}}}}
-\newcommand\OffBox{{\normalsize\ColorBox{color=orange!50}{}}}
-\newcommand\OnBox{{\normalsize\ColorBox{color=cyan!50}{}}}
-\makeatother
-
-\newcommand\DevHeader[1]{{\Large\DevBoxes\textbf{#1}\\}}
-\def\arraystretch{2}
-
-\newcommand\DevDef[2]{
-  \begin{minipage}[t]{\linewidth}
-    \begin{itemize}
-    \item\DevHeader{#1}
-      #2
-    \end{itemize}
-    \vspace{0.8cm}
-  \end{minipage}
-}
-\newcommand\Person[1]{
-\clearpage
-\section*{#1}
-\fancyhead[R]{#1}
-\setcounter{page}{1}
-\setcounter{subsection}{0}
-For shutting off, go through the checklist in the following order
-\begin{itemize}
-\item\OffBox Turn off equipments
-\item\OffBox Turn off power supplies
-\item\OffBox Turn off computers
-\end{itemize}
-Wait before everyone else finish their corresponding steps before starting the next one.\\
-For powering up, go through the checklist in the following order
-\begin{itemize}
-\item\OnBox Turn on computers
-\item\OnBox Turn on power supplies
-\item\OnBox Turn on equipments
-\item\OnBox Check computer connection to devices
-\end{itemize}
-Also wait before everyone else finish their corresponding steps before starting the next one.\\
-
-}
-\renewcommand{\thesubsection}{\arabic{subsection}}
-
 \parindent=0pt
-\title{Checklist}
-\date{August 2nd, 2017}
+\title{Why do capacitors usually only have a small value}
+\author{Yichao Yu}
 \begin{document}
 
-\Person{Yichao}
-\textbf{\Large
-  Equipments and power supplies are mostly located around the laser table on the library side.
-}\\
-\subsection{Equipments}
-\DevDef{Thorlabs temperature controller for Na Raman doubler}{
-  \textbf{1st level above Na Raman and D2 seed lasers}\\
-  Record temperature settings\\
+\maketitle
 
-  \begin{tabular}{|c|c|}
-    \hline
-    Setpoint&\hphantom{\hspace{3.5cm}}\\\hline
-  \end{tabular}\\
+In Lab 1 of PS3, there is a question about why capacitors usually has a small value.
+AFAIK, the student is supposed to relate this to the smallness of the electron charge in
+SI unit which I find to be problematic.
+This is a note that list all reasons I think such a question is problematic and some
+better answers that I can come up with.
 
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug power
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug in power
-  \item\OnBox Check temperature setting
-  \item\OnBox Turn on
-  \end{itemize}
-}
-\DevDef{Timebase driver for Na Raman and Na D2 (x2)}{
-  \textbf{1st level above Na Raman and D2 seed lasers}\\
-  Record current and T1 settings\\
+\section{Why such a explanation is problematic}
 
-  \begin{tabular}{|c|c|}
-    \hline
-    Raman Current&\hphantom{\hspace{3.5cm}}\\\hline
-    Raman T1&\\\hline
-    MOT Current&\hphantom{\hspace{3.5cm}}\\\hline
-    MOT T1&\\\hline
-  \end{tabular}\\
+To start, super-capacitors exist, and may have a capacitance of hundreds of $F$
+within a small volume.
+This alone suggests that this question is more about material properties that
+are not within the scope of this class.
 
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug power
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug in power
-  \item\OnBox Turn on
-  \item\OnBox Set current/temperature.
-  \item\OnBox Enable T1 survo
-  \item\OnBox Turn on current
-  \end{itemize}
-}
-\DevDef{Oscilloscope for Na D2 lock}{
-  \textbf{1st level above Na Raman amplifier}
-  \begin{itemize}
-  \item\OffBox Unplug from wall
-  \end{itemize}
-}
-\DevDef{MPB Raman amplifier}{
-  \textbf{1st level above Na MOT beam path}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Power off
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into wall
-  \item\OnBox Power on
-  \end{itemize}
-}
-\DevDef{Homebuilt lockbox for Na D2}{
-  \textbf{1st level above Na seed}\\
-  \textbf{Turn on-off together with the adjustable high voltage power supply above}\\
-  Record high voltage power supply output
+Now about the expected answer. Electron charge is about $1.602\times10^{-19}C$,
+if we were to use this as an explanation for why $C$ is such a large unit
+(which in turn means that $F = C / V$ is a large unit) we would expect capacitors to
+have a capacitance value on the order of $10^{-19}$, which is wrong for at least two reasons,
 
-  \begin{tabular}{|c|c|}
-    \hline
-    Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-  \end{tabular}\\
+\begin{enumerate}
+\item They are not.\\
+  In fact, due to parasitic capacitance, it is very hard to get stand alone capacitance smaller
+  than few $pF$.
+\item $1e$ is much smaller than the amount of charge we expect a normal capacitor to store.\\
+  And I don't believe there is an obvious way for the students to do a correct estimation
+  of how much charge the conductor in a capacitor can hold. (One is given below).
+\end{enumerate}
 
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unlock
-  \item\OffBox Turn down the voltage of the high voltage power supply to 0
-  \item\OffBox Unplug high voltage power on lockbox (zip tie)
-  \item\OffBox Unplug 15V from lockbox (zip tie)
-  \item\OffBox Turn off high voltage power supply
-  \item\OffBox Unplug high voltage power supply from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug high voltage power supply into the wall
-  \item\OnBox Turn on high voltage power supply (make sure the output is 0)
-  \item\OnBox Plug in 15V to lockbox
-  \item\OnBox Plug in high voltage to lockbox
-  \item\OnBox Turn up the voltage of the high voltage power supply
-  \item\OnBox Check HV output
-  \end{itemize}
-}
-\DevDef{SRS shutter driver for Na}{
-  \textbf{1st level above Na D2 beam path, below Variac}\\
-  Switch off/on with the switch on the back.
-}
-\DevDef{Variac for Na cell}{
-  \textbf{Above Na D2 beam path}\\
-  Record temperature and voltage settings\\
+Therefore, while electron charge being small indeed put some limit on how much charge a normal
+capacitor can store.
+It is non-trivial to actual do so and certainly not for students in this class.
+This is not even mentioning (see below) that this limit isn't the limiting factors in
+capacitor manufacturing.
 
-  \begin{tabular}{|c|c|}
-    \hline
-    Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-    Temperature&\hphantom{\hspace{3.5cm}}\\\hline
-  \end{tabular}\\
+It is good to give students an idea of the magnitude of different quantities, electron charge,
+capacitor values, safe voltages, etc.
+However, it is better to do so with more direct arguments. Even if the argument related to
+electron charge is what limits the value of conventional capacitors, it's not,
+it shouldn't be used as an example if the student cannot fully understand the argument,
+and they can't.
+Doing so would encourage them to skip the logic and make incorrect connections between
+quantities, which IMHO is a bad habit that is very hard to correct later on.
 
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn voltage to 0
-  \item\OffBox Switch off
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into wall
-  \item\OnBox Switch on
-  \item\OnBox Turn the voltage up \textbf{SLOWLY} and monitor the temperature at the same time.
-  \end{itemize}
-}
-\DevDef{Homebuilt lockbox for Na D1}{
-  \textbf{1st level above Na D2 beam path}\\
-  \textbf{Turn on-off together with the fixed high voltage power supply above}\\
+\section{The actual reason}
 
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unlock
-  \item\OffBox Unplug high voltage power on lockbox (zip tie)
-  \item\OffBox Unplug 15V from lockbox (zip tie)
-  \item\OffBox Unplug high voltage power supply from walls
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug high voltage power supply into the wall
-  \item\OnBox Plug in 15V to lockbox
-  \item\OnBox Plug in high voltage to lockbox
-  \item\OnBox Check HV output
-  \end{itemize}
-}
-\DevDef{Thorlabs temperature controller for Na D1 doubler}{
-  \textbf{1st level above Na D1}\\
-  Record temperature settings\\
+\subsection{TL;DR}
 
-  \begin{tabular}{|c|c|}
-    \hline
-    Setpoint&\hphantom{\hspace{3.5cm}}\\\hline
-  \end{tabular}\\
+It's complicated. Since units are arbitrarily defined, this question is essentially asking why
+the unit systems are designed in the way they are. Additionally, since the unit system
+was more-or-less defined based on the quantity that makes sense on human scale,
+we necessarily need to consider what is the correct human scale historically chosen.
+Below I present a few of the limiting factors based on the best I know of the unit system
+and material science.
+Note that I do not believe any of the following explanations are understandable for
+students taking PS3 (at this stage, or ever) and they are given mainly to show
+how complicated the issue is. It should hopefully also be an interesting read.
 
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug power
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug in power
-  \item\OnBox Check temperature setting
-  \item\OnBox Turn on
-  \end{itemize}
-}
-\DevDef{Thorlabs temperature controller for Na D1 seed}{
-  \textbf{1st level above Na D1 seed}\\
-  Record temperature settings\\
+\subsection{Limit from breakdown}
+In principle, this does not really limit the capacitor size since one can in principle always
+make a larger capacitor with lower breakdown voltage until running into manufacture limit,
+something I'll definitely \textbf{NOT} get into.
+Nevertheless, these are included here since the breakdown is the only thing
+we could remotely relate the electron charge value to.
 
-  \begin{tabular}{|c|c|}
-    \hline
-    Setpoint&\hphantom{\hspace{3.5cm}}\\\hline
-  \end{tabular}\\
+\subsubsection{The amount of charge one can store in a conductor}
+This is the closest limitation I (and Nick)
+could come up with that is related to electron charge.
 
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug power
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug in power
-  \item\OnBox Check temperature setting
-  \item\OnBox Turn on
-  \end{itemize}
-}
-\DevDef{Thorlabs current controller for Na D1 seed}{
-  \textbf{1st level above Na D1 seed}\\
-  Record current settings\\
+The smallness of the electron charge means that a lot of electrons needs to be added
+or removed from a conductor to hold a large amount of charge. Since all the net charges
+are stored on the surface of the conductor in equilibrium, what we need is basically
+the maximum 2D charge density on a normal conductor.
+A very simple model that should give the right order of magnitude is to assume the metal can
+afford a single layer of electron or positive ion to stick to a neutral surface.
+Based on the density and atomic mass of copper, the density of copper atoms is roughly
 
-  \begin{tabular}{|c|c|}
-    \hline
-    Current&\hphantom{\hspace{3.5cm}}\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug power
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug in power
-  \item\OnBox Check current setting
-  \item\OnBox Turn on
-  \end{itemize}
-}
-\subsection{Power supplies}
-\DevDef{Benchtop power supply}{
-  \textbf{2nd level above Na Variac}\\
-  Record voltage/current values:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-    Left Current&\\\hline
-    Right Voltage&\\\hline
-    Right Current&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug loads
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Turn off the power supply
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Homebuilt $24$V power supply}{
-  \textbf{2nd level above Cs tweezer controllers}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug load
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Switch off on the back
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Switch on
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Benchtop power supply}{
-  \textbf{2nd level above Na D1 seed controllers}\\
-  Record voltage/current values:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-    Left Current&\\\hline
-    Right Voltage&\\\hline
-    Right Current&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug loads
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Turn off the power supply
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Benchtop power supply}{
-  \textbf{2nd level above Cs tweezer, right of 24V power supply}\\
-  Record voltage/current values:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-    Left Current&\\\hline
-    Right Voltage&\\\hline
-    Right Current&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug loads
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Turn off the power supply
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Benchtop power supply}{
-  \textbf{1st level above Cs tweezer}\\
-  Record voltage/current values:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-    Left Current&\\\hline
-    Right Voltage&\\\hline
-    Right Current&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug loads
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Turn off the power supply
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{UPS}{
-  \textbf{2nd level above laser table}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on
-  \end{itemize}
-}
-\subsection{Computers}
-\DevDef{Computer control box for 1.0}{
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox (Do following three steps quickly)
-  \item\OffBox Turn off the box by flipping the switch on the front side of the box
-  \item\OffBox Unplug the high voltage (48V) power supply (circular plug)
-    on the front side of the box. Then unplug the power supply itself fromm the outlet.
-  \item\OffBox Unplug the 12V board power supply.
-    (L.T.E. one with a rectangular connector in the front)
-  \item\OffBox Unplug USB power on the front side near the fan.
-  \item\OffBox Zip tie the three unpluged powers to the computer control box.
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Connect to 3.5G Windfrek clock generator from Tweezer1.
-    Set frequency to 3.5G and amplitude to max.
-  \item\OnBox (Remove power connection zip ties and) Plug in USB power supply.
-  \item\OnBox (Do following three steps quickly)
-  \item\OnBox Plug in the 12V board power supply.
-  \item\OnBox Plug in high voltage power supply.
-  \item\OnBox Turn on the power switch of the box. The fans should start spinning.
-  \end{itemize}
-}
-\Person{Jon}
-\textbf{\Large
-  Equipments and power supplies are mostly located around the machine table facing the laser table
-  or the computer area.
-}\\
-\subsection{Equipments}
-\DevDef{Agilent function generator for Na 1.0 switching}{
-  \textbf{1st level above TiSapph facing computers}\\
-  Record parameters:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Ch1 Hi&\hphantom{\hspace{3.5cm}}\\\hline
-    Ch1 Lo&\\\hline
-    Ch2 Hi&\\\hline
-    Ch2 Lo&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into wall
-  \item\OnBox Turn on
-  \item\OnBox Set frequency, duty cycle, high/low voltages
-  \item\OnBox Set switching phase back
-  \end{itemize}
-}
-\DevDef{2nd version Till's current controller for Cs 1.5 (x2)}{
-  \textbf{1st level above 1.5 Cs MOT}\\
-  Record current values:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Top Current&\hphantom{\hspace{3.5cm}}\\\hline
-    Bottom Current&\hphantom{\hspace{3.5cm}}\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug power (zip tie to controller)
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug in power
-  \item\OnBox Turn on
-  \end{itemize}
-}
-\DevDef{Thorlabs current controller}{
-  \textbf{1st level below Cs 1.5 MOT drivers}\\
-  Unused\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug power
-  \end{itemize}
-}
-\DevDef{Homebuilt temperature servo for Cs 1.5 MOT (x2)}{
-  \textbf{1st level above Cs 1.5 MOT}\\
-  Switch off/on the front switch
-}
-\DevDef{Oscilloscope for Cs 1.5 MOT lock}{
-  \textbf{1st level above Cs 1.5 MOT}
-  \begin{itemize}
-  \item\OffBox Unplug from wall
-  \end{itemize}
-}
-\DevDef{Homebuilt lockbox for Cs 1.5 MOT}{
-  \textbf{1st level above Cs 1.5 MOT}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unlock
-  \item\OffBox Unplug 15V from lockbox (zip tie)
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug in 15V to lockbox
-  \end{itemize}
-}
-\DevDef{Function generator for Cs MOT 1.5 lockbox}{
-  \textbf{1st level under Cs MOT 1.5 lockbox}
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Record settings
-  \item\OffBox Turn off
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into wall
-  \item\OnBox Turn on
-  \item\OnBox Restore settings
-  \end{itemize}
-}
-\DevDef{HV amplifiers for 1.0 piezo mirrors}{
-  \textbf{Above the space beween Na 1.5 beam path and NaCs 1.5 chamber}\\
-  \textbf{Turn on-off together with the function generator below
-    and the high voltage power supply on the left}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off the function generator
-  \item\OffBox Unplug function generator output (zip tie and label)
-  \item\OffBox Unplug HV power supply from the wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plugin HV power supply to the wall
-  \item\OnBox Plugin function generator output
-  \item\OnBox Turn on the function generator
-  \end{itemize}
-}
-\DevDef{Pump}{
-  \textbf{1st level above NaCs 1.0 chamber}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug from walls
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into wall
-  \item\OnBox Turn on (should be enough)
-  \end{itemize}
-}
-\DevDef{Andor Camera for 1.0}{
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Switch off
-  \item\OffBox Switch off chiller
-  \item\OffBox Unplug camera power (zip tie to camera)
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug in camera power
-  \item\OnBox Switch on chiller
-  \item\OnBox Switch on
-  \end{itemize}
-}
-\subsection{Power supplies}
-\DevDef{Benchtop power supply}{
-  \textbf{2nd level above Cs 1.5 MOT controllers}\\
-  Record voltage/current values:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-    Left Current&\\\hline
-    Right Voltage&\\\hline
-    Right Current&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug loads
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Turn off the power supply
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Homebuilt $24$V power supply}{
-  \textbf{2nd level above Cs 1.5 MOT controllers}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug load
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Switch off on the back
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Switch on
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Benchtop power supply (x2)}{
-  \textbf{1st level above Na 1.5 bean path}\\
-  Record voltage/current values:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-    Left Current&\\\hline
-    Right Voltage&\\\hline
-    Right Current&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug loads
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Turn off the power supply
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Homebuilt $\pm15,5$V power supply}{
-  \textbf{2nd level above Na 1.5 beam path}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug load
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Switch off on the back
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Switch on
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Benchtop power supply (x2)}{
-  \textbf{2nd level above piezo mirror electronics}\\
-  Record voltage/current values:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-    Left Current&\\\hline
-    Right Voltage&\\\hline
-    Right Current&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug loads
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Turn off the power supply
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Benchtop power supply}{
-  \textbf{2nd level above NaCs 1.0 chamber}\\
-  Record voltage/current values:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-    Left Current&\\\hline
-    Right Voltage&\\\hline
-    Right Current&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug loads
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Turn off the power supply
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\subsection{Computers}
-\DevDef{Tweezer 2 computer}{
-  \textbf{Check following devices}
-  \begin{itemize}
-  \item\OnBox Andor camera
-  \end{itemize}
-}
-\DevDef{Tweezer 3 computer}{
-  \textbf{Check following devices}
-  \begin{itemize}
-  \item\OnBox Software radio
-  \end{itemize}
-}
-\Person{Lee}
-\textbf{\Large
-  Equipments and power supplies are mostly located around the laser table
-  on the computer area side.
-}\\
-\subsection{Equipments}
-\DevDef{PLL for 1.0 Cs MOT}{
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug all signals (zip tie together)
-  \item\OffBox Unplug 15V and 5V powers (zip tie together)
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plugin 15V and 5V powers
-  \item\OnBox Plugin all signals
-  \item\OnBox Apply settings according to note on Generic tab, Equipment Settings.
-  \end{itemize}
-}
-\DevDef{PLL for 1.0 Cs Raman}{
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug all signals (zip tie together)
-  \item\OffBox Unplug 15V and 5V powers (zip tie together)
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plugin 15V and 5V powers
-  \item\OnBox Plugin all signals
-  \item\OnBox Apply settings according to note on Generic tab, Equipment Settings.
-  \end{itemize}
-}
-\DevDef{Homebuilt temperature servo for Cs 1.0 MOT}{
-  \textbf{1st level above Cs tweezer/MOT lasers}\\
-  Switch off/on the front switch
-}
-\DevDef{1st version Till's current controller for Cs MOT}{
-  \textbf{1st level above Cs tweezer/MOT lasers}\\
-  Record current value:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Current&\hphantom{\hspace{3.5cm}}\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug power (zip tie to controller)
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug in power
-  \item\OnBox Turn on
-  \end{itemize}
-}
-\DevDef{Cs 1.0 MOT lock box}{
-  \textbf{1st level above Cs MOT lasers}
-  \begin{itemize}
-  \item\OffBox Make sure the laser is unlocked.
-  \end{itemize}
-}
-\DevDef{Novatech function generator}{
-  \textbf{1st level above Cs MOT lasers}
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Save settings
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Restore settings
-  \end{itemize}
-}
-\DevDef{New Focus Cs Raman lasers drivers (2x)}{
-  \textbf{1st level above Cs Raman lasers}\\
-  Record Temperature, Current, Piezo voltage\\
-  Temperature is accessible in the menu under system status\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    F3 Current&\hphantom{\hspace{3.5cm}}\\\hline
-    F3 Piezo Voltage&\\\hline
-    F3 Temperature&\\\hline
-    F4 Current&\\\hline
-    F4 Piezo Voltage&\\\hline
-    F4 Temperature&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug power
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug in power
-  \item\OnBox (Turn on)
-  \end{itemize}
-}
-\DevDef{SRS shutter driver for Cs}{
-  \textbf{1st level above Cs Raman lasers}\\
-  Switch off/on with the switch on the back.
-}
-\DevDef{New Focus lock box for Cs Raman}{
-  \textbf{1st level above Cs Raman lasers}\\
-  Unplug power.
-}
-\DevDef{Homebuilt temperature servo for Cs tweezer}{
-  \textbf{1st level above Cs tweezer}\\
-  Switch off/on the front switch
-}
-\DevDef{2nd version Till's current controller for Cs Tweezer}{
-  \textbf{1st level above Cs tweezer}\\
-  Record current value:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Current&\hphantom{\hspace{3.5cm}}\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug power (zip tie to controller)
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug in power
-  \item\OnBox Turn on
-  \end{itemize}
-}
-\DevDef{Thorlabs current controller}{
-  \textbf{1st level below Cs tweezer driver}\\
-  Unused\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug power
-  \end{itemize}
-}
-\DevDef{Thorlabs temperature controller for Cs tweezer}{
-  \textbf{1st level above Cs tweezer}\\
-  Record temperature settings\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Setpoint&\hphantom{\hspace{3.5cm}}\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug power
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug in power
-  \item\OnBox Check temperature setting
-  \item\OnBox Turn on
-  \end{itemize}
-}
-\DevDef{Intensity servo for Cs}{
-  \textbf{1st level above Cs tweezer}\\
-  Unplug power
-}
-\subsection{Power supplies}
-\DevDef{Benchtop power supply}{
-  \textbf{1st level above Cs tweezer/MOT lasers}\\
-  Record voltage/current values:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-    Left Current&\\\hline
-    Right Voltage&\\\hline
-    Right Current&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug loads
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Turn off the power supply
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Homebuilt $\pm15,5$V power supply}{
-  \textbf{2nd level above Cs tweezer/MOT lasers}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug load
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Switch off on the back
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Switch on
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Benchtop power supply}{
-  \textbf{1st level next to Cs Raman driver}\\
-  Record voltage/current values:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-    Current&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug loads
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Turn off the power supply
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Homebuilt $24$V power supply}{
-  \textbf{2nd level above Cs Raman lasers}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug load
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Switch off on the back
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Switch on
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Benchtop power supply for Cs Raman locking}{
-  \textbf{2nd level above Cs Raman lockbox}\\
-  Record voltage/current values:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-    Current&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug loads
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Turn off the power supply
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\subsection{Computers}
-\DevDef{Tweezer 1 computer}{
-  \textbf{Check following devices}
-  \begin{itemize}
-  \item\OnBox Thorlabs cameras
-  \item\OnBox Na Raman amplifier
-  \end{itemize}
-}
-\Person{Jessie}
-\textbf{\Large
-  Equipments and power supplies are mostly located around the machine table facing the 1.5 table.
-}\\
-\subsection{Equipments}
-\DevDef{TiSapph}{
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off pump, unplug from wall
-  \item\OffBox Turn off controller, unplug from wall
-  \item\OffBox Turn off chiller, unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into wall, turn on chiller
-  \item\OnBox Plug into wall, turn on controller
-  \item\OnBox Plug into wall, turn on pump
-  \end{itemize}
-}
-\DevDef{Quantel Laser}{
-  \textbf{1st level in the middle, facing 1.5 table}\\
-  Ask Frederic.
-  \vspace{1cm}
-}
-\DevDef{Intensity servo for Na}{
-  \textbf{1st level above Na tweezer, below 1.0 computer control box}\\
-  Unplug power
-}
-\DevDef{1st version Till's current controller for butterfly laser}{
-  \textbf{1st level above TiSapph}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug power (zip tie to controller)
-  \end{itemize}
-}
-\DevDef{Homebuilt temperature servo for butterfly laser}{
-  \textbf{1st level above TiSapph}\\
-  Switch off/on the front switch
-}
-\DevDef{PLL for 1.5 Cs MOT}{
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug all signals (zip tie together)
-  \item\OffBox Unplug 15V and 5V powers (zip tie together)
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plugin 15V and 5V powers
-  \item\OnBox Plugin all signals
-  \item\OnBox Apply settings ???
-  \end{itemize}
-}
-\subsection{Power supplies}
-\DevDef{Homebuilt $24$V power supply}{
-  \textbf{2nd level above NaCs 1.0 chamber, facing the drawers/wall}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug load
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Switch off on the back
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Switch on
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Benchtop power supply for dispensers}{
-  \textbf{1st level above NaCs 1.0 chamber}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug loads
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Turn off the power supply
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Benchtop power supply for 1.5 computer control clock}{
-  \textbf{2nd level next to 1.5 computer control box}\\
-  Record voltage/current values:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-    Current&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug loads
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Turn off the power supply
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Homebuilt $\pm15,5$V power supply}{
-  \textbf{2nd level above TiSapph}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug load
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Switch off on the back
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Switch on
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\subsection{Computers}
-\DevDef{Computer control box for 1.5}{
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox (Do following three steps quickly)
-  \item\OffBox Turn off the box by flipping the switch on the front side of the box
-  \item\OffBox Unplug the high voltage (48V) power supply (circular plug)
-    on the left side of the box. Then unplug the power supply itself fromm the outlet.
-  \item\OffBox Unplug the 12V board power supply.
-    (L.T.E. one with a rectangular connector in the front)
-  \item\OffBox Unplug USB power on the front side near the fan.
-  \item\OffBox Zip tie the three unpluged powers to the computer control box.
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Connect to 3.5G Windfrek clock generator from Tweezer1.
-    Set frequency to 3.5G and amplitude to max.
-  \item\OnBox (Remove power connection zip ties and) Plug in USB power supply.
-  \item\OnBox (Do following three steps quickly)
-  \item\OnBox Plug in the 12V board power supply.
-  \item\OnBox Plug in high voltage power supply. The fans should start spinning.
-  \item\OnBox Turn on the power switch of the box.
-  \end{itemize}
-}
-\Person{Frederic}
-\textbf{\Large
-  Equipments and power supplies are mostly on the 1.5 rack.
-}\\
-\subsection{Equipments}
-\DevDef{Andor Camera for 1.5}{
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Switch off
-  \item\OffBox Switch off chiller
-  \item\OffBox Unplug camera power (zip tie to camera)
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug in camera power
-  \item\OnBox Switch on chiller
-  \item\OnBox Switch on
-  \end{itemize}
-}
-\DevDef{1.5 Feshbach coils}{
-  \textbf{Before power shutdown}
-  \begin{itemize}
-  \item\OffBox Wrap exposed part in napkins to prevent condensations
-  \end{itemize}
-}
-\DevDef{1.5 IGBT}{
-  \textbf{Before power shutdown}
-  \begin{itemize}
-  \item\OffBox Wrap exposed part in napkins to prevent condensations
-  \end{itemize}
-}
-\DevDef{Cooling water}{
-  Valves to close/reopen:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    \OnBox\OffBox&\hphantom{\hspace{5cm}}\\\hline
-    \OnBox\OffBox&\hphantom{\hspace{5cm}}\\\hline
-    \OnBox\OffBox&\hphantom{\hspace{5cm}}\\\hline
-    \OnBox\OffBox&\hphantom{\hspace{5cm}}\\\hline
-    \OnBox\OffBox&\hphantom{\hspace{5cm}}\\\hline
-    \OnBox\OffBox&\hphantom{\hspace{5cm}}\\\hline
-    \OnBox\OffBox&\hphantom{\hspace{5cm}}\\\hline
-    \OnBox\OffBox&\hphantom{\hspace{5cm}}\\\hline
-    \OnBox\OffBox&\hphantom{\hspace{5cm}}\\\hline
-    \OnBox\OffBox&\hphantom{\hspace{5cm}}\\\hline
-    \OnBox\OffBox&\hphantom{\hspace{5cm}}\\\hline
-    \OnBox\OffBox&\hphantom{\hspace{5cm}}\\\hline
-  \end{tabular}\\
-}
-\DevDef{HV amplifiers for 1.5 piezo mirrors}{
-  \textbf{Top level of 1.5 rack}\\
-  \textbf{Turn on-off together with the function generator below
-    and the high voltage power supply above the 1.0 machine table}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off the function generator
-  \item\OffBox Unplug function generator output (zip tie and label)
-  \item\OffBox Unplug HV power supply from the wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plugin HV power supply to the wall
-  \item\OnBox Plugin function generator output
-  \item\OnBox Turn on the function generator
-  \end{itemize}
-}
-\DevDef{Pump}{
-  \textbf{Bottom level 1.5 Rack}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug from walls
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into wall
-  \item\OnBox Turn on (should be enough)
-  \end{itemize}
-}
-\subsection{Power supplies}
-\DevDef{Benchtop power supply}{
-  \textbf{2nd level (from the top) 1.5 Rack. Next to coil servo}\\
-  Record voltage/current values:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-    Left Current&\\\hline
-    Right Voltage&\\\hline
-    Right Current&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug loads
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Turn off the power supply
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Benchtop power supply}{
-  \textbf{Bottom level 1.5 Rack. Next to pump}\\
-  Record voltage/current values:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-    Current&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug loads
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Turn off the power supply
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\subsection{Computers}
-\DevDef{Tweezer 4 computer}{
-  \textbf{Check following devices}
-  \begin{itemize}
-  \item\OnBox Andor camera
-  \item\OnBox Thorlabs camera
-  \end{itemize}
+\eqar{
+  n_{Cu}=&\rho_{Cu} / m_{Cu}\\
+  =&8.96\mathrm{g}\cdot \mathrm{cm}^{-3} / 63.546\mathrm{g} \cdot 6.02\cdot10^{23}\\
+  =&8.49\cdot10^{22}\mathrm{cm}^{-3}
+  \intertext{Which corresponds to a surface charge density of}
+  \sigma_{Cu}=&n_{Cu}^{2/3}\\
+  =&1.93\cdot10^{15}\mathrm{cm}^{-2}
 }
 
+With our assumption of a single charge layer, this corresponds to a surface electric field of
+\eqar{
+  E=&\frac{e\sigma_{Cu}}{\varepsilon_0}\\
+  =&3.49\cdot10^{11}\mathrm{V}\cdot\mathrm{m}^{-1}
+}
+Any field higher than this will likely lead to field electron or ion emission.
+The number agrees in orders of magnitude with the typical field found in field ion
+or electron microscope which is ``a few V/\AA''.
+(Note that the in field ion microscope the background gas is being ionized
+and not the material surface so the material can likely afford a stronger field)
+
+(Note that the argument here does not fully apply to electrolytic capacitor since
+the charge is partially stored as ions)
+
+This limits the energy density (since its proportional to field square) of a capacitor
+but it's very hard to convert this to a capacitance since it's strongly manufacture process
+dependent. However, it is possible to compare this to the other effect that limits the
+energy density, dielectric strength.
+
+\subsubsection{Dielectric strength}
+This is the max field that can be applied on a material before breakdown occurs.
+It depends strongly on the material so I do not have a good way to estimate the value.
+However, from a table on Wikipedia, the typical values are between
+$10^{6}\ \text{and}\ 10^{9}\mathrm{V}\cdot\mathrm{m}^{-1}$,
+much smaller than the ion/electron emission threshold of conductors so this should be
+the limiting factor of the energy density in most (all) cases.
+
+\subsection{Actual reason, for real}
+As previously mentioned, the reason one typically get a small capacitor value in SI unit is,
+well, the SI unit itself. Since the size of a plate capacitor with $\varepsilon_r\approx1$
+is given by $\dfrac{\varepsilon_0 S}{d}$, this is really about why $\varepsilon_0$ has a tiny
+value in SI unit. As Nick pointed out, in order to understand this, we need to realize that
+the charge unit in SI is defined based on Ampere, which is defined based on force between
+current. Since $\dfrac{1}{\varepsilon_0}$ qualify the electric static force between a unit
+amount of charge, the reason capacitors are small is really because for the current
+that generate the ``standard'' (defined later) amount of force between two wires, the force
+between the charge delivered by that current in 1 second is large in SI unit.\\
+
+We can directly calculate the ratio of the two forces with a time scale of $t=1\mathrm{s}$
+and length scale of $l=1\mathrm{m}$
+\eqar{
+  F_{mag}=&\frac{\mu_0 I^2}{2\pi L}L\\
+  =&\frac{\mu_0 I^2}{2\pi}\\
+  F_{ele}=&\frac{Q^2}{4\pi\varepsilon_0 L^2}\\
+  =&\frac{I^2t^2}{4\pi\varepsilon_0 L^2}\\
+  \dfrac{F_{ele}}{F_{mag}}=&\frac{I^2t^2}{4\pi\varepsilon_0 L^2}\frac{2\pi}{\mu_0 I^2}\\
+  =&\frac{c^2t^2}{2L^2}\\
+  =&\frac{c^2}{v^2}
+}
+where $v\equiv\sqrt{2}\dfrac{L}{t}$ is a human velocity scale.
+Here we clearly see that the electronic static interaction is much larger than
+magnetic interaction \textbf{for unit charge and current in SI unit} because
+the SI unit is defined with human length and time scale which gives a velocity scale
+much smaller than the speed of light. In fact, the ``standard'' force between
+two current carrying wires is already much smaller than $1\mathrm{N}$ but it is not enough
+to make the corresponding electric static interaction small enough.
+
+Note that the discussion above was based on the definition of Ampere.
+However, given that the standard force generated between wires is much smaller than $1\mathrm{N}$,
+it is likely that the rough magnitude of the Ampere unit was historically selected
+for other reasons, likely related to how current is generated back then.
+I could not find a good note about relation between early generator and
+current unit definition and since this strongly depends on the winding numbers and
+early permanent magnet I would stop speculating how it is selected.
+
 \end{document}

### 2018-04-03 presentations/2018-04-04_hqoc/plot_eit.jl
[presentations/2018-04-04_hqoc] change eit plot

@@ -1,0 +1,27 @@
+#!/usr/bin/julia
+
+push!(LOAD_PATH, joinpath(@__DIR__, "../../lib"))
+
+using NaCsCalc.Utils: interactive
+using NaCsData
+using NaCsPlot
+using PyPlot
+using MAT
+
+matopen(joinpath(@__DIR__, "AT_690peak_1.mat")) do f
+    global xplot, yplot, yerrplot
+    xplot = read(f, "xplot")
+    yplot = read(f, "yplot")
+    yerrplot = read(f, "yerrplot")
+end
+
+const prefix = joinpath(@__DIR__, "eit")
+
+figure()
+errorbar(xplot[3:end], yplot[3:end], yerrplot[3:end])
+xlabel("Two photon detuning (MHz)")
+ylim([0, 1])
+grid()
+NaCsPlot.maybe_save("$(prefix)")
+
+NaCsPlot.maybe_show()

### 2018-04-05 experiments/cs_coprop_201712/plot_20171228_172950_multi_shift_trap.jl
[experiments/cs_coprop_201712] Plots for joint group meeting presentation

@@ -10,6 +10,8 @@ using DataStructures
 using LsqFit
 import NaCsCalc.Format: Unc, Sci
 
+NaCsPlot.bold()
+
 const iname_a = joinpath(@__DIR__, "data", "data_20171228_172950.mat")
 const params_a, logicals_a = NaCsData.load_striped_mat(iname_a)
 
@@ -209,5 +211,27 @@ ylabel("Frequency (kHz)")
 legend(bbox_to_anchor=(1.05, 1), loc=2, borderaxespad=0.0)
 grid()
 NaCsPlot.maybe_save("$(prefix)_resonance")
+
+figure()
+p = errorbar(TrapDepths, res_50_mf4, res_50_mf4_unc, label="\$50MHz\\ m_F=4\$", fmt="o")
+c = p[1][:get_color]()
+plot(trapdepths_plot, _trap_model.(trapdepths_plot, true, (trap_mf4_fit.param,)), color=c)
+gcf()[:text](0.89, 0.30,
+             "\$\\delta^{m_F4}_{50}=$(Unc(trap_mf4_param[2] * 15.5, trap_mf4_unc[2] * 15.5))\\ kHz\$",
+             color=c, fontsize=20, horizontalalignment="left", verticalalignment="center",
+             clip_on=false)
+p = errorbar(TrapDepths, res_62_mf4, res_62_mf4_unc, label="\$62MHz\\ m_F=4\$", fmt="o")
+c = p[1][:get_color]()
+plot(trapdepths_plot, _trap_model.(trapdepths_plot, false, (trap_mf4_fit.param,)), color=c)
+gcf()[:text](0.89, 0.15,
+             "\$\\delta^{m_F4}_{62}=$(Unc(trap_mf4_param[3] * 15.5, trap_mf4_unc[3] * 15.5))\\ kHz\$",
+             color=c, fontsize=20, horizontalalignment="left", verticalalignment="center",
+             clip_on=false)
+title("Resonance")
+xlabel("Trap depth (mW)")
+ylabel("Frequency (kHz)")
+legend(bbox_to_anchor=(1.05, 1), loc=2, borderaxespad=0.0)
+grid()
+NaCsPlot.maybe_save("$(prefix)_resonance_mf4")
 
 NaCsPlot.maybe_show()

### 2018-04-05 experiments/cs_coprop_201712/plot_20180103_211324_multi_shift_trap4.jl

@@ -10,6 +10,8 @@ using DataStructures
 using LsqFit
 import NaCsCalc.Format: Unc, Sci
 
+NaCsPlot.bold()
+
 const iname_a = joinpath(@__DIR__, "data", "data_20180103_211324.mat")
 const params_a, logicals_a = NaCsData.load_striped_mat(iname_a)
 
@@ -210,5 +212,27 @@ ylabel("Frequency (kHz)")
 legend(bbox_to_anchor=(1.05, 1), loc=2, borderaxespad=0.0)
 grid()
 NaCsPlot.maybe_save("$(prefix)_resonance")
+
+figure()
+p = errorbar(TrapDepths, res_50_mf4, res_50_mf4_unc, label="\$50MHz\\ m_F=4\$", fmt="o")
+c = p[1][:get_color]()
+plot(trapdepths_plot, _trap_model.(trapdepths_plot, true, (trap_mf4_fit.param,)), color=c)
+gcf()[:text](0.89, 0.45,
+             "\$\\delta^{m_F4}_{50}=$(Unc(trap_mf4_param[2] * 15.5, trap_mf4_unc[2] * 15.5))\\ kHz\$",
+             color=c, fontsize=20, horizontalalignment="left", verticalalignment="center",
+             clip_on=false)
+p = errorbar(TrapDepths, res_62_mf4, res_62_mf4_unc, label="\$62MHz\\ m_F=4\$", fmt="o")
+c = p[1][:get_color]()
+plot(trapdepths_plot, _trap_model.(trapdepths_plot, false, (trap_mf4_fit.param,)), color=c)
+gcf()[:text](0.89, 0.15,
+             "\$\\delta^{m_F4}_{62}=$(Unc(trap_mf4_param[3] * 15.5, trap_mf4_unc[3] * 15.5))\\ kHz\$",
+             color=c, fontsize=20, horizontalalignment="left", verticalalignment="center",
+             clip_on=false)
+title("Resonance")
+xlabel("Trap depth (mW)")
+ylabel("Frequency (kHz)")
+legend(bbox_to_anchor=(1.05, 1), loc=2, borderaxespad=0.0)
+grid()
+NaCsPlot.maybe_save("$(prefix)_resonance_mf4")
 
 NaCsPlot.maybe_show()

### 2018-04-16 presentations/2018-04-04_hqoc/plot_eit.jl
[presentations/2018-04-04_hqoc] update

@@ -19,7 +19,8 @@ const prefix = joinpath(@__DIR__, "eit")
 
 figure()
 errorbar(xplot[3:end], yplot[3:end], yerrplot[3:end])
-xlabel("Two photon detuning (MHz)")
+xlabel("\$\\delta\$, Two photon detuning (MHz)")
+ylabel("Two body survival")
 ylim([0, 1])
 grid()
 NaCsPlot.maybe_save("$(prefix)")

### 2018-05-25 experiments/eit_v0_201804/plot_20180421_002556_eit.jl
[experiments/eit_v0_201804] plot

@@ -1,0 +1,72 @@
+#!/usr/bin/julia
+
+push!(LOAD_PATH, joinpath(@__DIR__, "../../lib"))
+
+using NaCsCalc.Utils: interactive
+using NaCsData
+using NaCsPlot
+using PyPlot
+using DataStructures
+using LsqFit
+
+const iname_a = joinpath(@__DIR__, "data", "data_20180421_002556.mat")
+const params_a, logicals_a = NaCsData.load_striped_mat(iname_a)
+
+function selector(logicals)
+    @assert size(logicals, 2) == 1
+    if !logicals[1] || !logicals[2]
+        return Int[1, 0, 0]
+    end
+    return Int[1, 1, logicals[3] && logicals[4]]
+end
+
+data_2body = NaCsData.select_count(params_a, logicals_a, selector)
+
+const spec_a = (298.5 .+ linspace(-10, 10, 51),
+                298.5 .+ linspace(-5, 5, 51),
+                298.5 .+ linspace(-3, 3, 51),
+                298.5 .+ linspace(-3, 3, 51),
+                298.5 .+ linspace(-3, 3, 51))
+
+const split_2body = NaCsData.split_data(data_2body, spec_a)
+
+const prefix = joinpath(@__DIR__, "imgs", "data_20180421_002556")
+
+function fit_survival(model, data, p0; plotx=nothing, use_unc=false, plot_scale=1.1)
+    if use_unc
+        params, ratios, uncs = NaCsData.get_values(data)
+    else
+        params, ratios, uncs = NaCsData.get_values(data, 0.0)
+    end
+    if plotx === nothing
+        lo = minimum(params)
+        hi = maximum(params)
+        span = hi - lo
+        mid = (hi + lo) / 2
+        plotx = linspace(mid - span * plot_scale / 2, mid + span * plot_scale / 2, 10000)
+    end
+    if use_unc
+        fit = curve_fit(model, params, ratios[:, 2], 1 ./ uncs[:, 2].^2, p0)
+    else
+        fit = curve_fit(model, params, ratios[:, 2], p0)
+    end
+    return (param=fit.param, unc=estimate_errors(fit),
+            plotx=plotx, ploty=model.(plotx, (fit.param,)))
+end
+
+function eit_model(x, p)
[…]

### 2018-05-25 experiments/eit_v0_201804/plot_20180421_002556_eit.jl
[experiments/eit_v0_201804] update title

@@ -64,7 +64,7 @@ figure()
 NaCsPlot.plot_survival_data(split_2body[2], fmt="C0o")
 plot(fit_2body_2.plotx, fit_2body_2.ploty, "k")
 grid()
-title("EIT")
+title("EIT spectrum")
 xlabel("Two photon detuning (MHz)")
 ylabel("Probability of both survive")
 NaCsPlot.maybe_save("$(prefix)_eit-v0")

### 2018-05-25 experiments/eit_v0_201804/plot_20180421_002556_eit.jl
[presentations/damop-2018-poster] rename EIT

@@ -64,7 +64,7 @@ figure()
 NaCsPlot.plot_survival_data(split_2body[2], fmt="C0o")
 plot(fit_2body_2.plotx, fit_2body_2.ploty, "k")
 grid()
-title("EIT spectrum")
+title("Dark resonance spectrum")
 xlabel("Two photon detuning (MHz)")
 ylabel("Probability of both survive")
 NaCsPlot.maybe_save("$(prefix)_eit-v0")

### 2018-06-20 designs/pre-amp/notes.tex
[designs/pre-amp] more notes

\documentclass[10pt,fleqn]{article}

\usepackage{hyperref}

\begin{document}

\section{Value selection for active low pass filter}
\begin{tabular}{|c|c|c|c|c|c|c|}
  \hline
  Gain&$f_{cutoff}\ (\mathrm{kHz})$&$R_5\ (\mathrm{k\Omega})$&$R_6\ (\mathrm{k\Omega})$&$R_7\ (\mathrm{k\Omega})$&$C_{12}\ (\mathrm{pF})$&$C_{13}\ (\mathrm{pF})$\\\hline
  1&10&1.54&1.54&11.1&10000&910\\\hline
  1&20&4.99&5.0&4.64&2200&750\\\hline
  1&30&1.01&1.01&1.1&6800&2200\\\hline
  0.5&10&5.0&2.5&17.4&4700&750\\\hline
  0.5&20&2.0&1.01&10.7&5600&620\\\hline
  0.5&30&3.88&1.96&6.34&2200&620\\\hline
  0.25&10&2.21&0.562&18.7&15000&820\\\hline
  0.25&20&2.7&0.681&10.7&6800&750\\\hline
  0.25&30&1.82&0.464&6.57&6800&820\\\hline
\end{tabular}
The active filter uses a low-pass multiple-feedback (MFB) architecture
and the table gives the values to create a second order Bessel filter.
All the resistors and capacitors are currently in stock at Digikey.
See \href{http://www.ti.com/lit/an/sloa049b/sloa049b.pdf}
{Active Low-Pass Filter Design}\footnote{http://www.ti.com/lit/an/sloa049b/sloa049b.pdf}
for the formula used and comparison between different filter type and circuit topology.

\section{Other tweaks}
\begin{enumerate}
\item $R_8$ and $C_{14}$ can be used for additional filter.
\item If a higher cutoff frequency is needed, reduce or remove $C_2$ to increase the
  input cutoff frequency.
\end{enumerate}

\end{document}

### 2019-04-26 presentations/2019-04-27_shutdown/checklist.tex
[presentation/2019-04-27_shutdown] import equipment list

--- 2017-08-01 presentations/2017-08-02_shutdown/checklist.tex
@@
 \usepackage{hyperref}
+\usepackage{longtable}
+% \makeatletter
+% \let\oldlt\longtable
+% \let\endoldlt\endlongtable
+% \def\longtable{\@ifnextchar[\longtable@i \longtable@ii}
+% \def\longtable@i[#1]{\begin{figure}[t]
+% \onecolumn
+% \begin{minipage}{0.5\textwidth}
+% \oldlt[#1]
+% }
+% \def\longtable@ii{\begin{figure}[t]
+% \onecolumn
+% \begin{minipage}{0.5\textwidth}
+% \oldlt
+% }
+% \def\endlongtable{\endoldlt
+% \end{minipage}
+% \twocolumn
+% \end{figure}}
+% \makeatother
+
 \usetikzlibrary{
@@
 
+\onecolumn
 \Person{Yichao}{
@@
 }
+\begin{longtable}{|c|c|c|}
+  \hline
+  \textbf{Equipment}&\textbf{Location}&\textbf{Notes}\\\hline
+  \multicolumn{3}{|c|}{\textbf{Laser table facing computer or the wall} west $\rightarrow$ south}\\\hline
+  Benchtop power for Cs MOT beat lock&Lv1 above 1.0 Cs MOT&\\\hline
+  PLL for Cs MOT&Below Cs MOT&Save setting\\\hline
+  Home power (+-15,5)&Lv2 above Cs MOT&\\\hline
+  Valan&1.5 amplifier stack Lv1 above 1.0 Cs MOT&Save setting\\\hline
+  Till driver v2 for 1.5 Na Raman&Lv1 above 1.5 Na Raman&\\\hline
+  Temp servo for 1.5 Na Raman seed&Lv1 above 1.5 Na Raman&\\\hline
+  Temp servo for 1.5 Na Raman doubler&Lv1 above 1.5 Na Raman&\\\hline
+  PLL for Cs Raman&Next to 1.0 Cs Raman&Save setting\\\hline
+  New Focus driver for Cs Raman&Lv1 above 1.0 Cs Raman&Save setting\\\hline
+  Benchtop power (x3)&Lv2 above 1.0 Cs MOT&\\\hline
+  Home power (24V) x2&Lv2 above 1.0 Cs Raman&\\\hline
+  Benchtop power&Lv1 next to New Focus driver&\\\hline
+  Shutter driver&Lv1 above 1.0 Cs Raman&\\\hline
+  New Focus lock box for 1.0 Cs Raman&Lv1 above 1.0 Cs Raman&\\\hline
+  Thorlabs temp servo for 1.0 Na Raman doubler&Lv1 above 1.0 Na seed&\\\hline
+  Timebase drivers for 1.0 Na Raman and Na D2&Lv1 above Thorlabs temp servo&Save setting\\\hline
+  Benchtop power for 1.0 Cs Raman&Lv2 above New Focus lock box&\\\hline
+  High voltage power&Lv2 above timebase drivers&\\\hline
+  Home lock box for Na D2&Lv1 above 1.0 Na seed&\\\hline
+  MPB Raman laser&Lv1 above 1.0 Na MOT&Save setting\\\hline
+  Oscilloscope for Na D2 lock&Lv1 above MPB Raman laser&\\\hline
+  Benchtop power for 1.0 Na Raman seed&Lv2 above oscilloscope&\\\hline
+\end{longtable}
+\twocolumn
+
 \subsection{Equipments}
@@
 }
-\Person{Jon}{
+
+\onecolumn
+\Person{Kenneth}{
   Equipments and power supplies are mostly located around the machine table facing the laser table
@@
 }
+\begin{longtable}{|c|c|c|}
+  \hline
+  \textbf{Equipment}&\textbf{Location}&\textbf{Notes}\\\hline
+  \multicolumn{3}{|c|}{\textbf{Laser table side facing machine table} north $\rightarrow$ east}\\\hline
+  671 EOM stack&Floor&\\\hline
+  1550 Amp&Floor&\\\hline
+  Radio computer&Lv2&\\\hline
+  Benchtop power&Lv2 next to radio computer&\\\hline
+  High voltage power&Lv2 next to benchtop power&\\\hline
+  Variac for Na cell&Lv1 above 1.0 Na MOT&\\\hline
+  Shutter driver&Lv1 next to variac&\\\hline
+  Home lock box for 1.0 Na D1&Lv1 next to shutter driver&\\\hline
+  1038 Amp&Floor&\\\hline
+  1038 Timebase laser&Table&\\\hline
+  FPGA box for 1.0&Lv2&\\\hline
+  Thorlabs temp servo for Na D1 doubler&Lv1 above Na D1&\\\hline
+  Thorlabs temp servo for Na D1 seed&Lv1 above Na D1&\\\hline
+  Thorlabs current for Na D1 seed&Lv1 above Na D1&\\\hline
+  Benchtop power&Lv2 above Thorlabs controllers for Na D1 seed&\\\hline
+  Home power (24)&Lv2 next to benchtop power&\\\hline
+  Benchtop power x2&Lv2 next to Home power (24)&\\\hline
+  Till driver v2 for 976&Lv1 above Na D1 doubler&\\\hline
+  Thorlabs temp servo for Cs tweezer&Lv1 above Timebase 1038 beam&\\\hline
+  Thorlabs current (2A) (off)&Lv1 above Thorlabs temp servo&\\\hline
+  Till driver v2 for 671&Lv1 above Thorlabs current&\\\hline
+  Home temp servo x2&Lv1 above Timebase 1038 control box&\\\hline
+  Oscilloscope&Lv1&\\\hline
+  \multicolumn{3}{|c|}{\textbf{Machine table side facing laser table} south}\\\hline
+  Thorlabs current for 1.5 Cs MOT&Lv1 above 1.5 Cs&\\\hline
+  Till driver v2 for 1.5 Cs RP&Lv1 above 1.5 Cs&\\\hline
+  Home temp servo (x2) for 1.5 Cs MOT/RP&Lv1 above 1.5 Cs&\\\hline
+  Oscilloscope for 1.5 Cs&Lv1 above 1.5 Cs&\\\hline
+  Home lock box for 1.5 Cs&Lv1 above 1.5 Cs&\\\hline
+  Novatec for 1.5 Cs lock&Lv1 above 1.5 Cs&Save setting\\\hline
+  Benchtop power&Lv2 1.5 Cs MOT/RP current&\\\hline
+  Home power (24) x2&Lv2 next to benchtop power&\\\hline
+  Benchtop power&Lv2 on two home power (24)&\\\hline
+  Home power (+-15,5)&Lv2 middle&\\\hline
+  Benchtop power (x2) for uWave Amp&Lv2 next to home power (+-15,5)&\\\hline
+  Benchtop power (x2)&Lv1 above 1.5 Na&\\\hline
+  High voltage power&Lv1 next to 2 benchtop power&\\\hline
+  Function generator for 1.0 MOT piezo&Lv1&\\\hline
+  Temperature and pump controllers for cavity&Lv1 next to function generator&\\\hline
+  Water chiller for uWave breadboard&Floor&\\\hline
+  SAES pump&Lv1 above 1.0 chamber&\\\hline
+  Benchtop power x2&Lv2 next to coil servo&\\\hline
+\end{longtable}
+\twocolumn
 \subsection{Equipments}
@@
 }
-\Person{Lee}{
-  Equipments and power supplies are mostly located around the laser table
-  on the computer area side.\\
-  Check Yichao's part after everything are off.
-}
-\subsection{Equipments}
-\DevDef{PLL for 1.0 Cs MOT}{
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug all signals (zip tie together)
-  \item\OffBox Unplug 15V and 5V powers (zip tie together)
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plugin 15V and 5V powers
-  \item\OnBox Plugin all signals
-  \item\OnBox Apply settings according to note on Generic tab, Equipment Settings.
-  \end{itemize}
-}
-\DevDef{PLL for 1.0 Cs Raman}{
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug all signals (zip tie together)
-  \item\OffBox Unplug 15V and 5V powers (zip tie together)
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plugin 15V and 5V powers
-  \item\OnBox Plugin all signals
-  \item\OnBox Apply settings according to note on Generic tab, Equipment Settings.
-  \end{itemize}
-}
-\DevDef{Homebuilt temperature servo for Cs 1.0 MOT}{
-  \textbf{1st level above Cs tweezer/MOT lasers}\\
-  Switch off/on the front switch
-}
-\DevDef{1st version Till's current controller for Cs MOT}{
-  \textbf{1st level above Cs tweezer/MOT lasers}\\
-  Record current value:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Current&\hphantom{\hspace{3.5cm}}\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug power (zip tie to controller)
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug in power
-  \item\OnBox Turn on
-  \end{itemize}
-}
-\DevDef{Cs 1.0 MOT lock box}{
-  \textbf{1st level above Cs MOT lasers}
-  \begin{itemize}
-  \item\OffBox Make sure the laser is unlocked.
-  \end{itemize}
-}
-\DevDef{Novatech function generator}{
-  \textbf{1st level above Cs MOT lasers}
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Save settings
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Restore settings
-  \end{itemize}
-}
-\DevDef{New Focus Cs Raman lasers drivers (2x)}{
-  \textbf{1st level above Cs Raman lasers}\\
-  Record Temperature, Current, Piezo voltage\\
-  Temperature is accessible in the menu under system status\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    F3 Current&\hphantom{\hspace{3.5cm}}\\\hline
-    F3 Piezo Voltage&\\\hline
-    F3 Temperature&\\\hline
-    F4 Current&\\\hline
-    F4 Piezo Voltage&\\\hline
-    F4 Temperature&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug power
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug in power
-  \item\OnBox (Turn on)
-  \end{itemize}
-}
-\DevDef{SRS shutter driver for Cs}{
-  \textbf{1st level above Cs Raman lasers}\\
-  Switch off/on with the switch on the back.
-}
-\DevDef{New Focus lock box for Cs Raman}{
-  \textbf{1st level above Cs Raman lasers}\\
-  Unplug power.
-}
-\DevDef{Homebuilt temperature servo for Cs tweezer}{
-  \textbf{1st level above Cs tweezer}\\
-  Switch off/on the front switch
-}
-\DevDef{2nd version Till's current controller for Cs Tweezer}{
-  \textbf{1st level above Cs tweezer}\\
-  Record current value:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Current&\hphantom{\hspace{3.5cm}}\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug power (zip tie to controller)
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug in power
-  \item\OnBox Turn on
-  \end{itemize}
-}
-\DevDef{Thorlabs current controller}{
-  \textbf{1st level below Cs tweezer driver}\\
-  Unused\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug power
-  \end{itemize}
-}
-\DevDef{Thorlabs temperature controller for Cs tweezer}{
-  \textbf{1st level above Cs tweezer}\\
-  Record temperature settings\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Setpoint&\hphantom{\hspace{3.5cm}}\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug power
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug in power
-  \item\OnBox Check temperature setting
-  \item\OnBox Turn on
-  \end{itemize}
-}
-\DevDef{Intensity servo for Cs}{
-  \textbf{1st level above Cs tweezer}\\
-  Unplug power
-}
-\subsection{Power supplies}
-\DevDef{Benchtop power supply}{
-  \textbf{1st level above Cs tweezer/MOT lasers}\\
-  Record voltage/current values:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-    Left Current&\\\hline
-    Right Voltage&\\\hline
-    Right Current&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug loads
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Turn off the power supply
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Homebuilt $\pm15,5$V power supply}{
-  \textbf{2nd level above Cs tweezer/MOT lasers}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug load
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Switch off on the back
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Switch on
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Benchtop power supply}{
-  \textbf{1st level next to Cs Raman driver}\\
-  Record voltage/current values:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-    Current&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug loads
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Turn off the power supply
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Homebuilt $24$V power supply}{
-  \textbf{2nd level above Cs Raman lasers}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug load
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Switch off on the back
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Switch on
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Benchtop power supply for Cs Raman locking}{
-  \textbf{2nd level above Cs Raman lockbox}\\
-  Record voltage/current values:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-    Current&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug loads
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Turn off the power supply
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\subsection{Computers}
-\DevDef{Tweezer 1 computer}{
-  \textbf{Check following devices}
-  \begin{itemize}
-  \item\OnBox Thorlabs cameras
-  \item\OnBox Na Raman amplifier
-  \end{itemize}
-}
+
+\onecolumn
 \Person{Jessie}{
@@
 }
+\begin{longtable}{|c|c|c|}
+  \hline
+  \textbf{Equipment}&\textbf{Location}&\textbf{Notes}\\\hline
+  \textbf{Machine table Facing the wall}&north&\\\hline
+  Benchtop power&Lv2&\\\hline
+  Home power (24)&Lv2 above 1.0 tweezer breadboard&\\\hline
+  Home power (+-15,5)&Lv2 above home power (24)&\\\hline
+  Benchtop power x9&Lv2 next to home power (24) and (+-15,5)&\\\hline
+  Current servo for compensation coil&Lv1 below home power (24)&\\\hline
+  Kenneth servo for 1.0 Cs tweezer&Lv1&\\\hline
+  High voltage Amp for 630 lock&Lv1&\\\hline
+  Vincent servo x2 for STIRAP lasers&Lv1&\\\hline
+  Greiner servo for 1.0 Na tweezer&Lv1 above Vincent servos&\\\hline
+  Rack for STRAP&Lv1 next to Vincent servos&\\\hline
+  Till driver v2 x2 for STIRAP lasers&Lv1 above rack for 1.5&\\\hline
+  Home temp servo x3 for STIRAP&Lv2 next to 9x benchtop power&\\\hline
+  FPGA box for 1.5&Lv2&\\\hline
+  Home power (+-15,5)&Lv2 next to FPGA box&\\\hline
+  Benchtop power x2&Lv2 on home power (+-15,5)&\\\hline
+  Benchtop power&Lv2 next to home power (+-15,5)&\\\hline
+  Benchtop power&Floor rack Lv1&\\\hline
+  Till driver v2 x2 for 1.5 Cs Raman&Floor rack Lv2&\\\hline
+  Kenneth servo for 1.5 Cs Raman phase lock&Floor rack Lv2 above Till drivers&\\\hline
+  Benchtop power&Floor rack Lv2 next to Till drivers&\\\hline
+  Home temp servo x2 for 1.5 Cs Raman&Floor rack Lv2&\\\hline
+  Piezo driver for 1.5 Cs Raman&Floor rack Lv2 above home temp servos&\\\hline
+  Delay generator for 1.5 Na&Lv1 below 1.5 output panel&Save setting\\\hline
+  Till driver v2 for 1.0 Innolume&Lv1 next to delay generator&\\\hline
+  Kenneth servo for 1.5 tweezers&Lv1&\\\hline
+  Home temp servo for 1.0 Innolume&Lv1&\\\hline
+  Shutter driver&Lv1 on M2 controller&\\\hline
+  TiSapph&Floor&\\\hline
+  Function generator for 1.0 Na switching&Lv1 above TiSapph&Save setting\\\hline
+  Keithley power for 1.0 Innolume&Lv2 above TiSapph&\\\hline
+  Till driver v2 for 1.0 Cs MOT&Lv2 above 1.5 Cs MOT&\\\hline
+  Home temp servo for 1.0 Cs MOT&Lv2 on Till driver v2&\\\hline
+  Benchtop power&Lv2 facing computer&\\\hline
+  High voltage power&Above Lv2 on power outlet&\\\hline
+  \textbf{1.5 Rack}&&\\\hline
+  Home power (24)&Bottom level&\\\hline
+  SEAS pump controller&Middle left&\\\hline
+  Benchtop power&Middle next to pump controller&\\\hline
+  Oscilloscope for 1.5 monitor&Above pump controller&\\\hline
+  Benchtop power for 1.5 coil&Above oscilloscope&\\\hline
+  High voltage Amp for 1.5 MOT piezo&Top level&\\\hline
+  Function generator for 1.5 MOT piezo&Top level on high voltage Amp&\\\hline
+  \textbf{Below 1.5 table}&&\\\hline
+  Benchtop power x3&Near outer edge&\\\hline
+  IGBT stack&Floor&\\\hline
+  LED driver&Near inner edge&\\\hline
+  AWG computer&Floor&\\\hline
+  \textbf{Above 1.5 table}&&\\\hline
+  Benchtop power&Lv1&\\\hline
+  Benchtop power&Lv2&\\\hline
+  Radio computer&Lv2&\\\hline
+\end{longtable}
+\twocolumn
+
 \subsection{Equipments}
@@
 }
-\Person{Frederic}{
-  Equipments and power supplies are mostly on the 1.5 rack.\\
-  Check Jon's part after everything are off.
-}
-\subsection{Equipments}
-\DevDef{Andor Camera for 1.5}{
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Switch off
-  \item\OffBox Switch off chiller
-  \item\OffBox Unplug camera power (zip tie to camera)
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug in camera power
-  \item\OnBox Switch on chiller
-  \item\OnBox Switch on
-  \end{itemize}
-}
-\DevDef{1.5 Feshbach coils}{
-  \textbf{Before power shutdown}
-  \begin{itemize}
-  \item\OffBox Wrap exposed part in napkins to prevent condensations
-  \end{itemize}
-}
-\DevDef{1.5 IGBT}{
-  \textbf{Before power shutdown}
-  \begin{itemize}
-  \item\OffBox Wrap exposed part in napkins to prevent condensations
-  \end{itemize}
-}
-\DevDef{Cooling water}{
-  Valves to close/reopen:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    \OnBox\OffBox&\hphantom{\hspace{5cm}}\\\hline
-    \OnBox\OffBox&\hphantom{\hspace{5cm}}\\\hline
-    \OnBox\OffBox&\hphantom{\hspace{5cm}}\\\hline
-    \OnBox\OffBox&\hphantom{\hspace{5cm}}\\\hline
-    \OnBox\OffBox&\hphantom{\hspace{5cm}}\\\hline
-    \OnBox\OffBox&\hphantom{\hspace{5cm}}\\\hline
-    \OnBox\OffBox&\hphantom{\hspace{5cm}}\\\hline
-    \OnBox\OffBox&\hphantom{\hspace{5cm}}\\\hline
-    \OnBox\OffBox&\hphantom{\hspace{5cm}}\\\hline
-    \OnBox\OffBox&\hphantom{\hspace{5cm}}\\\hline
-    \OnBox\OffBox&\hphantom{\hspace{5cm}}\\\hline
-    \OnBox\OffBox&\hphantom{\hspace{5cm}}\\\hline
-  \end{tabular}\\
-}
-\DevDef{HV amplifiers for 1.5 piezo mirrors}{
-  \textbf{Top level of 1.5 rack}\\
-  \textbf{Turn on-off together with the function generator below
-    and the high voltage power supply above the 1.0 machine table}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off the function generator
-  \item\OffBox Unplug function generator output (zip tie and label)
-  \item\OffBox Unplug HV power supply from the wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plugin HV power supply to the wall
-  \item\OnBox Plugin function generator output
-  \item\OnBox Turn on the function generator
-  \end{itemize}
-}
-\DevDef{Pump}{
-  \textbf{Bottom level 1.5 Rack}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug from walls
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into wall
-  \item\OnBox Turn on (should be enough)
-  \end{itemize}
-}
-\subsection{Power supplies}
-\DevDef{Benchtop power supply}{
-  \textbf{2nd level (from the top) 1.5 Rack. Next to coil servo}\\
-  Record voltage/current values:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-    Left Current&\\\hline
-    Right Voltage&\\\hline
-    Right Current&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug loads
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Turn off the power supply
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Benchtop power supply}{
-  \textbf{Bottom level 1.5 Rack. Next to pump}\\
-  Record voltage/current values:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-    Current&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug loads
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Turn off the power supply
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\subsection{Computers}
-\DevDef{Tweezer 4 computer}{
-  \textbf{Check following devices}
-  \begin{itemize}
-  \item\OnBox Andor camera
-  \item\OnBox Thorlabs camera
-  \end{itemize}
-}
 

### 2019-04-26 presentations/2019-04-27_shutdown/checklist.tex
[presentation/2019-04-27_shutdown] equipment ids

--- 2017-08-01 presentations/2017-08-02_shutdown/checklist.tex
@@
 \title{Checklist}
-\date{August 2nd, 2017}
+\date{April 27th, 2019}
 \begin{document}
 
+\onecolumn
 \Person{Yichao}{
-  Equipments and power supplies are mostly located around the laser table on the library side.
-}
+  Equipments and power supplies are mostly located around the laser table facing the wall.
+}
+\begin{center}
+  {\LARGE\textbf{Equipment list}}
+\end{center}
+\begin{longtable}{|c|c|c|}
+  \hline
+  \textbf{ID}&\textbf{Equipment}&\textbf{Location}\\\hline
+  \multicolumn{3}{|c|}{\textbf{Laser table facing computer or the wall} west $\rightarrow$ south}\\\hline
+  1&Benchtop power for Cs MOT beat lock&Lv1 above 1.0 Cs MOT\\\hline
+  2&PLL for Cs MOT&Below Cs MOT\\\hline
+  3&Home power (+-15,5)&Lv2 above Cs MOT\\\hline
+  4&Valan&1.5 amplifier stack Lv1 above 1.0 Cs MOT\\\hline
+  5&Till driver v2 for 1.5 Na Raman&Lv1 above 1.5 Na Raman\\\hline
+  6&Temp servo for 1.5 Na Raman seed&Lv1 above 1.5 Na Raman\\\hline
+  7&Temp servo for 1.5 Na Raman doubler&Lv1 above 1.5 Na Raman\\\hline
+  8&PLL for Cs Raman&Next to 1.0 Cs Raman\\\hline
+  9&New Focus driver for Cs Raman&Lv1 above 1.0 Cs Raman\\\hline
+  10&Benchtop power (x3)&Lv2 above 1.0 Cs MOT\\\hline
+  11&Home power (24V) x2&Lv2 above 1.0 Cs Raman\\\hline
+  12&Benchtop power&Lv1 next to New Focus driver\\\hline
+  13&Shutter driver&Lv1 above 1.0 Cs Raman\\\hline
+  14&New Focus lock box for 1.0 Cs Raman&Lv1 above 1.0 Cs Raman\\\hline
+  15&Thorlabs temp servo for 1.0 Na Raman doubler&Lv1 above 1.0 Na seed\\\hline
+  16&Timebase drivers for 1.0 Na Raman and Na D2&Lv1 above Thorlabs temp servo\\\hline
+  17&Benchtop power for 1.0 Cs Raman&Lv2 above New Focus lock box\\\hline
+  18&High voltage power&Lv2 above timebase drivers\\\hline
+  19&Home lock box for Na D2&Lv1 above 1.0 Na seed\\\hline
+  20&MPB Raman laser&Lv1 above 1.0 Na MOT\\\hline
+  21&Oscilloscope for Na D2 lock&Lv1 above MPB Raman laser\\\hline
+  22&Benchtop power for 1.0 Na Raman seed&Lv2 above oscilloscope\\\hline
+\end{longtable}
+\twocolumn
+
 \subsection{Equipments}
@@
 }
-\Person{Jon}{
-  Equipments and power supplies are mostly located around the machine table facing the laser table
-  or the computer area.
-}
+
+\onecolumn
+\Person{Kenneth}{
+  Equipments and power supplies are mostly located between the machine table and the laser table.
+}
+\begin{center}
+  {\LARGE\textbf{Equipment list}}
+\end{center}
+\begin{longtable}{|c|c|c|}
+  \hline
+  \textbf{ID}&\textbf{Equipment}&\textbf{Location}\\\hline
+  \multicolumn{3}{|c|}{\textbf{Laser table side facing machine table} north $\rightarrow$ east}\\\hline
+  1&671 EOM stack&Floor\\\hline
+  2&1550 Amp&Floor\\\hline
+  3&Radio computer&Lv2\\\hline
+  4&Benchtop power&Lv2 next to radio computer\\\hline
+  5&High voltage power&Lv2 next to benchtop power\\\hline
+  6&Variac for Na cell&Lv1 above 1.0 Na MOT\\\hline
+  7&Shutter driver&Lv1 next to variac\\\hline
+  8&Home lock box for 1.0 Na D1&Lv1 next to shutter driver\\\hline
+  9&1038 Amp&Floor\\\hline
+  10&1038 Timebase laser&Table\\\hline
+  11&FPGA box for 1.0&Lv2\\\hline
+  12&Thorlabs temp servo for Na D1 doubler&Lv1 above Na D1\\\hline
+  13&Thorlabs temp servo for Na D1 seed&Lv1 above Na D1\\\hline
+  14&Thorlabs current for Na D1 seed&Lv1 above Na D1\\\hline
+  15&Benchtop power&Lv2 above Thorlabs controllers for Na D1 seed\\\hline
+  16&Home power (24)&Lv2 next to benchtop power\\\hline
+  17&Benchtop power x2&Lv2 next to Home power (24)\\\hline
+  18&Till driver v2 for 976&Lv1 above Na D1 doubler\\\hline
+  19&Thorlabs temp servo for Cs tweezer&Lv1 above Timebase 1038 beam\\\hline
+  20&Thorlabs current (2A) (off)&Lv1 above Thorlabs temp servo\\\hline
+  21&Till driver v2 for 671&Lv1 above Thorlabs current\\\hline
+  22&Home temp servo x2&Lv1 above Timebase 1038 control box\\\hline
+  23&Oscilloscope&Lv1\\\hline
+  \multicolumn{3}{|c|}{\textbf{Machine table side facing laser table} south}\\\hline
+  24&Thorlabs current for 1.5 Cs MOT&Lv1 above 1.5 Cs\\\hline
+  25&Till driver v2 for 1.5 Cs RP&Lv1 above 1.5 Cs\\\hline
+  26&Home temp servo (x2) for 1.5 Cs MOT/RP&Lv1 above 1.5 Cs\\\hline
+  27&Oscilloscope for 1.5 Cs&Lv1 above 1.5 Cs\\\hline
+  28&Home lock box for 1.5 Cs&Lv1 above 1.5 Cs\\\hline
+  29&Novatec for 1.5 Cs lock&Lv1 above 1.5 Cs\\\hline
+  30&Benchtop power&Lv2 1.5 Cs MOT/RP current\\\hline
+  31&Home power (24) x2&Lv2 next to benchtop power\\\hline
+  32&Benchtop power&Lv2 on two home power (24)\\\hline
+  33&Home power (+-15,5)&Lv2 middle\\\hline
+  34&Benchtop power (x2) for uWave Amp&Lv2 next to home power (+-15,5)\\\hline
+  35&Benchtop power (x2)&Lv1 above 1.5 Na\\\hline
+  36&High voltage power&Lv1 next to 2 benchtop power\\\hline
+  37&Function generator for 1.0 MOT piezo&Lv1\\\hline
+  38&Temperature and pump controllers for cavity&Lv1 next to function generator\\\hline
+  39&Water chiller for uWave breadboard&Floor\\\hline
+  40&SAES pump&Lv1 above 1.0 chamber\\\hline
+  41&Benchtop power x2&Lv2 next to coil servo\\\hline
+\end{longtable}
+\twocolumn
 \subsection{Equipments}
@@
 }
-\Person{Lee}{
-  Equipments and power supplies are mostly located around the laser table
-  on the computer area side.
-}
-\subsection{Equipments}
-\DevDef{PLL for 1.0 Cs MOT}{
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug all signals (zip tie together)
-  \item\OffBox Unplug 15V and 5V powers (zip tie together)
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plugin 15V and 5V powers
-  \item\OnBox Plugin all signals
-  \item\OnBox Apply settings according to note on Generic tab, Equipment Settings.
-  \end{itemize}
-}
-\DevDef{PLL for 1.0 Cs Raman}{
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug all signals (zip tie together)
-  \item\OffBox Unplug 15V and 5V powers (zip tie together)
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plugin 15V and 5V powers
-  \item\OnBox Plugin all signals
-  \item\OnBox Apply settings according to note on Generic tab, Equipment Settings.
-  \end{itemize}
-}
-\DevDef{Homebuilt temperature servo for Cs 1.0 MOT}{
-  \textbf{1st level above Cs tweezer/MOT lasers}\\
-  Switch off/on the front switch
-}
-\DevDef{1st version Till's current controller for Cs MOT}{
-  \textbf{1st level above Cs tweezer/MOT lasers}\\
-  Record current value:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Current&\hphantom{\hspace{3.5cm}}\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug power (zip tie to controller)
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug in power
-  \item\OnBox Turn on
-  \end{itemize}
-}
-\DevDef{Cs 1.0 MOT lock box}{
-  \textbf{1st level above Cs MOT lasers}
-  \begin{itemize}
-  \item\OffBox Make sure the laser is unlocked.
-  \end{itemize}
-}
-\DevDef{Novatech function generator}{
-  \textbf{1st level above Cs MOT lasers}
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Save settings
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Restore settings
-  \end{itemize}
-}
-\DevDef{New Focus Cs Raman lasers drivers (2x)}{
-  \textbf{1st level above Cs Raman lasers}\\
-  Record Temperature, Current, Piezo voltage\\
-  Temperature is accessible in the menu under system status\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    F3 Current&\hphantom{\hspace{3.5cm}}\\\hline
-    F3 Piezo Voltage&\\\hline
-    F3 Temperature&\\\hline
-    F4 Current&\\\hline
-    F4 Piezo Voltage&\\\hline
-    F4 Temperature&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug power
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug in power
-  \item\OnBox (Turn on)
-  \end{itemize}
-}
-\DevDef{SRS shutter driver for Cs}{
-  \textbf{1st level above Cs Raman lasers}\\
-  Switch off/on with the switch on the back.
-}
-\DevDef{New Focus lock box for Cs Raman}{
-  \textbf{1st level above Cs Raman lasers}\\
-  Unplug power.
-}
-\DevDef{Homebuilt temperature servo for Cs tweezer}{
-  \textbf{1st level above Cs tweezer}\\
-  Switch off/on the front switch
-}
-\DevDef{2nd version Till's current controller for Cs Tweezer}{
-  \textbf{1st level above Cs tweezer}\\
-  Record current value:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Current&\hphantom{\hspace{3.5cm}}\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug power (zip tie to controller)
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug in power
-  \item\OnBox Turn on
-  \end{itemize}
-}
-\DevDef{Thorlabs current controller}{
-  \textbf{1st level below Cs tweezer driver}\\
-  Unused\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug power
-  \end{itemize}
-}
-\DevDef{Thorlabs temperature controller for Cs tweezer}{
-  \textbf{1st level above Cs tweezer}\\
-  Record temperature settings\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Setpoint&\hphantom{\hspace{3.5cm}}\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug power
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug in power
-  \item\OnBox Check temperature setting
-  \item\OnBox Turn on
-  \end{itemize}
-}
-\DevDef{Intensity servo for Cs}{
-  \textbf{1st level above Cs tweezer}\\
-  Unplug power
-}
-\subsection{Power supplies}
-\DevDef{Benchtop power supply}{
-  \textbf{1st level above Cs tweezer/MOT lasers}\\
-  Record voltage/current values:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-    Left Current&\\\hline
-    Right Voltage&\\\hline
-    Right Current&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug loads
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Turn off the power supply
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Homebuilt $\pm15,5$V power supply}{
-  \textbf{2nd level above Cs tweezer/MOT lasers}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug load
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Switch off on the back
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Switch on
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Benchtop power supply}{
-  \textbf{1st level next to Cs Raman driver}\\
-  Record voltage/current values:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-    Current&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug loads
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Turn off the power supply
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Homebuilt $24$V power supply}{
-  \textbf{2nd level above Cs Raman lasers}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug load
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Switch off on the back
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Switch on
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Benchtop power supply for Cs Raman locking}{
-  \textbf{2nd level above Cs Raman lockbox}\\
-  Record voltage/current values:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-    Current&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug loads
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Turn off the power supply
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\subsection{Computers}
-\DevDef{Tweezer 1 computer}{
-  \textbf{Check following devices}
-  \begin{itemize}
-  \item\OnBox Thorlabs cameras
-  \item\OnBox Na Raman amplifier
-  \end{itemize}
-}
+
+\onecolumn
 \Person{Jessie}{
-  Equipments and power supplies are mostly located around the machine table facing the 1.5 table.
-}
+  Equipments and power supplies are mostly located between the machine table and the 1.5 table.
+}
+\begin{center}
+  {\LARGE\textbf{Equipment list}}
+\end{center}
+\begin{longtable}{|c|c|c|}
+  \hline
+  \textbf{ID}&\textbf{Equipment}&\textbf{Location}\\\hline
+  \multicolumn{3}{|c|}{\textbf{Machine table Facing the wall} north}\\\hline
+  1&Benchtop power&Lv2\\\hline
+  2&Home power (24)&Lv2 above 1.0 tweezer breadboard\\\hline
+  3&Home power (+-15,5)&Lv2 above home power (24)\\\hline
+  4&Benchtop power x9&Lv2 next to home power (24) and (+-15,5)\\\hline
+  5&Current servo for compensation coil&Lv1 below home power (24)\\\hline
+  6&Kenneth servo for 1.0 Cs tweezer&Lv1\\\hline
+  7&High voltage Amp for 630 lock&Lv1\\\hline
+  8&Vincent servo x2 for STIRAP lasers&Lv1\\\hline
+  9&Greiner servo for 1.0 Na tweezer&Lv1 above Vincent servos\\\hline
+  10&Rack for STRAP&Lv1 next to Vincent servos\\\hline
+  11&Till driver v2 x2 for STIRAP lasers&Lv1 above rack for 1.5\\\hline
+  12&Home temp servo x3 for STIRAP&Lv2 next to 9x benchtop power\\\hline
+  13&FPGA box for 1.5&Lv2\\\hline
+  14&Home power (+-15,5)&Lv2 next to FPGA box\\\hline
+  15&Benchtop power x2&Lv2 on home power (+-15,5)\\\hline
+  16&Benchtop power&Lv2 next to home power (+-15,5)\\\hline
+  17&Benchtop power&Floor rack Lv1\\\hline
+  18&Till driver v2 x2 for 1.5 Cs Raman&Floor rack Lv2\\\hline
+  19&Kenneth servo for 1.5 Cs Raman phase lock&Floor rack Lv2 above Till drivers\\\hline
+  20&Benchtop power&Floor rack Lv2 next to Till drivers\\\hline
+  21&Home temp servo x2 for 1.5 Cs Raman&Floor rack Lv2\\\hline
+  22&Piezo driver for 1.5 Cs Raman&Floor rack Lv2 above home temp servos\\\hline
+  23&Delay generator for 1.5 Na&Lv1 below 1.5 output panel\\\hline
+  24&Till driver v2 for 1.0 Innolume&Lv1 next to delay generator\\\hline
+  25&Kenneth servo for 1.5 tweezers&Lv1\\\hline
+  26&Home temp servo for 1.0 Innolume&Lv1\\\hline
+  27&Shutter driver&Lv1 on M2 controller\\\hline
+  28&TiSapph&Floor\\\hline
+  29&Function generator for 1.0 Na switching&Lv1 above TiSapph\\\hline
+  30&Keithley power for 1.0 Innolume&Lv2 above TiSapph\\\hline
+  31&Till driver v2 for 1.0 Cs MOT&Lv2 above 1.5 Cs MOT\\\hline
+  32&Home temp servo for 1.0 Cs MOT&Lv2 on Till driver v2\\\hline
+  33&Benchtop power&Lv2 facing computer\\\hline
+  34&High voltage power&Above Lv2 on power outlet\\\hline
+  \multicolumn{3}{|c|}{1.5 Rack}\\\hline
+  35&Home power (24)&Bottom level\\\hline
+  36&SEAS pump controller&Middle left\\\hline
+  37&Benchtop power&Middle next to pump controller\\\hline
+  38&Oscilloscope for 1.5 monitor&Above pump controller\\\hline
+  39&Benchtop power for 1.5 coil&Above oscilloscope\\\hline
+  40&High voltage Amp for 1.5 MOT piezo&Top level\\\hline
+  41&Function generator for 1.5 MOT piezo&Top level on high voltage Amp\\\hline
+  \multicolumn{3}{|c|}{Below 1.5 table}\\\hline
+  42&Benchtop power x3&Near outer edge\\\hline
+  43&IGBT stack&Floor\\\hline
+  44&LED driver&Near inner edge\\\hline
+  45&AWG computer&Floor\\\hline
+  \multicolumn{3}{|c|}{Above 1.5 table}\\\hline
+  46&Benchtop power&Lv1\\\hline
+  47&Benchtop power&Lv2\\\hline
+  48&Radio computer&Lv2\\\hline
+\end{longtable}
+\twocolumn
+
 \subsection{Equipments}
@@
 }
-\Person{Frederic}{
-  Equipments and power supplies are mostly on the 1.5 rack.
-}
-\subsection{Equipments}
-\DevDef{Andor Camera for 1.5}{
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Switch off
-  \item\OffBox Switch off chiller
-  \item\OffBox Unplug camera power (zip tie to camera)
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug in camera power
-  \item\OnBox Switch on chiller
-  \item\OnBox Switch on
-  \end{itemize}
-}
-\DevDef{1.5 Feshbach coils}{
-  \textbf{Before power shutdown}
-  \begin{itemize}
-  \item\OffBox Wrap exposed part in napkins to prevent condensations
-  \end{itemize}
-}
-\DevDef{1.5 IGBT}{
-  \textbf{Before power shutdown}
-  \begin{itemize}
-  \item\OffBox Wrap exposed part in napkins to prevent condensations
-  \end{itemize}
-}
-\DevDef{Cooling water}{
-  Valves to close/reopen:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    \OnBox\OffBox&\hphantom{\hspace{5cm}}\\\hline
-    \OnBox\OffBox&\hphantom{\hspace{5cm}}\\\hline
-    \OnBox\OffBox&\hphantom{\hspace{5cm}}\\\hline
-    \OnBox\OffBox&\hphantom{\hspace{5cm}}\\\hline
-    \OnBox\OffBox&\hphantom{\hspace{5cm}}\\\hline
-    \OnBox\OffBox&\hphantom{\hspace{5cm}}\\\hline
-    \OnBox\OffBox&\hphantom{\hspace{5cm}}\\\hline
-    \OnBox\OffBox&\hphantom{\hspace{5cm}}\\\hline
-    \OnBox\OffBox&\hphantom{\hspace{5cm}}\\\hline
-    \OnBox\OffBox&\hphantom{\hspace{5cm}}\\\hline
-    \OnBox\OffBox&\hphantom{\hspace{5cm}}\\\hline
-    \OnBox\OffBox&\hphantom{\hspace{5cm}}\\\hline
-  \end{tabular}\\
-}
-\DevDef{HV amplifiers for 1.5 piezo mirrors}{
-  \textbf{Top level of 1.5 rack}\\
-  \textbf{Turn on-off together with the function generator below
-    and the high voltage power supply above the 1.0 machine table}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off the function generator
-  \item\OffBox Unplug function generator output (zip tie and label)
-  \item\OffBox Unplug HV power supply from the wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plugin HV power supply to the wall
-  \item\OnBox Plugin function generator output
-  \item\OnBox Turn on the function generator
-  \end{itemize}
-}
-\DevDef{Pump}{
-  \textbf{Bottom level 1.5 Rack}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug from walls
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into wall
-  \item\OnBox Turn on (should be enough)
-  \end{itemize}
-}
-\subsection{Power supplies}
-\DevDef{Benchtop power supply}{
-  \textbf{2nd level (from the top) 1.5 Rack. Next to coil servo}\\
-  Record voltage/current values:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-    Left Current&\\\hline
-    Right Voltage&\\\hline
-    Right Current&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug loads
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Turn off the power supply
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Benchtop power supply}{
-  \textbf{Bottom level 1.5 Rack. Next to pump}\\
-  Record voltage/current values:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-    Current&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug loads
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Turn off the power supply
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\subsection{Computers}
-\DevDef{Tweezer 4 computer}{
-  \textbf{Check following devices}
-  \begin{itemize}
-  \item\OnBox Andor camera
-  \item\OnBox Thorlabs camera
-  \end{itemize}
-}
 

### 2019-04-26 presentations/2019-04-27_shutdown/checklist.tex
[presentation/2019-04-27_shutdown] WIP: checklists

--- 2017-08-01 presentations/2017-08-02_shutdown/checklist.tex
@@
 \usepackage{hyperref}
+\usepackage{longtable}
+
 \usetikzlibrary{
@@
 \title{Checklist}
-\date{August 2nd, 2017}
+\date{April 27th, 2019}
 \begin{document}
 
+\onecolumn
 \Person{Yichao}{
-  Equipments and power supplies are mostly located around the laser table on the library side.\\
-  Check Lee's part after everything are off.
-}
+  Equipments and power supplies are mostly located around the laser table facing the wall.
+}
+\begin{center}
+  {\LARGE\textbf{Equipment list}}
+\end{center}
+\begin{longtable}{|c|c|c|}
+  \hline
+  \textbf{ID}&\textbf{Equipment}&\textbf{Location}\\\hline
+  \multicolumn{3}{|c|}{\textbf{Laser table facing computer or the wall} west $\rightarrow$ south}\\\hline
+  1&Benchtop power 2chn for Cs MOT beat lock&Lv1 above 1.0 Cs MOT\\\hline
+  2&PLL for Cs MOT&Below Cs MOT\\\hline
+  3&Home power ($\pm$15,5)&Lv2 above Cs MOT\\\hline
+  4&Valan&1.5 amplifier stack Lv1 above 1.0 Cs MOT\\\hline
+  5&Till driver v2 for 1.5 Na Raman&Lv1 above 1.5 Na Raman\\\hline
+  6&Temp servo for 1.5 Na Raman seed&Lv1 above 1.5 Na Raman\\\hline
+  7&Temp servo for 1.5 Na Raman doubler&Lv1 above 1.5 Na Raman\\\hline
+  8&PLL for Cs Raman&Next to 1.0 Cs Raman\\\hline
+  9&New Focus driver x2 for Cs Raman&Lv1 above 1.0 Cs Raman\\\hline
+  10&Benchtop power (x3)&Lv2 above 1.0 Cs MOT\\\hline
+  11&Home power (24V) x2&Lv2 above 1.0 Cs Raman\\\hline
+  12&Benchtop power&Lv1 next to New Focus drivers\\\hline
+  13&Shutter driver&Lv1 above 1.0 Cs Raman\\\hline
+  14&New Focus lock box for 1.0 Cs Raman&Lv1 above 1.0 Cs Raman\\\hline
+  15&Thorlabs temp servo for 1.0 Na Raman doubler&Lv1 above 1.0 Na seed\\\hline
+  16&Timebase drivers for 1.0 Na Raman and Na D2&Lv1 above Thorlabs temp servo\\\hline
+  17&Benchtop power for 1.0 Cs Raman&Lv2 above New Focus lock box\\\hline
+  18&High voltage power&Lv2 above timebase drivers\\\hline
+  19&Home lock box for Na D2&Lv1 above 1.0 Na seed\\\hline
+  20&MPB Raman laser&Lv1 above 1.0 Na MOT\\\hline
+  21&Oscilloscope for Na D2 lock&Lv1 above MPB Raman laser\\\hline
+  22&Benchtop power for 1.0 Na Raman seed&Lv2 above oscilloscope\\\hline
+\end{longtable}
+\twocolumn
+
 \subsection{Equipments}
-\DevDef{Thorlabs temperature controller for Na Raman doubler}{
-  \textbf{1st level above Na Raman and D2 seed lasers}\\
+\DevDef{PLL for Cs MOT [2]}{
+  \textbf{Below Cs MOT}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug all signals (zip tie together)
+  \item\OffBox Unplug 15V and 5V powers (zip tie together)
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plugin 15V and 5V powers
+  \item\OnBox Plugin all signals
+  \item\OnBox Apply settings
+  \end{itemize}
+}
+\DevDef{Valan [4]}{
+  \textbf{1.5 amplifier stack Lv1 above 1.0 Cs MOT}\\
+  Check with 1.5 to record setting\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Frequency&\hphantom{\hspace{3.5cm}}\\\hline
+    Amplitude&\hphantom{\hspace{3.5cm}}\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Restore settings
+  \end{itemize}
+}
+\DevDef{Till driver v2 for 1.5 Na Raman [5]}{
+  \textbf{Lv1 above 1.5 Na Raman}\\
+  Record current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Current&\hphantom{\hspace{3.5cm}}\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off
+  \item\OffBox Unplug power (zip tie to controller)
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug in power
+  \item\OnBox Turn on
+  \end{itemize}
+}
+\DevDef{Temp servo for 1.5 Na Raman seed [6]}{
+  \textbf{Lv1 above 1.5 Na Raman}\\
+  Check plugged into UPS.
+}
+\DevDef{Temp servo for 1.5 Na Raman doubler [7]}{
+  \textbf{Lv1 above 1.5 Na Raman}\\
+  Check plugged into UPS.
+}
+\DevDef{PLL for Cs Raman [8]}{
+  \textbf{Next to 1.0 Cs Raman}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug all signals (zip tie together)
+  \item\OffBox Unplug 15V and 5V powers (zip tie together)
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plugin 15V and 5V powers
+  \item\OnBox Plugin all signals
+  \item\OnBox Apply settings
+  \end{itemize}
+}
+\DevDef{New Focus driver x2 for Cs Raman [9]}{
+  \textbf{Lv1 above 1.0 Cs Raman}\\
+  Record Temperature, Current, Piezo voltage\\
+  Temperature is accessible in the menu under system status\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    F3 Current&\hphantom{\hspace{3.5cm}}\\\hline
+    F3 Piezo Voltage&\\\hline
+    F3 Temperature&\\\hline
+    F4 Current&\\\hline
+    F4 Piezo Voltage&\\\hline
+    F4 Temperature&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off output.
+  \item\OffBox Check plugged into UPS.
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox (Turn on)
+  \end{itemize}
+}
+\DevDef{Shutter driver [13]}{
+  \textbf{Lv1 above 1.0 Cs Raman}\\
+  Switch off/on with the switch on the back.
+}
+\DevDef{New Focus lock box for 1.0 Cs Raman [14]}{
+  \textbf{Lv1 above 1.0 Cs Raman}\\
+  Unplug power.
+}
+\DevDef{Thorlabs temp servo for 1.0 Na Raman doubler [15]}{
+  \textbf{Lv1 above 1.0 Na seed}\\
   Record temperature settings\\
@@
 
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug power
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug in power
-  \item\OnBox Check temperature setting
-  \item\OnBox Turn on
-  \end{itemize}
-}
-\DevDef{Timebase driver for Na Raman and Na D2 (x2)}{
-  \textbf{1st level above Na Raman and D2 seed lasers}\\
+  Check plugged into UPS.
+}
+
+\DevDef{Timebase drivers for 1.0 Na Raman and Na D2 [16]}{
+  \textbf{Lv1 above Thorlabs temp servo}\\
   Record current and T1 settings\\
@@
     Raman T1&\\\hline
-    MOT Current&\hphantom{\hspace{3.5cm}}\\\hline
-    MOT T1&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug power
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug in power
+    D2 Current&\hphantom{\hspace{3.5cm}}\\\hline
+    D2 T1&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off output.
+  \item\OffBox Check plugged into UPS.
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
   \item\OnBox Turn on
-  \item\OnBox Set current/temperature.
-  \item\OnBox Enable T1 survo
-  \item\OnBox Turn on current
-  \end{itemize}
-}
-\DevDef{Oscilloscope for Na D2 lock}{
-  \textbf{1st level above Na Raman amplifier}
-  \begin{itemize}
-  \item\OffBox Unplug from wall
-  \end{itemize}
-}
-\DevDef{MPB Raman amplifier}{
-  \textbf{1st level above Na MOT beam path}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Power off
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into wall
-  \item\OnBox Power on
-  \end{itemize}
-}
-\DevDef{Homebuilt lockbox for Na D2}{
-  \textbf{1st level above Na seed}\\
+  \end{itemize}
+}
+
+\DevDef{Home lock box for Na D2 [19]}{
+  \textbf{Lv1 above 1.0 Na seed}\\
   \textbf{Turn on-off together with the adjustable high voltage power supply above}\\
@@
 }
-\DevDef{SRS shutter driver for Na}{
-  \textbf{1st level above Na D2 beam path, below Variac}\\
-  Switch off/on with the switch on the back.
-}
-\DevDef{Variac for Na cell}{
-  \textbf{Above Na D2 beam path}\\
+
+\DevDef{MPB Raman laser [20]}{
+  \textbf{Lv1 above 1.0 Na MOT}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Power off
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into wall
+  \item\OnBox Power on
+  \end{itemize}
+}
+\DevDef{Oscilloscope for Na D2 lock [21]}{
+  \textbf{Lv1 above MPB Raman laser}\\
+
+  \begin{itemize}
+  \item\OffBox Unplug from wall
+  \end{itemize}
+}
+\subsection{Power supplies}
+\DevDef{Benchtop power 2chn for Cs MOT beat lock [1]}{
+  \textbf{Lv1 above 1.0 Cs MOT}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    Left Current&\\\hline
+    Right Voltage&\\\hline
+    Right Current&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug loads
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Turn off the power supply
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+
+\DevDef{Home power ($\pm$15,5) [3]}{
+  \textbf{Lv2 above Cs MOT}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug load
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Switch off on the back
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Switch on
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+
+\DevDef{Benchtop power (x3) [10]}{
+  \textbf{Lv2 above 1.0 Cs MOT}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    No. 1 Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    No. 1 Current&\\\hline
+    No. 2 Voltage&\\\hline
+    No. 2 Current&\\\hline
+    No. 3 Voltage&\\\hline
+    No. 3 Current&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug loads
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Turn off the power supply
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+
+\DevDef{Home power (24V) x2 [11]}{
+  \textbf{Lv2 above 1.0 Cs Raman}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug load
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Switch off on the back
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Switch on
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+
+\DevDef{Benchtop power [12]}{
+  \textbf{Lv1 next to New Focus driver}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    Current&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug loads
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Turn off the power supply
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+
+\DevDef{Benchtop power for 1.0 Cs Raman [17]}{
+  \textbf{Lv2 above New Focus lock box}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    Current&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug loads
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Turn off the power supply
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+
+\DevDef{High voltage power [18]}{
+  \textbf{Lv2 above timebase drivers}\\
+  Follow home lock box for Na D2 [19].
+}
+
+\DevDef{Benchtop power for 1.0 Na Raman seed [22]}{
+  \textbf{Lv2 above oscilloscope}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    Current&\\\hline
+  \end{tabular}\\
+
+  Check plugged into UPS.
+}
+\subsection{Computers}
+\DevDef{Control computers}{
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Check update.
+  \item\OffBox Turn off.
+  \item\OffBox Unplug from UPS.
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Get UPS back
+  \item\OnBox Turn on.
+  \end{itemize}
+}
+\DevDef{Computer UPS}{
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Move to the lab.
+  \item\OffBox Plug into backup power.
+  \item\OffBox Plug in pump/temp controllers.
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug load back into the wall (or where they belongs).
+  \item\OnBox Move back.
+  \item\OnBox Plug computers back in.
+  \end{itemize}
+}
+
+\onecolumn
+\Person{Kenneth}{
+  Equipments and power supplies are mostly located between the machine table and the laser table.
+}
+\begin{center}
+  {\LARGE\textbf{Equipment list}}
+\end{center}
+\begin{longtable}{|c|c|c|}
+  \hline
+  \textbf{ID}&\textbf{Equipment}&\textbf{Location}\\\hline
+  \multicolumn{3}{|c|}{\textbf{Laser table side facing machine table} north $\rightarrow$ east}\\\hline
+  1&671 EOM stack&Floor\\\hline
+  2&1550 Amp&Floor\\\hline
+  3&Radio computer&Lv2\\\hline
+  4&Benchtop power 2chn&Lv2 next to radio computer\\\hline
+  5&High voltage power&Lv2 next to benchtop power\\\hline
+  6&Variac for Na cell&Lv1 above 1.0 Na MOT\\\hline
+  7&Shutter driver&Lv1 next to variac\\\hline
+  8&Home lock box for 1.0 Na D1&Lv1 next to shutter driver\\\hline
+  9&1038 Amp&Floor\\\hline
+  10&1038 Timebase laser&Table\\\hline
+  11&FPGA box for 1.0&Lv2\\\hline
+  12&Thorlabs temp servo for Na D1 doubler&Lv1 above Na D1\\\hline
+  13&Thorlabs temp servo for Na D1 seed&Lv1 above Na D1\\\hline
+  14&Thorlabs current for Na D1 seed&Lv1 above Na D1\\\hline
+  15&Benchtop power 2chn&Lv2 above Thorlabs controllers for Na D1 seed\\\hline
+  16&Home power (24)&Lv2 next to benchtop power\\\hline
+  17&Benchtop power x2 (2chn x1)&Lv2 next to Home power (24)\\\hline
+  18&Till driver v2 for 976&Lv1 above Na D1 doubler\\\hline
+  19&Thorlabs temp servo for Cs tweezer&Lv1 above Timebase 1038 beam\\\hline
+  20&Thorlabs current (2A) (off)&Lv1 above Thorlabs temp servo\\\hline
+  21&Till driver v2 for 671&Lv1 above Thorlabs current\\\hline
+  22&Temp servo x2&Lv1 above Timebase 1038 control box\\\hline
+  23&Oscilloscope&Lv1\\\hline
+  \multicolumn{3}{|c|}{\textbf{Machine table side facing laser table} south}\\\hline
+  24&Thorlabs current for 1.5 Cs MOT&Lv1 above 1.5 Cs\\\hline
+  25&Till driver v2 for 1.5 Cs RP&Lv1 above 1.5 Cs\\\hline
+  26&Temp servo (x2) for 1.5 Cs MOT/RP&Lv1 above 1.5 Cs\\\hline
+  27&Oscilloscope for 1.5 Cs&Lv1 above 1.5 Cs\\\hline
+  28&Home lock box for 1.5 Cs&Lv1 above 1.5 Cs\\\hline
+  29&Novatec for 1.5 Cs lock&Lv1 above 1.5 Cs\\\hline
+  30&Benchtop power 2chn&Lv2 1.5 Cs MOT/RP current\\\hline
+  31&Home power (24) x2&Lv2 next to benchtop power\\\hline
+  32&Benchtop power&Lv2 on two home power (24)\\\hline
+  33&Home power ($\pm$15,5)&Lv2 middle\\\hline
+  34&Benchtop power (x2) for uWave Amp&Lv2 next to home power ($\pm$15,5)\\\hline
+  35&Benchtop power (x2)&Lv1 above 1.5 Na\\\hline
+  36&High voltage power&Lv1 next to 2 benchtop power\\\hline
+  37&Function generator for 1.0 MOT piezo&Lv1\\\hline
+  38&Temperature and pump controllers for cavity&Lv1 next to function generator\\\hline
+  39&Water chiller for uWave breadboard&Floor\\\hline
+  40&SAES pump&Lv1 above 1.0 chamber\\\hline
+  41&Benchtop power x2 (2chn x1)&Lv2 next to coil servo\\\hline
+\end{longtable}
+\twocolumn
+\subsection{Equipments}
+\DevDef{671 EOM stack [1]}{
+  \textbf{Floor}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    No. 1 Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    No. 1 Left Current&\\\hline
+    No. 1 Right Voltage&\\\hline
+    No. 1 Right Current&\\\hline
+    Thorlabs Current&\\\hline
+    No. 2 Voltage&\\\hline
+    No. 2 Current&\\\hline
+    &\\\hline
+    &\\\hline
+    &\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug loads
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Turn off the power supply
+  \item\OffBox Unplug from wall
+  \item\OffBox
+  \item\OffBox
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
+  \item\OnBox Plug the load back in
+  \item\OnBox
+  \item\OnBox
+  \end{itemize}
+}
+
+\DevDef{1550 Amp [2]}{
+  \textbf{Floor}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox
+  \item\OffBox
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox
+  \item\OnBox
+  \end{itemize}
+}
+
+\DevDef{Variac for Na cell [6]}{
+  \textbf{Lv1 above 1.0 Na MOT}\\
   Record temperature and voltage settings\\
@@
 
+  Check if we can use the backup power. (Through the UPS)
   \textbf{Turn off check list}
@@
 }
-\DevDef{Homebuilt lockbox for Na D1}{
-  \textbf{1st level above Na D2 beam path}\\
+
+\DevDef{Shutter driver [7]}{
+  \textbf{Lv1 next to variac}\\
+  Switch off/on with the switch on the back.
+}
+
+\DevDef{Home lock box for 1.0 Na D1 [8]}{
+  \textbf{Lv1 next to shutter driver}\\
   \textbf{Turn on-off together with the fixed high voltage power supply above}\\
@@
 }
-\DevDef{Thorlabs temperature controller for Na D1 doubler}{
-  \textbf{1st level above Na D1}\\
+
+\DevDef{1038 Amp [9]}{
+  \textbf{Floor}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox
+  \item\OffBox
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox
+  \item\OnBox
+  \end{itemize}
+}
+
+\DevDef{1038 Timebase laser [10]}{
+  \textbf{Table}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox
+  \item\OffBox
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox
+  \item\OnBox
+  \end{itemize}
+}
+
+\DevDef{Thorlabs temp servo for Na D1 doubler [12]}{
+  \textbf{Lv1 above Na D1}\\
   Record temperature settings\\
@@
 
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug power
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug in power
-  \item\OnBox Check temperature setting
-  \item\OnBox Turn on
-  \end{itemize}
-}
-\DevDef{Thorlabs temperature controller for Na D1 seed}{
-  \textbf{1st level above Na D1 seed}\\
+  Check plugged into UPS.
+}
+
+\DevDef{Thorlabs temp servo for Na D1 seed [13]}{
+  \textbf{Lv1 above Na D1}\\
   Record temperature settings\\
@@
 
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug power
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug in power
-  \item\OnBox Check temperature setting
-  \item\OnBox Turn on
-  \end{itemize}
-}
-\DevDef{Thorlabs current controller for Na D1 seed}{
-  \textbf{1st level above Na D1 seed}\\
+  Check plugged into UPS.
+}
+
+\DevDef{Thorlabs current for Na D1 seed [14]}{
+  \textbf{Lv1 above Na D1}\\
   Record current settings\\
@@
 }
+
+\DevDef{Till driver v2 for 976 [18]}{
+  \textbf{Lv1 above Na D1 doubler}\\
+  Record current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Current&\hphantom{\hspace{3.5cm}}\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off
+  \item\OffBox Unplug power (zip tie to controller)
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug in power
+  \item\OnBox Turn on
+  \end{itemize}
+}
+
+\DevDef{Thorlabs temp servo for Cs tweezer [19]}{
+  \textbf{Lv1 above Timebase 1038 beam}\\
+  Record temperature settings\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Setpoint&\hphantom{\hspace{3.5cm}}\\\hline
+  \end{tabular}\\
+
+  Check plugged into UPS.
+}
+
+\DevDef{Till driver v2 for 671 [21]}{
+  \textbf{Lv1 above Thorlabs current}\\
+  Record current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Current&\hphantom{\hspace{3.5cm}}\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off
+  \item\OffBox Unplug power (zip tie to controller)
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug in power
+  \item\OnBox Turn on
+  \end{itemize}
+}
+
+\DevDef{Temp servo x2 [22]}{
+  \textbf{Lv1 above Timebase 1038 control box}\\
+  Check plugged into UPS.
+}
+
+\DevDef{Oscilloscope [23]}{
+  \textbf{Lv1}\\
+
+  \begin{itemize}
+  \item\OffBox Unplug from wall
+  \end{itemize}
+}
+
+\DevDef{Thorlabs current for 1.5 Cs MOT [24]}{
+  \textbf{Lv1 above 1.5 Cs}\\
+  Record current settings\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Current&\hphantom{\hspace{3.5cm}}\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off
+  \item\OffBox Unplug power
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug in power
+  \item\OnBox Check current setting
+  \item\OnBox Turn on
+  \end{itemize}
+}
+
+\DevDef{Till driver v2 for 1.5 Cs RP [25]}{
+  \textbf{Lv1 above 1.5 Cs}\\
+  Record current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Current&\hphantom{\hspace{3.5cm}}\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off
+  \item\OffBox Unplug power (zip tie to controller)
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug in power
+  \item\OnBox Turn on
+  \end{itemize}
+}
+
+\DevDef{Temp servo (x2) for 1.5 Cs MOT/RP [26]}{
+  \textbf{Lv1 above 1.5 Cs}\\
+  Check plugged into UPS.
+}
+
+\DevDef{Oscilloscope for 1.5 Cs [27]}{
+  \textbf{Lv1 above 1.5 Cs}\\
+
+  \begin{itemize}
+  \item\OffBox Unplug from wall
+  \end{itemize}
+}
+
+\DevDef{Home lock box for 1.5 Cs [28]}{
+  \textbf{Lv1 above 1.5 Cs}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unlock
+  \item\OffBox Unplug 15V from lockbox (zip tie)
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug in 15V to lockbox
+  \end{itemize}
+}
+
+\DevDef{Novatec for 1.5 Cs lock [29]}{
+  \textbf{Lv1 above 1.5 Cs}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Save settings
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Restore settings
+  \end{itemize}
+}
+
+\DevDef{Function generator for 1.0 MOT piezo [37]}{
+  \textbf{Lv1}\\
+
+  \textbf{Turn on-off together with the HV amplifiers for 1.0 piezo mirrors above
+    and the high voltage power supply on the left}\\
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off the function generator
+  \item\OffBox Unplug function generator output (zip tie and label)
+  \item\OffBox Unplug HV power supply from the wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plugin HV power supply to the wall
+  \item\OnBox Plugin function generator output
+  \item\OnBox Turn on the function generator
+  \end{itemize}
+}
+
+\DevDef{Temperature and pump controllers for cavity [38]}{
+  \textbf{Lv1 next to function generator}\\
+
+  Check plugged into UPS.
+}
+
+\DevDef{Water chiller for uWave breadboard [39]}{
+  \textbf{Floor}\\
+}
+
+\DevDef{SAES pump [40]}{
+  \textbf{Lv1 above 1.0 chamber}\\
+
+  Check plugged into UPS.
+}
 \subsection{Power supplies}
-\DevDef{Benchtop power supply}{
-  \textbf{2nd level above Na Variac}\\
+\DevDef{Benchtop power 2chn [4]}{
+  \textbf{Lv2 next to radio computer}\\
   Record voltage/current values:\\
@@
 }
-\DevDef{Homebuilt $24$V power supply}{
-  \textbf{2nd level above Cs tweezer controllers}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug load
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Switch off on the back
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Switch on
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Benchtop power supply}{
-  \textbf{2nd level above Na D1 seed controllers}\\
+
+\DevDef{High voltage power [5]}{
+  \textbf{Lv2 next to benchtop power}\\
+  Follow home lock box for Na D2 [8].
+}
+
+\DevDef{Benchtop power 2chn [15]}{
+  \textbf{Lv2 above Thorlabs controllers for Na D1 seed}\\
   Record voltage/current values:\\
@@
 }
-\DevDef{Benchtop power supply}{
-  \textbf{2nd level above Cs tweezer, right of 24V power supply}\\
+
+\DevDef{Home power (24) [16]}{
+  \textbf{Lv2 next to benchtop power}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug load
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Switch off on the back
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Switch on
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+
+\DevDef{Benchtop power x2 (2chn x1) [17]}{
+  \textbf{Lv2 next to Home power (24)}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    No. 1 Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    No. 1 Current&\\\hline
+    No. 2 Left Voltage&\\\hline
+    No. 2 Left Current&\\\hline
+    No. 2 Right Voltage&\\\hline
+    No. 2 Right Current&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug loads
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Turn off the power supply
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+
+\DevDef{Benchtop power 2chn [30]}{
+  \textbf{Lv2 1.5 Cs MOT/RP current}\\
   Record voltage/current values:\\
@@
 }
-\DevDef{Benchtop power supply}{
-  \textbf{1st level above Cs tweezer}\\
+
+\DevDef{Home power (24) x2 [31]}{
+  \textbf{Lv2 next to benchtop power}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug load
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Switch off on the back
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Switch on
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+
+\DevDef{Benchtop power [32]}{
+  \textbf{Lv2 on two home power (24)}\\
   Record voltage/current values:\\
@@
     \hline
-    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-    Left Current&\\\hline
-    Right Voltage&\\\hline
-    Right Current&\\\hline
+    Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    Current&\\\hline
   \end{tabular}\\
@@
 }
-\DevDef{UPS}{
-  \textbf{2nd level above laser table}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
+
+\DevDef{Home power ($\pm$15,5) [33]}{
+  \textbf{Lv2 middle}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug load
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Switch off on the back
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Switch on
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+
+\DevDef{Benchtop power (x2) for uWave Amp [34]}{
+  \textbf{Lv2 next to home power ($\pm$15,5)}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    No. 1 Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    No. 1 Current&\\\hline
+    No. 2 Voltage&\\\hline
+    No. 2 Current&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug uWave input (tie).
+  \item\OffBox Turn low voltage one to (-)5V.
+  \item\OffBox Turn down higher voltage one to 0.
+  \item\OffBox Unplug load, label/tie.
+  \item\OffBox Switch off power supplies.
+  \item\OffBox Unplug from wall.
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall.
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}.
+  \item\OnBox Plug -5V.
+  \item\OnBox Plug higher voltage one.
+  \item\OnBox Turn higher voltage up to original value.
+  \item\OnBox Turn low voltage one down.
+  \item\OnBox Plug uWave back in.
+  \end{itemize}
+}
+
+\DevDef{Benchtop power (x2) [35]}{
+  \textbf{Lv1 above 1.5 Na}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    No. 1 Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    No. 1 Current&\\\hline
+    No. 2 Voltage&\\\hline
+    No. 2 Current&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug loads
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Turn off the power supply
   \item\OffBox Unplug from wall
@@
   \item\OnBox Plug into the wall
-  \item\OnBox Turn on
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
+  \item\OnBox Plug the load back in
+  \end{itemize}
+}
+
+\DevDef{High voltage power [36]}{
+  \textbf{Lv1 next to 2 benchtop power}
+}
+
+\DevDef{Benchtop power x2 (2chn x1) [41]}{
+  \textbf{Lv2 next to coil servo}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    No. 1 Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    No. 1 Left Current&\\\hline
+    No. 1 Right Voltage&\\\hline
+    No. 1 Right Current&\\\hline
+    No. 2 Voltage&\\\hline
+    No. 2 Current&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug loads
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Turn off the power supply
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
+  \item\OnBox Plug the load back in
   \end{itemize}
@@
 \subsection{Computers}
-\DevDef{Computer control box for 1.0}{
+\DevDef{Radio computer [3]}{
+  \textbf{Lv2}\\
+}
+
+\DevDef{FPGA box for 1.0 [11]}{
+  \textbf{Lv2}\\
   \textbf{Turn off check list}
@@
 }
-\Person{Jon}{
-  Equipments and power supplies are mostly located around the machine table facing the laser table
-  or the computer area.\\
-  Check Jessie's part after everything are off.
-}
+
+\onecolumn
+\Person{Jessie}{
+  Equipments and power supplies are mostly located between the machine table and the 1.5 table.
+}
+\begin{center}
+  {\LARGE\textbf{Equipment list}}
+\end{center}
+\begin{longtable}{|c|c|c|}
+  \hline
+  \textbf{ID}&\textbf{Equipment}&\textbf{Location}\\\hline
+  \multicolumn{3}{|c|}{\textbf{Machine table Facing the wall} north}\\\hline
+  1&Benchtop power 2chn&Lv2\\\hline
+  2&Home power (24)&Lv2 above 1.0 tweezer breadboard\\\hline
+  3&Home power ($\pm$15,5)&Lv2 above home power (24)\\\hline
+  4&Benchtop power x9 (2chn x3)&Lv2 next to home power (24) and ($\pm$15,5)\\\hline
+  5&Current servo for compensation coil&Lv1 below home power (24)\\\hline
+  6&Kenneth servo for 1.0 Cs tweezer&Lv1\\\hline
+  7&High voltage Amp for 630 lock&Lv1\\\hline
+  8&Vincent servo x2 for STIRAP lasers&Lv1\\\hline
+  9&Greiner servo for 1.0 Na tweezer&Lv1 above Vincent servos\\\hline
+  10&Rack for STRAP&Lv1 next to Vincent servos\\\hline
+  11&Till driver v2 x2 for STIRAP lasers&Lv1 above rack for 1.5\\\hline
+  12&Temp servo x3 for STIRAP&Lv2 next to 9x benchtop power\\\hline
+  13&FPGA box for 1.5&Lv2\\\hline
+  14&Home power ($\pm$15,5)&Lv2 next to FPGA box\\\hline
+  15&Benchtop power x2&Lv2 on home power ($\pm$15,5)\\\hline
+  16&Benchtop power&Lv2 next to home power ($\pm$15,5)\\\hline
+  17&Benchtop power x2 (2chn x1)&Floor rack Lv1\\\hline
+  18&Till driver v2 x2 for 1.5 Cs Raman&Floor rack Lv2\\\hline
+  19&Kenneth servo for 1.5 Cs Raman phase lock&Floor rack Lv2 above Till drivers\\\hline
+  20&Benchtop power&Floor rack Lv2 next to Till drivers\\\hline
+  21&Temp servo x2 for 1.5 Cs Raman&Floor rack Lv2\\\hline
+  22&Piezo driver for 1.5 Cs Raman&Floor rack Lv2 above home temp servos\\\hline
+  23&Delay generator for 1.5 Na&Lv1 below 1.5 output panel\\\hline
+  24&Till driver v2 for 1.0 Innolume&Lv1 next to delay generator\\\hline
+  25&Kenneth servo for 1.5 tweezers&Lv1\\\hline
+  26&Temp servo for 1.0 Innolume&Lv1\\\hline
+  27&Shutter driver&Lv1 on M2 controller\\\hline
+  28&TiSapph&Floor\\\hline
+  29&Function generator for 1.0 Na switching&Lv1 above TiSapph\\\hline
+  30&Keithley power for 1.0 Innolume&Lv2 above TiSapph\\\hline
+  31&Till driver v2 for 1.0 Cs MOT&Lv2 above 1.5 Cs MOT\\\hline
+  32&Temp servo for 1.0 Cs MOT&Lv2 on Till driver v2\\\hline
+  33&Benchtop power 2chn&Lv2 facing computer\\\hline
+  34&High voltage power&Above Lv2 on power outlet\\\hline
+  \multicolumn{3}{|c|}{1.5 Rack}\\\hline
+  35&Home power (24)&Bottom level\\\hline
+  36&SEAS pump controller&Middle left\\\hline
+  37&Benchtop power&Middle next to pump controller\\\hline
+  38&Oscilloscope for 1.5 monitor&Above pump controller\\\hline
+  39&Benchtop power 2chn for 1.5 coil&Above oscilloscope\\\hline
+  40&High voltage Amp for 1.5 MOT piezo&Top level\\\hline
+  41&Function generator for 1.5 MOT piezo&Top level on high voltage Amp\\\hline
+  \multicolumn{3}{|c|}{Below 1.5 table}\\\hline
+  42&Benchtop power x3&Near outer edge\\\hline
+  43&IGBT stack&Floor\\\hline
+  44&LED driver&Near inner edge\\\hline
+  45&AWG computer&Floor\\\hline
+  \multicolumn{3}{|c|}{Above 1.5 table}\\\hline
+  46&Benchtop power&Lv1\\\hline
+  47&Benchtop power&Lv2\\\hline
+  48&Radio computer&Lv2\\\hline
+\end{longtable}
+\twocolumn
+
 \subsection{Equipments}
-\DevDef{Agilent function generator for Na 1.0 switching}{
-  \textbf{1st level above TiSapph facing computers}\\
-  Record parameters:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Ch1 Hi&\hphantom{\hspace{3.5cm}}\\\hline
-    Ch1 Lo&\\\hline
-    Ch2 Hi&\\\hline
-    Ch2 Lo&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into wall
-  \item\OnBox Turn on
-  \item\OnBox Set frequency, duty cycle, high/low voltages
-  \item\OnBox Set switching phase back
-  \end{itemize}
-}
-\DevDef{2nd version Till's current controller for Cs 1.5 (x2)}{
-  \textbf{1st level above 1.5 Cs MOT}\\
-  Record current values:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Top Current&\hphantom{\hspace{3.5cm}}\\\hline
-    Bottom Current&\hphantom{\hspace{3.5cm}}\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug power (zip tie to controller)
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug in power
-  \item\OnBox Turn on
-  \end{itemize}
-}
-\DevDef{Thorlabs current controller}{
-  \textbf{1st level below Cs 1.5 MOT drivers}\\
-  Unused\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug power
-  \end{itemize}
-}
-\DevDef{Homebuilt temperature servo for Cs 1.5 MOT (x2)}{
-  \textbf{1st level above Cs 1.5 MOT}\\
-  Switch off/on the front switch
-}
-\DevDef{Oscilloscope for Cs 1.5 MOT lock}{
-  \textbf{1st level above Cs 1.5 MOT}
-  \begin{itemize}
-  \item\OffBox Unplug from wall
-  \end{itemize}
-}
-\DevDef{Homebuilt lockbox for Cs 1.5 MOT}{
-  \textbf{1st level above Cs 1.5 MOT}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unlock
-  \item\OffBox Unplug 15V from lockbox (zip tie)
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug in 15V to lockbox
-  \end{itemize}
-}
-\DevDef{Function generator for Cs MOT 1.5 lockbox}{
-  \textbf{1st level under Cs MOT 1.5 lockbox}
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Record settings
-  \item\OffBox Turn off
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into wall
-  \item\OnBox Turn on
-  \item\OnBox Restore settings
-  \end{itemize}
-}
-\DevDef{HV amplifiers for 1.0 piezo mirrors}{
-  \textbf{Above the space beween Na 1.5 beam path and NaCs 1.5 chamber}\\
-  \textbf{Turn on-off together with the function generator below
-    and the high voltage power supply on the left}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off the function generator
-  \item\OffBox Unplug function generator output (zip tie and label)
-  \item\OffBox Unplug HV power supply from the wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plugin HV power supply to the wall
-  \item\OnBox Plugin function generator output
-  \item\OnBox Turn on the function generator
-  \end{itemize}
-}
-\DevDef{Pump}{
-  \textbf{1st level above NaCs 1.0 chamber}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug from walls
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into wall
-  \item\OnBox Turn on (should be enough)
-  \end{itemize}
-}
-\DevDef{Andor Camera for 1.0}{
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Switch off
-  \item\OffBox Switch off chiller
-  \item\OffBox Unplug camera power (zip tie to camera)
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug in camera power
-  \item\OnBox Switch on chiller
-  \item\OnBox Switch on
-  \end{itemize}
-}
-\subsection{Power supplies}
-\DevDef{Benchtop power supply}{
-  \textbf{2nd level above Cs 1.5 MOT controllers}\\
-  Record voltage/current values:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-    Left Current&\\\hline
-    Right Voltage&\\\hline
-    Right Current&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug loads
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Turn off the power supply
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Homebuilt $24$V power supply}{
-  \textbf{2nd level above Cs 1.5 MOT controllers}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug load
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Switch off on the back
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Switch on
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Benchtop power supply (x2)}{
-  \textbf{1st level above Na 1.5 bean path}\\
-  Record voltage/current values:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-    Left Current&\\\hline
-    Right Voltage&\\\hline
-    Right Current&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug loads
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Turn off the power supply
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Homebuilt $\pm15,5$V power supply}{
-  \textbf{2nd level above Na 1.5 beam path}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug load
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Switch off on the back
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Switch on
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Benchtop power supply (x2)}{
-  \textbf{2nd level above piezo mirror electronics}\\
-  Record voltage/current values:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-    Left Current&\\\hline
-    Right Voltage&\\\hline
-    Right Current&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug loads
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Turn off the power supply
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Benchtop power supply}{
-  \textbf{2nd level above NaCs 1.0 chamber}\\
-  Record voltage/current values:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-    Left Current&\\\hline
-    Right Voltage&\\\hline
-    Right Current&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug loads
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Turn off the power supply
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\subsection{Computers}
-\DevDef{Tweezer 2 computer}{
-  \textbf{Check following devices}
-  \begin{itemize}
-  \item\OnBox Andor camera
-  \end{itemize}
-}
-\DevDef{Tweezer 3 computer}{
-  \textbf{Check following devices}
-  \begin{itemize}
-  \item\OnBox Software radio
-  \end{itemize}
-}
-\Person{Lee}{
-  Equipments and power supplies are mostly located around the laser table
-  on the computer area side.\\
-  Check Yichao's part after everything are off.
-}
-\subsection{Equipments}
-\DevDef{PLL for 1.0 Cs MOT}{
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug all signals (zip tie together)
-  \item\OffBox Unplug 15V and 5V powers (zip tie together)
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plugin 15V and 5V powers
-  \item\OnBox Plugin all signals
-  \item\OnBox Apply settings according to note on Generic tab, Equipment Settings.
-  \end{itemize}
-}
-\DevDef{PLL for 1.0 Cs Raman}{
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug all signals (zip tie together)
-  \item\OffBox Unplug 15V and 5V powers (zip tie together)
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plugin 15V and 5V powers
-  \item\OnBox Plugin all signals
-  \item\OnBox Apply settings according to note on Generic tab, Equipment Settings.
-  \end{itemize}
-}
-\DevDef{Homebuilt temperature servo for Cs 1.0 MOT}{
-  \textbf{1st level above Cs tweezer/MOT lasers}\\
-  Switch off/on the front switch
-}
-\DevDef{1st version Till's current controller for Cs MOT}{
-  \textbf{1st level above Cs tweezer/MOT lasers}\\
-  Record current value:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Current&\hphantom{\hspace{3.5cm}}\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug power (zip tie to controller)
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug in power
-  \item\OnBox Turn on
-  \end{itemize}
-}
-\DevDef{Cs 1.0 MOT lock box}{
-  \textbf{1st level above Cs MOT lasers}
-  \begin{itemize}
-  \item\OffBox Make sure the laser is unlocked.
-  \end{itemize}
-}
-\DevDef{Novatech function generator}{
-  \textbf{1st level above Cs MOT lasers}
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Save settings
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Restore settings
-  \end{itemize}
-}
-\DevDef{New Focus Cs Raman lasers drivers (2x)}{
-  \textbf{1st level above Cs Raman lasers}\\
-  Record Temperature, Current, Piezo voltage\\
-  Temperature is accessible in the menu under system status\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    F3 Current&\hphantom{\hspace{3.5cm}}\\\hline
-    F3 Piezo Voltage&\\\hline
-    F3 Temperature&\\\hline
-    F4 Current&\\\hline
-    F4 Piezo Voltage&\\\hline
-    F4 Temperature&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug power
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug in power
-  \item\OnBox (Turn on)
-  \end{itemize}
-}
-\DevDef{SRS shutter driver for Cs}{
-  \textbf{1st level above Cs Raman lasers}\\
-  Switch off/on with the switch on the back.
-}
-\DevDef{New Focus lock box for Cs Raman}{
-  \textbf{1st level above Cs Raman lasers}\\
-  Unplug power.
-}
-\DevDef{Homebuilt temperature servo for Cs tweezer}{
-  \textbf{1st level above Cs tweezer}\\
-  Switch off/on the front switch
-}
-\DevDef{2nd version Till's current controller for Cs Tweezer}{
-  \textbf{1st level above Cs tweezer}\\
-  Record current value:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Current&\hphantom{\hspace{3.5cm}}\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug power (zip tie to controller)
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug in power
-  \item\OnBox Turn on
-  \end{itemize}
-}
-\DevDef{Thorlabs current controller}{
-  \textbf{1st level below Cs tweezer driver}\\
-  Unused\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug power
-  \end{itemize}
-}
-\DevDef{Thorlabs temperature controller for Cs tweezer}{
-  \textbf{1st level above Cs tweezer}\\
-  Record temperature settings\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Setpoint&\hphantom{\hspace{3.5cm}}\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Turn off
-  \item\OffBox Unplug power
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug in power
-  \item\OnBox Check temperature setting
-  \item\OnBox Turn on
-  \end{itemize}
-}
-\DevDef{Intensity servo for Cs}{
-  \textbf{1st level above Cs tweezer}\\
-  Unplug power
-}
-\subsection{Power supplies}
-\DevDef{Benchtop power supply}{
-  \textbf{1st level above Cs tweezer/MOT lasers}\\
-  Record voltage/current values:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-    Left Current&\\\hline
-    Right Voltage&\\\hline
-    Right Current&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug loads
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Turn off the power supply
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Homebuilt $\pm15,5$V power supply}{
-  \textbf{2nd level above Cs tweezer/MOT lasers}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug load
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Switch off on the back
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Switch on
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Benchtop power supply}{
-  \textbf{1st level next to Cs Raman driver}\\
-  Record voltage/current values:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-    Current&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug loads
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Turn off the power supply
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Homebuilt $24$V power supply}{
-  \textbf{2nd level above Cs Raman lasers}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug load
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Switch off on the back
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Switch on
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Benchtop power supply for Cs Raman locking}{
-  \textbf{2nd level above Cs Raman lockbox}\\
-  Record voltage/current values:\\
-
-  \begin{tabular}{|c|c|}
-    \hline
-    Voltage&\hphantom{\hspace{3.5cm}}\\\hline
-    Current&\\\hline
-  \end{tabular}\\
-
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug loads
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Turn off the power supply
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\subsection{Computers}
-\DevDef{Tweezer 1 computer}{
-  \textbf{Check following devices}
-  \begin{itemize}
-  \item\OnBox Thorlabs cameras
-  \item\OnBox Na Raman amplifier
-  \end{itemize}
-}
-\Person{Jessie}{
-  Equipments and power supplies are mostly located around the machine table facing the 1.5 table.\\
-  Check Frederic's part after everything are off.
-}
-\subsection{Equipments}
+\DevDef{Current servo for compensation coil [5]}{
+  \textbf{Lv1 below home power (24)}\\
+}
+
+\DevDef{Kenneth servo for 1.0 Cs tweezer [6]}{
+  \textbf{Lv1}\\
+}
+
+\DevDef{High voltage Amp for 630 lock [7]}{
+  \textbf{Lv1}\\
+}
+
+\DevDef{Vincent servo x2 for STIRAP lasers [8]}{
+  \textbf{Lv1}\\
+}
+
+\DevDef{Greiner servo for 1.0 Na tweezer [9]}{
+  \textbf{Lv1 above Vincent servos}\\
+}
+
+\DevDef{Rack for STRAP [10]}{
+  \textbf{Lv1 next to Vincent servos}\\
+}
+
+\DevDef{Till driver v2 x2 for STIRAP lasers [11]}{
+  \textbf{Lv1 above rack for 1.5}\\
+}
+
+\DevDef{Temp servo x3 for STIRAP [12]}{
+  \textbf{Lv2 next to 9x benchtop power}\\
+}
+
+\DevDef{FPGA box for 1.5 [13]}{
+  \textbf{Lv2}\\
+}
+
+\DevDef{Till driver v2 x2 for 1.5 Cs Raman [18]}{
+  \textbf{Floor rack Lv2}\\
+}
+
+\DevDef{Kenneth servo for 1.5 Cs Raman phase lock [19]}{
+  \textbf{Floor rack Lv2 above Till drivers}\\
+}
+
+\DevDef{Temp servo x2 for 1.5 Cs Raman [21]}{
+  \textbf{Floor rack Lv2}\\
+}
+
+\DevDef{Piezo driver for 1.5 Cs Raman [22]}{
+  \textbf{Floor rack Lv2 above home temp servos}\\
+}
+
+\DevDef{Delay generator for 1.5 Na [23]}{
+  \textbf{Lv1 below 1.5 output panel}\\
+}
+
+\DevDef{Till driver v2 for 1.0 Innolume [24]}{
+  \textbf{Lv1 next to delay generator}\\
+}
+
+\DevDef{Kenneth servo for 1.5 tweezers [25]}{
+  \textbf{Lv1}\\
+}
+
+\DevDef{Temp servo for 1.0 Innolume [26]}{
+  \textbf{Lv1}\\
+}
+
+\DevDef{Shutter driver [27]}{
+  \textbf{Lv1 on M2 controller}\\
+}
+
+\DevDef{TiSapph [28]}{
+  \textbf{Floor}\\
+}
+
+\DevDef{Function generator for 1.0 Na switching [29]}{
+  \textbf{Lv1 above TiSapph}\\
+}
+
+\DevDef{Keithley power for 1.0 Innolume [30]}{
+  \textbf{Lv2 above TiSapph}\\
+}
+
+\DevDef{Till driver v2 for 1.0 Cs MOT [31]}{
+  \textbf{Lv2 above 1.5 Cs MOT}\\
+}
+
+\DevDef{Temp servo for 1.0 Cs MOT [32]}{
+  \textbf{Lv2 on Till driver v2}\\
+}
+
+\DevDef{SEAS pump controller [36]}{
+  \textbf{Middle left}\\
+}
+
+\DevDef{Oscilloscope for 1.5 monitor [38]}{
+  \textbf{Above pump controller}\\
+}
+
+\DevDef{High voltage Amp for 1.5 MOT piezo [40]}{
+  \textbf{Top level}\\
+}
+
+\DevDef{Function generator for 1.5 MOT piezo [41]}{
+  \textbf{Top level on high voltage Amp}\\
+}
+
+\DevDef{IGBT stack [43]}{
+  \textbf{Floor}\\
+}
+
+\DevDef{LED driver [44]}{
+  \textbf{Near inner edge}\\
+}
+
 \DevDef{TiSapph}{
@@
 }
-\DevDef{PLL for 1.5 Cs MOT}{
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug all signals (zip tie together)
-  \item\OffBox Unplug 15V and 5V powers (zip tie together)
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plugin 15V and 5V powers
-  \item\OnBox Plugin all signals
-  \item\OnBox Apply settings ???
-  \end{itemize}
-}
 \subsection{Power supplies}
+\DevDef{Benchtop power 2chn [1]}{
+  \textbf{Lv2}\\
+}
+
+\DevDef{Home power (24) [2]}{
+  \textbf{Lv2 above 1.0 tweezer breadboard}\\
+}
+
+\DevDef{Home power ($\pm$15,5) [3]}{
+  \textbf{Lv2 above home power (24)}\\
+}
+
+\DevDef{Benchtop power x9 (2chn x3) [4]}{
+  \textbf{Lv2 next to home power (24) and ($\pm$15,5)}\\
+}
+
+\DevDef{Home power ($\pm$15,5) [14]}{
+  \textbf{Lv2 next to FPGA box}\\
+}
+
+\DevDef{Benchtop power x2 [15]}{
+  \textbf{Lv2 on home power ($\pm$15,5)}\\
+}
+
+\DevDef{Benchtop power [16]}{
+  \textbf{Lv2 next to home power ($\pm$15,5)}\\
+}
+
+\DevDef{Benchtop power x2 (2chn x1) [17]}{
+  \textbf{Floor rack Lv1}\\
+}
+
+\DevDef{Benchtop power [20]}{
+  \textbf{Floor rack Lv2 next to Till drivers}\\
+}
+
+\DevDef{Benchtop power 2chn [33]}{
+  \textbf{Lv2 facing computer}\\
+}
+
+\DevDef{High voltage power [34]}{
+  \textbf{Above Lv2 on power outlet}\\
+}
+
+\DevDef{Home power (24) [35]}{
+  \textbf{Bottom level}\\
+}
+
+\DevDef{Benchtop power [37]}{
+  \textbf{Middle next to pump controller}\\
+}
+
+\DevDef{Benchtop power 2chn for 1.5 coil [39]}{
+  \textbf{Above oscilloscope}\\
+}
+
+\DevDef{Benchtop power x3 [42]}{
+  \textbf{Near outer edge}\\
+}
+
+\DevDef{Benchtop power [46]}{
+  \textbf{Lv1}\\
+}
+
+\DevDef{Benchtop power [47]}{
+  \textbf{Lv2}\\
+}
+
 \DevDef{Homebuilt $24$V power supply}{
@@
 \subsection{Computers}
+\DevDef{AWG computer [45]}{
+  \textbf{Floor}\\
+}
+
+\DevDef{Radio computer [48]}{
+  \textbf{Lv2}\\
+}
+
 \DevDef{Computer control box for 1.5}{

### 2019-05-08 presentations/2019-04-27_shutdown/checklist.tex
[presentation/2019-04-27_shutdown] Finish checklist

@@
 Also wait before everyone else finish their corresponding steps before starting the next one.\\
+
+Please check to make sure the temperature controller for a laser is not turned off before
+the laser itself is. If a temperature controller is powered by homebuilt power supply,
+mark the output so that it won't be unplugged from the power supply and plug the whole
+power supply into the UPS instead of turning off.
+Homebuilt power supplies on the UPS should still be switched off if there's no load on it
+that needs to be on to reduce load on the UPS/external power.\\
+
+For machine table and 1.5 table, use a normal power strip to collect devices that
+needs to be on the UPS. We'll plug the power strip into an actual UPS after the computer
+is shut down and the UPS's are freed up.\\
+
+All numbering are from bottom to top and from left to right.\\
 
@@
   \textbf{Lv2}\\
+  Ask Yichao
 }
@@
 \onecolumn
-\Person{Jessie}{
+\Person{Jessie and Lewis}{
   Equipments and power supplies are mostly located between the machine table and the 1.5 table.
@@
   35&Home power (24)&Bottom level\\\hline
-  36&SEAS pump controller&Middle left\\\hline
+  36&SAES pump controller&Middle left\\\hline
   37&Benchtop power&Middle next to pump controller\\\hline
@@
   \textbf{Lv1 below home power (24)}\\
-}
-
-\DevDef{Kenneth servo for 1.0 Cs tweezer [6]}{
-  \textbf{Lv1}\\
+  Ask Lewis\\
 }
@@
   \textbf{Lv1}\\
+  Ask Lewis\\
 }
@@
   \textbf{Lv1}\\
-}
-
-\DevDef{Greiner servo for 1.0 Na tweezer [9]}{
-  \textbf{Lv1 above Vincent servos}\\
+  Ask Lewis\\
 }
@@
   \textbf{Lv1 next to Vincent servos}\\
+  Ask Lewis\\
 }
@@
   \textbf{Lv1 above rack for 1.5}\\
+  Record current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    No. 1 Current&\hphantom{\hspace{3.5cm}}\\\hline
+    No. 2 Current&\\\hline
+  \end{tabular}\\
+
+  Ask Lewis\\
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off
+  \item\OffBox Unplug power (zip tie to controller)
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug in power
+  \item\OnBox Turn on
+  \end{itemize}
 }
@@
   \textbf{Lv2 next to 9x benchtop power}\\
-}
-
-\DevDef{FPGA box for 1.5 [13]}{
-  \textbf{Lv2}\\
+
+  Ask Lewis\\
+  Check plugged into UPS.
 }
@@
   \textbf{Floor rack Lv2}\\
+  Record current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    No. 1 Current&\hphantom{\hspace{3.5cm}}\\\hline
+    No. 2 Current&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off
+  \item\OffBox Unplug power (zip tie to controller)
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug in power
+  \item\OnBox Turn on
+  \end{itemize}
 }
@@
   \textbf{Floor rack Lv2}\\
+  Check plugged into UPS.
 }
@@
   \textbf{Lv1 below 1.5 output panel}\\
+  Record current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    \hphantom{\hspace{3.5cm}}&\hphantom{\hspace{3.5cm}}\\\hline
+    &\\\hline
+    &\\\hline
+    &\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox
+  \item\OffBox
+  \item\OffBox
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox
+  \item\OnBox
+  \item\OnBox
+  \end{itemize}
 }
@@
   \textbf{Lv1 next to delay generator}\\
-}
-
-\DevDef{Kenneth servo for 1.5 tweezers [25]}{
-  \textbf{Lv1}\\
+  Record current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Current&\hphantom{\hspace{3.5cm}}\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off
+  \item\OffBox Unplug power (zip tie to controller)
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug in power
+  \item\OnBox Turn on
+  \end{itemize}
 }
@@
   \textbf{Lv1}\\
+  Check plugged into UPS.
 }
@@
   \textbf{Lv1 on M2 controller}\\
+  Switch off/on with the switch on the back.
 }
@@
   \textbf{Floor}\\
-}
-
-\DevDef{Function generator for 1.0 Na switching [29]}{
-  \textbf{Lv1 above TiSapph}\\
-}
-
-\DevDef{Keithley power for 1.0 Innolume [30]}{
-  \textbf{Lv2 above TiSapph}\\
-}
-
-\DevDef{Till driver v2 for 1.0 Cs MOT [31]}{
-  \textbf{Lv2 above 1.5 Cs MOT}\\
-}
-
-\DevDef{Temp servo for 1.0 Cs MOT [32]}{
-  \textbf{Lv2 on Till driver v2}\\
-}
-
-\DevDef{SEAS pump controller [36]}{
-  \textbf{Middle left}\\
-}
-
-\DevDef{Oscilloscope for 1.5 monitor [38]}{
-  \textbf{Above pump controller}\\
-}
-
-\DevDef{High voltage Amp for 1.5 MOT piezo [40]}{
-  \textbf{Top level}\\
-}
-
-\DevDef{Function generator for 1.5 MOT piezo [41]}{
-  \textbf{Top level on high voltage Amp}\\
-}
-
-\DevDef{IGBT stack [43]}{
-  \textbf{Floor}\\
-}
-
-\DevDef{LED driver [44]}{
-  \textbf{Near inner edge}\\
-}
-
-\DevDef{TiSapph}{
   \textbf{Turn off check list}
@@
 }
-\DevDef{Quantel Laser}{
-  \textbf{1st level in the middle, facing 1.5 table}\\
-  Ask Frederic.
-  \vspace{1cm}
-}
-\DevDef{Intensity servo for Na}{
-  \textbf{1st level above Na tweezer, below 1.0 computer control box}\\
-  Unplug power
-}
-\DevDef{1st version Till's current controller for butterfly laser}{
-  \textbf{1st level above TiSapph}\\
+
+\DevDef{Function generator for 1.0 Na switching [29]}{
+  \textbf{Lv1 above TiSapph}\\
+  Record High, Low, Frequency, Phase, Duty cycle\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    No. 1 High V&\hphantom{\hspace{3.5cm}}\\\hline
+    No. 1 Low V&\\\hline
+    No. 1 Frequency&\\\hline
+    No. 1 Phase&\\\hline
+    No. 1 Duty cycle&\\\hline
+    No. 2 High V&\hphantom{\hspace{3.5cm}}\\\hline
+    No. 2 Low V&\\\hline
+    No. 2 Frequency&\\\hline
+    No. 2 Phase&\\\hline
+    No. 2 Duty cycle&\\\hline
+  \end{tabular}\\
+}
+
+\DevDef{Keithley power for 1.0 Innolume [30]}{
+  \textbf{Lv2 above TiSapph}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    Current&\\\hline
+  \end{tabular}\\
+
+  Turn off after the Innolume is off.
+}
+
+\DevDef{Till driver v2 for 1.0 Cs MOT [31]}{
+  \textbf{Lv2 above 1.5 Cs MOT}\\
+  Record current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Current&\hphantom{\hspace{3.5cm}}\\\hline
+  \end{tabular}\\
+
   \textbf{Turn off check list}
@@
   \end{itemize}
-}
-\DevDef{Homebuilt temperature servo for butterfly laser}{
-  \textbf{1st level above TiSapph}\\
-  Switch off/on the front switch
-}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug in power
+  \item\OnBox Turn on
+  \end{itemize}
+}
+
+\DevDef{Temp servo for 1.0 Cs MOT [32]}{
+  \textbf{Lv2 on Till driver v2}\\
+  Check plugged into UPS.
+}
+
+\DevDef{SAES pump controller [36]}{
+  \textbf{Middle left}\\
+
+  Check plugged into UPS.
+}
+
+\DevDef{Oscilloscope for 1.5 monitor [38]}{
+  \textbf{Above pump controller}\\
+
+  \begin{itemize}
+  \item\OffBox Unplug from wall
+  \end{itemize}
+}
+
+\DevDef{High voltage Amp for 1.5 MOT piezo [40]}{
+  \textbf{Top level}\\
+}
+
+\DevDef{Function generator for 1.5 MOT piezo [41]}{
+  \textbf{Top level on high voltage Amp}\\
+
+  1.0 turn off procedure for reference:\\
+  \textbf{Turn on-off together with the HV amplifiers for 1.0 piezo mirrors above
+    and the high voltage power supply on the left}\\
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Turn off the function generator
+  \item\OffBox Unplug function generator output (zip tie and label)
+  \item\OffBox Unplug HV power supply from the wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plugin HV power supply to the wall
+  \item\OnBox Plugin function generator output
+  \item\OnBox Turn on the function generator
+  \end{itemize}
+}
+
+\DevDef{IGBT stack [43]}{
+  \textbf{Floor}\\
+}
+
+\DevDef{LED driver [44]}{
+  \textbf{Near inner edge}\\
+}
+
 \subsection{Power supplies}
@@
   \textbf{Lv2}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    Left Current&\\\hline
+    Right Voltage&\\\hline
+    Right Current&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug loads
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Turn off the power supply
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
+  \item\OnBox Plug the load back in
+  \end{itemize}
 }
@@
   \textbf{Lv2 above 1.0 tweezer breadboard}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug load
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Switch off on the back
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Switch on
+  \item\OnBox Plug the load back in
+  \end{itemize}
 }
@@
   \textbf{Lv2 above home power (24)}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug load
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Switch off on the back
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Switch on
+  \item\OnBox Plug the load back in
+  \end{itemize}
 }
@@
   \textbf{Lv2 next to home power (24) and ($\pm$15,5)}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    \small{No. 1 Voltage/Current}&\hphantom{\hspace{4.5cm}}\\\hline
+    \small{No. 2 Left Voltage/Current}&\\\hline
+    \small{No. 2 Right Voltage/Current}&\\\hline
+    \small{No. 3 Voltage/Current}&\\\hline
+    \small{No. 4 Voltage/Current}&\\\hline
+    \small{No. 5 Left Voltage/Current}&\\\hline
+    \small{No. 5 Right Voltage/Current}&\\\hline
+    \small{No. 6 Left Voltage/Current}&\\\hline
+    \small{No. 6 Right Voltage/Current}&\\\hline
+    \small{No. 7 Voltage/Current}&\\\hline
+    \small{No. 8 Voltage/Current}&\\\hline
+    \small{No. 9 Voltage/Current}&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug loads
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Turn off the power supply
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
+  \item\OnBox Plug the load back in
+  \end{itemize}
 }
@@
   \textbf{Lv2 next to FPGA box}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug load
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Switch off on the back
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Switch on
+  \item\OnBox Plug the load back in
+  \end{itemize}
 }
@@
   \textbf{Lv2 on home power ($\pm$15,5)}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    No. 1 Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    No. 1 Current&\\\hline
+    No. 2 Voltage&\\\hline
+    No. 2 Current&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug loads
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Turn off the power supply
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
+  \item\OnBox Plug the load back in
+  \end{itemize}
 }
@@
   \textbf{Lv2 next to home power ($\pm$15,5)}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    Current&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug loads
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Turn off the power supply
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
+  \item\OnBox Plug the load back in
+  \end{itemize}
 }
@@
   \textbf{Floor rack Lv1}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    No. 1 Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    No. 1 Current&\\\hline
+    No. 2 Left Voltage&\\\hline
+    No. 2 Left Current&\\\hline
+    No. 2 Right Voltage&\\\hline
+    No. 2 Right Current&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug loads
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Turn off the power supply
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
+  \item\OnBox Plug the load back in
+  \end{itemize}
 }
@@
   \textbf{Floor rack Lv2 next to Till drivers}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    Current&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug loads
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Turn off the power supply
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
+  \item\OnBox Plug the load back in
+  \end{itemize}
 }
@@
   \textbf{Lv2 facing computer}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    Left Current&\\\hline
+    Right Voltage&\\\hline
+    Right Current&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug loads
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Turn off the power supply
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
+  \item\OnBox Plug the load back in
+  \end{itemize}
 }
@@
   \textbf{Bottom level}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug load
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Switch off on the back
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Switch on
+  \item\OnBox Plug the load back in
+  \end{itemize}
 }
@@
   \textbf{Middle next to pump controller}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    Current&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug loads
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Turn off the power supply
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
+  \item\OnBox Plug the load back in
+  \end{itemize}
 }
@@
   \textbf{Above oscilloscope}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Left Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    Left Current&\\\hline
+    Right Voltage&\\\hline
+    Right Current&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug loads
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Turn off the power supply
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
+  \item\OnBox Plug the load back in
+  \end{itemize}
 }
@@
   \textbf{Near outer edge}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    No. 1 Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    No. 1 Current&\\\hline
+    No. 2 Voltage&\\\hline
+    No. 2 Current&\\\hline
+    No. 3 Voltage&\\\hline
+    No. 3 Current&\\\hline
+  \end{tabular}\\
+
+  May need to be adjusted for the uWave Amp.\\
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug loads
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Turn off the power supply
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
+  \item\OnBox Plug the load back in
+  \end{itemize}
 }
@@
   \textbf{Lv1}\\
+  Record voltage/current values:\\
+
+  \begin{tabular}{|c|c|}
+    \hline
+    Voltage&\hphantom{\hspace{3.5cm}}\\\hline
+    Current&\\\hline
+  \end{tabular}\\
+
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Unplug loads
+  \item\OffBox Label and zip tie loads to the power supply
+  \item\OffBox Turn off the power supply
+  \item\OffBox Unplug from wall
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Plug into the wall
+  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
+  \item\OnBox Plug the load back in
+  \end{itemize}
 }
@@
   \textbf{Lv2}\\
-}
-
-\DevDef{Homebuilt $24$V power supply}{
-  \textbf{2nd level above NaCs 1.0 chamber, facing the drawers/wall}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug load
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Switch off on the back
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Switch on
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Benchtop power supply for dispensers}{
-  \textbf{1st level above NaCs 1.0 chamber}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug loads
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Turn off the power supply
-  \item\OffBox Unplug from wall
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Plug into the wall
-  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
-\DevDef{Benchtop power supply for 1.5 computer control clock}{
-  \textbf{2nd level next to 1.5 computer control box}\\
   Record voltage/current values:\\
@@
 }
-\DevDef{Homebuilt $\pm15,5$V power supply}{
-  \textbf{2nd level above TiSapph}\\
-  \textbf{Turn off check list}
-  \begin{itemize}
-  \item\OffBox Unplug load
-  \item\OffBox Label and zip tie loads to the power supply
-  \item\OffBox Switch off on the back
-  \end{itemize}
-  \textbf{Turn on check list}
-  \begin{itemize}
-  \item\OnBox Switch on
-  \item\OnBox Plug the load back in
-  \end{itemize}
-}
+
 \subsection{Computers}
-\DevDef{AWG computer [45]}{
-  \textbf{Floor}\\
-}
-
-\DevDef{Radio computer [48]}{
+\DevDef{Control computers}{
+  \textbf{Turn off check list}
+  \begin{itemize}
+  \item\OffBox Check update.
+  \item\OffBox Turn off.
+  \item\OffBox Unplug from UPS.
+  \end{itemize}
+  \textbf{Turn on check list}
+  \begin{itemize}
+  \item\OnBox Get UPS back
+  \item\OnBox Turn on.
+  \end{itemize}
+}
+\DevDef{FPGA box for 1.5 [13]}{
   \textbf{Lv2}\\
-}
-
-\DevDef{Computer control box for 1.5}{
   \textbf{Turn off check list}
@@
 }
+\DevDef{AWG computer [45]}{
+  \textbf{Floor}\\
+  Ask Yichao
+}
+\DevDef{Radio computer [48]}{
+  \textbf{Lv2}\\
+  Ask Yichao
+}
 

### 2019-05-26 experiments/nacs_201904/plot_20190521_lifetime_cmp.jl
[experiments/nacs_201904] tweak text for the talk

@@ -90,9 +90,9 @@ ax[:set_xticks]([0.1, 1, 10, 100])
 ax[:set_xticklabels](["0.1", "1", "10", "100"])
 ylim([0.15, 0.7])
 xlim([0.1, 100])
-title("Lifetime")
-xlabel("Wait time (ms)")
-ylabel("Two body survival")
+title("Photo Association")
+xlabel("PA time (ms)")
+ylabel("Na + Cs survival")
 NaCsPlot.maybe_save("$(prefix)_log")
 
 figure()
@@ -106,9 +106,9 @@ legend()
 grid()
 ylim([0.25, 0.7])
 xlim([0, 30])
-title("Lifetime")
-xlabel("Wait time (ms)")
-ylabel("Two body survival")
+title("Photo Association")
+xlabel("PA time (ms)")
+ylabel("Na + Cs survival")
 NaCsPlot.maybe_save("$(prefix)_lin")
 
 NaCsPlot.maybe_show()

### 2019-06-04 lib/NaCsData/scripts/strip_mat.jl
[lib/NaCsData] workaround MAT bug

@@ -80,12 +80,37 @@ end
 
 const opts = process_args()
 
+# Work around MAT.jl bug
+function clear_char!(dict::Dict)
+    for k in keys(dict)
+        v = dict[k]
+        if isa(v, Char)
+            dict[k] = String([v])
+        else
+            clear_char!(v)
+        end
+    end
+end
+function clear_char!(ary::Array)
+    for i in 1:length(ary)
+        v = ary[i]
+        if isa(v, Char)
+            ary[i] = String([v])
+        else
+            clear_char!(v)
+        end
+    end
+end
+function clear_char!(o)
+end
+
 matopen(opts.iname) do mf
     pl = read(mf, "ParamList")
     sa = read(mf, "Analysis")["SingleAtomLogical"]
     scan = read(mf, "Scan")
     param_name = scan["ParamName"]
     sg = haskey(scan, "ScanGroup") ? scan["ScanGroup"] : Dict{String,Any}()
+    clear_char!(sg)
     if eltype(sa) == Bool
         sa = UInt8.(sa)
     end

### 2019-06-04 experiments/pa_201906/plot_20190602_pa32.jl
[experiments/pa_201906] plot 33+22 pa

@@ -1,0 +1,67 @@
+#!/usr/bin/julia
+
+push!(LOAD_PATH, joinpath(@__DIR__, "../../lib"))
+
+import NaCsCalc.Format: Unc, Sci
+using NaCsCalc.Utils: interactive
+using NaCsData
+using NaCsPlot
+using PyPlot
+using DataStructures
+using LsqFit
+using MAT
+
+function load_data(names, selector)
+    local datas
+    for name in names
+        param, counts = matopen(joinpath(@__DIR__, "data", "data_$name.mat")) do fd
+            sg = read(fd, "ScanGroup")
+            f = sg["base"]["params"]["fWavemeter"]
+            c = read(fd, "SingleAtomLogical") .!= 0
+            return [f for _ in 1:size(c, 3)], c
+        end
+        data = NaCsData.select_count(param, counts, selector)
+        if !@isdefined datas
+            datas = data
+        else
+            datas = [datas; data]
+        end
+    end
+    return datas
+end
+
+const names_files = ["data_20190602_pa32_names.mat"]
+const datas = [load_data(matopen(fd->read(fd, "names"), joinpath(@__DIR__, "data", names_file)),
+                         NaCsData.select_single((1, 2,), (3, 4,)))
+               for names_file in names_files]
+const datas_na = [load_data(matopen(fd->read(fd, "names"),
+                                    joinpath(@__DIR__, "data", names_file)),
+                            NaCsData.select_single((1, 2,), (3,)))
+                  for names_file in names_files]
+const datas_cs = [load_data(matopen(fd->read(fd, "names"),
+                                    joinpath(@__DIR__, "data", names_file)),
+                            NaCsData.select_single((1, 2,), (4,)))
+                  for names_file in names_files]
+const datas_cs_cs = [load_data(matopen(fd->read(fd, "names"),
+                                       joinpath(@__DIR__, "data", names_file)),
+                               NaCsData.select_single((-1, 2,), (-3, 4,)))
+                     for names_file in names_files]
+const datas_na_na = [load_data(matopen(fd->read(fd, "names"),
+                                       joinpath(@__DIR__, "data", names_file)),
+                               NaCsData.select_single((1, -2,), (3, -4,)))
+                     for names_file in names_files]
+
[…]

### 2019-09-02 experiments/pa_201909/plot_20190901_162053_pa.jl
[experiments/pa_201909] Zoom into the second peak

@@ -1,0 +1,134 @@
+#!/usr/bin/julia
+
+push!(LOAD_PATH, joinpath(@__DIR__, "../../lib"))
+
+import NaCsCalc.Format: Unc, Sci
+using NaCsCalc.Utils: interactive
+using NaCsData
+using NaCsPlot
+using PyPlot
+using DataStructures
+using LsqFit
+using MAT
+
+function load_data(names, selector)
+    local datas
+    for name in names
+        param, counts = matopen(joinpath(@__DIR__, "data", "data_$name.mat")) do fd
+            pl = read(fd, "ParamList")
+            sg = read(fd, "ScanGroup")
+            f = sg["base"]["params"]["fWavemeter0"]
+            # amps = sg["base"]["vars"]["params"][2]["Merge"]["PA"]["Amp"]
+            c = read(fd, "SingleAtomLogical") .!= 0
+            return [f for i in 1:size(c, 3)], c
+        end
+        data = NaCsData.select_count(param, counts, selector)
+        if !@isdefined datas
+            datas = data
+        else
+            datas = [datas; data]
+        end
+    end
+    # datas = datas[[1:2:size(datas, 1) 2:2:size(datas, 1)]]
+    # datas = NaCsData.map_params((i1, i2, v)->v[1], datas)
+    return datas
+end
+
+const names_files = ["names_20190901_162053.mat",
+                     "names_20190901_222839.mat"]
+const datas = [load_data(matopen(fd->read(fd, "names"), joinpath(@__DIR__, "data", names_file)),
+                         NaCsData.select_single((1, 2,), (3, 4,)))
+               for names_file in names_files]
+const datas_na = [load_data(matopen(fd->read(fd, "names"), joinpath(@__DIR__, "data", names_file)),
+                            NaCsData.select_single((1, 2,), (3,)))
+                  for names_file in names_files]
+const datas_cs = [load_data(matopen(fd->read(fd, "names"), joinpath(@__DIR__, "data", names_file)),
+                            NaCsData.select_single((1, 2,), (4,)))
+                  for names_file in names_files]
+const datas_nana = [load_data(matopen(fd->read(fd, "names"), joinpath(@__DIR__, "data", names_file)),
[…]

### 2019-09-03 experiments/pa_201909/plot_20190902_112810_pa.jl
[experiments/pa_201909] 5 mW

@@ -1,0 +1,134 @@
+#!/usr/bin/julia
+
+push!(LOAD_PATH, joinpath(@__DIR__, "../../lib"))
+
+import NaCsCalc.Format: Unc, Sci
+using NaCsCalc.Utils: interactive
+using NaCsData
+using NaCsPlot
+using PyPlot
+using DataStructures
+using LsqFit
+using MAT
+
+function load_data(names, selector)
+    local datas
+    for name in names
+        param, counts = matopen(joinpath(@__DIR__, "data", "data_$name.mat")) do fd
+            pl = read(fd, "ParamList")
+            sg = read(fd, "ScanGroup")
+            f = sg["base"]["params"]["fWavemeter0"]
+            # amps = sg["base"]["vars"]["params"][2]["Merge"]["PA"]["Amp"]
+            c = read(fd, "SingleAtomLogical") .!= 0
+            return [f for i in 1:size(c, 3)], c
+        end
+        data = NaCsData.select_count(param, counts, selector)
+        if !@isdefined datas
+            datas = data
+        else
+            datas = [datas; data]
+        end
+    end
+    # datas = datas[[1:2:size(datas, 1) 2:2:size(datas, 1)]]
+    # datas = NaCsData.map_params((i1, i2, v)->v[1], datas)
+    return datas
+end
+
+const names_files = ["names_20190902_112810.mat",
+                     "names_20190902_153514.mat"]
+const datas = [load_data(matopen(fd->read(fd, "names"), joinpath(@__DIR__, "data", names_file)),
+                         NaCsData.select_single((1, 2,), (3, 4,)))
+               for names_file in names_files]
+const datas_na = [load_data(matopen(fd->read(fd, "names"), joinpath(@__DIR__, "data", names_file)),
+                            NaCsData.select_single((1, 2,), (3,)))
+                  for names_file in names_files]
+const datas_cs = [load_data(matopen(fd->read(fd, "names"), joinpath(@__DIR__, "data", names_file)),
+                            NaCsData.select_single((1, 2,), (4,)))
+                  for names_file in names_files]
+const datas_nana = [load_data(matopen(fd->read(fd, "names"), joinpath(@__DIR__, "data", names_file)),
[…]

### 2019-09-03 experiments/pa_201909/plot_20190903_062132_pa.jl
[experiments/pa_201909] Lower frequency to check for 10 mW tweezer PA line

@@ -1,0 +1,132 @@
+#!/usr/bin/julia
+
+push!(LOAD_PATH, joinpath(@__DIR__, "../../lib"))
+
+import NaCsCalc.Format: Unc, Sci
+using NaCsCalc.Utils: interactive
+using NaCsData
+using NaCsPlot
+using PyPlot
+using DataStructures
+using LsqFit
+using MAT
+
+function load_data(names, selector)
+    local datas
+    for name in names
+        param, counts = matopen(joinpath(@__DIR__, "data", "data_$name.mat")) do fd
+            pl = read(fd, "ParamList")
+            sg = read(fd, "ScanGroup")
+            f = sg["base"]["params"]["fWavemeter0"]
+            # amps = sg["base"]["vars"]["params"][2]["Merge"]["PA"]["Amp"]
+            c = read(fd, "SingleAtomLogical") .!= 0
+            return [f for i in 1:size(c, 3)], c
+        end
+        data = NaCsData.select_count(param, counts, selector)
+        if !@isdefined datas
+            datas = data
+        else
+            datas = [datas; data]
+        end
+    end
+    # datas = datas[[1:2:size(datas, 1) 2:2:size(datas, 1)]]
+    # datas = NaCsData.map_params((i1, i2, v)->v[1], datas)
+    return datas
+end
+
+const names_files = ["names_20190903_062132.mat"]
+const datas = [load_data(matopen(fd->read(fd, "names"), joinpath(@__DIR__, "data", names_file)),
+                         NaCsData.select_single((1, 2,), (3, 4,)))
+               for names_file in names_files]
+const datas_na = [load_data(matopen(fd->read(fd, "names"), joinpath(@__DIR__, "data", names_file)),
+                            NaCsData.select_single((1, 2,), (3,)))
+                  for names_file in names_files]
+const datas_cs = [load_data(matopen(fd->read(fd, "names"), joinpath(@__DIR__, "data", names_file)),
+                            NaCsData.select_single((1, 2,), (4,)))
+                  for names_file in names_files]
+const datas_nana = [load_data(matopen(fd->read(fd, "names"), joinpath(@__DIR__, "data", names_file)),
+                              NaCsData.select_single((1, -2,), (3,)))
[…]

### 2019-09-04 presentations/2019-09-05_itamp/plot_raman.jl
[presentations/2019-09-05_itamp] RSC

@@ -1,0 +1,84 @@
+#!/usr/bin/julia
+
+push!(LOAD_PATH, joinpath(@__DIR__, "../../lib"))
+
+import NaCsCalc.Utils: interactive
+import NaCsCalc: Trap
+using NaCsPlot
+using PyPlot
+
+# matplotlib["rcParams"][:update](Dict("font.weight" => "normal"))
+
+const m_Na = 23e-3 / 6.02e23
+const η_rx = Trap.η(m_Na, 479e3, 2π / 589e-9) * √(2) * 0.96
+const η_ry = Trap.η(m_Na, 492e3, 2π / 589e-9) * √(2) * 0.933
+const η_az = Trap.η(m_Na, 85.7e3, 2π / 589e-9) * 0.67
+const η_az_op = Trap.η(m_Na, 85.7e3, 2π / 589e-9)
+
+"""
+    emission(v, isσ::Bool) -> (sinθ, cosθ)
+
+Given an uniform distribution in `[0, 1]` of `v` this function will return a distribution
+of `cosθ` that matches a dipole emission pattern (the type of the transition is determined by
+`isσ`).
+"""
+function emission_angle(v::T, isσ::Bool) where T<:AbstractFloat
+    # Returns `cosθ`. The caller should be ready to handle `|cosθ| > 1`
+    # The PDFs of the `θ` distribution are
+    # `3 / 4 * (1 - cos²θ) * sinθ` for π light and
+    # `3 / 8 * (1 + cos²θ) * sinθ` for σ± light
+    # The corresponding CDFs are
+    # `1 / 4 * (3cosθ - cos³θ) + 1 / 2` for π light and
+    # `1 / 8 * (3cosθ + cos³θ) + 1 / 2` for σ± light
+    # For a random number `v` we need to solve
+    # `3cosθ - cos³θ = 4v - 2` for π light and
+    # `3cosθ + cos³θ = 8v - 4` for σ± light
+    # The (real) solution is
+    # `cosθ = x + 1 / x` where `x = ∛(2√(v² - v) - 2v + 1)` for π light and
+    # `cosθ = x - 1 / x` where `x = ∛(√(16v² - 16v + 5) + 4v - 2)` for σ± light
+    # Note that the `x` for π polarization is complex
[…]

### 2019-11-08 experiments/sfg_power/plot_powers_20191031.jl
[experiments/sfg_power] Plot power calibration

@@ -1,0 +1,88 @@
+#!/usr/bin/julia
+
+push!(LOAD_PATH, joinpath(@__DIR__, "../../lib"))
+
+using NaCsCalc.Utils: interactive
+using NaCsData
+using NaCsPlot
+using PyPlot
+using LsqFit
+import NaCsCalc.Format: Unc, Sci
+
+const prefix = joinpath(@__DIR__, "imgs", "powers_20191031")
+
+P1550(θ) = 7.43 .* sind.(2 .* (θ - 2.44)).^2
+P1040(θ) = 9.94 .* sind.(2 .* (θ + 1.4)).^2
+
+const Input1550 = [0.150; P1550.([8, 12, 15, 18, 26, 36, 47])]
+const Input1040 = [0.150; P1040.([4, 6, 10, 16, 24, 32, 44])]
+const Output = [0.00252, 0.01030, 0.0440, 0.165,
+                0.451, 1.70 / 0.479 * 0.451, 3.44 / 0.479 * 0.451, 4.70 / 0.479 * 0.451]
+
+fit_data(model, x, y, p0; kws...) =
+    fit_data(model, x, y, nothing, p0; kws...)
+
+function fit_data(model, params, ratios, uncs, p0;
+                  plotx=nothing, plot_lo=nothing, plot_hi=nothing, plot_scale=1.1)
+    use_unc = uncs !== nothing
+    if plotx === nothing
+        lo = minimum(params)
+        hi = maximum(params)
+        span = hi - lo
+        mid = (hi + lo) / 2
+        if plot_lo === nothing
+            plot_lo = mid - span * plot_scale / 2
+            if plot_lo * lo <= 0
+                plot_lo = 0
+            end
+        end
+        if plot_hi === nothing
+            plot_hi = mid + span * plot_scale / 2
+            if plot_hi * hi <= 0
+                plot_hi = 0
+            end
+        end
+        plotx = linspace(plot_lo, plot_hi, 10000)
+    end
+    if use_unc
+        fit = curve_fit(model, params, ratios, uncs.^-(2/3), p0)
+    else
+        fit = curve_fit(model, params, ratios, p0)
+    end
+    param = fit.param
+    unc = estimate_errors(fit)
+    return (param=param, unc=unc,
+            uncs=Unc.(param, unc, Sci),
+            plotx=plotx, ploty=model.(plotx, (fit.param,)))
+end
+
[…]

### 2019-11-23 notes/sideband_obe/sideband_obe.tex
[notes] reorganize

--- 2014-09-19 sideband/obe/obe.tex
@@
 }
-where $B^{\alpha\beta}$ is the branching ratio, $\Gamma_1$ is the $F$ pumping power ($(1, 1) \rightarrow (2, 2)'$ light), $\Gamma_2$ is the $m_F$ pumping power ($(2, 1) \rightarrow (2, 2)'$ light) and $\varepsilon$ is the off-resonance coupling of the $m_F$ pumping light to the $(2, 2) \rightarrow (2, 3)'$ transition.
+where $B^{\alpha\beta}$ is the branching ratio, $\Gamma_1$ is the $F$ pumping power ($(1, 1) \rightarrow (2, 2)'$ light), $\Gamma_2$ is the $m_F$ pumping power ($(2, 1) \rightarrow (2, 2)'$ light), $\varepsilon$ is the off-resonance coupling of the $m_F$ pumping light to the $(2, 2) \rightarrow (2, 3)'$ transition and $\gamma_{mn}$ is the state independent direction averaged recoil coupling between state $m$ and $n$.
+\eqar{
+  \gamma_{mn}=&\gamma_{nm}\\
+  \sum_{m}\gamma_{mn}=&1
+}
+
+With $0.6\%$ polarization misalignment and for $\Gamma_1$ and $\Gamma_2$ normalized to the pumping rate of the $(1, 1)$ and $(2, 1)$ states.
+\eqar{
+  \Gamma^{\alpha\beta}=&\begin{pmatrix}
+    0.500\Gamma_1&0.006\Gamma_2&0.500\Gamma_2\\
+    0.333\Gamma_1&0.171\Gamma_2&0.333\Gamma_2\\
+    0.167\Gamma_1&0.002\Gamma_2&0.167\Gamma_2
+  \end{pmatrix}\\
+  \Gamma^a_m=&\Gamma_1\\
+  \Gamma^b_m=&0.179\Gamma_2\\
+  \Gamma^c_m=&\Gamma_2
+}
+If we use the $D1$ transition to do the pumping instead the matrix becomes
+\eqar{
+  \Gamma^{\alpha\beta}=&\begin{pmatrix}
+    0.500\Gamma_1&0.006\Gamma_2&0.500\Gamma_2\\
+    0.333\Gamma_1&0.004\Gamma_2&0.333\Gamma_2\\
+    0.167\Gamma_1&0.002\Gamma_2&0.167\Gamma_2
+  \end{pmatrix}\\
+  \Gamma^a_m=&\Gamma_1\\
+  \Gamma^b_m=&0.012\Gamma_2\\
+  \Gamma^c_m=&\Gamma_2
+}
 

### 2019-11-24 notes/two-photon-broadening/note.tex
[notes/two-photon-broadening] Notes about two photon broadening/loss/scattering for molecule formation

\documentclass[10pt,fleqn]{article}
% \usepackage[journal=rsc]{chemstyle}
% \usepackage{mhchem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{esint}
\usepackage{bbm}
\usepackage{amscd}
\usepackage{caption}
\usepackage{picinpar}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{tikz-3dplot}
\usepackage{indentfirst}
\usepackage{wrapfig}
\usepackage{units}
\usepackage{textcomp}
\usepackage[utf8x]{inputenc}
% \usepackage{feyn}
\usepackage{feynmp}
\usepackage{xkeyval}
\usepackage{xargs}
\usepackage{verbatim}
\usepackage{pgfplots}
\usepackage{hyperref}
\usetikzlibrary{
  arrows,
  calc,
  decorations.pathmorphing,
  decorations.pathreplacing,
  decorations.markings,
  fadings,
  positioning,
  shapes
}

\DeclareGraphicsRule{*}{mps}{*}{}
\newcommand{\ud}{\mathrm{d}}
\newcommand{\ue}{\mathrm{e}}
\newcommand{\ui}{\mathrm{i}}
\newcommand{\res}{\mathrm{Res}}
\newcommand{\Tr}{\mathrm{Tr}}
\newcommand{\dsum}{\displaystyle\sum}
\newcommand{\dprod}{\displaystyle\prod}
\newcommand{\dlim}{\displaystyle\lim}
\newcommand{\dint}{\displaystyle\int}
\newcommand{\fsno}[1]{{\!\not\!{#1}}}
\newcommand{\eqar}[1]
{
  \begin{align*}
    #1
  \end{align*}
}
\newcommand{\texp}[2]{\ensuremath{{#1}\times10^{#2}}}
\newcommand{\dexp}[2]{\ensuremath{{#1}\cdot10^{#2}}}
\newcommand{\eval}[2]{{\left.{#1}\right|_{#2}}}
\newcommand{\paren}[1]{{\left({#1}\right)}}
\newcommand{\lparen}[1]{{\left({#1}\right.}}
\newcommand{\rparen}[1]{{\left.{#1}\right)}}
\newcommand{\abs}[1]{{\left|{#1}\right|}}
\newcommand{\sqr}[1]{{\left[{#1}\right]}}
\newcommand{\crly}[1]{{\left\{{#1}\right\}}}
\newcommand{\angl}[1]{{\left\langle{#1}\right\rangle}}
\newcommand{\tpdiff}[4][{}]{{\paren{\frac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}}_{#4}}}
\newcommand{\tpsdiff}[4][{}]{{\paren{\frac{\partial^{#1}}{\partial {#3}{}^{#1}}{#2}}_{#4}}}
\newcommand{\pdiff}[3][{}]{{\frac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}}}
\newcommand{\diff}[3][{}]{{\frac{\ud^{#1} {#2}}{\ud {#3}{}^{#1}}}}
\newcommand{\psdiff}[3][{}]{{\frac{\partial^{#1}}{\partial {#3}{}^{#1}} {#2}}}
\newcommand{\sdiff}[3][{}]{{\frac{\ud^{#1}}{\ud {#3}{}^{#1}} {#2}}}
\newcommand{\tpddiff}[4][{}]{{\left(\dfrac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}\right)_{#4}}}
\newcommand{\tpsddiff}[4][{}]{{\paren{\dfrac{\partial^{#1}}{\partial {#3}{}^{#1}}{#2}}_{#4}}}
\newcommand{\pddiff}[3][{}]{{\dfrac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}}}
\newcommand{\ddiff}[3][{}]{{\dfrac{\ud^{#1} {#2}}{\ud {#3}{}^{#1}}}}
\newcommand{\psddiff}[3][{}]{{\frac{\partial^{#1}}{\partial{}^{#1} {#3}} {#2}}}
\newcommand{\sddiff}[3][{}]{{\frac{\ud^{#1}}{\ud {#3}{}^{#1}} {#2}}}
\usepackage{fancyhdr}
\usepackage{multirow}
\usepackage{fontenc}
% \usepackage{tipa}
\usepackage{ulem}
\usepackage{color}
\usepackage{cancel}
\newcommand{\hcancel}[2][black]{\setbox0=\hbox{#2}%
  \rlap{\raisebox{.45\ht0}{\textcolor{#1}{\rule{\wd0}{1pt}}}}#2}
\pagestyle{fancy}
\setlength{\headheight}{67pt}
\fancyhead{}
\fancyfoot{}
\fancyfoot[C]{\thepage}
\fancyhead[R]{}
\renewcommand{\footruleskip}{0pt}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0pt}

\newcommand\pgfmathsinandcos[3]{%
  \pgfmathsetmacro#1{sin(#3)}%
  \pgfmathsetmacro#2{cos(#3)}%
}
\newcommand\LongitudePlane[3][current plane]{%
  \pgfmathsinandcos\sinEl\cosEl{#2} % elevation
  \pgfmathsinandcos\sint\cost{#3} % azimuth
  \tikzset{#1/.estyle={cm={\cost,\sint*\sinEl,0,\cosEl,(0,0)}}}
}
\newcommand\LatitudePlane[3][current plane]{%
  \pgfmathsinandcos\sinEl\cosEl{#2} % elevation
  \pgfmathsinandcos\sint\cost{#3} % latitude
  \pgfmathsetmacro\yshift{\cosEl*\sint}
  \tikzset{#1/.estyle={cm={\cost,0,0,\cost*\sinEl,(0,\yshift)}}} %
}
\newcommand\DrawLongitudeCircle[2][1]{
  \LongitudePlane{\angEl}{#2}
  \tikzset{current plane/.prefix style={scale=#1}}
  % angle of "visibility"
  \pgfmathsetmacro\angVis{atan(sin(#2)*cos(\angEl)/sin(\angEl))} %
  \draw[current plane] (\angVis:1) arc (\angVis:\angVis+180:1);
  \draw[current plane,dashed] (\angVis-180:1) arc (\angVis-180:\angVis:1);
}
\newcommand\DrawLatitudeCircleArrow[2][1]{
  \LatitudePlane{\angEl}{#2}
  \tikzset{current plane/.prefix style={scale=#1}}
  \pgfmathsetmacro\sinVis{sin(#2)/cos(#2)*sin(\angEl)/cos(\angEl)}
  % angle of "visibility"
  \pgfmathsetmacro\angVis{asin(min(1,max(\sinVis,-1)))}
  \draw[current plane,decoration={markings, mark=at position 0.6 with {\arrow{<}}},postaction={decorate},line width=.6mm] (\angVis:1) arc (\angVis:-\angVis-180:1);
  \draw[current plane,dashed,line width=.6mm] (180-\angVis:1) arc (180-\angVis:\angVis:1);
}
\newcommand\DrawLatitudeCircle[2][1]{
  \LatitudePlane{\angEl}{#2}
  \tikzset{current plane/.prefix style={scale=#1}}
  \pgfmathsetmacro\sinVis{sin(#2)/cos(#2)*sin(\angEl)/cos(\angEl)}
  % angle of "visibility"
  \pgfmathsetmacro\angVis{asin(min(1,max(\sinVis,-1)))}
  \draw[current plane] (\angVis:1) arc (\angVis:-\angVis-180:1);
  \draw[current plane,dashed] (180-\angVis:1) arc (180-\angVis:\angVis:1);
}
\newcommand\coil[1]{
  {\rh * cos(\t * pi r)}, {\apart * (2 * #1 + \t) + \rv * sin(\t * pi r)}
}
\makeatletter
\define@key{DrawFromCenter}{style}[{->}]{
  \tikzset{DrawFromCenterPlane/.style={#1}}
}
\define@key{DrawFromCenter}{r}[1]{
  \def\@R{#1}
}
\define@key{DrawFromCenter}{center}[(0, 0)]{
  \def\@Center{#1}
}
\define@key{DrawFromCenter}{theta}[0]{
  \def\@Theta{#1}
}
\define@key{DrawFromCenter}{phi}[0]{
  \def\@Phi{#1}
}
\presetkeys{DrawFromCenter}{style, r, center, theta, phi}{}
\newcommand*\DrawFromCenter[1][]{
  \setkeys{DrawFromCenter}{#1}{
    \pgfmathsinandcos\sint\cost{\@Theta}
    \pgfmathsinandcos\sinp\cosp{\@Phi}
    \pgfmathsinandcos\sinA\cosA{\angEl}
    \pgfmathsetmacro\DX{\@R*\cost*\cosp}
    \pgfmathsetmacro\DY{\@R*(\cost*\sinp*\sinA+\sint*\cosA)}
    \draw[DrawFromCenterPlane] \@Center -- ++(\DX, \DY);
  }
}
\newcommand*\DrawFromCenterText[2][]{
  \setkeys{DrawFromCenter}{#1}{
    \pgfmathsinandcos\sint\cost{\@Theta}
    \pgfmathsinandcos\sinp\cosp{\@Phi}
    \pgfmathsinandcos\sinA\cosA{\angEl}
    \pgfmathsetmacro\DX{\@R*\cost*\cosp}
    \pgfmathsetmacro\DY{\@R*(\cost*\sinp*\sinA+\sint*\cosA)}
    \draw[DrawFromCenterPlane] \@Center -- ++(\DX, \DY) node {#2};
  }
}
\makeatother
\tikzstyle{snakearrow} = [decorate, decoration={pre length=0.2cm,
  post length=0.2cm, snake, amplitude=.4mm,
  segment length=2mm},thick, ->]
%% document-wide tikz options and styles
\tikzset{%
  >=latex, % option for nice arrows
  inner sep=0pt,%
  outer sep=2pt,%
  mark coordinate/.style={inner sep=0pt,outer sep=0pt,minimum size=3pt,
    fill=black,circle}%
}
\addtolength{\hoffset}{-1.3cm}
\addtolength{\voffset}{-2cm}
\addtolength{\textwidth}{3cm}
\addtolength{\textheight}{2.5cm}
\renewcommand{\footskip}{10pt}
\setlength{\headwidth}{\textwidth}
\setlength{\headsep}{20pt}
\setlength{\marginparwidth}{0pt}
\parindent=0pt
\title{Notes on two photon scattering of the molecular state}

% \DeclareCaptionLabelFormat{sectionnumber}{#1 \thesection.#2}
% \captionsetup{labelformat=sectionnumber}

\makeatletter
\long\def\my@drawfill#1#2;{%
  \@skipfalse
  \fill[#1,draw=none] #2;
  \@skiptrue
  \draw[#1,fill=none] #2;
}
\newif\if@skip
\newcommand{\skipit}[1]{%
  \if@skip
  \else
  #1
  \fi
}
\newcommand{\drawfill}[1][]{%
  \my@drawfill{#1}}
\makeatother

\begin{document}

\maketitle

\section{Experiment observations}
We have seen experimental evidences of an anomalous scattering / loss in the
lifetime of the ground atomic / molecular states as well as broadening in excited state
line width. We have measured power dependencies for some of the processes that is
consistent with a two photon process from the ground state (or equivalently a one
photon process from the excited state). The measurement we have done includes

\begin{enumerate}
\item Line width and decay time measurement of Raman process near $v=0$ ($1038 \mathrm{nm}$)\\
  The result is consistent with a $300 \mathrm{MHz}$ to $600 \mathrm{MHz}$
  excited state line width.\\
  We did not make a power dependency measurement.\\
  We measured carefully at multiple red detunings, which all shows similar results.\\
  We measured one point not as carefully for blue detuning
  ($18 \mathrm{GHz}$ or $10 \mathrm{GHz}$ detuned depending on the excited state $J$)
  which shows similar result as the corresponding red detuning.
\item Excited state line width for $v=0$.\\
  The line width is narrow ($\leqslant 50 \mathrm{MHz}$)
  when the tweezer is near $976 \mathrm{nm}$ but is wide ($\geqslant 500 \textrm{MHz}$)
  when the tweezer is near $1038 \mathrm{nm}$ red detuned from the $v=0$ resonance
  by a few hundred GHz.\\
  We did not make a power dependency measurement.
\item Line width of a ``mysterious'' line\\
  Tweezer $100 \mathrm{GHz}$ red detuned.\\
  Line width $\approx 100 \mathrm{MHz}$
  (determined to be narrow at the time but could have some broadening)\\
  We did not make a power dependency measurement.
\item $|F^{Cs}=3, m_{F}^{Cs}=3; F^{Na}=2, m_{F}^{Na}=2\rangle$ lifetime
  in $307366 \mathrm{GHz}$ tweezer.\\
  We measured a shorter than expected lifetime.\\
  The dependency of the loss rate to tweezer power is consistent with the prediction of
  a two photo process from the tweezer. In another word, it is consistent with
  a excited state broadened proportional to the tweezer power.
\item $|F^{Cs}=3, m_{F}^{Cs}=3; F^{Na}=2, m_{F}^{Na}=2\rangle$ lifetime
  in $306638 \mathrm{GHz}$ tweezer.\\
  We measured a shorter than expected lifetime.\\
  The power dependency may be consistent with a single photon process.
\item $v=12$ line width.\\
  Narrow ($25 \mathrm{MHz}$) for tweezer at around $307366 \mathrm{GHz}$
  (blue detuned $\approx 900\mathrm{GHz}$). (No tweezer power dependency taken.)\\
  Narrow ($20 \mathrm{MHz}$) for tweezer at $306612 \mathrm{GHz}$
  (blue detuned $\approx 130\mathrm{GHz}$). (No tweezer power dependency taken.)
  We have also indirectly observed a Raman coupling to a deeper molecular bound state
  between the tweezer and the PA probe beam.\\
  Broad ($250 \mathrm{MHz}$) for tweezer at $306344.5 \mathrm{GHz}$
  (red detuned $\approx 150\mathrm{GHz}$). Linearly depending on tweezer power.\\
\item $v=14$ line width.\\
  Broad ($200 \mathrm{MHz}$) for tweezer at around $307366 \mathrm{GHz}$
  (red detuned $\approx 1900\mathrm{GHz}$). Linearly depending on tweezer power.\\
\item Raman blue detuned from $v=12$.\\
  Tweezer at around $306614 \mathrm{GHz}$.\\
  No Rabi flopping observed.
\end{enumerate}

\section{Preliminary explanations for some of the results}
The power dependencies we measured makes it clear that we very likely
have some two photon (from ground state, one photon from excited state) process involved.
We originally suspected a two photon process to a higher excited state but Olivier also
suggested potentially a coupling to the ground state (unbound) motional continuum.
This initially seems improbable due to the small matrix element with the ground state.
However, I later learned that due to the mismatch in the excited state and ground state
electronic potential, the excited state only have about $20\%$ projection onto the ground
bound state. In another word, even though the coupling to a particular ground trapped
state is small, the total coupling to the ground state continuum is actually significant.\\

In terms of a two photon coupling (from ground state) to higher excited state,
it is harder to calculate but it is easy to believe the existence of highly lossy
state either from radiative or non-radiative (pre-dissociation) process.\\

In terms of a two photon coupling (from ground state) back to the ground electronic state,
it should be easier to calculate (see below) and can more easily explain the apparent
sensitivity to the detuning (red vs blue) of the excited state line width measurements.
We have also directly measured a coupling to the ground bound state when we switched
to blue detuning.

\section{Caveat in the interpretation}

There are two kinds of measurements above
\begin{enumerate}
\item Ground state scattering/loss rate\\
  This includes Raman decay time / line width and atomic state 2-body lifetime.
\item Excited state line width.
\end{enumerate}

The first kind of measurement mainly involve a single laser frequency
or two that are not very far apart ($\approx 300 \mathrm{MHz}$).
This single frequency is also detuned from any known excited state frequency
by tens to hundreds of GHz (up to around $1 \mathrm{THz}$).
This is more directly related to the loss we care about.
(FWIW, the loss during Raman process is one of this type of measurements).\\

The second kind of measurement usually involve two laser frequencies.
\footnote{We've done measurements using the tweezer as PA without additional frequencies but
  those data are generally assumed to be power broadened since we cannot turn down the
  tweezer power too much during the measurement. Therefore, the tweezer PA measurement
  don't usually offer us much information on the excited state line width.}
One of the two frequencies is detuned by few GHz to a THz and the other one is scanned
around the resonance by up to a few GHz.\\

Since we usually express the difference in the ground state scattering rate in terms of
a difference in the excited state line width (lifetime), it is tempting to compare this
line width to the excited state line width direction measured at the same tweezer
frequency. This is the main reason why we were measuring Raman transition using
tweezer around $306614 \mathrm{GHz}$ after observing narrow line width for the nearby
excited state.\\

However, the two are not directly comparable. When we use the directly measured
excited state line width ($\Gamma_e$) to calculate the ground state scattering rate ($\gamma$)
for a certain large detuning ($\Delta$) as,

\[ \gamma=\Gamma\frac{\Omega_1\Omega_2}{\Delta^2} \]

(where $\Omega_1$ and $\Omega_2$ are the single photon Rabi frequencies), we have
assumed that the loss of the excited state
(i.e. the continuum the excited state is coupled to in order to decay)
does not depend strongly on the final energy of the two photon process.
Depending on the structure of the continuum we couple to via the two photon process,
this may be a bad assumption.\\

This has subtly different implications for two photon couple up or two photon couple down.

\subsection{Two photon coupling up}
\begin{wrapfigure}{R}{9cm}
  \begin{center}
    \begin{tikzpicture}
      \draw[->, line width=2] (0, -0.5) -- (0, 5.5);
      \draw[line width=1] (0.5, 0) -- (2, 0) node[right] {$|g\rangle$};
      \draw[line width=1] (0.5, 2.3) -- (2, 2.3) node[right] {$|e\rangle$};
      \fill[opacity=0.2] (0.5, 3.8) rectangle (2, 5.4);
      \drawfill[domain=-0.8:0.8,smooth,variable=\y,red,line width=1,
      fill opacity=0.2]
      plot ({2.8 + 0.8 * exp(-100*pow(\y-0.5, 2)) +
        0.5 * exp(-40*pow(\y-0.2, 2)) +
        0.7 * exp(-70*pow(\y+0.1, 2)) +
        0.9 * exp(-50*pow(\y+0.6, 2))},{\y + 4.6})
      \skipit{--} (2.7, 4.6 + 0.8) \skipit{--} (2.7, 4.6 - 0.8) \skipit{-- cycle};
      \node[below] at (3.4, 4.6 - 0.9) {\small{Loss rate}};

      \draw[->, line width=1,blue] (1.25, 0) -- node[right] {$\Omega_1$} (1.25, 2);
      \draw[->, line width=1,green!80!black] (1.25, 2) -- node[right] {$\Omega_2$} (1.25, 4.0);
      \draw[dashed] (0.5, 4.0) -- (3.72, 4.0);
      \node at (3, 0.2) {(A)};
      \begin{scope}[shift={(4, 0)}]
        \draw[line width=1] (0.5, 0) -- (2, 0) node[right] {$|g\rangle$};
        \draw[line width=1] (0.5, 2.3) -- (2, 2.3) node[right] {$|e\rangle$};
        \fill[opacity=0.2] (0.5, 3.8) rectangle (2, 5.4);
        \drawfill[domain=-0.8:0.8,smooth,variable=\y,red,line width=1,
        fill opacity=0.2]
        plot ({2.8 + 0.8 * exp(-100*pow(\y-0.5, 2)) +
          0.5 * exp(-40*pow(\y-0.2, 2)) +
          0.7 * exp(-70*pow(\y+0.1, 2)) +
          0.9 * exp(-50*pow(\y+0.6, 2))},{\y + 4.6})
        \skipit{--} (2.7, 4.6 + 0.8) \skipit{--} (2.7, 4.6 - 0.8) \skipit{-- cycle};
        \node[below] at (3.4, 4.6 - 0.9) {\small{Loss rate}};

        \draw[->, line width=1,green!80!black] (1.25, 2.3) -- node[right] {$\Omega_2$} (1.25, 4.3);
        \draw[dashed] (0.5, 4.3) -- (2.85, 4.3);
        \node at (3, 0.2) {(B)};
      \end{scope}
    \end{tikzpicture}
  \end{center}
  \caption{Two photon coupling to a (lossy) continuum. (A) Off resonance measurement,
    (B) On resonance measurement.}
  \label{two-up-1}
\end{wrapfigure}

See figure \ref{two-up-1}A, the loss mechanism we suspect is a two photon coupling
to a lossy continuum with a frequency dependent loss rate
\footnote{The loss rate depends on the laser power, i.e. $\Omega_1$ and $\Omega_2$. Here
  ``loss rate'' essentially mean the loss rate per power squared, which is proportional to
  the square of the coupling from $|e\rangle$ and the density of state.
  Also note here since the second beam is coupling to a continuum rather than a single state
  in the generic case, $\Omega_2$ is not a single number but a function of frequency
  depending of the selection of normalization of the continuum.}.
Generically, the loss rate is not flat which may give us a frequency dependent
two photon loss rate. One way to see the difference between a detuned measurement
and a on-resonance (with the singe photon excited state $|e\rangle$)
measurement of the two photon decay rate is that the two process does not have the same
two photon frequencies. For the on-resonance measurement using the same laser that couples
$|e\rangle$ to the higher excited state (figure \ref{two-up-1}B),
the loss rate experienced by the two photon resonance can be different.
Since the loss rate can have an arbitrary dependency on frequency, one shouldn't expect
the difference in the loss rate to be included in the detuning factor when calculating
the scattering in the off-resonance case.\\

\begin{wrapfigure}{R}{5cm}
  \begin{center}
    \begin{tikzpicture}
      \draw[->, line width=2] (0, -0.5) -- (0, 5.5);

      \draw[dashed] (-0.05, 0) node[left] {$0$} -- (1.5, 0);
      \draw[dashed] (-0.05, 2.3) node[left] {$\omega_0$} -- (1.5, 2.3);
      \draw[dashed] (-0.05, 4.3) node[left] {$\omega_0 + \omega$} -- (1.5, 4.3);

      \draw[line width=1] (1.5, 0) -- (2, 0) node[right] {$|g\rangle$};
      \draw[line width=1] (1.5, 2.3) -- (2, 2.3) node[right] {$|e_1\rangle$};
      \draw[line width=1] (1.5, 4.3) -- (2, 4.3) node[right] {$|e_2\rangle$};
      \draw[line width=1] (0.2, 0) -- node[below] {$|g'\rangle$} (0.7, 0);
      \draw[snakearrow, line width=1, red] (1.75, 4.3) -- node[below left=0.2cm]
      {\large $\Gamma$} (0.45, 0);

      \draw[->, line width=1,blue] (1.75, 0) -- node[right] {$\omega$, $\Omega_1$} (1.75, 2);
      \draw[->, line width=1,green!80!black] (1.75, 2) --
      node[right] {$\omega$, $\Omega_2$} (1.75, 4);

      \draw[dashed] (0.5, 4) -- (2, 4);
      \draw[<->] (1, 4.3) -- (1, 4);
      \node[below] at (0.8, 4) {\footnotesize $\Delta\!\equiv\!\omega_0\!-\!\omega$};

      \draw[dashed] (1.3, 2) -- (2, 2);
      \draw[<->] (1.32, 2.3) -- (1.32, 2);
      \node[right] at (1.33, 2.13) {\footnotesize $\Delta$};
    \end{tikzpicture}
  \end{center}
  \caption{Four level model.}
  \label{two-up-2}
\end{wrapfigure}

As a more concrete example, we'll consider a single two photon excited state with
a stable single photon excited state.\\

See figure \ref{two-up-2}. The ground state $|g\rangle$ is coupled to $|e_1\rangle$,
$|e_1\rangle$ is coupled to $|e_2\rangle$ and $|e_2\rangle$ can decay to another ground
state $|g'\rangle$ with decay rate $\Gamma$ and a $100\%$ branching ratio.
The energy of the two ground states $|g\rangle$ and $|g'\rangle$ are both $0$,
the energy of $|e_1\rangle$ is $\omega_0$ and the energy of $|e_2\rangle$ is $\omega_0+\omega$.\\

The states are coupled by a single external laser with frequency $\omega$.
The laser drives the $|g\rangle\leftrightarrow|e_1\rangle$ transition
with a Rabi frequency $\Omega_1$ and the $|g\rangle\leftrightarrow|e_1\rangle$ transition
with a Rabi frequency $\Omega_2$. The single photon detuning on the $|e_1\rangle$ and
the two photon detuning on $|e_2\rangle$ are both $-\Delta\equiv\omega-\omega_0$.\\

For simplicity we have ignored the decay of the $|e_1\rangle$ state
and we assume the laser frequency is the same as the $|e_1\rangle$ $|e_2\rangle$
energy splitting. We will also assume that $\Omega_{1,2}\ll\Delta\ll\omega<\omega_0$
as well as $\Gamma\ll\Delta$. Some of the conditions may not be true in the real experiment
but this example should be enough to demonstrate the correct way to calculate
the scattering rate.\\

We'll calculate the scattering rate of the state $|g\rangle$ using a few different methods.
\footnote{All of the calculation below ignores the frequency dependency of the $|g'\rangle$
  continuum $|e_2\rangle$ decays to. All the scattering rate should be scaled by
  a factor of $\paren{\dfrac{2\omega}{\omega+\omega_0}}^3$.}

\subsubsection{Off resonance Raman scattering}

We can treat this as an off-resonance Raman scattering process.
The Raman Rabi rate for the $|g\rangle\rightarrow|e_1\rangle\rightarrow|e_2\rangle$ is

\[\Omega_R=\frac{\Omega_1\Omega_2}{2\Delta}\]

since $\Omega_R\ll\Omega_1\ll\Delta$, the off resonant scattering rate is,

\eqar{
  \gamma\approx&\frac{\Gamma}{4}\frac{\Omega_R^2}{\Delta^2}\\
  =&\frac{\Gamma}{16}\frac{\Omega_1^2\Omega_2^2}{\Delta^4}
}

\subsubsection{Single photon off resonance scattering from coupled excited state}
\begin{wrapfigure}{R}{10cm}
  \begin{center}
    \begin{tikzpicture}
      \draw[->, line width=2] (0, -0.5) -- (0, 3.5);

      \draw[dashed] (-0.05, 0) node[left] {$0$} -- (1.5, 0);
      \draw[dashed] (-0.05, 2.15) node[left] {$\omega_0 - \Omega_2/2$} -- (1.5, 2.15);
      \draw[dashed] (-0.05, 2.45) node[left] {$\omega_0 + \Omega_2/2$} -- (1.5, 2.45);

      \draw[line width=1] (1.5, 0) -- (2, 0) node[right] {$|g\rangle$};
      \draw[line width=1] (1.5, 2.15) -- (2, 2.15) node[right] {$|-\rangle$};
      \draw[line width=1] (1.5, 2.45) -- (2, 2.45) node[right] {$|+\rangle$};
      \draw[line width=1] (0.2, 0) -- node[below] {$|g'\rangle$} (0.7, 0);
      \draw[snakearrow, line width=1, red] (1.75, 2.15) -- node[below right]
      {\large $\Gamma/2$} (0.5, 0);
      \draw[snakearrow, line width=1, red] (1.75, 2.45) -- node[left=0.1cm]
      {\large $\Gamma/2$} (0.3, 0);

      \node[above] at (1, 2.6) {(A)};

      \begin{scope}[shift={(3, 0)}]
        % \draw[dashed] (-0.05, 0) -- (1.5, 0);
        % \draw[dashed] (-0.05, 2.15) -- (1.5, 2.15);
        % \draw[dashed] (-0.05, 2.45) -- (1.5, 2.45);

        \draw[line width=1] (1.5, 0) -- (2, 0) node[right] {$|g\rangle$};
        \draw[line width=1] (1.5, 2.15) -- (2, 2.15) node[right] {$|-\rangle$};
        \draw[line width=1] (1.5, 2.45) -- (2, 2.45) node[right] {$|+\rangle$};
        \draw[line width=1] (0.2, 0) -- node[below] {$|g'\rangle$} (0.7, 0);
        \draw[<->, line width=1, blue] (2, 0) -- node[right]
        {$\frac{D_1}{\sqrt2}$} (2, 2.15);
        \draw[<->, line width=1, blue] (1.9, 0) -- node[above left]
        {$\frac{D_1}{\sqrt2}$} (1.9, 2.45);
        \draw[<->, line width=1, red] (0.2, 0) -- node[left=0.1]
        {$\frac{D'}{\sqrt2}$} (1.5, 2.45);
        \draw[<->, line width=1, red] (0.43, 0) -- (1.6, 2.15);
        \node[red, below right] at (0.9, 1.075) {$\frac{-D'}{\sqrt2}$};

        \node[above] at (1, 2.6) {(B)};
      \end{scope}
    \end{tikzpicture}
  \end{center}
  \caption{Coupled excited states. (B) Dipole moments between new states.}
  \label{two-up-coupled}
\end{wrapfigure}

More directly related to the excited state linewidth measurement, we can first couple the
two excited states together with $\Omega_2$.\\

See figure \ref{two-up-coupled}A. The excited states becomes

\[|\pm\rangle=\frac{1}{\sqrt2}\paren{|e_1\rangle\pm|e_2\rangle}\]

with energy $\omega_0\pm\Omega_2/2$ and each with a lifetime of $\dfrac\Gamma2$.
The Rabi frequency between the two excited states and the ground state is
$\Omega_\pm=\dfrac{\Omega_1}{\sqrt2}$.\\
The scattering from the two excited states are
\eqar{
  \gamma_\pm\approx&\frac{\Gamma}{8}\frac{\Omega_\pm^2}{\paren{\Delta\mp\Omega_2/2}^2}\\
  \approx&\frac{\Gamma}{16}\frac{\Omega_1^2}{\Delta^2}
}
and the total scattering rate
\eqar{
  \gamma=&\gamma_-+\gamma_+\\
  \approx&\frac{\Gamma}{8}\frac{\Omega_1^2}{\Delta^2}
}
which clearly doesn't agree with the result we calculated above.

\subsubsection{Single photon off resonance scattering from coupled excited state
  (the correct way)}

The apparent disagreement between the two result above suggests that one of them must be wrong
and it turns out that the second one is incorrect due to the wrong assumption it made.\\

In this case, the issue manifests itself as an incorrect off resonant scattering rate
from the excited state. There is not problem in coupling the excited state first to get
$|\pm\rangle$ but the decay process from the two states are not independent which give rise
to a different scattering rate away from resonance. (when $\Delta\gg\Omega_2$).
Instead, the scattering from the two excited states have to be treated as interfering
Raman processes and their amplitudes needs to be added, which will lead to cancellation
as we'll see soon, before squared to get the scattering rate.\\

\subsection{Two photon coupling down}

% Ground state coupling calculation

\end{document}

### 2019-11-24 notes/two-photon-broadening/note.tex
[notes/two-photon-broadening] Finish two photon coupling up

@@
 \subsubsection{Single photon off resonance scattering from coupled excited state}
-\begin{wrapfigure}{R}{10cm}
+\begin{wrapfigure}{R}{7.3cm}
   \begin{center}
@@
 
-      \begin{scope}[shift={(3, 0)}]
+      \begin{scope}[shift={(2.6, 0)}]
         % \draw[dashed] (-0.05, 0) -- (1.5, 0);
@@
 
+The correct way to calculate this requires using the dipole moment between the states
+\footnote{And the formula also correctly takes into account the density of state of
+  the scattered photon and gives the correct
+  $\paren{\dfrac{2\omega}{\omega+\omega_0}}^3$ factor}.
+For the purpose of this note, however, it is enough to only calculate the interference term
+and scales our previous result correspondingly.\\
+
+Let the $D_1=\langle g|\hat d|e_1\rangle$ and $D_2=\langle g'|\hat d|e_2\rangle$ be
+the dipole moment coupling $e_1$ and $e_2$ to the corresponding ground states $g$ and $g'$.
+The dipole moments between the new states are shown in figure \ref{two-up-coupled}B
+\footnote{The sign of the dipole moment depends on the selection of the phase for
+  $|\pm\rangle$ but the relative sign of the product does not depend on the phase selection}.\\
+
+The wrong way to calculate the scattering gives a factor of
+\eqar{
+  &\paren{\frac{D'}{\sqrt2}\frac{D_1}{\sqrt2}\frac{1}{\Delta+\Omega_2/2}}^2+\paren{\frac{-D'}{\sqrt2}\frac{D_1}{\sqrt2}\frac{1}{\Delta-\Omega_2/2}}^2\\
+  \approx&2\paren{\frac{D'}{\sqrt2}\frac{D_1}{\sqrt2}\frac{1}{\Delta}}^2\\
+  =&\frac{D'^2D_1^2}{2\Delta^2}
+}
+The correct way gives,
+\eqar{
+  &\paren{\frac{D'}{\sqrt2}\frac{D_1}{\sqrt2}\frac{1}{\Delta+\Omega_2/2}+\frac{-D'}{\sqrt2}\frac{D_1}{\sqrt2}\frac{1}{\Delta-\Omega_2/2}}^2\\
+  =&\frac{D'^2D_1^2}{4}\paren{\frac{1}{\Delta+\Omega_2/2}-\frac{1}{\Delta-\Omega_2/2}}^2\\
+  =&\frac{D'^2D_1^2}{4}\paren{\frac{\Delta-\Omega_2/2-\Delta-\Omega_2/2}{\Delta^2-\Omega_2^2/4}}^2\\
+  \approx&\frac{D'^2D_1^2\Omega_2^2}{4\Delta^4}
+}
+which means that we should scale the incorrect result above by
+\[\frac{D'^2D_1^2\Omega_2^2}{4\Delta^4}\frac{2\Delta^2}{D'^2D_1^2}=\frac{\Omega_2^2}{2\Delta^2}\]
+and the correct answer is
+\eqar{
+  \gamma=&\frac{\Gamma}{8}\frac{\Omega_1^2}{\Delta^2}\frac{\Omega_2^2}{2\Delta^2}\\
+  =&\frac{\Gamma}{16}\frac{\Omega_1^2\Omega_2^2}{\Delta^4}
+}
+which is exactly what we got above.
+
 \subsection{Two photon coupling down}

### 2019-11-24 notes/two-photon-broadening/note.tex
[notes/two-photon-broadening] tweak format, add v=0 off resonance PA rate measurement, add summary

@@
   which shows similar result as the corresponding red detuning.
+\item Off resonance PA rate (lifetime) in $|F^{\mathrm{Cs}}\!=\!4, m_{F}^{\mathrm{Cs}}\!=\!4; F^{\mathrm{Na}}\!=\!2, m_{F}^{\mathrm{Na}}\!=\!2\rangle$
+  near $v=0$ PA line.\\
+  The result is consistent with the Raman line width and decay time measurements above
+  which gives a wide excited state line width.
 \item Excited state line width for $v=0$.\\
@@
   We did not make a power dependency measurement.
-\item $|F^{Cs}=3, m_{F}^{Cs}=3; F^{Na}=2, m_{F}^{Na}=2\rangle$ lifetime
+\item $|F^{\mathrm{Cs}}\!=\!3, m_{F}^{\mathrm{Cs}}\!=\!3; F^{\mathrm{Na}}\!=\!2, m_{F}^{\mathrm{Na}}\!=\!2\rangle$ lifetime
   in $307366 \mathrm{GHz}$ tweezer.\\
@@
   a excited state broadened proportional to the tweezer power.
-\item $|F^{Cs}=3, m_{F}^{Cs}=3; F^{Na}=2, m_{F}^{Na}=2\rangle$ lifetime
+\item $|F^{\mathrm{Cs}}\!=\!3, m_{F}^{\mathrm{Cs}}\!=\!3; F^{\mathrm{Na}}\!=\!2, m_{F}^{\mathrm{Na}}\!=\!2\rangle$ lifetime
   in $306638 \mathrm{GHz}$ tweezer.\\
@@
       \begin{scope}[shift={(2.6, 0)}]
-        % \draw[dashed] (-0.05, 0) -- (1.5, 0);
-        % \draw[dashed] (-0.05, 2.15) -- (1.5, 2.15);
-        % \draw[dashed] (-0.05, 2.45) -- (1.5, 2.45);
-
         \draw[line width=1] (1.5, 0) -- (2, 0) node[right] {$|g\rangle$};
@@
 
+\subsubsection{Summary for two photon coupling down}
+
+In the particular case (two photon excite to a single state) we calculated,
+the naive calculation using coupled excited state (i.e. direct result from PA measurement)
+gives the wrong result because of the interference from different scattering channels.
+More generally, to avoid this problem one need to realize,
+\begin{enumerate}
+\item The scattering is never a one photon process, one need to calculate the rate
+  after considering all photon involved.
+\item It is OK to couple some intermediate states first and use a dressed state picture
+  to eliminate the number of photon/coupling/intermediate states involved. However,
+  the coupled result may not be a single state and the scattering from the resulting
+  states may not follow a simple $\Delta^{-2}$ rule.
+\end{enumerate}
+
 \subsection{Two photon coupling down}

### 2019-11-24 notes/two-photon-broadening/note.tex
[notes/two-photon-broadening] add \mbox to avoid line break in the middle of figure reference

@@
 
-See figure \ref{two-up-1}A, the loss mechanism we suspect is a two photon coupling
+See \mbox{figure \ref{two-up-1}A}, the loss mechanism we suspect is a two photon coupling
 to a lossy continuum with a frequency dependent loss rate
@@
 two photon frequencies. For the on-resonance measurement using the same laser that couples
-$|e\rangle$ to the higher excited state (figure \ref{two-up-1}B),
+$|e\rangle$ to the higher excited state (\mbox{figure \ref{two-up-1}B}),
 the loss rate experienced by the two photon resonance can be different.
@@
 
-See figure \ref{two-up-2}. The ground state $|g\rangle$ is coupled to $|e_1\rangle$,
+See \mbox{figure \ref{two-up-2}}. The ground state $|g\rangle$ is coupled to $|e_1\rangle$,
 $|e_1\rangle$ is coupled to $|e_2\rangle$ and $|e_2\rangle$ can decay to another ground
@@
 
-See figure \ref{two-up-coupled}A. The excited states becomes
+See \mbox{figure \ref{two-up-coupled}A}. The excited states becomes
 
@@
 the dipole moment coupling $e_1$ and $e_2$ to the corresponding ground states $g$ and $g'$.
-The dipole moments between the new states are shown in figure \ref{two-up-coupled}B
+The dipole moments between the new states are shown in \mbox{figure \ref{two-up-coupled}B
 \footnote{The sign of the dipole moment depends on the selection of the phase for
-  $|\pm\rangle$ but the relative sign of the product does not depend on the phase selection}.\\
+  $|\pm\rangle$ but the relative sign of the product does not depend on the phase selection}.}\\
 

### 2019-11-24 notes/two-photon-broadening/note.tex
[notes/two-photon-broadening] typo in summary title. Raggedright. Figure hight
[notes/two-photon-broadening] coupling down

@@
 \begin{document}
+\maketitle
 
-\maketitle
+\raggedright
 
@@
 \subsubsection{Single photon off resonance scattering from coupled excited state}
-\begin{wrapfigure}{R}{7.3cm}
+\begin{wrapfigure}[10]{R}{7cm}
   \begin{center}
@@
 
-More directly related to the excited state linewidth measurement, we can first couple the
+More directly related to the excited state line width measurement, we can first couple the
 two excited states together with $\Omega_2$.\\
@@
 
-\subsubsection{Summary for two photon coupling down}
+\subsubsection{Summary for two photon coupling up}
 
@@
 \subsection{Two photon coupling down}
+\begin{wrapfigure}{R}{8.4cm}
+  \begin{center}
+    \begin{tikzpicture}
+      \draw[->, line width=2] (0, -0.5) -- (0, 4);
+      \draw[line width=1] (1, 0) node[left] {$|0\rangle$} -- (2, 0);
+      \draw (1, 0.1) -- (2, 0.1);
+      \draw (1, 0.2) -- (2, 0.2);
+      \node[rotate=90] at (1.5, 0.5) {$\cdots$};
+      \node[left] at (1, 0.5) {$|n\rangle$};
+      \draw (1, 0.8) -- (2, 0.8);
+      \draw (1, 0.9) -- (2, 0.9);
+      \fill[opacity=0.2] (1, 1) rectangle (2, 1.5);
+
+      \draw[line width=1] (1, 3.5) node[left] {$|e\rangle$} -- (2, 3.5);
+
+      \draw[dashed] (1, 3) -- (2, 3);
+      \draw[->, line width=1,green!80!black] (1.5, 3) -- node[right] {$\Omega_2$} (1.7, 1.2);
+      \draw[->, line width=1,blue] (1.2, 0) -- node[above left] {$\Omega_1$} (1.5, 3);
+
+      \node[above] at (1.5, 3.65) {(A)};
+      \begin{scope}[shift={(1.4, 0)}]
+        \draw[line width=1] (1, 0) -- (2, 0);
+        \draw (1, 0.1) -- (2, 0.1);
+        \draw (1, 0.2) -- (2, 0.2);
+        \node[rotate=90] at (1.5, 0.5) {$\cdots$};
+        \draw (1, 0.8) -- (2, 0.8);
+        \draw (1, 0.9) -- (2, 0.9);
+        \fill[opacity=0.2] (1, 1) rectangle (2, 1.5);
+
+        \draw[line width=1] (1, 3.5) -- (2, 3.5);
+
+        \draw[dashed] (1, 3) -- (2, 3);
+        \draw[<->, line width=1,blue] (1.65, 0) -- node[above left] {$\Omega_1$} (1.65, 3);
+
+        \node[above] at (1.5, 3.65) {(B)};
+      \end{scope}
+      \begin{scope}[shift={(2.8, 0)}]
+        \draw[line width=1] (1, -0.5) node[left] {$|\!-\!1\rangle$} -- (2, -0.5);
+        \draw[line width=1] (1, 0) -- (2, 0);
+        \draw (1, 0.1) -- (2, 0.1);
+        \draw (1, 0.2) -- (2, 0.2);
+        \node[rotate=90] at (1.5, 0.5) {$\cdots$};
+        \draw (1, 0.8) -- (2, 0.8);
+        \draw (1, 0.9) -- (2, 0.9);
+        \fill[opacity=0.2] (1, 1) rectangle (2, 1.5);
+
+        \draw[line width=1] (1, 3.5) -- (2, 3.5);
+
+        \draw[dashed] (1, 3) -- (2, 3);
+        \draw[<->, line width=1,green!80!black] (1.51, 3) -- (1.7, -0.5);
+        \node[above right,green!80!black] at (1.6, 1.5) {$\Omega_2$};
+        \draw[<->, line width=1,blue] (1.2, 0) -- node[above left] {$\Omega_1$} (1.49, 3);
+
+        \node[above] at (1.5, 3.65) {(C)};
+      \end{scope}
+      \begin{scope}[shift={(4.2, 0)}]
+        \draw[line width=1] (1, 0) -- (2, 0);
+        \draw (1, 0.1) -- (2, 0.1);
+        \draw (1, 0.2) -- (2, 0.2);
+        \node[rotate=90] at (1.5, 0.5) {$\cdots$};
+        \draw (1, 0.8) -- (2, 0.8);
+        \draw (1, 0.9) -- (2, 0.9);
+        \fill[opacity=0.2] (1, 1) rectangle (2, 1.5);
+
+        \draw[line width=1] (1, 3.5) -- (2, 3.5);
+
+        \draw[dashed] (1, 3) -- (2, 3);
+        \draw[->, dashed, line width=0.3,blue] (1.5, 3) -- node[right] {$\Omega_1'$} (1.7, 1.2);
+        \draw[->, line width=1,blue] (1.2, 0) -- node[above left] {$\Omega_1$} (1.5, 3);
+
+        \node[above] at (1.5, 3.65) {(D)};
+      \end{scope}
+      \begin{scope}[shift={(5.6, 0)}]
+        \fill[red,opacity=0.2] (1.8, -0.5) rectangle (2.5, 0.5);
+        \draw[line width=1] (1, 0) -- (1.7, 0);
+        \draw (1, 0.1) -- (1.7, 0.1);
+        \draw (1, 0.2) -- (1.7, 0.2);
+        \node[rotate=90] at (1.35, 0.5) {$\cdots$};
+        \draw (1, 0.8) -- (1.7, 0.8);
+        \draw (1, 0.9) -- (1.7, 0.9);
+        \fill[opacity=0.2] (1, 1) rectangle (1.7, 1.5);
+
+        \draw[line width=1] (1, 3.5) -- (2.5, 3.5);
+
+        \draw[dashed] (1, 3) -- (2.5, 3);
+        \draw[<->, line width=1,blue] (1.4, 0) -- node[above left] {$\Omega_1$} (1.75, 3);
+        \draw[<->, line width=1,blue] (2.1, 0) -- node[above right] {$\Omega_1'$} (1.75, 3);
+
+        \node[above] at (1.75, 3.65) {(E)};
+      \end{scope}
+    \end{tikzpicture}
+  \end{center}
+  \caption{Coupling to ground state motional continuum. (A) Raman into motional continuum.
+    (B) Single ground HF state, single laser frequency. (C) Single ground HF state,
+    two frequencies for molecular Raman. (D) Unexpected sideband in laser.
+    (E) Zero energy continuum.}
+  \label{two-down}
+\end{wrapfigure}
+
+The potential second photon coupling down pathway is very similar.
+See \mbox{figure \ref{two-down}A}. The loss is caused by the ground state (atomic or molecular)
+coupling to the ground motional continuum.\\
+
+We can also directly apply the two points from the summary above.
+\begin{enumerate}
+\item In order to calculate ground state loss, we should consider the Raman process,
+  which will likely have very different motional energies compared to the motional energy
+  coupling down from the excited state.
+\item The excited state is coupled to an atomic motional continuum and the resulting loss
+  will have a very different profile from then $\Delta^{-2}$ scaling. Even if we
+  see a broadening of the excited state due to this coupling, it does not mean much
+  for the corresponding ground state loss rate.
+\end{enumerate}
+
+The two kinds of ground state scattering measurements we have are atomic state PA rate
+and molecular state scattering (using Raman transition).
+Assuming the laser is clean and no other states are involved,
+\begin{enumerate}
+\item For atomic scattering rate (\mbox{figure \ref{two-down}B}), there is only
+  one frequency so the Raman process can only come back down to the same energy as
+  the initial state, which is not in an continuum.
+\item For molecular scattering rate during transfer (\mbox{figure \ref{two-down}C}),
+  similarly, the only energy the molecular state could couple to is the initial energy
+  or a deeper bound state (2x the binding energy). Neither of these is a continuum either.\\
+  The atomic state can indeed be coupled to the continuum but it should be much weaker than
+  the molecular state (the up leg is much smaller) and we have not measured a decrease in
+  atomic 2-body lifetime when the Raman beam is turned on.
+\end{enumerate}
+Therefore, in order to generate any loss from this process for the ground state,
+we need to have either,
+\begin{enumerate}
+\item Additional frequencies in the laser (\mbox{figure \ref{two-down}D}) which
+  can couple the state of interest to the motional continuum. Or,
+\item Continuum that has zero energy (\mbox{figure \ref{two-down}E}) that the Raman beam
+  can couple to.\\
+  Candidate for this continuum includes the center of mass (COM) motional states and
+  the motional continuum from other HF states.\\
+  The COM motional continuum actually also starts at a positive energy so it doesn't seems
+  possible. The continuum from other HF states is much more promising especially since
+  we know that the $|F^{\mathrm{Cs}}\!=\!3, m_{F}^{\mathrm{Cs}}\!=\!3; F^{\mathrm{Na}}\!=\!2, m_{F}^{\mathrm{Na}}\!=\!2\rangle$ state has a strong coupling to the molecular excited states.
+  However, this cannot be applied to the $|F^{\mathrm{Cs}}\!=\!3, m_{F}^{\mathrm{Cs}}\!=\!3; F^{\mathrm{Na}}\!=\!2, m_{F}^{\mathrm{Na}}\!=\!2\rangle$ state lifetime since it is already
+  the HF state with the lowest energy.
+\end{enumerate}
+
+\subsection{Summary for interpreting and connecting excited state and ground state results}
+
+From the discussion above, we see that no matter what kind of couple we have,
+the excited state line width may not be directly related to the life time in the tweezer
+of the corresponding frequency. For up coupling, the result is more closely related
+to the lifetime for tweezer of the average frequency, whereas for down coupling,
+the lifetime may not be related to the excited state line width at all.
 

### 2019-11-25 notes/two-photon-broadening/note.tex
[notes/two-photon-broadening] Calculating the coupling to the ground state continuum using harmonic oscillator states as basis

@@
 
-% Ground state coupling calculation
+\section{Loss due to coupling to ground state motional continuum}
+
+Calculating the loss rate for coupling to the continuum requires knowledge of the
+continuum wavefunction. This is hard to do accurately for states with significant
+energy since the fine energy spacing will blow up the number of states involved.
+Fortunately, since we know the interaction potential is short range and much deeper
+than any of the motional energy scales, we can make certain approximations in order
+to get the coupling to the continuum based on the known coupling to the trapped atomic
+states in the tweezer.\\
+
+First of all, we are going to ignore the COM motion and only consider the relative motion.
+This shouldn't affect our answer for coupling to the relative motional continuum too much
+but it does prevent us from calculating the coupling to the COM motional continuum.
+Since the COM motional continuum only exists at roughly the same energy levels as the
+relative motion, this should not be an issue (the coupling to the relative continuum
+at the same energy should always be stronger).\\
+
+We'll also only consider $L=0$ motional states since,
+\begin{enumerate}
+\item The selection rule means that we can only couple to at most a few low $L$ states.
+\item The coupling to $L\neq0$ states are weaker due to smaller wave function amplitude
+  for short distance.
+\end{enumerate}
+
+We can then consider a small enough volume around the $r=0$ of the relative coordinate.
+The coupling to the excited molecular state is entirely determined by the wavefunction
+inside. The wavefunction inside is determined by the boundary condition,
+which for $L=0$\footnote{Or for any particular $L$ and $m_L$} is a single number,
+and the energy of the state. Since the energy of the motional state is much smaller than
+the depth of the interaction potential, we can expect the shape of the wavefunction
+to be almost independent of the energy and the amplitude of it to be proportional to
+the boundary condition. In the weak interaction limit\footnote{This should be true for most
+  motional state with the exception of $|F^{\mathrm{Cs}}\!=\!3, m_{F}^{\mathrm{Cs}}\!=\!3; F^{\mathrm{Na}}\!=\!2, m_{F}^{\mathrm{Na}}\!=\!2\rangle$ state.},
+we can assume that the boundary condition is given by the value of
+the non-interacting wavefunctions at $r=0$.\\
+
+In the ground motional state, the trapping frequencies are $\omega_i$ where $i=1,2,3$
+along the three axis. The value of the wavefunction at $r=0$ is,
+
+\eqar{
+  \psi_0=&\prod_{i=1}^{3}\paren{\frac{m\omega_i}{\pi\hbar}}^{1/4}\\
+  =&\paren{\frac{m^3\omega_1\omega_2\omega_3}{\pi^3\hbar^3}}^{1/4}
+}
+
+Assume the Raman Rabi frequency between the initial state and the ground motional state
+is $\Omega_R$, the Raman Rabi frequency for another motional state would be,
+
+\eqar{
+  \Omega_R'=&\Omega_R\psi'(r=0)\paren{\frac{\pi^3\hbar^3}{m^3\omega_1\omega_2\omega_3}}^{1/4}
+}
+
+In order to calculate the coupling to the continuum, we'll start with a discrete set of states
+and and then take the energy gap to $0$ to calculate the result for true continuum.
+We'll use two different sets of states to calculate for cross-checking\footnote{
+  Note that both calculations will be done under the same assumptions given above so their
+  agreement does not necessarily mean that the assumption is valid.}.
+
+\subsection{Harmonic oscillator states}
+
+We can treat the continuum as the limit of a infinitely loose 3D harmonic oscillator state.
+Assuming a trapping frequency $\omega$, we are interested in the value of the wavefunction
+at $r=0$ for large $n$ where $n$ is the radial quantum number (energy gap of $2\omega$).
+
+I'll calculate this value using two methods as well.
+
+\subsubsection{Using radial wavefunction $u=r\psi_r$}
+
+After doing the subsitution of $u=r\psi_r(r)$, the Schr\"odinger equation for $u$ becomes
+that of a 1D harmonic oscillator with a hard wall at $r=0$. The eigenstates are the odd
+harmonic oscillator states for the normal 1D potential and $\psi(r=0)$ is given by $\left.\dfrac{1}{\sqrt{4\pi}}\ddiff{u}{r}\right|_{r=0}$.\\
+
+The normalized wavefunction for $u$ is,
+
+\eqar{
+  u_n=&\frac{(-1)^n\sqrt{2}}{\sqrt{2^{2n+1}(2n+1)!}}\paren{\frac{m\omega}{\pi\hbar}}^{1/4}\exp\paren{-\frac{m\omega r^2}{2\hbar}}H_{2n+1}\paren{\sqrt{\frac{m\omega}{\hbar}}r}\\
+  \psi(r=0)=&\left.\dfrac{1}{\sqrt{4\pi}}\ddiff{u}{r}\right|_{r=0}\\
+  =&\dfrac{1}{\sqrt{2\pi}}\frac{(-1)^n}{\sqrt{2^{2n+1}(2n+1)!}}\paren{\frac{m\omega}{\pi\hbar}}^{1/4}
+  \left.\ddiff{}{r}H_{2n+1}\paren{\sqrt{\frac{m\omega}{\hbar}}r}\right|_{r=0}\\
+  =&\dfrac{1}{\sqrt{2\pi}}\frac{(-1)^n}{\sqrt{2^{2n+1}(2n+1)!}}\paren{\frac{m\omega}{\pi\hbar}}^{1/4}\sqrt{\frac{m\omega}{\hbar}}2(2n + 1) H_{2n}\paren{0}\\
+  =&\frac{(-1)^n}{\sqrt{2^{2n+2}(2n+1)!}}2(2n + 1)(-2)^n (2n - 1)!!\paren{\frac{m\omega}{\pi\hbar}}^{3/4}\\
+  =&\frac{2^{n+1}(2n + 1) (2n - 1)!}{(n-1)!2^{n-1}\sqrt{2^{2n+2}(2n+1)!}}\paren{\frac{m\omega}{\pi\hbar}}^{3/4}\\
+  =&\sqrt{\frac{(2n + 1)!}{2^{2n}n^2}}\frac{1}{(n-1)!}\paren{\frac{m\omega}{\pi\hbar}}^{3/4}\\
+  =&\sqrt{\frac{\sqrt{2\pi (2n+1)}(2n+1)^{2n+1}}{2^{2n}n^2\ue^{2n+1}}}\frac{\ue^{n-1}}{\sqrt{2\pi (n-1)}(n-1)^{n-1}}\paren{\frac{m\omega}{\pi\hbar}}^{3/4}\\
+  \approx&\sqrt{\frac{\sqrt{2\pi(2n+1)}(2n+1)^{2n+1}}{\pi\ue^{3}(2n-2)^{2n+1}}}\paren{\frac{m\omega}{\pi\hbar}}^{3/4}\\
+  \approx&\paren{\frac{4n}{\pi}}^{1/4}\paren{\frac{m\omega}{\pi\hbar}}^{3/4}
+}
+
+\subsubsection{Using 3D harmonic wavefunction}
+\eqar{
+  \psi(r=0)=&\frac{1}{\sqrt{4\pi}}\sqrt{\sqrt{\frac{m^3\omega^3}{4\pi\hbar^3}}\frac{2^{n+3}n!}{(2n+1)!!}}L_n^{1/2}(0)\\
+  =&\frac{1}{\sqrt{4\pi}}\sqrt{\sqrt{\frac{m^3\omega^3}{4\pi\hbar^3}}\frac{2^{n+3}2^n}{(2n+1)!}}n!L_n^{1/2}(0)\\
+  \approx&\frac{1}{\sqrt{4\pi}}\sqrt{\sqrt{\frac{m^3\omega^3}{\pi\hbar^3}}\frac{2^{2n+2}}{(2n+1)!}}\frac{n! 2\sqrt{n}}{\sqrt{\pi}}\\
+  \approx&\frac{1}{\sqrt{4\pi}}\sqrt{\frac{\pi 2^{2n+2}\ue^{2n+1}}{\sqrt{2\pi (2n+1)}(2n+1)^{2n+1}}}\sqrt{2\pi n}\paren{\frac{n}{\ue}}^n\frac{2\sqrt{n}}{\sqrt{\pi}}\paren{\frac{m\omega}{\pi\hbar}}^{3/4}\\
+  =&\sqrt{\frac{2\pi (2n)^{2n+2}\ue}{\pi\sqrt{2\pi (2n+1)}(2n+1)^{2n+1}}}\paren{\frac{m\omega}{\pi\hbar}}^{3/4}\\
+  \approx&\paren{\frac{4n}{\pi}}^{1/4}\paren{\frac{m\omega}{\pi\hbar}}^{3/4}
+}
+which agrees with the other method.\\
+
+The Raman Rabi frequency to the motional state is therefore,
+\eqar{
+  \Omega_R'=&\Omega_R\psi'(r=0)\paren{\frac{\pi^3\hbar^3}{m^3\omega_1\omega_2\omega_3}}^{1/4}\\
+  =&\Omega_R\paren{\frac{4n}{\pi}}^{1/4}\paren{\frac{m\omega}{\pi\hbar}}^{3/4}\paren{\frac{\pi^3\hbar^3}{m^3\omega_1\omega_2\omega_3}}^{1/4}\\
+  =&\Omega_R\paren{\frac{4n\omega^3}{\pi\omega_1\omega_2\omega_3}}^{1/4}
+}
+The decay rate is
+\eqar{
+  \gamma=&\frac{2\pi\Omega_R'^2}{2\omega}\\
+  =&\frac{\pi\Omega_R^2}{\omega}\sqrt{\frac{4n\omega^3}{\pi\omega_1\omega_2\omega_3}}\\
+  =&\Omega_R^2\sqrt{\frac{2\pi E}{\omega_1\omega_2\omega_3}}
+}
+where $E$ is the energy (in frequency unit) of the continuum energy we are coupling to.
 

### 2019-11-25 notes/two-photon-broadening/note.tex
[notes/two-photon-broadening] Calculating the coupling to the ground state continuum using spherical well states as basis

@@
 
+\subsection{Spherical box}
+
+We can also treat the continuum as the spectrum of a large spherical infinitely deep well
+when the radius of the sphere $R$ is infinite.
+The radial wavefunctions of the eigenstates are,
+
+\eqar{
+  u_n=&\sqrt{\frac{2}{R}}\sin\paren{\frac{\pi nr}{R}}
+}
+
+with energy\footnote{In frequency unit} $E=\dfrac{\pi^2\hbar n^2}{2mR^2}$.
+Energy gap between neighboring state is $\Delta E\approx\dfrac{\pi^2\hbar n}{mR^2}$,
+
+\eqar{
+  \psi(r=0)=&\left.\dfrac{1}{\sqrt{4\pi}}\ddiff{u}{r}\right|_{r=0}\\
+  =&\frac{\pi n}{\sqrt{2\pi R}R}\\
+  \Omega_R'=&\Omega_R\psi'(r=0)\paren{\frac{\pi^3\hbar^3}{m^3\omega_1\omega_2\omega_3}}^{1/4}\\
+  =&\Omega_R\frac{\pi n}{\sqrt{2\pi R}R}\paren{\frac{\pi^3\hbar^3}{m^3\omega_1\omega_2\omega_3}}^{1/4}
+}
+
+The decay rate is
+\eqar{
+  \gamma=&\frac{2\pi\Omega_R'^2}{\Delta E}\\
+  =&2\pi\Omega_R^2\frac{\pi^2 n^2}{2\pi R^3}\sqrt{\frac{\pi^3\hbar^3}{m^3\omega_1\omega_2\omega_3}}\frac{mR^2}{\pi^2\hbar n}\\
+  =&\Omega_R^2\frac{n}{R}\sqrt{\frac{\pi^3\hbar}{m\omega_1\omega_2\omega_3}}\\
+  =&\Omega_R^2\frac{1}{R}\sqrt{\frac{\pi^3\hbar}{m\omega_1\omega_2\omega_3}\frac{2mR^2E}{\pi^2\hbar}}\\
+  =&\Omega_R^2\sqrt{\frac{2\pi E}{\omega_1\omega_2\omega_3}}
+}
+Which is the same result we got using the harmonic oscillator states.
+
 \end{document}

### 2019-11-25 notes/two-photon-broadening/note.tex
[notes/two-photon-broadening] Do not specify what Rabi frequency we are calculating.
The calculation can be used in multiple cases so we can be generic about it.
Also tweak some footnote wording.

--- 2019-11-25 notes/two-photon-broadening/note.tex
@@
 
-Assume the Raman Rabi frequency between the initial state and the ground motional state
-is $\Omega_R$, the Raman Rabi frequency for another motional state would be,
+Assume the Rabi frequency between the state of interest and the ground motional state
+is $\Omega$\footnote{This can be either a Raman Rabi frequency for ground state loss rate,
+  or the up leg single photon Rabi frequency for the excited state broadening.},
+the Rabi frequency for another motional state would be,
 
 \eqar{
-  \Omega_R'=&\Omega_R\psi'(r=0)\paren{\frac{\pi^3\hbar^3}{m^3\omega_1\omega_2\omega_3}}^{1/4}
+  \Omega'=&\Omega\psi'(r=0)\paren{\frac{\pi^3\hbar^3}{m^3\omega_1\omega_2\omega_3}}^{1/4}
 }
@@
   Note that both calculations will be done under the same assumptions given above so their
-  agreement does not necessarily mean that the assumption is valid.}.
+  agreement does not validate the assumption.}.
 
@@
 
-The Raman Rabi frequency to the motional state is therefore,
+The Rabi frequency to the motional state is therefore,
 \eqar{
-  \Omega_R'=&\Omega_R\psi'(r=0)\paren{\frac{\pi^3\hbar^3}{m^3\omega_1\omega_2\omega_3}}^{1/4}\\
-  =&\Omega_R\paren{\frac{4n}{\pi}}^{1/4}\paren{\frac{m\omega}{\pi\hbar}}^{3/4}\paren{\frac{\pi^3\hbar^3}{m^3\omega_1\omega_2\omega_3}}^{1/4}\\
-  =&\Omega_R\paren{\frac{4n\omega^3}{\pi\omega_1\omega_2\omega_3}}^{1/4}
+  \Omega'=&\Omega\psi'(r=0)\paren{\frac{\pi^3\hbar^3}{m^3\omega_1\omega_2\omega_3}}^{1/4}\\
+  =&\Omega\paren{\frac{4n}{\pi}}^{1/4}\paren{\frac{m\omega}{\pi\hbar}}^{3/4}\paren{\frac{\pi^3\hbar^3}{m^3\omega_1\omega_2\omega_3}}^{1/4}\\
+  =&\Omega\paren{\frac{4n\omega^3}{\pi\omega_1\omega_2\omega_3}}^{1/4}
 }
@@
 \eqar{
-  \gamma=&\frac{2\pi\Omega_R'^2}{2\omega}\\
-  =&\frac{\pi\Omega_R^2}{\omega}\sqrt{\frac{4n\omega^3}{\pi\omega_1\omega_2\omega_3}}\\
-  =&\Omega_R^2\sqrt{\frac{2\pi E}{\omega_1\omega_2\omega_3}}
+  \gamma=&\frac{2\pi\Omega'^2}{2\omega}\\
+  =&\frac{\pi\Omega^2}{\omega}\sqrt{\frac{4n\omega^3}{\pi\omega_1\omega_2\omega_3}}\\
+  =&\Omega^2\sqrt{\frac{2\pi E}{\omega_1\omega_2\omega_3}}
 }
@@
 
+\subsection{Spherical box}
+
+We can also treat the continuum as the spectrum of a large spherical infinitely deep well
+when the radius of the sphere $R$ is infinite.
+The radial wavefunctions of the eigenstates are,
+
+\eqar{
+  u_n=&\sqrt{\frac{2}{R}}\sin\paren{\frac{\pi nr}{R}}
+}
+
+with energy\footnote{In frequency unit} $E=\dfrac{\pi^2\hbar n^2}{2mR^2}$.
+Energy gap between neighboring state is $\Delta E\approx\dfrac{\pi^2\hbar n}{mR^2}$,
+
+\eqar{
+  \psi(r=0)=&\left.\dfrac{1}{\sqrt{4\pi}}\ddiff{u}{r}\right|_{r=0}\\
+  =&\frac{\pi n}{\sqrt{2\pi R}R}\\
+  \Omega'=&\Omega\psi'(r=0)\paren{\frac{\pi^3\hbar^3}{m^3\omega_1\omega_2\omega_3}}^{1/4}\\
+  =&\Omega\frac{\pi n}{\sqrt{2\pi R}R}\paren{\frac{\pi^3\hbar^3}{m^3\omega_1\omega_2\omega_3}}^{1/4}
+}
+
+The decay rate is
+\eqar{
+  \gamma=&\frac{2\pi\Omega'^2}{\Delta E}\\
+  =&2\pi\Omega^2\frac{\pi^2 n^2}{2\pi R^3}\sqrt{\frac{\pi^3\hbar^3}{m^3\omega_1\omega_2\omega_3}}\frac{mR^2}{\pi^2\hbar n}\\
+  =&\Omega^2\frac{n}{R}\sqrt{\frac{\pi^3\hbar}{m\omega_1\omega_2\omega_3}}\\
+  =&\Omega^2\frac{1}{R}\sqrt{\frac{\pi^3\hbar}{m\omega_1\omega_2\omega_3}\frac{2mR^2E}{\pi^2\hbar}}\\
+  =&\Omega^2\sqrt{\frac{2\pi E}{\omega_1\omega_2\omega_3}}
+}
+Which is the same result we got using the harmonic oscillator states.
+
 \end{document}

### 2019-11-25 notes/two-photon-broadening/note.tex
[notes/two-photon-broadening] Gramma/spelling

@@
   the motional continuum from other HF states.\\
-  The COM motional continuum actually also starts at a positive energy so it doesn't seems
+  The COM motional continuum actually also starts at a positive energy so it doesn't seem
   possible. The continuum from other HF states is much more promising especially since
@@
 we can assume that the boundary condition is given by the value of
-the non-interacting wavefunctions at $r=0$.\\
+the non-interacting wavefunction at $r=0$.\\
 
@@
 
-After doing the subsitution of $u=r\psi_r(r)$, the Schr\"odinger equation for $u$ becomes
+After doing the substitution of $u=r\psi_r(r)$, the Schr\"odinger equation for $u$ becomes
 that of a 1D harmonic oscillator with a hard wall at $r=0$. The eigenstates are the odd

### 2019-11-27 notes/two-photon-broadening/note.tex
[notes/two-photon-broadening] Fixes and corrections

@@
 
-\[ \gamma=\Gamma\frac{\Omega_1\Omega_2}{\Delta^2} \]
+\[ \gamma=\Gamma\frac{\Omega_1\Omega_2}{4\Delta^2} \]
 
@@
   we know that the $|F^{\mathrm{Cs}}\!=\!3, m_{F}^{\mathrm{Cs}}\!=\!3; F^{\mathrm{Na}}\!=\!2, m_{F}^{\mathrm{Na}}\!=\!2\rangle$ state has a strong coupling to the molecular excited states.
-  However, this cannot be applied to the $|F^{\mathrm{Cs}}\!=\!3, m_{F}^{\mathrm{Cs}}\!=\!3; F^{\mathrm{Na}}\!=\!2, m_{F}^{\mathrm{Na}}\!=\!2\rangle$ state lifetime since it is already
-  the HF state with the lowest energy.
+  \sout{However, this cannot be applied to the $|F^{\mathrm{Cs}}\!=\!3, m_{F}^{\mathrm{Cs}}\!=\!3; F^{\mathrm{Na}}\!=\!2, m_{F}^{\mathrm{Na}}\!=\!2\rangle$ state lifetime since it is already
+    the HF state with the lowest energy.}
+  Kang-Kuen and Kenneth pointed out that $|F^{\mathrm{Cs}}\!=\!3, m_{F}^{\mathrm{Cs}}\!=\!3; F^{\mathrm{Na}}\!=\!1, m_{F}^{\mathrm{Na}}\!=\!1\rangle$ is the state with the lowest energy
+  so $|F^{\mathrm{Cs}}\!=\!3, m_{F}^{\mathrm{Cs}}\!=\!3; F^{\mathrm{Na}}\!=\!2, m_{F}^{\mathrm{Na}}\!=\!2\rangle$ indeed have a (in fact, multiple Zeeman states) continuum to couple to.
 \end{enumerate}
@@
 }
+where $\psi'(r=0)$ is the value of the wavefunction for the other motional state at $r=0$.\\
 

### 2020-02-14 experiments/nacs_202002/plot_20200206_155743_coprop_det.jl
[experiments/nacs_202002] Coprop

@@ -1,0 +1,107 @@
+#!/usr/bin/julia
+
+push!(LOAD_PATH, joinpath(@__DIR__, "../../lib"))
+
+import NaCsCalc.Format: Unc, Sci
+using NaCsCalc.Utils: interactive
+using NaCsData
+using NaCsPlot
+using PyPlot
+using DataStructures
+using LsqFit
+
+const inames = ["data_20200206_155743.mat"]
+const datas = [NaCsData.load_striped_mat(joinpath(@__DIR__, "data", iname)) for iname in inames]
+const maxcnts = [typemax(Int)]
+const specs_na = [-3.2 .+ linspace(-125, 125, 26)]
+const specs_cs = [linspace(-80, 120, 26)]
+select_datas(datas, selector, maxcnts, specs) =
+    [NaCsData.split_data(NaCsData.select_count(data..., selector, maxcnt), spec)
+     for (data, maxcnt, spec) in zip(datas, maxcnts, specs)]
+
+fit_data(model, x, y, p0; kws...) =
+    fit_data(model, x, y, nothing, p0; kws...)
+
+function fit_data(model, params, ratios, uncs, p0;
+                  plotx=nothing, plot_lo=nothing, plot_hi=nothing, plot_scale=1.1)
+    use_unc = uncs !== nothing
+    if plotx === nothing
+        lo = minimum(params)
+        hi = maximum(params)
+        span = hi - lo
+        mid = (hi + lo) / 2
+        if plot_lo === nothing
+            plot_lo = mid - span * plot_scale / 2
+            if plot_lo * lo <= 0
+                plot_lo = 0
+            end
+        end
+        if plot_hi === nothing
+            plot_hi = mid + span * plot_scale / 2
+            if plot_hi * hi <= 0
+                plot_hi = 0
+            end
+        end
+        plotx = linspace(plot_lo, plot_hi, 10000)
+    end
+    if use_unc
+        fit = curve_fit(model, params, ratios, uncs.^-(2/3), p0)
+    else
+        fit = curve_fit(model, params, ratios, p0)
+    end
+    param = fit.param
+    unc = estimate_errors(fit)
+    return (param=param, unc=unc,
[…]

### 2020-02-14 experiments/nacs_202002/plot_20200206_coprop_rabi_coherence.jl
[experiments/nacs_202002] Coprop Rabi coherence

@@ -1,0 +1,158 @@
+#!/usr/bin/julia
+
+push!(LOAD_PATH, joinpath(@__DIR__, "../../lib"))
+
+import NaCsCalc.Format: Unc, Sci
+using NaCsCalc.Utils: interactive
+using NaCsData
+using NaCsPlot
+using PyPlot
+using DataStructures
+using LsqFit
+
+const inames = ["data_20200206_173305.mat",
+                "data_20200206_204557.mat",
+                "data_20200206_190515.mat"]
+const datas = [NaCsData.load_striped_mat(joinpath(@__DIR__, "data", iname)) for iname in inames]
+const maxcnts = [typemax(Int),
+                 typemax(Int),
+                 typemax(Int)]
+const specs = [linspace(0, 0.05, 21),
+               0.5 .+ linspace(0, 0.05, 21),
+               1 .+ linspace(0, 0.05, 21)]
+select_datas(datas, selector, maxcnts, specs) =
+    [NaCsData.split_data(NaCsData.select_count(data..., selector, maxcnt), spec)
+     for (data, maxcnt, spec) in zip(datas, maxcnts, specs)]
+
+fit_data(model, x, y, p0; kws...) =
+    fit_data(model, x, y, nothing, p0; kws...)
+
+function fit_data(model, params, ratios, uncs, p0;
+                  plotx=nothing, plot_lo=nothing, plot_hi=nothing, plot_scale=1.1)
+    use_unc = uncs !== nothing
+    if plotx === nothing
+        lo = minimum(params)
+        hi = maximum(params)
+        span = hi - lo
+        mid = (hi + lo) / 2
+        if plot_lo === nothing
+            plot_lo = mid - span * plot_scale / 2
+            if plot_lo * lo <= 0
+                plot_lo = 0
+            end
+        end
+        if plot_hi === nothing
+            plot_hi = mid + span * plot_scale / 2
+            if plot_hi * hi <= 0
+                plot_hi = 0
+            end
+        end
+        plotx = linspace(plot_lo, plot_hi, 10000)
+    end
+    if use_unc
[…]

### 2020-02-21 experiments/nacs_202002/plot_20200220_raman_vs_freq_3311.jl
[experiments/nacs_202002] Linewidth frequency dependency

@@ -1,0 +1,78 @@
+#!/usr/bin/julia
+
+push!(LOAD_PATH, joinpath(@__DIR__, "../../lib"))
+
+import NaCsCalc.Format: Unc, Sci
+using NaCsCalc.Utils: interactive
+using NaCsData
+using NaCsPlot
+using PyPlot
+using DataStructures
+using LsqFit
+
+fit_data(model, x, y, p0; kws...) =
+    fit_data(model, x, y, nothing, p0; kws...)
+
+function fit_data(model, params, ratios, uncs, p0;
+                  plotx=nothing, plot_lo=nothing, plot_hi=nothing, plot_scale=1.1)
+    use_unc = uncs !== nothing
+    if plotx === nothing
+        lo = minimum(params)
+        hi = maximum(params)
+        span = hi - lo
+        mid = (hi + lo) / 2
+        if plot_lo === nothing
+            plot_lo = mid - span * plot_scale / 2
+            if plot_lo * lo <= 0
+                plot_lo = 0
+            end
+        end
+        if plot_hi === nothing
+            plot_hi = mid + span * plot_scale / 2
+            if plot_hi * hi <= 0
+                plot_hi = 0
+            end
+        end
+        plotx = linspace(plot_lo, plot_hi, 10000)
+    end
+    if use_unc
+        fit = curve_fit(model, params, ratios, uncs.^-(2/3), p0)
+    else
+        fit = curve_fit(model, params, ratios, p0)
+    end
+    param = fit.param
+    unc = estimate_errors(fit)
+    return (param=param, unc=unc,
+            uncs=Unc.(param, unc, Sci),
+            plotx=plotx, ploty=model.(plotx, (fit.param,)))
+end
+
+function fit_survival(model, data, p0; use_unc=true, kws...)
+    if use_unc
+        params, ratios, uncs = NaCsData.get_values(data)
+        return fit_data(model, params, ratios[:, 2], uncs[:, 2], p0; kws...)
+    else
+        params, ratios, uncs = NaCsData.get_values(data, 0.0)
+        return fit_data(model, params, ratios[:, 2], p0; kws...)
+    end
+end
+
+tweezer = [460.7, 480.7, 490.7, 522, 530, 550.7]
+widths = [17.6, 22.6, 52, 430, 118, 20.7]
[…]

### 2020-05-28 experiments/nacs_202003/fit_20200326_223438_raman_3322_2.jl
[experiments/nacs_202003] DAMOP plots

@@ -257,4 +257,53 @@ ylabel("Two-body survival")
 tight_layout(pad=0.6)
 NaCsPlot.maybe_save("$(prefix)")
 
+function model_lorentzian(x, p)
+    p[1] .- p[2] ./ (1 .+ ((x .- p[3]) ./ (p[4] / 2)).^2)
+end
+fit_l10 = fit_survival(model_lorentzian, data_nacs_10, [0.35, 0.25, 594, 5])
+
+figure()
+NaCsPlot.plot_survival_data(data_nacs_10, fmt="C0.", label="0.10 ms")
+plot(fit_l10.plotx, fit_l10.ploty, "C0")
+legend(fontsize="x-small", loc="lower right")
+grid()
+xlabel("2-Photon Detuning (770XXX kHz)")
+ylabel("Two-body survival")
+NaCsPlot.maybe_save("$(prefix)_damop_f")
+
+figure()
+NaCsPlot.plot_survival_data(data_nacs_10, fmt="C0.", label="0.10 ms")
+plot(fit_l10.plotx, fit_l10.ploty, "C0")
+x₋ = fit_l10.param[3] - fit_l10.param[4] / 2
+x₊ = fit_l10.param[3] + fit_l10.param[4] / 2
+y_pm = (model_lorentzian(x₋, fit_l10.param) + model_lorentzian(x₊, fit_l10.param)) / 2
+ax = gca()
+ax.annotate("", (x₋ - 1, y_pm), xytext=(x₋ - 11, y_pm),
+            arrowprops=Dict(:color=>"C3"))
+ax.annotate("", (x₊ + 1, y_pm), xytext=(x₊ + 11, y_pm),
+            arrowprops=Dict(:color=>"C3"))
+text(573, 0.16, "\$\\mathbf{\\Gamma_{FWHM}=$(fit_l10.uncs[4]) kHz}\$",
+     fontsize=17, color="C3")
+legend(fontsize="x-small", loc="lower right")
+grid()
+xlabel("2-Photon Detuning (770XXX kHz)")
+ylabel("Two-body survival")
+NaCsPlot.maybe_save("$(prefix)_damop_f_text")
+
+figure()
+# const plot_time = linspace(0, 0.45, 1000)
+NaCsPlot.plot_survival_data(data_nacs_t, fmt="C0.", label="770.59429 MHz")
[…]

### 2020-05-28 experiments/nacs_202005/fit_20200524_161707_raman_3322.jl
[experiments/nacs_202005] 625 GHz, 6 mW, including damop time plot

@@ -1,0 +1,118 @@
+#!/usr/bin/julia
+
+push!(LOAD_PATH, joinpath(@__DIR__, "../../lib"))
+
+include("../nacs_202003/molecular_raman_model.jl")
+
+import NaCsCalc.Format: Unc, Sci
+using NaCsCalc
+using NaCsCalc.Utils: interactive
+using NaCsData
+using NaCsData.Fitting: fit_data, fit_survival
+using NaCsPlot
+using PyPlot
+using DataStructures
+using LsqFit
+
+const inames = ["data_20200524_161707.mat"]
+const datas = [NaCsData.load_striped_mat(joinpath(@__DIR__, "data", iname)) for iname in inames]
+const maxcnts = [typemax(Int)]
+const specs = [([0; [0.04, 0.07, 0.10, 0.135, 0.17, 0.22, 0.26] * 2.5 .- 0.01], # 6 mW, 770.487 MHz
+                [0.0], # 6 mW, 0 ms
+                487 .+ (-2.5:0.5:2.5), # 6 mW, 0.23 ms
+                487 .+ (-2.5:0.5:2.5), # 6 mW, 0.42 ms
+                ),
+               ]
+
+select_datas(datas, selector, maxcnts, specs) =
+    [NaCsData.split_data(NaCsData.select_count(data..., selector, maxcnt), spec)
+     for (data, maxcnt, spec) in zip(datas, maxcnts, specs)]
+
+function get_ratio_val(data)
+    params, ratios, uncs = NaCsData.get_values(data)
+    return ratios[2], uncs[2]
+end
+
+const datas_nacs = select_datas(datas, NaCsData.select_single((1, 2), (3, 4,)), maxcnts, specs)
+const data_nacs_t = datas_nacs[1][1] # Survival 1
+const data_nacs_00 = datas_nacs[1][2] # Survival 1
+const data_nacs_22 = datas_nacs[1][3] # Survival 1
+const data_nacs_41 = datas_nacs[1][4] # Survival 1
+
+const data_fit = [NaCsData.map_params((i, v) -> (v, 0.0, 1), data_nacs_00);
+                  NaCsData.map_params((i, v) -> (v, 0.22, 1), data_nacs_22);
[…]

### 2020-05-29 experiments/nacs_202003/fit_20200326_223438_raman_3322_2.jl
[experiments/nacs_202003] Add pointer to time plot for DAMOP

@@ -291,15 +291,14 @@ ylabel("Two-body survival")
 NaCsPlot.maybe_save("$(prefix)_damop_f_text")
 
 figure()
-# const plot_time = linspace(0, 0.45, 1000)
 NaCsPlot.plot_survival_data(data_nacs_t, fmt="C0.", label="770.59429 MHz")
 plot(plot_time, model_2d.(plot_time, 594.29, (param_1,)), "C0")
 legend(fontsize="x-small", loc="upper right")
-# text(0.09, 0.12, ("\$f_{res}=$(uncs_1[3] / 1000 + 770)\$ MHz\n" *
-#                   "\$\\Omega_{Raman}=2\\pi\\times$(uncs_1[4] / 2π)\$ kHz\n" *
-#                   "\$\\Gamma_{atom}=2\\pi\\times$(uncs_1[5] / 2π * 1000)\$ Hz\n" *
-#                   "\$\\Gamma_{molecule}=2\\pi\\times$(uncs_1[6] / 2π)\$ kHz\n"),
-#      color="C0", fontsize="small")
+annotate("Atom", (0, 0.32), xytext=(0.1, 0.34), arrowprops=Dict(:color=>"C3"), color="C3")
+annotate("Molecule", (0.147, 0.0344),
+         xytext=(0.08, 0.15), arrowprops=Dict(:color=>"C3"), color="C3")
+annotate("Atom", (0.26, 0.1),
+         xytext=(0.29, 0.17), arrowprops=Dict(:color=>"C3"), color="C3")
 xlim([0, 0.46])
 grid()
 xlabel("Raman time (ms)")

### 2020-05-29 experiments/nacs_202003/fit_20200326_223438_raman_3322_2.jl
[experiments/nacs_202003] molecule lifetime for DAMOP

@@ -305,4 +305,15 @@ xlabel("Raman time (ms)")
 ylabel("Two-body survival")
 NaCsPlot.maybe_save("$(prefix)_damop_t")
 
+figure()
+NaCsPlot.plot_survival_data(data_nacs_m, fmt="C0s")
+plot(plot_m_time, model_expoff(plot_m_time, gen_exp_param(fit.param, 5, 9, 2)), "C0-")
+text(0.1, 0.07, "\$\\tau=$(1000 / uncs_1[6])\\ \\mathrm{\\mu s}\$", color="C3")
+xlim([0, 0.32])
+title("Molecule lifetime")
+grid()
+xlabel("Molecule Hold Time (ms)")
+ylabel("Two-body survival")
+NaCsPlot.maybe_save("$(prefix)_damop_m_t")
+
 NaCsPlot.maybe_show()

### 2020-05-29 experiments/nacs_202003/fit_20200326_223438_raman_3322_2.jl
[experiments/nacs_202003] Change DAMOP molecule lifetime y label to molecule survival

@@ -313,7 +313,7 @@ xlim([0, 0.32])
 title("Molecule lifetime")
 grid()
 xlabel("Molecule Hold Time (ms)")
-ylabel("Two-body survival")
+ylabel("Molecule survival")
 NaCsPlot.maybe_save("$(prefix)_damop_m_t")
 
 NaCsPlot.maybe_show()

### 2020-05-30 presentations/damop-2020/plot_raman.jl
[presentations/damop-2020] thicker ratio line

@@ -36,30 +36,35 @@ grid()
 ax = gca()
 ax2 = ax.twinx()
 l3 = ax2.plot(data[:, 1] .- 288625.081, abs.(data[:, 2] ./ data[:, 4]), "C2",
-              label="\$\\frac{\\Omega_{Raman}}{\\Gamma_{scatter}}\$")
+              label="\$\\frac{\\Omega_{Raman}}{\\Gamma_{scatter}}\$", linewidth=4)
 ls = [l1; l2; l3]
 legend(ls, [l.get_label() for l in ls], fontsize="small",
        loc="lower right", bbox_to_anchor=(1, 0.05))
 xlim([-45, 45])
 ylim([0, 60])
 ax2.tick_params(axis="y", labelcolor="C2")
+setp(ax2.get_yticklabels(), fontweight="bold")
 NaCsPlot.maybe_save("$(prefix)_v0")
 
 figure()
-l1 = plot(data[:, 1] .- 351271.53, abs.(data[:, 2] ./ 2π / 1000), "C0", label="\$\\Omega_{Raman}\$")
-l2 = plot(data[:, 1] .- 351271.53, abs.(data[:, 4] ./ 2π / 1000), "C1", label="\$\\Gamma_{scatter}\$")
+l1 = plot(data[:, 1] .- 351271.53, abs.(data[:, 2] ./ 2π / 1000), "C0",
+          label="\$\\Omega_{Raman}\$")
+l2 = plot(data[:, 1] .- 351271.53, abs.(data[:, 4] ./ 2π / 1000), "C1",
+          label="\$\\Gamma_{scatter}\$")
 ylabel("\$2\\pi\\cdot \\mathrm{kHz}\$")
 xlabel("One-Photon Detuning (GHz)")
 ylim([0, 800])
 grid()
 ax = gca()
 ax2 = ax.twinx()
-l3 = ax2.plot(data[:, 1] .- 351271.53, abs.(data[:, 2] ./ data[:, 4]), "C2", label="\$\\frac{\\Omega_{Raman}}{\\Gamma_{scatter}}\$")
+l3 = ax2.plot(data[:, 1] .- 351271.53, abs.(data[:, 2] ./ data[:, 4]), "C2",
+              label="\$\\frac{\\Omega_{Raman}}{\\Gamma_{scatter}}\$", linewidth=4)
 ls = [l1; l2; l3]
[…]

### 2020-05-30 experiments/nacs_202003/fit_20200326_223438_raman_3322_2.jl
[experiments/nacs_202003] DAMOP frequency plot center

@@ -262,31 +262,35 @@ function model_lorentzian(x, p)
 end
 fit_l10 = fit_survival(model_lorentzian, data_nacs_10, [0.35, 0.25, 594, 5])
 
+const data_nacs_10_shift = NaCsData.map_params((i, v)->v - fit_l10.param[3], data_nacs_10)
+
 figure()
-NaCsPlot.plot_survival_data(data_nacs_10, fmt="C0.", label="0.10 ms")
-plot(fit_l10.plotx, fit_l10.ploty, "C0")
+NaCsPlot.plot_survival_data(data_nacs_10_shift, fmt="C0.", label="0.10 ms")
+plot(fit_l10.plotx .- fit_l10.param[3], fit_l10.ploty, "C0")
 legend(fontsize="x-small", loc="lower right")
+text(-24, 0.32, "\$f_{Raman}=$(770 + fit_l10.uncs[3] / 1000) \\mathrm{MHz}\$", color="C0", fontsize="small")
 grid()
-xlabel("2-Photon Detuning (770XXX kHz)")
+xlabel("Detuning from resonance (kHz)")
 ylabel("Two-body survival")
 NaCsPlot.maybe_save("$(prefix)_damop_f")
 
 figure()
-NaCsPlot.plot_survival_data(data_nacs_10, fmt="C0.", label="0.10 ms")
-plot(fit_l10.plotx, fit_l10.ploty, "C0")
+NaCsPlot.plot_survival_data(data_nacs_10_shift, fmt="C0.", label="0.10 ms")
+plot(fit_l10.plotx .- fit_l10.param[3], fit_l10.ploty, "C0")
 x₋ = fit_l10.param[3] - fit_l10.param[4] / 2
 x₊ = fit_l10.param[3] + fit_l10.param[4] / 2
 y_pm = (model_lorentzian(x₋, fit_l10.param) + model_lorentzian(x₊, fit_l10.param)) / 2
 ax = gca()
-ax.annotate("", (x₋ - 1, y_pm), xytext=(x₋ - 11, y_pm),
+ax.annotate("", (-fit_l10.param[4] / 2 - 1, y_pm), xytext=(-fit_l10.param[4] / 2 - 11, y_pm),
             arrowprops=Dict(:color=>"C3"))
-ax.annotate("", (x₊ + 1, y_pm), xytext=(x₊ + 11, y_pm),
[…]

### 2020-07-19 lib/NaCsPlot/src/NaCsPlot.jl
[NaCsPlot] update for svg backend metadata support

@@ -65,7 +65,9 @@ function save(name; close=true)
     metadata = Dict("Creator"=>nothing, "Producer"=>nothing, "CreationDate"=>nothing)
     savefig("$name.pdf"; bbox_inches="tight", transparent=true, metadata=metadata)
     savefig("$name.png"; bbox_inches="tight", transparent=true, metadata=metadata)
-    savefig("$name.svg"; bbox_inches="tight", transparent=true, metadata=metadata)
+    savefig("$name.svg"; bbox_inches="tight", transparent=true,
+            metadata=Dict("Creator"=>nothing, "Date"=>nothing,
+                          "Format"=>nothing, "Type"=>nothing))
     close && PyPlot.close()
     return
 end

### 2020-07-19 experiments/nacs_202007/fit_20200703_201618_raman15_3322_2.jl
[experiments/nacs_202007] plot for postdoc interviewe

@@ -193,4 +193,26 @@ colorbar()
 tight_layout(pad=0.6)
 NaCsPlot.maybe_save("$(prefix)")
 
+figure()
+NaCsPlot.plot_survival_data([data_nacs_00; data_nacs_t], fmt="C0.", label="769.919 MHz")
+plot(plot_time, model_2d.(plot_time, -81.0, (param_1,)), "C0")
+xlim([0, 0.26])
+ylim([0, ylim()[2]])
+legend(fontsize="x-small", loc="upper right")
+grid()
+xlabel("Raman time (ms)")
+ylabel("Two-body survival")
+NaCsPlot.maybe_save("$(prefix)_postdoc_t")
+
+figure()
+imshow(mol_2d, aspect="auto", interpolation="none", origin="lower",
+       extent=[img_time[1] - step(img_time) / 2, img_time[end] + step(img_time) / 2,
+               img_freq[1] - step(img_freq) / 2, img_freq[end] + step(img_freq) / 2])
+xlabel("Raman time (ms)")
+ylabel("2-Photon Detuning (770XXX kHz)")
+grid()
+colorbar()
+title("Molecule Population")
+NaCsPlot.maybe_save("$(prefix)_postdoc_2d_mol")
+
 NaCsPlot.maybe_show()

### 2020-07-21 experiments/nacs_202007/fit_20200703_201618_raman15_3322_2.jl
[experiments/nacs_202007] scale molecular ratio plot

@@ -205,7 +205,7 @@ ylabel("Two-body survival")
 NaCsPlot.maybe_save("$(prefix)_postdoc_t")
 
 figure()
-imshow(mol_2d, aspect="auto", interpolation="none", origin="lower",
+imshow(mol_2d ./ param_1[2], aspect="auto", interpolation="none", origin="lower",
        extent=[img_time[1] - step(img_time) / 2, img_time[end] + step(img_time) / 2,
                img_freq[1] - step(img_freq) / 2, img_freq[end] + step(img_freq) / 2])
 xlabel("Raman time (ms)")

### 2020-07-21 presentations/2020-postdoc/sequence.tex
[presentations/2020-postdoc] More tweaks, add more detail, styles

--- 2017-05-26 presentations/na_cool_paper/sequence.tex
@@
 \begin{document}
-\begin{tikzpicture}
+\begin{tikzpicture}[scale=0.9]
   % 0.0 - 1.6 axial (1.6)
@@
   \begin{scope}
-    \clip (4.6, -2.1) rectangle (17.8, 3.5);
+    \clip (4.6, -2.1) rectangle (17.8, 2.0);
     %% Pulse mark
@@
     %% Tweezer
-    \draw[line width=1.5,purple] (0, 2.4) -- (22.4, 2.4);
-    \foreach \i in {0,...,99} {
-      \filldraw[line width=1,purple] (\i*22.4/100, 2.4) rectangle (\i*22.4/100+0.06, 3.5);
-    }
+    % \draw[line width=1.5,purple] (0, 2.4) -- (22.4, 2.4);
+    % \foreach \i in {0,...,99} {
+    %   \filldraw[line width=1,purple] (\i*22.4/100, 2.4) rectangle (\i*22.4/100+0.06, 3.5);
+    % }
 
@@
     }
-    \path[blue] (2.8*2+0.8, 0) node[below,align=center] {\textbf{Axis 1}\\\textit{Axial}};
+    \path[blue] (2.8*2+0.8, 1) node[above,align=center] {\textit{Axial $z$}};
     \foreach \i in {0,...,3} {
-      \path (5.6*\i + 0.8, 1) node[above,blue,align=center] {\textbf{$n$-th}\\\textbf{order}};
-      \path (5.6*\i + 3.6, 1) node[above,blue,align=center] {\textbf{$(n-1)$-th}\\\textbf{order}};
+      \path (5.6*\i + 0.8, -0.15) node[below,blue,align=center] {\textbf{$m$-th}\\\textbf{order}};
+      \path (5.6*\i + 3.6, -0.15) node[below,blue,align=center] {\textbf{$(\!m-1\!)$-th}\\\textbf{order}};
     }
@@
       \filldraw[fill=orange!30,draw=orange,line width=1.2]
-      (2.8*\i+1.58, -2) rectangle (2.8*\i+1.91, -0.7);
+      (2.8*\i+1.58, -2) rectangle (2.8*\i+1.91, -1);
       \filldraw[fill=orange!30,draw=orange,line width=1.2]
-      (2.8*\i+2.48, -2) rectangle (2.8*\i+2.81, -0.7);
+      (2.8*\i+2.48, -2) rectangle (2.8*\i+2.81, -1);
     }
@@
 
-  \fill[white,path fading=fade img right] (16.8, -2.2) rectangle (17.81, 3.51);
-  \fill[white,path fading=fade img right] (16.8, -2.2) rectangle (17.81, 3.51);
-  \fill[white,path fading=fade img right] (16.8, -2.2) rectangle (17.81, 3.51);
+  \fill[white,path fading=fade img right] (16.8, -2.2) rectangle (17.81, 1.6);
+  \fill[white,path fading=fade img right] (16.8, -2.2) rectangle (17.81, 1.6);
+  \fill[white,path fading=fade img right] (16.8, -2.2) rectangle (17.81, 1.6);
 
-  \fill[white,path fading=fade img left] (5.6, -2.2) rectangle (4.59, 3.51);
-  \fill[white,path fading=fade img left] (5.6, -2.2) rectangle (4.59, 3.51);
-  \fill[white,path fading=fade img left] (5.6, -2.2) rectangle (4.59, 3.51);
+  \fill[white,path fading=fade img left] (5.6, -2.2) rectangle (4.59, 1.6);
+  \fill[white,path fading=fade img left] (5.6, -2.2) rectangle (4.59, 1.6);
+  \fill[white,path fading=fade img left] (5.6, -2.2) rectangle (4.59, 1.6);
 
-  \path (5.0, 2.3) node[left,purple,align=center] {\textbf{Tweezer}};
-  \path (4.8, 0.5) node[left,align=center] {\textbf{Raman}};
-  \path (5.15, -1.5) node[left,orange,align=center] {\textbf{Optical}\\\textbf{pumping}};
-  \draw[line width=2,orange,->] (5.6,-2) -- (17.8,-2) node[right, below] {\scalebox{2}{$t$}};
+  % \path (5.0, 2.3) node[left,purple,align=center] {\textbf{Tweezer}};
+  \node[above,align=center] at (5.7, 1.7) {\large \textbf{Raman}};
+  \node[below,orange,align=center] at (5.7, -2.4)
+  {\large \textbf{Optical}\\\large \textbf{pumping}};
+  \draw[line width=2,orange,->,>=stealth] (5.6,-2) -- (17.8,-2) node[right, below] {\scalebox{2}{$t$}};
 
@@
   (5.6,-2) -- node[below=15pt] {\scalebox{1.5}{One cooling cycle}} (16.8,-2);
-
-  %% Sub figure label
-  \path (3.8,2.5) node[above=8pt] {\scalebox{1.2}{(C)}};
 \end{tikzpicture}

### 2020-07-22 presentations/2020-postdoc/plot_wavefunction.jl
[presentations/2020-postdoc] feedbacks

@@ -1,0 +1,48 @@
+#!/usr/bin/julia
+
+push!(LOAD_PATH, joinpath(@__DIR__, "../../lib"))
+
+import NaCsCalc.Format: Unc, Sci
+using NaCsCalc
+using NaCsCalc.Utils: interactive
+using NaCsData
+using NaCsData.Fitting: fit_data, fit_survival
+using NaCsPlot
+using PyPlot
+# using DataStructures
+# using LsqFit
+using LibArchive
+
+using DelimitedFiles
+
+function read_csv_compressed(fname, args...; kwargs...)
+    LibArchive.Reader(fname) do reader
+        LibArchive.support_format_raw(reader)
+        LibArchive.support_filter_all(reader)
+        LibArchive.next_header(reader)
+        readdlm(reader, args...; kwargs...)
+    end
+end
+
+const fname31 = joinpath(@__DIR__, "3311boundstate.csv.zst")
+const fname32 = joinpath(@__DIR__, "3322boundstate.csv.zst")
+const fname42 = joinpath(@__DIR__, "4422boundstate.csv.zst")
+const data31 = read_csv_compressed(fname31, ',', Float64)
+const data32 = read_csv_compressed(fname32, ',', Float64)
+const data42 = read_csv_compressed(fname42, ',', Float64)
+
+const prefix = joinpath(@__DIR__, "imgs", "wavefunction")
+
+figure()
+plot(data42[:, 1], data42[:, 2] .* 1e4, "C2", label="Na(2,2) Cs(4,4)")
+plot(data32[:, 1], data32[:, 2] .* 1e4, "C1", label="Na(2,2) Cs(3,3)")
+plot(data31[:, 1], data31[:, 2] .* 1e4, "C3--", label="Na(1,1) Cs(3,3)")
+grid()
+xlim([0, 3080])
+ylim([0, 7.3])
+ylabel("Probability density")
+xlabel("R (Angstroms)")
+legend(fontsize="x-small")
+NaCsPlot.maybe_save("$(prefix)")
+
+NaCsPlot.maybe_show()

### 2020-11-04 lib/NaCsData/src/load.jl
[lib/NaCsData] filter and sorting of data

@@ -47,6 +47,18 @@ SortedData1{K,Vs} = SortedData{1,2,K,Vs}
     end
 end
 
+function Base.sort!(data::SortedData{1}; kws...)
+    perm = sortperm(data.params; kws...)
+    permute!(data.params, perm)
+    permute!(data.values, perm)
+    return data
+end
+
+function Base.filter(f, data::SortedData{1})
+    idxs = findall(f, data.params)
+    return data[idxs]
+end
+
 @inline Base.size(data::SortedData) = size(data.params)..., depth(data.values)
 @inline Base.lastindex(data::SortedData) = lastindex(data.params)
 @inline Base.size(data::SortedData{N}, dim) where {N} = if dim <= N
@@ -131,6 +143,10 @@ CountData(params::AbstractArray{T,N}, counts::AbstractArray{T2,N2}) where {N,N2,
 @inline _maybe_countvalues(v::Number) = v
 @inline _maybe_countvalues(v::AbstractArray{T,N}) where {T,N} = CountValues{N}(v)
 @inline Base.getindex(vals::CountValues, args...) = _maybe_countvalues(vals.counts[args...])
+function Base.permute!(vals::CountValues{2}, perm::AbstractVector)
+    vals.counts .= vals.counts[perm, :]
+    return vals
+end
 
 function load_count_csv(fname)
     data = readdlm(fname, ',', Float64, skipstart=1)
@@ -197,6 +213,11 @@ end
     return _maybe_survivalvalues(vals.ratios[args...], vals.uncs[args...])
 end
 @inline depth(vals::SurvivalValues{N2}) where {N2} = size(vals.ratios, N2)
+function Base.permute!(vals::SurvivalValues{2}, perm::AbstractVector)
+    vals.ratios .= vals.ratios[perm, :]
+    vals.uncs .= vals.uncs[perm, :]
+    return vals
+end
 
 # TODO
 const SurvivalValues1 = SurvivalValues{2}

### 2020-11-23 presentations/defense/scripts/plot_raman_transfer_gamma_vs_omega.jl
[figure] gamma vs omega showing the improvement for 2 ASE filter

@@ -1,0 +1,73 @@
+#!/usr/bin/julia
+
+push!(LOAD_PATH, joinpath(@__DIR__, "../../../lib"))
+
+import NaCsCalc.Format: Unc, Sci
+using NaCsCalc
+using NaCsCalc.Utils: interactive
+using NaCsData
+using NaCsData.Fitting: fit_data, fit_survival
+using NaCsPlot
+using PyPlot
+using PyCall
+using DataStructures
+using LsqFit
+using MAT
+
+const Γ_mol_0 = [1.87, 0.528, 0.298]
+const unc_Γ_mol_0 = [0.10, 0.045, 0.028]
+const Γ_mol_1 = [1.30, 0.395, 0.170]
+const unc_Γ_mol_1 = [0.10, 0.041, 0.010]
+const Γ_mol_2 = [0.781]
+const unc_Γ_mol_2 = [0.050]
+
+const Ω_mol_0 = [4.023, 1.182, 0.488]
+const unc_Ω_mol_0 = [0.059, 0.033, 0.015]
+const Ω_mol_1 = [3.971, 1.173, 0.4912]
+const unc_Ω_mol_1 = [0.089, 0.025, 0.0082]
+const Ω_mol_2 = [3.282]
+const unc_Ω_mol_2 = [0.042]
+
+const prefix = joinpath(@__DIR__, "../figures/raman_transfer_gamma_vs_omega")
+
+figure()
+ax = gca()
+errorbar(Ω_mol_0, Γ_mol_0, xerr=unc_Ω_mol_0, yerr=unc_Γ_mol_0, fmt="C0o-", label="0 filter")
+errorbar(Ω_mol_1, Γ_mol_1, xerr=unc_Ω_mol_1, yerr=unc_Γ_mol_1, fmt="C1o-", label="1 filter")
+# errorbar(Ω_mol_2, Γ_mol_2, xerr=unc_Ω_mol_2, yerr=unc_Γ_mol_2, fmt="C2o-", label="2 filter")
+legend(loc="upper left", fontsize="x-small")
+xscale("log")
+yscale("log")
+grid()
+xlim([0.42, 4.4])
+ylim([0.14, 2.2])
+minorticks_off()
+xticks([0.5, 1, 2, 4], ["0.5", "1", "2", "4"])
+yticks([0.2, 0.4, 0.8, 1.6], ["0.2", "0.4", "0.8", "1.6"])
[…]

### 2020-12-06 presentations/2020-defense/scripts/plot_interaction_shift_atomic_wavefunction.jl
[presentations/2020-defense] interaction shift

@@ -1,0 +1,54 @@
+#!/usr/bin/julia
+
+push!(LOAD_PATH, joinpath(@__DIR__, "../../../lib"))
+
+import NaCsCalc.Format: Unc, Sci
+using NaCsCalc
+using NaCsCalc.Utils: interactive
+using NaCsData
+using NaCsData.Fitting: fit_data, fit_survival
+using NaCsPlot
+using PyPlot
+# using DataStructures
+# using LsqFit
+using LibArchive
+
+using DelimitedFiles
+
+function read_csv_compressed(fname, args...; kwargs...)
+    LibArchive.Reader(fname) do reader
+        LibArchive.support_format_raw(reader)
+        LibArchive.support_filter_all(reader)
+        LibArchive.next_header(reader)
+        readdlm(reader, args...; kwargs...)
+    end
+end
+
+const fname31 = joinpath(@__DIR__, "../../2020-postdoc/3311boundstate.csv.zst")
+const fname32 = joinpath(@__DIR__, "../../2020-postdoc/3322boundstate.csv.zst")
+const fname42 = joinpath(@__DIR__, "../../2020-postdoc/4422boundstate.csv.zst")
+const data31 = read_csv_compressed(fname31, ',', Float64)
+const data32 = read_csv_compressed(fname32, ',', Float64)
+const data42 = read_csv_compressed(fname42, ',', Float64)
+
+const prefix = joinpath(@__DIR__, "../figures/interaction_shift_atomic_wavefunction")
+
+
+figure()
+plot(data42[:, 1], data42[:, 2] .* 2e6, "C2", label="Na(2,2) Cs(4,4)")
+plot(data32[:, 1], data32[:, 2] .* 2e6, "C1", label="Na(2,2) Cs(3,3)")
+plot(data31[:, 1], data31[:, 2] .* 2e6, "C3--", label="Na(1,1) Cs(3,3)")
+axvline(100, color="C0", ls="dashed", linewidth=3)
+grid()
+xscale("log")
+yscale("log")
+xlim([2.7, 3000])
+ylim([0.0015, 1450])
+xticks([10, 100, 1000], ["10", "100", "1000"])
+xlabel("R (Angstroms)", fontsize=20)
+ylabel("\$\\left|\\psi(R)\\right|^2\$", fontsize=20)
+gca().tick_params(axis="both", which="major", labelsize=15)
+legend(fontsize="x-small")
+NaCsPlot.maybe_save("$(prefix)")
+
+NaCsPlot.maybe_show()

### 2020-12-06 presentations/2020-defense/scripts/plot_interaction_shift_energies.jl

@@ -1,0 +1,132 @@
+#!/usr/bin/julia
+
+push!(LOAD_PATH, joinpath(@__DIR__, "../../../lib"))
+
+import NaCsCalc.Format: Unc, Sci
+using NaCsCalc
+using NaCsCalc.Utils: interactive
+using NaCsData
+using NaCsData.Fitting: fit_data, fit_survival
+using NaCsPlot
+using PyPlot
+# using DataStructures
+# using LsqFit
+using LibArchive
+
+using DelimitedFiles
+
+function read_csv_compressed(fname, args...; kwargs...)
+    LibArchive.Reader(fname) do reader
+        LibArchive.support_format_raw(reader)
+        LibArchive.support_filter_all(reader)
+        LibArchive.next_header(reader)
+        readdlm(reader, args...; kwargs...)
+    end
+end
+
+const data = read_csv_compressed(joinpath(@__DIR__, "../../thesis/data/InteractionShiftLevels.csv.zst"), ',', Float64)
+const idx_a0 = first(searchsorted(data[:, 1], 0))
+const perturb_slope = (data[idx_a0, 2] - data[idx_a0 - 1, 2]) /
+    (data[idx_a0, 1] - data[idx_a0 - 1, 1])
+
+const prefix = joinpath(@__DIR__, "../figures/interaction_shift_energies")
+
+function interpolate_data(a, idx)
+    idx_a = first(searchsorted(data[:, 1], a))
+    v1 = data[idx_a - 1, idx]
+    v2 = data[idx_a, idx]
+    a1 = data[idx_a - 1, 1]
+    a2 = data[idx_a, 1]
+    return (v1 * (a2 - a) + v2 * (a - a1)) / (a2 - a1)
+end
+
+figure(figsize=[5.6, 4.9])
+plot([-0.5, 0.5], [-0.5 * perturb_slope, 0.5 * perturb_slope],
+     ls="dotted", color="gray")
+plot(data[:, 1], data[:, 2], "C0") # 0, 0
+text(-0.065, -16.4, "\$|m_{\\mathrm{rel},z},m_{\\mathrm{COM},z}\\rangle\\!=\\!|0,0\\rangle\$",
+     color="C0", fontsize=14)
[…]

### 2020-12-06 presentations/2020-defense/scripts/plot_interaction_shift_spectrum.jl

@@ -1,0 +1,194 @@
+#!/usr/bin/julia
+
+push!(LOAD_PATH, joinpath(@__DIR__, "../../../lib"))
+
+import NaCsCalc.Format: Unc, Sci
+using NaCsCalc
+using NaCsCalc.Utils: interactive
+using NaCsData
+using NaCsData.Fitting: fit_data, fit_survival
+using NaCsPlot
+using PyPlot
+using DataStructures
+
+const expdir = joinpath(@__DIR__, "../../../experiments")
+
+const inames = ["nacs_201808/data/data_20180815_000658.mat",
+                "nacs_201808/data/data_20180815_091610.mat",
+                "nacs_201808/data/data_20180815_231138.mat"]
+const datas = [NaCsData.load_striped_mat(joinpath(expdir, iname)) for iname in inames]
+const maxcnts = [typemax(Int),
+                 typemax(Int),
+                 typemax(Int)]
+const specs = [
+    OrderedDict(
+        :n0=>.-(7 .+ linspace(-40, 40, 81)),
+        :n1=>.-(7 .+ linspace(-40, 40, 81)),
+    ),
+    OrderedDict(
+        :n0=>.-(7 .+ linspace(-60.0, 10.0, 81)),
+        :n1=>.-(7 .+ linspace(-60.0, 10.0, 81)),
+    ),
+    OrderedDict(
+        :cs=>.-linspace(-80.0, 80.0, 161),
+        :na=>.-linspace(-80.0, 80.0, 161),
+    ),
+]
+
+select_datas(datas, selector, maxcnts, specs) =
+    [NaCsData.split_data(NaCsData.select_count(data..., selector, maxcnt), spec)
+     for (data, maxcnt, spec) in zip(datas, maxcnts, specs)]
+
+const datas_nacs_cs = select_datas(datas, NaCsData.select_single((1, 2), (4,)), maxcnts, specs)
+const datas_cs = select_datas(datas, NaCsData.select_single((-1, 2), (4,)), maxcnts, specs)
+const datas_nacs_na = select_datas(datas, NaCsData.select_single((1, 2), (3,)), maxcnts, specs)
[…]

### 2020-12-06 presentations/2020-defense/scripts/plot_raman_transfer_fit_two_ase.jl
[presentations/2020-defense] WIP: raman transfer

@@ -1,0 +1,190 @@
+#!/usr/bin/julia
+
+push!(LOAD_PATH, joinpath(@__DIR__, "../../../lib"))
+
+include("../../../experiments/nacs_202003/molecular_raman_model.jl")
+
+import NaCsCalc.Format: Unc, Sci
+using NaCsCalc
+using NaCsCalc.Utils: interactive
+using NaCsData
+using NaCsData.Fitting: fit_data, fit_survival
+using NaCsPlot
+using PyPlot
+using DataStructures
+using LsqFit
+
+const expdir = joinpath(@__DIR__, "../../../experiments")
+
+const inames = ["nacs_202010/data/data_20201001_203322.mat",
+                "nacs_202010/data/data_20201006_190214.mat",
+                "nacs_202010/data/data_20201002_085901.mat",
+                "nacs_202010/data/data_20201003_102015.mat"]
+const datas = [NaCsData.load_striped_mat(joinpath(expdir, iname)) for iname in inames]
+const maxcnts = [typemax(Int),
+                 typemax(Int),
+                 typemax(Int),
+                 typemax(Int)]
+const specs = [[0; [0.02, 0.04, 0.07, 0.085, 0.10, 0.13, 0.145, 0.16,
+                    0.175, 0.19, 0.22, 0.25, 0.28, 0.31, 0.34, 0.37,
+                    0.40, 0.43, 0.46, 0.49] .* 1.6 .- 0.01], # 15 mW, 770.5704 MHz
+               ([0], # t=0
+                [0], # pi pulse
+                [0, 0.03, 0.06, 0.11, 0.15, 0.2, 0.3, 0.4, 0.8, 1.5]), # molecule lifetime
+               ([0.0], # 15 mW, 0 ms
+                570.4 .+ (-8:1.6:8), # 15 mW, 0.13 ms
+                570.4 .+ (-11:2.2:11), # 15 mW, 0.26 ms
+                ),
+               ([0.0, 2, 4, 10],
+                [0.0, 20, 40, 80, 120],
+                [0.0, 20, 40, 80, 160] .* 2,
+                [0.0, 25, 50, 100],
+                [0.0, 50, 100, 200],
+                [0.0, 50, 100, 200] .* 2),
+               ]
+
[…]

### 2020-12-06 presentations/2020-defense/scripts/plot_raman_transfer_theory_ratio.jl

@@ -1,0 +1,97 @@
+#!/usr/bin/julia
+
+push!(LOAD_PATH, joinpath(@__DIR__, "../../../lib"))
+
+import NaCsCalc.Format: Unc, Sci
+using NaCsCalc
+using NaCsCalc.Utils: interactive
+using NaCsData
+using NaCsData.Fitting: fit_data, fit_survival
+using NaCsPlot
+using PyPlot
+# using DataStructures
+# using LsqFit
+using LibArchive
+
+using DelimitedFiles
+
+read_zst_csv(fname) = LibArchive.Reader(fname) do reader
+    LibArchive.support_format_raw(reader)
+    LibArchive.support_filter_all(reader)
+    LibArchive.next_header(reader)
+    readdlm(reader, ',', skipstart=1)
+end
+
+const fname = joinpath(@__DIR__, "../../molecular_raman_paper/data/50MHz_linewidth_8TotalExcitedStates_3322_80kHzConfinement_3.75mWPowerAtAtom.csv.zst")
+const fname2 = joinpath(@__DIR__, "../../molecular_raman_paper/data/50MHz_linewidth_8TotalExcitedStates_3322_80kHzConfinement_3.75mWPowerAtAtom_ThresholdContribution.csv.zst")
+const data = read_zst_csv(fname)
+const data2 = read_zst_csv(fname2)
+const prefix = joinpath(@__DIR__, "../figures/raman_transfer_theory_ratio")
+
+figure()
+ax1 = gca()
+plot(data[:, 1] .- 339724.57, abs.(data[:, 2] ./ 2π / 1000), "C1",
+     label="\$v'=40\$")
+plot(data[:, 1] .- 288625.081, abs.(data[:, 2] ./ 2π / 1000), "C0",
+     label="\$v'=0\$")
+grid()
+yscale("log")
+ax1.yaxis.set_minor_formatter(matplotlib.ticker.NullFormatter())
+xlim([-300, 300])
+ylim([6, 20000])
+xlabel("One-Photon Detuning (GHz)")
+ylabel("\$\\Omega_{\\mathrm{Raman}}~(2\\pi\\!\\times\\!\\mathrm{kHz})\$")
+legend(fontsize=13.88, loc="center left", handlelength=1, handletextpad=0.3)
[…]

### 2020-12-07 presentations/2020-defense/scripts/plot_raman_transfer_gamma_vs_omega.jl
[presentations/2020-defense] ASE and two-photon

@@ -35,7 +35,7 @@ ax = gca()
 errorbar(Ω_mol_0, Γ_mol_0, xerr=unc_Ω_mol_0, yerr=unc_Γ_mol_0, fmt="C0o-", label="0 filter")
 errorbar(Ω_mol_1, Γ_mol_1, xerr=unc_Ω_mol_1, yerr=unc_Γ_mol_1, fmt="C1o-", label="1 filter")
 # errorbar(Ω_mol_2, Γ_mol_2, xerr=unc_Ω_mol_2, yerr=unc_Γ_mol_2, fmt="C2o-", label="2 filter")
-legend(loc="upper left", fontsize="x-small")
+legend(loc="upper center", fontsize="x-small")
 xscale("log")
 yscale("log")
 grid()
@@ -46,8 +46,8 @@ xticks([0.5, 1, 2, 4], ["0.5", "1", "2", "4"])
 yticks([0.2, 0.4, 0.8, 1.6], ["0.2", "0.4", "0.8", "1.6"])
 # ax.xaxis.set_minor_formatter(matplotlib.ticker.NullFormatter())
 # ax.yaxis.set_minor_formatter(matplotlib.ticker.NullFormatter())
-xlabel("\$\\Omega_{\\mathrm{R}}~(\\mathrm{2\\pi\\cdot kHz})\$")
-ylabel("\$\\Gamma_{\\mathrm{m}}~(\\mathrm{2\\pi\\cdot kHz})\$")
+xlabel("\$\\Omega_{\\mathrm{Raman}}~(\\mathrm{2\\pi\\times kHz})\$")
+ylabel("\$\\Gamma_{\\mathrm{scatter}}~(\\mathrm{2\\pi\\times kHz})\$")
 NaCsPlot.maybe_save("$(prefix)_0-1")
 
 figure()
@@ -55,7 +55,7 @@ ax = gca()
 errorbar(Ω_mol_0, Γ_mol_0, xerr=unc_Ω_mol_0, yerr=unc_Γ_mol_0, fmt="C0o-", label="0 filter")
 errorbar(Ω_mol_1, Γ_mol_1, xerr=unc_Ω_mol_1, yerr=unc_Γ_mol_1, fmt="C1o-", label="1 filter")
 errorbar(Ω_mol_2, Γ_mol_2, xerr=unc_Ω_mol_2, yerr=unc_Γ_mol_2, fmt="C2o-", label="2 filter")
[…]

### 2020-12-07 presentations/2020-defense/scripts/plot_raman_transfer_scatter_scaling.jl

@@ -1,0 +1,134 @@
+#!/usr/bin/julia
+
+push!(LOAD_PATH, joinpath(@__DIR__, "../../../lib"))
+
+import NaCsCalc.Format: Unc, Sci
+using NaCsCalc
+using NaCsCalc.Utils: interactive
+using NaCsData
+using NaCsData.Fitting: fit_data, fit_survival
+using NaCsPlot
+using PyPlot
+using PyCall
+using DataStructures
+using LsqFit
+using MAT
+
+# 1: 288503 GHz
+# 2: 288560 GHz
+
+const pwrs = [15, 6, 3]
+const Γ_atom1 = [32.5, 2.77, 0.573]
+const unc_Γ_atom1 = [3.1, 0.27, 0.078]
+const Γ_atom2 = [24.5, 2.40, 0.572]
+const unc_Γ_atom2 = [2.3, 0.20, 0.063]
+const Γ_mol1 = [0.700, 0.227, 0.159]
+const unc_Γ_mol1 = [0.045, 0.020, 0.023]
+const Γ_mol2 = [1.30, 0.395, 0.170]
+const unc_Γ_mol2 = [0.10, 0.041, 0.010]
+
+const Γ_mol_diff = Γ_mol2 .- Γ_mol1
+const unc_Γ_mol_diff = sqrt.(unc_Γ_mol1.^2 .+ unc_Γ_mol2.^2)
+
+function gen_model_power(pwr)
+    return (x, p)->x.^pwr .* p[1]
+end
+
+model_lin0(x, p) = x .* p[1]
+model_lin1(x, p) = x .* p[1] .+ p[2]
+model_quad0(x, p) = x.^2 .* p[1]
+
+fit1_Γ_atom1 = fit_data(gen_model_power(1.58), pwrs, Γ_atom1, unc_Γ_atom1, [0.2], plot_lo=0)
+fit1_Γ_atom2 = fit_data(gen_model_power(1.58), pwrs, Γ_atom2, unc_Γ_atom2, [0.2], plot_lo=0)
+fit2_Γ_atom1 = fit_data(gen_model_power(2.58), pwrs, Γ_atom1, unc_Γ_atom1, [0.03], plot_lo=0)
+fit2_Γ_atom2 = fit_data(gen_model_power(2.58), pwrs, Γ_atom2, unc_Γ_atom2, [0.03], plot_lo=0)
+
[…]

### 2020-12-07 presentations/2020-defense/scripts/plot_raman_transfer_spectrum_postfilter.jl

@@ -1,0 +1,96 @@
+#!/usr/bin/julia
+
+push!(LOAD_PATH, joinpath(@__DIR__, "../../../lib"))
+
+import NaCsCalc.Format: Unc, Sci
+using NaCsCalc
+using NaCsCalc.Utils: interactive
+using NaCsData
+using NaCsData.Fitting: fit_data, fit_survival
+using NaCsPlot
+using PyPlot
+# using DataStructures
+# using LsqFit
+using LibArchive
+using Statistics
+
+using DelimitedFiles
+
+function read_csv_compressed(fname, args...; kwargs...)
+    LibArchive.Reader(fname) do reader
+        LibArchive.support_format_raw(reader)
+        LibArchive.support_filter_all(reader)
+        LibArchive.next_header(reader)
+        readdlm(reader, args...; kwargs...)
+    end
+end
+
+const data = read_csv_compressed(
+    joinpath(@__DIR__, "../../thesis/data/Timebase1038ASE_20200718_193100/data.csv.zst"),
+    ',', Float64)
+
+const params = (
+    bw = 2,
+    xthresh = 0.00005,
+    yzero = 0.006,
+    # xcutoff1 = 0.2705,
+    # xcutoff2 = 0.301,
+    lambda0 = 999.85, # nm
+    lambda1 = 1100.85, # nm
+)
+
+function process_data(data, params)
+    curxs = [data[1, 1]]
+    ymin = ymax = data[1, 2]
+    xs = Float64[]
+    ys = Float64[]
+    uncs = Float64[]
+    for i in 2:size(data, 1)
+        x = data[i, 1]
+        y = data[i, 2]
+        if x - curxs[end] <= params.xthresh
+            push!(curxs, x)
+            if y < ymin
+                ymin = y
+            elseif y > ymax
+                ymax = y
+            end
+            continue
+        end
+        if length(curxs) > 1
+            push!(xs, mean(curxs) * (params.lambda1 - params.lambda0) + params.lambda0)
+            if ymin < params.yzero
+                ymin = -0.0001
+            end
+            push!(ys, (ymin + ymax) / 2 / params.bw)
+            push!(uncs, (ymax - ymin) / 2 / params.bw)
+        end
+        resize!(curxs, 1)
+        curxs[1] = x
+        ymin = ymax = y
+    end
+    if length(curxs) > 1
[…]

### 2020-12-07 presentations/2020-defense/scripts/plot_raman_transfer_spectrum_prefilter.jl

@@ -1,0 +1,96 @@
+#!/usr/bin/julia
+
+push!(LOAD_PATH, joinpath(@__DIR__, "../../../lib"))
+
+import NaCsCalc.Format: Unc, Sci
+using NaCsCalc
+using NaCsCalc.Utils: interactive
+using NaCsData
+using NaCsData.Fitting: fit_data, fit_survival
+using NaCsPlot
+using PyPlot
+# using DataStructures
+# using LsqFit
+using LibArchive
+using Statistics
+
+using DelimitedFiles
+
+function read_csv_compressed(fname, args...; kwargs...)
+    LibArchive.Reader(fname) do reader
+        LibArchive.support_format_raw(reader)
+        LibArchive.support_filter_all(reader)
+        LibArchive.next_header(reader)
+        readdlm(reader, args...; kwargs...)
+    end
+end
+
+const data = read_csv_compressed(
+    joinpath(@__DIR__, "../../thesis/data/Timebase1038_20200702_094907/data.csv.zst"),
+    ',', Float64)
+
+const params = (
+    bw = 2,
+    xthresh = 0.0001,
+    yzero = 0.02,
+    # xcutoff1 = 0.2705,
+    # xcutoff2 = 0.301,
+    lambda0 = 1009, # nm
+    lambda1 = 1109, # nm
+)
+
+function process_data(data, params)
+    curxs = [data[1, 1]]
+    ymin = ymax = data[1, 2]
+    xs = Float64[]
+    ys = Float64[]
+    uncs = Float64[]
+    for i in 2:size(data, 1)
+        x = data[i, 1]
+        y = data[i, 2]
+        if x - curxs[end] <= params.xthresh
+            push!(curxs, x)
+            if y < ymin
+                ymin = y
+            elseif y > ymax
+                ymax = y
+            end
+            continue
+        end
+        if length(curxs) > 1
+            push!(xs, mean(curxs) * (params.lambda1 - params.lambda0) + params.lambda0)
+            if ymin < params.yzero
+                ymin = -0.0001
+            end
+            push!(ys, (ymin + ymax) / 2 / params.bw)
+            push!(uncs, (ymax - ymin) / 2 / params.bw)
+        end
+        resize!(curxs, 1)
+        curxs[1] = x
+        ymin = ymax = y
+    end
+    if length(curxs) > 1
[…]

### 2020-12-08 presentations/2020-defense/scripts/plot_raman_transfer_theory_ratio.jl
[presentations/2020-defense] Tweaks for completed first draft

@@ -72,7 +72,7 @@ yscale("log")
 ax3.yaxis.set_minor_formatter(matplotlib.ticker.NullFormatter())
 yticks([0.1, 1, 10], ["0.1", "1", "10"])
 xlim([-300, 300])
-ylim([0.02, 40])
+ylim([0.02, 30])
 xlabel("One-Photon Detuning (GHz)")
 ylabel("\$\\Omega_{\\mathrm{Raman}}/\\Gamma_{\\mathrm{scatter}}\$")
 legend(fontsize=13.88, loc="upper left", bbox_to_anchor=(0, 0.8),

### 2020-12-10 presentations/2020-defense/scripts/plot_raman_transfer_scatter_scaling.jl
[presentations/2020-defense] Two photo scattering tweaks

@@ -108,26 +108,29 @@ const prefix = joinpath(@__DIR__, "../figures/raman_transfer_scatter_scaling")
 # ylabel("\$\\Gamma_{\\mathrm{m}}~(\\mathrm{2\\pi\\times kHz})\$")
 # NaCsPlot.maybe_save("$(prefix)_mol")
 
+const diffscale = (1 / (711 - 560)^2) / (1 / (711 - 560)^2 - 1 / (711 - 503)^2)
+
 figure()
 ax = gca()
-errorbar(pwrs, Γ_mol_diff, unc_Γ_mol_diff, fmt="C0o")
-plot(fit1_Γ_mol_diff.plotx, fit1_Γ_mol_diff.ploty, "C0--")
-plot(fit2_Γ_mol_diff.plotx, fit2_Γ_mol_diff.ploty, "C0")
+errorbar(pwrs, Γ_mol_diff .* diffscale, unc_Γ_mol_diff .* diffscale, fmt="C0o")
+plot(fit1_Γ_mol_diff.plotx, fit1_Γ_mol_diff.ploty .* diffscale, "C0--", label="Linear")
+plot(fit2_Γ_mol_diff.plotx, fit2_Γ_mol_diff.ploty .* diffscale, "C0", label="Quadratic")
 xlim([2.4, 17])
-ylim([0.008, 0.8])
+ylim([0.016, 1.6])
 xscale("log")
 yscale("log")
+legend(loc="upper left", fontsize="small")
 grid()
-text(3.8, 0.02,
-     ("\$\\Delta\\Gamma_{\\mathrm{m}}=P^2\\cdot2\\pi\\times$(fit2_Γ_mol_diff.uncs[1] .* 1000)" *
+text(3.1, 0.031,
+     ("\$\\Gamma^{\\mathrm{\\Delta dep}}_{\\mathrm{scatter}}=P^2\\cdot2\\pi\\times$(fit2_Γ_mol_diff.uncs[1] .* 1000 * diffscale)" *
       "~\\mathrm{Hz/mW^2}\$"), fontsize="small", color="C0")
 ax.xaxis.set_minor_formatter(matplotlib.ticker.NullFormatter())
 ax.yaxis.set_minor_formatter(matplotlib.ticker.NullFormatter())
 ax.set_xticks(3:17, minor=true)
 xticks([3, 6, 12], ["3", "6", "12"])
[…]

### 2020-12-10 presentations/2020-defense/scripts/plot_raman_transfer_gamma_vs_omega.jl
[presentations/2020-defense] ASE

@@ -32,8 +32,8 @@ const prefix = joinpath(@__DIR__, "../figures/raman_transfer_gamma_vs_omega")
 
 figure()
 ax = gca()
-errorbar(Ω_mol_0, Γ_mol_0, xerr=unc_Ω_mol_0, yerr=unc_Γ_mol_0, fmt="C0o-", label="0 filter")
-errorbar(Ω_mol_1, Γ_mol_1, xerr=unc_Ω_mol_1, yerr=unc_Γ_mol_1, fmt="C1o-", label="1 filter")
+errorbar(Ω_mol_0, Γ_mol_0, xerr=unc_Ω_mol_0, yerr=unc_Γ_mol_0, fmt="C3o-", label="0 filter")
+errorbar(Ω_mol_1, Γ_mol_1, xerr=unc_Ω_mol_1, yerr=unc_Γ_mol_1, fmt="C0o-", label="1 filter")
 # errorbar(Ω_mol_2, Γ_mol_2, xerr=unc_Ω_mol_2, yerr=unc_Γ_mol_2, fmt="C2o-", label="2 filter")
 legend(loc="upper center", fontsize="x-small")
 xscale("log")
@@ -52,9 +52,12 @@ NaCsPlot.maybe_save("$(prefix)_0-1")
 
 figure()
 ax = gca()
-errorbar(Ω_mol_0, Γ_mol_0, xerr=unc_Ω_mol_0, yerr=unc_Γ_mol_0, fmt="C0o-", label="0 filter")
-errorbar(Ω_mol_1, Γ_mol_1, xerr=unc_Ω_mol_1, yerr=unc_Γ_mol_1, fmt="C1o-", label="1 filter")
+errorbar(Ω_mol_0, Γ_mol_0, xerr=unc_Ω_mol_0, yerr=unc_Γ_mol_0, fmt="C3o-", label="0 filter")
+errorbar(Ω_mol_1, Γ_mol_1, xerr=unc_Ω_mol_1, yerr=unc_Γ_mol_1, fmt="C0o-", label="1 filter")
 errorbar(Ω_mol_2, Γ_mol_2, xerr=unc_Ω_mol_2, yerr=unc_Γ_mol_2, fmt="C2o-", label="2 filter")
+annotate("", xy=(Ω_mol_2[1] - 0.3 / 4, Γ_mol_2[1] - 0.3 / 4),
+         xytext=(Ω_mol_2[1] - 0.3 * 1.25, Γ_mol_2[1] - 0.3 * 1.25),
[…]

### 2020-12-10 presentations/2020-defense/scripts/plot_raman_transfer_spectrum_prefilter.jl

@@ -86,6 +86,10 @@ ax = gca()
 mask = matplotlib.patches.Rectangle((1036.1, 0), 2.8, 2.4, facecolor="C0", alpha=0.7)
 ax.add_patch(mask)
 errorbar(processed.xs, processed.ys, processed.uncs, linestyle="None")
+annotate("ASE", xy=(1073.9, 1.144),
+         xytext=(1082.8, 1.540),
+         arrowprops=Dict(:width=>5, :headlength=>10, :headwidth=>12, :color=>"C0"),
+         color="C0", fontsize=28)
 grid()
 xlim([params.lambda0, params.lambda1])
 ylim([0, 2.4])

### 2020-12-10 presentations/2020-defense/scripts/plot_interaction_shift_energies.jl
[presentations/2020-defense] Interaction Shift

@@ -44,23 +44,15 @@ figure(figsize=[5.6, 4.9])
 plot([-0.5, 0.5], [-0.5 * perturb_slope, 0.5 * perturb_slope],
      ls="dotted", color="gray")
 plot(data[:, 1], data[:, 2], "C0") # 0, 0
-text(-0.065, -16.4, "\$|m_{\\mathrm{rel},z},m_{\\mathrm{COM},z}\\rangle\\!=\\!|0,0\\rangle\$",
+text(0.17, 4.7,
+     "\$|m_{\\mathrm{rel},z},\\!m_{\\mathrm{COM},z}\\rangle\$\n\$=\\!|0,\\!0\\rangle\$",
      color="C0", fontsize=14)
-# plot(data[:, 1], data[:, 3], "C1--") # 1, 0
-# text(-0.200, -10.0, "\$|0,1\\rangle\$", color="C1", fontsize=14)
-# plot(data[:, 1], data[:, 4], "C2--") # 0, 1
-# text(-0.470, 15.0, "\$|1,0\\rangle\$", color="C2", fontsize=14)
 plot(data[:, 1], data[:, 5], "C3") # 2, 0
-text(-0.350, 2.1, "\$|0,2\\rangle\$", color="C3", fontsize=14)
+text(-0.480, -7.1, "\$|0,\\!2\\rangle\$", color="C3", fontsize=14)
 plot(data[:, 1], data[:, 6], "C4") # 1, 1
-text(-0.276, 27.2, "\$|2,0\\rangle\$", color="C4", fontsize=14)
+text(-0.490, 23.0, "\$|2,\\!0\\rangle\$", color="C4", fontsize=14)
 plot(data[:, 1], data[:, 7], "C5") # 0, 2
-text(-0.490, 39.6, "\$|1,1\\rangle\$", color="C5", fontsize=14)
-# plot(data[:, 1], data[:, 8], "C6--") # 3, 0
-# text(-0.370, 37.0, "\$|0,3\\rangle\$", color="C6", fontsize=14)
-# plot(data[:, 1], data[:, 9], "C7--") # 2, 1
-# plot(data[:, 1], data[:, 10], "C8--") # 1, 2
-# plot(data[:, 1], data[:, 11], "C9--") # 0, 3
+text(-0.490, 39.6, "\$|1,\\!1\\rangle\$", color="C5", fontsize=14)
 grid()
 xlim([-0.5, 0.5])
 ylim([-50, 50])
[…]

### 2020-12-11 presentations/2020-defense/scripts/plot_conclusion_ground_raman.jl
[presentations/2020-defense] Tweak procedure drawing and update ground state Raman figure

@@ -1,0 +1,45 @@
+#!/usr/bin/julia
+
+push!(LOAD_PATH, joinpath(@__DIR__, "../../../lib"))
+
+import NaCsCalc.Format: Unc, Sci
+using NaCsCalc
+using NaCsCalc.Utils: interactive
+using NaCsData
+using NaCsData.Fitting: fit_data, fit_survival
+using NaCsPlot
+using PyPlot
+using PyCall
+using DataStructures
+using MAT
+
+const data = matread(joinpath(@__DIR__, "../data/groundstate_raman_rabi.mat"))
+
+const x = data["x"]
+const y = data["y"]
+const dy = data["dy"]
+
+function model_rabi(x, p)
+    offset, amp, Γ, γ, Ω = p
+    return offset .+ amp .* exp.(.-Γ .* x) .* (1 .- (1 .- exp.(.-γ .* x) .* cos.(Ω .* x)) ./ 2)
+end
+
+# const param = [0.3833, 0.287, 0.0133, 0.067, 2π * 0.1705]
+const param = [0, 1, 0.0133, 0.067, 2π * 0.1705]
+
+const prefix = joinpath(@__DIR__, "../figures/conclusion_ground_raman")
+
+const plotx = linspace(0, 26, 1000)
+
+figure()
+errorbar(x[2:end] .* 1e6, (y[2:end] .- 0.3833) ./ 0.287,
+         dy[2:end] ./ 0.287, fmt="C0o")
+plot(plotx, model_rabi(plotx, param), "C0")
+grid()
+xlim([0, 27])
+ylim([0, 1.0])
+xlabel("Raman Time (\$\\mathrm{\\mu s}\$)")
+ylabel("Fraction of FB molecule")
+NaCsPlot.maybe_save("$(prefix)")
+
+NaCsPlot.maybe_show()

### 2020-12-12 presentations/2020-defense/scripts/plot_raman_transfer_spectrum.jl
[presentations/2020-defense] Slide tweaks
* Capitalization
* Colon after "Photo credit"
* New System
* Explicitly specify figure extension
* Overview figure position
* Subscript font
* Reference font size
* Raman energy diagram alignment between slides
* Acknowledgement slide blending

@@ -1,0 +1,97 @@
+#!/usr/bin/julia
+
+push!(LOAD_PATH, joinpath(@__DIR__, "../../../lib"))
+
+include("../../../experiments/nacs_202003/molecular_raman_model.jl")
+
+import NaCsCalc.Format: Unc, Sci
+using NaCsCalc
+using NaCsCalc.Utils: interactive
+using NaCsData
+using NaCsData.Fitting: fit_data, fit_survival
+using NaCsPlot
+using PyPlot
+using DataStructures
+using LsqFit
+
+const expdir = joinpath(@__DIR__, "../../../experiments")
+
+const inames = ["nacs_202003/data/data_20200326_101325.mat",
+                "nacs_202003/data/data_20200326_223438.mat",
+                "nacs_202003/data/data_20200327_004910.mat",
+                "nacs_202003/data/data_20200330_033004.mat"]
+const datas = [NaCsData.load_striped_mat(joinpath(expdir, iname)) for iname in inames]
+const maxcnts = [typemax(Int),
+                 typemax(Int),
+                 typemax(Int),
+                 typemax(Int)]
+const specs = [(593.0 .+ [-20; -6:2:6; 20], # 15 mW, 0.09 ms
+                522.7 .+ [-15; -4.5:1.5:4.5; 15], # 12 mW, 0.12 ms
+                447.5 .+ [-10; -3:0.6:3; 5], # 9 mW, 0.16 ms
+                369.5 .+ [-5; -2:0.5:2; 5], # 6 mW, 0.27 ms
+                287.5 .+ [-5; -0.6:0.15:0.6; 5], # 3 mW, 0.9 ms
+                ),
+               (593.0 .+ [-30; -7.5:1.5:7.5; 30], # 15 mW, 0.1 ms
+                593.0 .+ [-30; -7.5:1.5:7.5; 30], # 15 mW, 0.14 ms
+                ),
+               ([0], # 15 mW, 0 ms
+                593.0 .+ [-30; -7.5:1.5:7.5; 30], # 15 mW, 0.1 ms
+                593.0 .+ [-30; -7.5:1.5:7.5; 30], # 15 mW, 0.14 ms
+                ),
+               (593.0 .+ [-30; -7.5:1.5:7.5; 30], # 15 mW, 0.32 ms
[…]

### 2020-12-12 presentations/2020-defense/scripts/plot_rsc_raman_op.jl

@@ -1,0 +1,186 @@
+#!/usr/bin/julia
+
+
+push!(LOAD_PATH, joinpath(@__DIR__, "../../../lib"))
+using NaCsCalc.Atomic: all_scatter_D
+import NaCsCalc: Trap
+using NaCsCalc
+using NaCsCalc.Utils: binomial_estimate, thread_rng
+using NaCsData
+using NaCsSim.DecayRabi: propagate_multistates, average_multistates, Γ_to_rates
+using DataStructures
+using PyPlot
+using NaCsPlot
+using Cubature
+
+const prefix = joinpath(@__DIR__, "../figures/rsc")
+
+const m_Na = 23e-3 / 6.02e23
+const η_ax = Trap.η(m_Na, 67e3, 2π / 589e-9) / √(2)
+const η_ax_op = Trap.η(m_Na, 67e3, 2π / 589e-9)
+const η_ra1 = Trap.η(m_Na, 430e3, 2π / 589e-9)
+const η_ra2 = Trap.η(m_Na, 590e3, 2π / 589e-9)
+
+"""
+    emission(v, isσ::Bool) -> (sinθ, cosθ)
+
+Given an uniform distribution in `[0, 1]` of `v` this function will return a distribution
+of `cosθ` that matches a dipole emission pattern (the type of the transition is determined by
+`isσ`).
+"""
+function emission_angle(v::T, isσ::Bool) where T<:AbstractFloat
+    # Returns `cosθ`. The caller should be ready to handle `|cosθ| > 1`
+    # The PDFs of the `θ` distribution are
+    # `3 / 4 * (1 - cos²θ) * sinθ` for π light and
+    # `3 / 8 * (1 + cos²θ) * sinθ` for σ± light
+    # The corresponding CDFs are
+    # `1 / 4 * (3cosθ - cos³θ) + 1 / 2` for π light and
+    # `1 / 8 * (3cosθ + cos³θ) + 1 / 2` for σ± light
+    # For a random number `v` we need to solve
+    # `3cosθ - cos³θ = 4v - 2` for π light and
+    # `3cosθ + cos³θ = 8v - 4` for σ± light
+    # The (real) solution is
+    # `cosθ = x + 1 / x` where `x = ∛(2√(v² - v) - 2v + 1)` for π light and
[…]

### 2020-12-16 presentations/2020-defense/scripts/plot_conclusion_ground_raman.jl
[presentations/2020-defense] Slide tweaks
* FB -> Feshbach
* Date
* Fix mask dimension on interaction result slide
* Consistent bound length and atom size/color/order

@@ -39,7 +39,7 @@ grid()
 xlim([0, 27])
 ylim([0, 1.0])
 xlabel("Raman Time (\$\\mathrm{\\mu s}\$)")
-ylabel("Fraction of FB molecule")
+ylabel("Fraction of Feshbach molecule")
 NaCsPlot.maybe_save("$(prefix)")
 
 NaCsPlot.maybe_show()
